### 2014-06-20 Docs/sampling.tex
Added files from WL_Emulator

\documentclass[11pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{color}
\usepackage{aas_macros}

\addtolength{\hoffset}{-2.5cm}
\addtolength{\textwidth}{4.5cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textheight}{4.5cm}

\title{Sampling the cosmological parameter space}
\author{}
\date{}

\begin{document}

\maketitle

\section*{The problem}
The target of this work is to get an even sampling of the cosmological parameter space in which points are as spread as possible, within some range; our first application is getting an even sampling of the $(\Omega_m,w,\sigma_8)$ parameter space. To do this we use a similar procedure as \cite{coyote2} and reduce ourselves to the following problem: we want to draw $N$ sample points $\mathbf{x}$ in a $D$ dimensional hypercube of unit side ($\mathbf{x}\in[0,1]^D$) so that the points are as spread as possible. We also want to enforce the \textit{latin hypercube} structure: when projecting the sample on each dimension, the projected points must not overlap.

\section*{The cost function}
To solve this problem we adopt an optimization approach, in which we define a measure of how "spread" the points are; given a set of $N$ points (or a \textit{design} to use the same terminology as \cite{coyote2}) $\mathcal{D}$, one can define a \textit{cost} function $d_{(p,\lambda)}(\mathcal{D})$

\begin{equation}
\label{cost}
d_{(p,\lambda)}(\mathcal{D}) = \left(\frac{2}{N(N-1)}\sum_{i<j}\left[\frac{D^{1/p}}{\rho_p(\mathbf{x}_i,\mathbf{x}_j)}\right]^\lambda\right)^{1/\lambda}
\end{equation}
%
and $\rho_p$ is just the $p$-distance between two points
\begin{equation}
\label{pdistance}
\rho_p(\mathbf{x}_i,\mathbf{x}_j)=\left[\sum_{d=1}^D\left\vert x_i^d-x_j^d\right\vert^p\right]^{1/p}
\end{equation}
%
What we want is find a design $\mathcal{D}$ that minimizes (\ref{cost}) maintaining the latin hypercube structure. To get an intuition of what's the meaning of this, for $(D,p,\lambda)=(3,2,1)$ this problem is equivalent to the one of minimizing the potential energy of $N$ unit point charges confined in a cube: the repulsive Coulomb force will make sure that these charges are as spread apart as possible.

\section*{The algorithm}
We use a rough approximation of the simulated annealing algorithm to perform this task: remember that we want to find a latin hypercube design that minimizes (\ref{cost}); the simplest latin hypercube one can think about is a completely diagonal one, call it $\mathcal{D}_0$, defined by the points $x_i^d\equiv i/(N-1)$, $i=0...N-1$, for which one can compute the cost function (which will not depend on $p$, try to believe)
\begin{equation}
\label{diagonalcost}
d_0(N,\lambda) = \left(\frac{2(N-1)^{\lambda-1}}{N}\sum_{i<j}\frac{1}{\vert i-j\vert^\lambda}\right)^{1/\lambda}
\end{equation}
%
This design of course is far from optimal, but we can improve it by shuffling the particles coordinates for each dimension independently, this will greatly improve the cost of the design. What we can do next is exchange the single coordinates of particle pairs and see if this leads to a cost improvement or not: we can iterate this procedure many times to fine tune to the optimum. In detail the algorithm that we use consists in the following steps:
\begin{enumerate}
\item Start from the diagonal design $\mathcal{D}_0$: $x_i^d\equiv i/(N-1)$
\item Shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$ where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$
\item Pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$
\item Compute the new cost function, if this is less than the previous step, keep the exchange, otherwise revert the coordinate swap
\item Repeat steps 3 and 4 
\end{enumerate}
%
we found that $10^5$ iterations are enough to achieve convergence (to at least a local optimum) for $N=100$ points in $D=3$ dimensions with the "Coulomb" cost function with $p=2$ and $\lambda=1$.

\section*{Results}
Using $(N,D,p,\lambda)=(100,3,2,1)$ we computed the cost of the diagonal design $d_0(100,1)\approx8.4$ and we repeated our simplified algorithm for 10 different choices of the random seed required for the random steps in the procedure. The results are shown in Figure \ref{costfig}, which shows a good degree of convergence to an optimum which is independent of the random seed used. Note that the the first random shuffle of the coordinates already knocks down the cost from $\sim$8 to $\sim$3. 
%
\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{Figures/cost.png}
\end{center}
\caption{Cost function calculated as in (\ref{cost}) as a function of the iteration step for 10 different random seeds}
\label{costfig}
\end{figure}
%
Figure \ref{3Ddistr} show the 3D distribution of points scaled to the $(\Omega_m,w,\sigma_8)$ space in the diagonal configuration, after the first random shuffle and at the found optimum. Figure \ref{2Dproj} shows the analogous 2D projections. 
%
\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{Figures/3dpoints_diagonal.png}
\includegraphics[scale=0.4]{Figures/3dpoints_first_shuffle.png}
\includegraphics[scale=0.4]{Figures/3dpoints.png}
\end{center}
\caption{Three dimensional distrubution of parameter values at the initial step (top left), after the first random shuffle (top right) and at the optimum (bottom)}
\label{3Ddistr}
\end{figure}
%
\begin{figure}
\begin{center}
\includegraphics[scale=0.25]{Figures/diag1.png}
\includegraphics[scale=0.25]{Figures/diag2.png}
\includegraphics[scale=0.25]{Figures/diag3.png}
\includegraphics[scale=0.25]{Figures/first_shuffle1.png}
\includegraphics[scale=0.25]{Figures/first_shuffle2.png}
\includegraphics[scale=0.25]{Figures/first_shuffle3.png}
\includegraphics[scale=0.25]{Figures/optimum1.png}
\includegraphics[scale=0.25]{Figures/optimum2.png}
\includegraphics[scale=0.25]{Figures/optimum3.png}
\end{center}
\caption{Two dimensional projections of parameter values at the initial step (top), after the first random shuffle (middle) and at the optimum (bottom)}
\label{2Dproj}
\end{figure} 
%
We can see that the optimization procedure distributes the points in a spherical geometry and gets rid of some of the clumpyness. 
\bibliographystyle{apalike}
\bibliography{ref}

\end{document}

### 2014-06-20 GaussianProcess/__init__.py

@@ -1,0 +1,3 @@
+from .interpolation import *
+
+__version__="0.1"

### 2014-06-20 GaussianProcess/equations.py

@@ -1,0 +1,102 @@
+import numpy as np
+from scipy.misc import logsumexp
+
+#################################################################################
+##################These are useful to compute the covariance function############
+#################################################################################
+
+def logCovTemplate(x,w):
+	return -0.5*x**2/w**2
+
+
+def logCovFunction(cosmoParameters,hyperParameters):
+
+	if(cosmoParameters.shape[1] != len(hyperParameters[3:])):
+		raise IndexError("Number of hyperparameters must be number of cosmological parameters + 3!")
+
+	#Tensorize
+	cosmoTensor = cosmoParameters[np.newaxis,:,:] - cosmoParameters[:,np.newaxis,:]
+
+	#Compute products
+	return logCovTemplate(cosmoTensor,hyperParameters[np.newaxis,np.newaxis,3:]).sum(axis=2)
+
+def fullLogCov(cosmoParameters,hyperParameters):
+
+	if(len(hyperParameters) != cosmoParameters.shape[1]+3):
+		raise IndexError("Number of hyperparameters must be number of cosmological parameters + 3!")
+
+	simpleCov = logCovFunction(cosmoParameters,hyperParameters)
+
+	#Combine with the theta hyperparameters
+	denseAddOn = np.zeros(simpleCov.shape)
+	
+	noiseAddOn = -np.ones(simpleCov.shape) * np.inf
+	noiseAddOn[np.diag_indices(simpleCov.shape[0])] = 0.0
+
+	#Perform the logsumexp
+	return logsumexp(np.array([simpleCov,denseAddOn,noiseAddOn]),axis=0,b=hyperParameters[:3,np.newaxis,np.newaxis])
+
+#####################################################################################################
+################Construction of the likelihood for the hyperparameters###############################
+################useful for MCMC optimum hyperparameters searches#####################################
+#####################################################################################################
+
+#Here symData is just a vector with as many elements as the number of simulations
+def logSimLikelihood(parLogCov,simData):
+
+	if(parLogCov.shape[0]!=len(simData)):
+		raise IndexError("parameter covariance and simData must be of the same size!!")
+
+	covInv = np.linalg.inv(np.exp(parLogCov))
+	return -0.5*np.dot(simData,np.dot(covInv,simData))
+
+#Go with flat priors to start
+def logHyperPrior(hyperParameters):
+
+	for i in range(len(hyperParameters)):
[…]

### 2014-06-20 GaussianProcess/interpolation.py

@@ -1,0 +1,140 @@
+from .equations import *
+
+import numpy as np
+from scipy.optimize import minimize
+
+class Process:
+	"""
+	This is an object wrapper for the equations module, which actually performs all the linear algebra;
+	the goal is to interpolate a scalar function that depends on N parameters knowing its values on 
+	S different simulation points (each of these points is a vector of size N).
+	The constructor takes the following parameters:
+
+	:param cosmoParams:
+		S x N numpy array with the S choices of N parameters (these are the points on which we run the simulations)
+
+	:param simData:
+		S sized numpy array with the values of the particular descriptor bin on each of the simulation points
+
+	"""
+
+	def __init__(self,cosmoParams,simData):
+
+		#Check validity of initialization
+		if len(simData.shape) != 1:
+			raise ValueError("simData array must be one dimensional! (scalar functions only for now :( )")
+
+		if simData.shape[0] != cosmoParams.shape[0]:
+			raise ValueError("there should be an entry of simData for each simulation point!!")
+
+		#Initialize
+		self.cosmoParams = cosmoParams
+		self.simData = simData
+
+	def interpolate(self,hyperParameters=None):
+		"""
+		This method returns an interpolation function handler similarly to the one scipy.interp1d does; the interpolation
+		needs the value of the hyperparameters in order to continue, so either you supply it as a 1d numpy array of size N+3
+		or an exception is raised. You can also try to find the optimum hyperparameter values by running hyperOptimumFind.
+
+		:param hyperParameters:
+			numpy array of size N + 3 with the hyperparameters used to perform the interpolation
+		"""
+
+		#Check for presence of hyperparameters, if none can be found throw an exception
+		if hyperParameters == None:
+			
+			if hasattr(self,"hyperParameters"):
+				hyperParameters = self.hyperParameters
+			else:
+				raise ValueError("I don't know which values for the hyperparameters to use!")
+
+		self.covFunction = np.exp(fullLogCov(self.cosmoParams,hyperParameters))
+		self.covinvFunction = np.linalg.inv(self.covFunction)
+
+		#Build the function handler to return
+		def interpolator(newPoint):
+
+			#Check validity of input
+			if(newPoint.shape[1] != self.cosmoParams.shape[1]):
[…]

### 2014-06-20 GaussianProcess/wrapper/_WLInterpolate.c

@@ -1,0 +1,84 @@
+/*Python wrapper module for JMK interpolation code;
+the method used is the same as in 
+http://dan.iel.fm/posts/python-c-extensions/ 
+
+The module is called _WLInterpolate and it defines a method called
+WLInterpolate()
+*/
+
+#include <Python.h>
+#include <numpy/arrayobject.h>
+
+#include "function.h"
+
+//Python module docstrings 
+static char module_docstring[] = "This module provides a python interface for the Weak Lensing Statistics interpolator";
+static char WLInterpolate_docstring[] = "Calculate the binned statistic in question given a set of cosmological parameters";
+
+//WL_Interpolate declaration
+static PyObject *_WLInterpolate_WLInterpolate(PyObject *self, PyObject *args); 
+
+//_WLInterpolate method definitions
+static PyMethodDef module_methods[] = {
+	{"WLInterpolate",_WLInterpolate_WLInterpolate,METH_VARARGS,WLInterpolate_docstring},
+	{NULL,NULL,0,NULL}
+};
+
+//_WLInterpolate constructor
+PyMODINIT_FUNC init_WLInterpolate(void){
+
+	PyObject *m = Py_InitModule3("_WLInterpolate",module_methods,module_docstring);
+	if(m==NULL) return;
+
+	/*Load numpy functionality*/
+	import_array();
+
+}
+
+//WL_Interpolate implementation
+static PyObject *_WLInterpolate_WLInterpolate(PyObject *self, PyObject *args){
+
+	PyObject *cosmo_params_obj;
+	int Nbins;
+
+	/*Parse the input tuple*/
+	if(!PyArg_ParseTuple(args,"Oi",&cosmo_params_obj,&Nbins)){ 
+		return NULL;
+	}
+
+	/*Interpret the input object as numpy array*/
+	PyObject *cosmo_params_array = PyArray_FROM_OTF(cosmo_params_obj,NPY_DOUBLE,NPY_IN_ARRAY);
+
+	/*If that didn't work, throw an exception*/
+	if(cosmo_params_array==NULL){
+		return NULL;
+	}
+
+	/*How many cosmological parameters are there?*/
+	int Nparams = (int)PyArray_DIM(cosmo_params_array,0);
+
+	/*Get pointer to the cosmological parameters as C types*/
+	double *cosmo_params = (double *)PyArray_DATA(cosmo_params_array);
+
+	/*Create a new array object, which will be the output of the method*/
[…]

### 2014-06-20 GaussianProcess/wrapper/function.c

@@ -1,0 +1,13 @@
+
+void function(double *parameters,int Nparams,double *descriptor,int Nbins){
+
+	int i,j;
+
+	for(j=0;j<Nbins;j++){
+		descriptor[j] = 1.0 + j;
+		for(i=0;i<Nparams;i++){
+			descriptor[j] += parameters[i];
+		}
+	}
+
+}

### 2014-06-20 GaussianProcess/wrapper/function.h

@@ -1,0 +1,6 @@
+#ifndef __FUNCTION_H
+#define __FUNCTION_H
+
+void function(double *parameters,int Nparams,double *descriptor,int Nbins);
+
+#endif

### 2014-06-20 GaussianProcess/wrapper/setup.py

@@ -1,0 +1,14 @@
+from distutils.core import setup,Extension
+import numpy.distutils.misc_util
+
+setup(
+	name="WLInterpolate",
+	version="0.1",
+	author = "Andrea Petri",
+	author_email = "apetri@phys.columbia.edu",
+	url = "https://github.com/apetri/WL_Emulator",
+	description = "Python wrapper of Weak Lensing Emulator",
+	install_requires = ["numpy"],
+	ext_modules=[Extension("_WLInterpolate",["_WLInterpolate.c","function.c"])],
+	include_dirs=numpy.distutils.misc_util.get_numpy_include_dirs(),
+)

### 2014-06-20 MCMC/MCMC.py

@@ -1,0 +1,93 @@
+# !python
+# This code is the last step in WL emulator
+# It takes in any likelihood function, output the parameter probability distribution.
+# Last modification by Jia (05/08/2014)
+
+import numpy as np
+from scipy import *
+import scipy.optimize as op
+import emcee
+
+# params
+steps = 100 # MCMC steps, total steps will be steps*nwalkers
+dp = array([0.03, 0.2, 0.05]) # dp between hi-cosmo and fidu-cosmo
+fidu_params = array([0.26, -1.0, 0.8])
+
+# Build test model (linear interpolation)
+cosmo_mat=(genfromtxt('cosmo_mat_13subfields_1000R_021bins')).reshape(4,1000,-1)
+cov_mat = np.cov(cosmo_mat[0], rowvar = 0)# rowvar is the row contaning observations
+cov_inv = np.mat(cov_mat).I # covariance matrix inverted
+fidu_avg, him_avg, hiw_avg, his_avg = mean(cosmo_mat, axis = 1)
+
+dNdm = (him_avg - fidu_avg)/dp[0]
+dNdw =(hiw_avg - fidu_avg)/dp[1] 
+dNds = (his_avg - fidu_avg)/dp[2]
+X = np.mat([dNdm, dNdw, dNds])
+
+# fit using analytical solution
+def cosmo_fit (obs):
+	Y = np.mat(obs-fidu_avg)
+	del_p = ((X*cov_inv*X.T).I)*(X*cov_inv*Y.T)
+	m, w, s = np.squeeze(np.array(del_p.T))+fidu_params
+	del_N = Y-del_p.T*X
+	chisq = float(del_N*cov_inv*del_N.T)
+	return chisq, m, w, s
+fitSIM = array(map(cosmo_fit,cosmo_mat[0]))
+
+#### MCMC using emcee ##########
+
+obs = fidu_avg # use fiducial cosmology as observation, to be fitted parameters.
+
+# prior
+def lnprior(params):
+	'''This gives the flat prior.
+	Returns:
+	0:	if the params are in the regions of interest.
+	-inf:	otherwise.'''
+	m, w, s = params
+	if -0.23 < m < 0.78 and -5.36 < w < 3.15 and -0.1 < s < 1.49:
+		return 0.0
+	else:
+		return -np.inf
+
+# likelihood function
+def lnlike (params, obs):
[…]

### 2014-06-20 Sampler/build_options.py

@@ -1,0 +1,255 @@
+#Python glue program to generate C options to be read from inifile
+
+import StringIO
+
+############################################
+#########Type in your options here!!########
+############################################
+
+DEFAULT_OPTIONS_FILENAME = "default_options.ini"
+C_HANDLER_SOURCE = "options.c"
+C_OPTIONS_HEADER = "options.h"
+
+#Scalar options (name = value)
+
+#Format is: (Category,Parameter_name,Parameter_type,Default_value)
+
+dimensionality=[
+("dimensionality","dimensions",int,3),
+("dimensionality","number_of_points",int,10),
+("dimensionality","p",float,2.0),
+("dimensionality","lambda",float,1.0)
+]
+
+random=[
+("random","seed",int,1)
+]
+
+io=[
+("input/output","save_cost",int,1),
+("input/output","cost_file[128]",str,"cost.txt"),
+("input/output","points_file[128]",str,"points.txt"),
+("input/output","save_initial_step",int,0),
+("input/output","diagonal_file[128]",str,"points_diagonal.txt"),
+("input/output","first_shuffle_file[128]",str,"first_shuffle.txt")
+]
+
+scalar_options=[
+("Geometrical quantities of the problem",dimensionality),
+("Random seeds",random),
+("Input/output paths",io)
+]
+
+#Vector options (num_par = Size_of_the_vector; arr_name = Name_of_the_vector)
+
+#Format is (Category,Number_of_parameters_name,array_parameter_name,num_elements,Parameter_type,Default_values) (only int,float supported)
+
+vector_options=[]
+
+###############################################################
+#########Do not modify anything below here!!!!#################
+###############################################################
+
+def ini_string(value,ptype):
+	if ptype==str:
+		return value
+	elif ptype in(float,int):
+		return str(value)
+	else:
+		raise ValueError("Unknown parameter type")
+
+def declaration_string(ptype):
+	if ptype==str:
+		return 'char'
+	elif ptype==int:
+		return 'int'
+	elif ptype==float:
+		return 'float'
+	else:
+		raise ValueError("Unknown parameter type")
+
+def print_format(ptype):
+	if ptype==str:
+		return '%s'
+	elif ptype==int:
[…]

### 2014-06-20 Sampler/cost.c

@@ -1,0 +1,116 @@
+#include <math.h>
+#include "sampler.h"
+
+/*This function computes the p-distance between 2 points in D dimensions:
+the exponent p is tunable*/
+
+double distance(double *x,double *y,int D,float p){
+
+	double dist = 0.0;
+	int i;
+
+	for(i=0;i<D;i++){
+		dist += pow(fabs(x[i]-y[i]),p);
+	}
+
+	return pow(dist,1.0/p);
+
+}
+
+/*This is the cost function of the problem: it is a sum of all the reciprocal of 
+the pairs distances, with some tunable exponent lambda; note that the final
+1/lambda exponentiation is not performed here!*/
+
+double cost(double **data,int Npoints,int D,float p,float lambda){
+
+	double sum = 0.0;
+	int i,j;
+
+	for(i=0;i<Npoints;i++){
+		for(j=i+1;j<Npoints;j++){
+
+			//Add the contribution of pair (i,j) to the cost function
+			sum += pow(pow(D,1.0/p)/distance(data[i],data[j],D,p),lambda); 
+
+		}
+	}
+
+	return (2.0/(Npoints*(Npoints-1)))*sum;
+
+}
+
+/*This computes the cost function in the particular case in which all the points are 
+equally spaced on the diagonal of the hypercube*/
+
+double diagonalCost(int Npoints,float lambda){
+
+	double sum = 0.0;
+	int i,j;
+
+	for(i=0;i<Npoints;i++){
+		for(j=i+1;j<Npoints;j++){
+
+			//Add the contribution of pair (i,j) to the cost function
+			sum += pow((Npoints-1)*1.0/(j-i),lambda); 
+
+		}
+	}
+
+	return (2.0/(Npoints*(Npoints-1)))*sum;
+
+}
+
+/*This function computes the variation of the cost when a pair of coordinates is exchanged;
+this function also performs an in-place swap of the coordinates. More specifically:
+this function swaps coordinate d of points i1 and i2 and returns the variation of the cost
+function due to this swap*/
+
+double swap(double **data,int Npoints,int D,float p,float lambda,int i1,int i2, int d){
+
+	double costBefore,costAfter,temp;
+	int i;
+
+	//initialize to 0
+	costBefore = costAfter = 0.0;
+
[…]

### 2014-06-20 Sampler/sampler.c

@@ -1,0 +1,217 @@
+#include <stdio.h>
+#include <stdlib.h>
+
+#include <gsl/gsl_permutation.h>
+#include <gsl/gsl_randist.h>
+#include <gsl/gsl_rng.h>
+
+#include "ini.h"
+#include "options.h"
+#include "sampler.h"
+
+int save_points(char *filename,double **data,int Npoints,int D);
+
+int main(int argc, char **argv){
+
+	//Check for correct number of arguments
+	if(argc<2){
+		fprintf(stderr,"Usage: %s <ini_options_file> <random_seed(optional)>\n",*argv);
+		exit(1);
+	}
+
+	sys_options options;
+
+	//parse options from INI options file provided from command line
+	if(ini_parse(argv[1],handler,&options)<0){
+		fprintf(stderr,"Couldn't read %s, quitting...\n",argv[1]);
+		exit(1);
+	}
+
+	//options are parsed, fill in the parameters
+
+	int D = options.dimensions, Npoints = options.number_of_points;
+	float p = options.p, lambda = options.lambda;
+
+	//Log parsed options
+	fprintf(stdout,"%d points in %d dimensions\n",Npoints,D);
+	fprintf(stdout,"p=%.1f, lambda=%.1f\n",p,lambda);
+	
+	int i,d,i1,i2,iterCount;
+	
+	const gsl_rng_type *T;
+	gsl_rng *r;
+	gsl_permutation *perm = gsl_permutation_alloc(Npoints);
+
+	double **data,currentCost,deltaCost;
+
+	FILE *costFile;
+
+	//Allocate resources for data points
+	if((data = (double **)malloc(sizeof(double *)*Npoints)) == NULL){
+		perror("malloc() failed");
+		exit(1);
+	}
+
+	for(i=0;i<Npoints;i++){
+		if((data[i] = (double *)malloc(sizeof(double)*D)) == NULL){
+			perror("malloc() failed");
+			exit(1);
+		}
+	}
+
+	//Initialize random number generator
+	gsl_rng_env_setup();
+	T = gsl_rng_default;
+	r = gsl_rng_alloc(T);
+
+	//Initialize permutation
+	gsl_permutation_init(perm);
+
+	//Initialize coordinates
+	for(i=0;i<Npoints;i++){
+		for(d=0;d<D;d++){
+			data[i][d] = ((double)perm->data[i])/(Npoints-1);
+		}
+	}
+
+	//Save the diagonal configuration to file if prompted by options
+	if(options.save_initial_step){
+
[…]

### 2014-06-20 Sampler/sampler.h

@@ -1,0 +1,11 @@
+#ifndef __SAMPLER_H
+#define __SAMPLER_H
+
+//function prototypes
+double distance(double *x,double *y,int D,float p);
+double cost(double **data,int Npoints,int D,float p,float lambda);
+double diagonalCost(int Npoints,float lambda);
+double swap(double **data,int Npoints,int D,float p,float lambda,int i1,int i2, int d);
+void swapBack(double **data,int i1,int i2,int d);
+
+#endif

### 2014-06-20 Sampler/stop.c

@@ -1,0 +1,3 @@
+/*This file contains the criteria used to stop
+the while loop in the main execution*/
+

### 2014-06-20 Sampler/to_precambrian.py

@@ -1,0 +1,36 @@
+#######################################################
+###This is a simple script that will translate#########
+###the (Om,w,si8) values into a file that could########
+###be read by Precambrian to set up the runs in########
+##############the IG Pipeline##########################
+import sys
+import numpy as np
+
+########################################################
+#######Values of fixed cosmological parameters##########
+########################################################
+
+obh2 = 0.0227
+wa = 0.00
+ns = 0.960
+As = 2.41e-9
+h = 0.700
+
+if(len(sys.argv)<3):
+	print "Usage: python %s <(Om,w,si8) points file> <Precambrian output file>"%sys.argv[0]
+	exit(1)
+
+print "%s -----> %s"%(sys.argv[1],sys.argv[2])
+
+points = np.loadtxt(sys.argv[1])
+
+outFile = file(sys.argv[2],"w")
+
+outFile.write("#Obh2   Om    Ol     w0     wa   ns     As     si8    h\n\n")
+
+for i in range(points.shape[0]):
+	outFile.write("%.4f %.3f %.3f %.3f %.3f %.3f %.2e %.3f %.3f\n"%(obh2,points[i,0],1-points[i,0],points[i,1],wa,ns,As,points[i,2],h))
+
+outFile.close()
+
+print "DONE!\n"

### 2014-06-20 Sampler/visualize3d.py

@@ -1,0 +1,171 @@
+import os,sys,glob
+
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+##############################################
+########Tunable options#######################
+##############################################
+
+frames_directory = "frames"
+keep_frames = False
+frames_per_second = 10
+plot_projections = True
+
+scale_to_cosmological = True
+parameter_labels = [r"$\Omega_m$",r"$w$",r"$\sigma_8$"]
+parameter_low = np.array([0.07,-3.0,0.1])
+parameter_high = np.array([1.0,0.0,1.5])
+
+#Prompt user for correct usage
+if(len(sys.argv)<3):
+	print "Usage python %s <points_filename> <output_movie_filename>"
+	exit(1)
+
+#Create directory for frames
+try:
+	os.mkdir(frames_directory)
+except OSError:
+	pass
+
+#Load txt file with points in 3D space
+points = np.loadtxt(sys.argv[1])
+
+if(points.shape[1] != len(parameter_labels)):
+	raise ValueError("parameter_labels and number of parameters must be the same!")
+
+#Maybe scale to cosmological parameter values?
+if(scale_to_cosmological):
+	points = parameter_low[np.newaxis,:] + points * (parameter_high[np.newaxis,:] - parameter_low[np.newaxis,:])
+
+	#Save the actual cosmological parameters values to a txt file
+	rootName = sys.argv[1].split(".")[0]
+	np.savetxt(rootName+"_cosmological.txt",points) 
+
+
+#Plot the 2D projections first if option is provided
+if(plot_projections):
+
+	plt.scatter(points[:,0],points[:,1],color="red")
+	
+	if(scale_to_cosmological):
+		plt.xlabel(parameter_labels[0],fontsize=16)
+		plt.ylabel(parameter_labels[1],fontsize=16)
+		plt.xlim(parameter_low[0],parameter_high[0])
+		plt.ylim(parameter_low[1],parameter_high[1])
+	else:
+		plt.xlabel(r"$x_1$",fontsize=16)
+		plt.ylabel(r"$x_2$",fontsize=16)
+		plt.xlim(0,1)
+		plt.ylim(0,1)
+
+	plt.savefig("projection1.png")
[…]

### 2014-06-20 examples/MCMC.py

@@ -1,0 +1,75 @@
+import sys
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import minimize
+import emcee
+from emcee.utils import MPIPool
+
+import triangle
+
+import GaussianProcess
+import GaussianProcess.equations as equations
+
+#Initialize MPI pool used for parallelization
+pool = MPIPool()
+
+if not pool.is_master():
+
+	pool.wait()
+	sys.exit(0)
+
+
+#Interpolate the function using a Gaussian process (find the optimum and confidence contours with MCMC)
+cosmoParams = np.array([1.0,2.0,3.0,4.0,5.0])
+simData = np.array([1.5,2.0,-0.5,4.0,5.0])
+
+if pool.is_master():
+	process = GaussianProcess.Process(cosmoParams[:,np.newaxis],simData)
+	process.hyperOptimumFind(bounds=((0.1,3.9),(0.1,3.9),(0.1,3.9),(0.1,3.9)),Nguesses=15)
+
+#Give it a shot with MCMC
+
+#4 parameters
+ndim=4
+
+#32 walkers
+nwalkers=32
+
+#Initialize positions of the walkers
+p0 = np.ones((nwalkers,ndim))
+p0[:,0] = np.random.uniform(low=0.1,high=3.9,size=nwalkers)
+p0[:,1] = np.random.uniform(low=0.1,high=3.9,size=nwalkers)
+p0[:,2] = np.random.uniform(low=0.1,high=3.9,size=nwalkers)
+p0[:,3] = np.random.uniform(low=0.1,high=3.9,size=nwalkers)
+
+#Sampler initialization
+sampler = emcee.EnsembleSampler(nwalkers,ndim,equations.logHyperLikelihood,args=[cosmoParams[:,np.newaxis],simData,False],pool=pool)
+
+#Burn in 
+
+if pool.is_master():
+	print "burn in..."
+
+pos,prob,state = sampler.run_mcmc(p0,1000)
+sampler.reset()
+
+#Run chain after burn in
+
+if pool.is_master():
+	print "running MCMC..."
+
+sampler.run_mcmc(pos,10000)
+
+#Plot result
+
+if pool.is_master():
+	
+	print "Plotting..."
+	p = sampler.flatchain
+	fig = triangle.corner(np.array([p[:,3],p[:,2]]).transpose(),plot_datapoints=False,labels=[r"$r_1$",r"$\theta_3$"])
[…]

### 2014-06-20 examples/interp1d.py

@@ -1,0 +1,50 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+import GaussianProcess
+
+
+#Interpolate the function using a Gaussian process 
+cosmoParams = np.array([1.0,2.0,3.0,4.0,5.0])
+simData = np.array([1.5,2.0,-0.5,4.0,5.0])
+
+#Build the gaussian process object knowing the simulation data at the chosen points
+process = GaussianProcess.Process(cosmoParams[:,np.newaxis],simData)
+
+plt.plot(cosmoParams,simData,linestyle='none',marker='o',label='simulated data')
+
+#Choose new points to interpolate
+newPoint = np.arange(0.0,6.0,0.2)[:,np.newaxis]
+
+#Try how it looks like using one set of hyperparameters
+
+hyperparams = np.array([1.0,0.5,0.0,0.95])
+
+#Build interpolator object
+siminterp = process.interpolate(hyperparams) 
+
+#Compute interpolated values and errorbars
+intData,errData = siminterp(newPoint)
+
+#Plot
+plt.errorbar(newPoint,intData,yerr=np.sqrt(errData),color='green',label='noiseless interpolation')
+
+#Try how it looks like using various another set of hyperparameters
+hyperparams = np.array([1.0,0.5,3.0,3.5])
+
+#Build interpolator object
+siminterp = process.interpolate(hyperparams) 
+
+#Compute interpolated values and errorbars
+intData,errData = siminterp(newPoint)
+
+#Plot
+plt.errorbar(newPoint,intData,yerr=np.sqrt(errData),color='red',label='noisy interpolation')
+
+plt.xlim(0,6)
+plt.ylim(-3,7)
+plt.xlabel(r'$x$',fontsize=18)
+plt.ylabel(r'$f(x)$',fontsize=18)
+plt.legend(loc='upper left')
+
+plt.savefig("gaussInterp.png")

### 2014-06-20 examples/optimum.py

@@ -1,0 +1,14 @@
+import GaussianProcess
+
+import numpy as np
+from scipy.optimize import minimize
+
+#Interpolate the function using a Gaussian process (find the optimum)
+cosmoParams = np.array([1.0,2.0,3.0,4.0,5.0])
+simData = np.array([1.5,2.0,-0.5,4.0,5.0])
+
+#Build process object
+process = GaussianProcess.Process(cosmoParams[:,np.newaxis],simData)
+
+#Find maximul likelihood hyperparameters
+process.hyperOptimumFind(bounds=((0.01,4.9),(0.01,4.9),(0.01,4.9),(0.01,4.9)),Nguesses=5)

### 2014-06-20 setup.py

@@ -1,0 +1,44 @@
+import os,sys,re
+
+try:
+	from setuptools import setup
+	setup
+except ImportError:
+	from distutils.core import setup
+	setup
+
+def rd(filename):
+	
+	f = file(filename,"r")
+	r = f.read()
+	f.close()
+
+	return r
+
+
+vre = re.compile("__version__ = \"(.*?)\"")
+m = rd(os.path.join(os.path.dirname(os.path.abspath(__file__)),
+                    "GaussianProcess", "__init__.py"))
+version = vre.findall(m)[0]
+
+
+setup(
+	name="GaussianProcess",
+	version=version,
+	author="Andrea Petri, Jia Liu, Jan M. Kratochvil",
+	author_email="apetri@phys.columbia.edu",
+	packages=["GaussianProcess"],
+	url="?",
+	license="?",
+	description="Toolkit for Gaussian Process Regression",
+	long_description=rd("README.md"),
+	install_requires=["numpy","scipy"],
+	classifiers=[
+		"Development Status :: 2 - Pre-Alpha",
+		"Intended Audience :: Science/Research",
+		"Operating System :: OS Independent",
+		"Programming Language :: Python",
+		"Programming Language :: C",
+		"License :: Public Domain"
+	],
+)

### 2014-11-03 Paper_minkowski/paper.tex
added paper files

%\documentclass[useAMS, usenatbib,usegraphicx,letter]{mn2e}
%\documentclass[11pt]{article}
\documentclass[reprint,aps,prd,superscriptaddress,showkeys]{revtex4-1}
\usepackage{epsfig,amsmath,natbib}

\usepackage{aas_macros}
\usepackage{amssymb}
 \usepackage{amsmath}
 \usepackage{dsfont}
 \usepackage{hyperref}
 \usepackage{color}
\hypersetup{
	colorlinks=false,
	citecolor=green
}
% \usepackage{graphicx}
% \usepackage{epstopdf}
% \usepackage{natbib}

\begin{document}

\title{CFHTLens Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments}

\author{Andrea Petri}
\email{apetri@phys.columbia.edu}
\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\author{Jia Liu}
\affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}

\author{Zolt\'an Haiman}
\affiliation{Department of Astronomy, Columbia University, New York, NY 10027, USA}

\author{Lam Hui}
\affiliation{Department of Physics, Columbia University, New York, NY 10027, USA}

\author{Jan M. Kratochvil}
\affiliation{Astrophysics and Cosmology Research Unit, University of KwaZulu-Natal, Westville, Durban 4000, South Africa}

\author{Morgan May}
\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}

\date{\today}

\label{firstpage}

\begin{abstract}
Weak lensing surveys have the potential... we consider CFHT \citep{CFHTFu}
\end{abstract}

\keywords{Weak Gravitational Lensing --- Data analysis --- Methods: analytical,numerical,statistical}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
In this work...

%%%%%%%%%%%%%%%%%%%%%%%%%% DATA AND SIMULATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Data and simulations}

\subsection{CFHTLens data reduction}
\subsection{Simulation design}
\subsection{Ray Tracing Simulations}

%%%%%%%%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Statistical methods}
The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameters triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a bayesian fashion in order to compute parameter confidence intervals.

\subsection{Descriptors}
The statistical descriptors we consider on this work are the Minkowski Functionals (MFs) and the low order moments (LM) of the convergence field. The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence random field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$. Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ images
%
\begin{equation*}
\label{v0meas}
V_0(\kappa_0)=\frac{1}{A}\int_A\Theta(\kappa(\pmb{\theta})-\kappa_0)d\pmb{\theta},
\end{equation*}
\begin{equation}
\label{v1meas}
V_1(\kappa_0)=\frac{1}{4A}\int_A\delta(\kappa(\pmb{\theta})-\kappa_0)\sqrt{\kappa_x^2+\kappa_y^2}d\pmb{\theta},
\end{equation}
\begin{equation*}
\label{v2meas}
V_2(\kappa_0)=\frac{1}{2\pi A}\int_A\delta(\kappa(\pmb{\theta})-\kappa_0)\frac{2\kappa_x\kappa_y\kappa_{xy}-\kappa_x^2\kappa_{yy}-\kappa_y^2\kappa_{xx}}{\kappa_x^2+\kappa_y^2}d\pmb{\theta}.
\end{equation*}
%
Where $A$ is the total area of the fields of view we have been using and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences. The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, while $V_1,V_2$ are sensitive to the correlations between nearby pixels. In addition to these topological descriptors, we consider a set of low order moments (LM) of the convergence field (two quadratic, three cubic and four quartic), which are defined in the following way
%
\begin{equation}
\begin{matrix}
\mathrm{LM_2}: \sigma_{0,1}^2 = \langle\kappa^2\rangle,\langle\vert\nabla\kappa\vert^2\rangle, \\ \\
\mathrm{LM_3}: S_{0,1,2} = \langle\kappa^3\rangle,\langle\kappa\vert\nabla\kappa\vert^2\rangle,\langle\kappa^2\nabla^2\kappa\rangle, \\ \\
\mathrm{LM_4}: K_{0,1,2,3} = \langle\kappa^4\rangle,\langle\kappa^2\vert\nabla\kappa\vert^2\rangle,\langle\kappa^3\nabla^2\kappa\rangle,\langle\vert\nabla\kappa\vert^4\rangle.
\end{matrix}
\end{equation}
%
If the $\kappa$ field was Gaussian, one could express all the Minkowski Functionals in terms of the LM2 moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones. In reality, weak lensing convergence fields, as the CFHTLens ones, are non--Gaussian and the MF and LM descriptors are in principle equivalent. \citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order. Such perturbative series, however, have been shown not to converge in \citep{Petri2013} unless the weak lensing fields are smoothed with windows of size comparable to $\sim 15^\prime$. Because of this, throughout this work, we treat MF and LM as independent statistical descriptors.

\subsection{Cosmological parameter inferences}
In this paragraph we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLens observations; we make use of the MF and LM statistical descriptors outlined in the previous paragraph. We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLens data. In this notation, $i$ is an index that refers to the particular bin on which the descriptor is evaluated (for example $i$ can range from 0 to 9 for the LM statistic and from 0 to $N_b-1$ for a Minkowski Functional measured on $N_b$ different excursion sets). Once we make an assumption for the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ and for the parameter priors $\Pi(\mathbf{p})$, we can use the Bayes theorem to compute the parameter likelihood $\mathcal{L}_p$ as follows

\begin{equation}
\label{parameterlikelihood}
\mathcal{L}_p(\mathbf{p}\vert D_i) = \frac{\mathcal{L}_d(D_i\vert \mathbf{p})\Pi(\mathbf{p})}{N_{\mathcal{L}}}
\end{equation}
%
where $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that ensures the proper normalization for $\mathcal{L}_p$; we make the usual assumption that the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ is a Gaussian

\begin{equation}
\mathcal{L}_d(D_i\vert \mathbf{p}) \propto \exp{\left\{-\frac{1}{2}[\mathbf{D}-\mathbf{M(p)}]\mathbf{C}^{-1}[\mathbf{D}-\mathbf{M(p)}]\right\}}
\end{equation} 
%
where the normalization constant $((2\pi)^{N_b}\det{\mathbf{C}})^{1/2}$ is parameter independent; the simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
\begin{equation}
M_i(\mathbf{p}) = \frac{1}{R}\sum_{r=1}^R M_i^r 
\end{equation}
%
and the covariance matrix 
\begin{equation}
C_{ij} = \frac{1}{R-1} \sum_{r=1}^R [M_i^r(\mathbf{p}_0)-M_i(\mathbf{p}_0)][M_j^r(\mathbf{p}_0)-M_j(\mathbf{p}_0)]
\end{equation}
%
is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model--independent. When computing parameter constraints from CFHTLens weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$. Parameter inferences are made estimating the location of the maximum of the parameter likelihood in (\ref{parameterlikelihood}), which we call $\mathbf{p}_{ML}(D_i)$ as well as its confidence contours. A $N\sigma$--confidence contour of $\mathcal{L}_p(\mathbf{p}\vert D_i)$ is defined to be the subset of points in parameter space on which the likelihood has a constant value $c_N$ and 
\begin{equation}
\int_{\mathcal{L}>c_N} \mathcal{L}_p(\mathbf{p}\vert D_i) d\mathbf{p} = \frac{1}{\sqrt{2\pi}}\int_{-N}^N dx e^{-x^2/2}
\end{equation}
%
Given the low dimensionality of the parameter space we consider $(N_p=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on a finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$, and hence we are able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.

%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgements}
We thank the Stampede cluster who saved our day

\bibliography{ref}
\label{lastpage}
\end{document}

### 2014-11-04 Paper_minkowski/paper.tex
update paper.tex

@@
 \begin{abstract}
-Weak lensing surveys have the potential... we consider CFHT \citep{CFHTFu}
+Weak lensing surveys have the potential... we consider CFHTLens \citep{CFHTFu}
 \end{abstract}
@@
 \subsection{CFHTLens data reduction}
+
 \subsection{Simulation design}
+In this paragraph we give a description of the method we used to sample the parameter space in our simulation effort.
+We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$: in order to do this we sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
+We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
+Let a \textit{design} $\mathcal{D}$ be the set of this irregularly spaced $N$ points: we wish to find an optimal design, in which the points are spread as uniformly as possible inside the box.
+Following \citep{coyote2}, we choose our optimal design as the minimum of the cost function
+
+\begin{equation}
+\label{costfunction}
+d(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}
+\end{equation} 
+%
+This problem is mathematically equivalent to the minimization of the Coulomb potential energy of $N$ unit charges in a unit box, which will make sure that the charges are as evenly spread as possible throughout the confining volume.
+Finding the optimal design $\mathcal{D}_m$ that minimized (\ref{costfunction}) can be computationally very demanding, and hence we decided to use a simplified approach that, although approximate, serves our purposes for the grid design.
+We use an iterative procedure:
+\begin{enumerate}
+\item We start from the diagonal design $\mathcal{D}_0$: $x_i^d\equiv i/(N-1)$
+\item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$ where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$
+\item We pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$
+\item We compute the new cost function, if this is less than the previous step, we keep the exchange, otherwise we revert the coordinate swap
+\item We repeat steps 3 and 4 until the relative cost function change is less than a chosen accuracy parameter $\epsilon$ 
+\end{enumerate}
+%
+We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}$, which we show in
+Figure \ref{designfig}.
+%
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/design.eps}
+\caption{$(\Omega_m,w)$ and $(w,\sigma_8)$ projections of our the simulation design; the blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
+\label{designfig}
+\end{center}
+\end{figure*}
+%
+For each parameter point on the grid $\mathbf{p}$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLens shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
+Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will serve the parameter inferences as in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
 \subsection{Ray Tracing Simulations}
+\label{raysim}
 
@@
 \subsection{Cosmological parameter inferences}
+\label{cosmostats}
 In this paragraph we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLens observations; we make use of the MF and LM statistical descriptors outlined in the previous paragraph.
@@
 \begin{equation}
-\mathcal{L}_d(D_i\vert \mathbf{p}) \propto \exp{\left\{-\frac{1}{2}[\mathbf{D}-\mathbf{M(p)}]\mathbf{C}^{-1}[\mathbf{D}-\mathbf{M(p)}]\right\}}
+\label{datalikelihood}
+\begin{matrix}
+\mathcal{L}_d(D_i\vert \mathbf{p}) = ((2\pi)^{N_b}\det{\mathbf{C}})^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})} \\ \\
+\chi^2(D_i\vert \mathbf{p}) = \mathbf{(D - M(p))C^{-1}(D-M(p))}
+\end{matrix}
 \end{equation} 
 %
-where the normalization constant $((2\pi)^{N_b}\det{\mathbf{C}})^{1/2}$ is parameter independent; the simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
+The simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
 \begin{equation}
@@
 %
-is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model--independent.
+is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model--independent; because of this the normalization constant in (\ref{datalikelihood}) is also model--independent.
 When computing parameter constraints from CFHTLens weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.

### 2014-11-04 Paper_minkowski/paper.tex
update paper and ref

@@
 %
-We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}$, which we show in
+We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in
 Figure \ref{designfig}.
@@
 %
-For each parameter point on the grid $\mathbf{p}$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLens shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
+For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLens shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
 Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will serve the parameter inferences as in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
@@
 Given the low dimensionality of the parameter space we consider $(N_p=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on a finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$, and hence we are able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.
+We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M_(\mathbf{p})$ at an arbitrary intermediate point; we decided to use a Radial Basis Function (RBF) interpolation scheme.
+We approximate the model descriptor as
+\begin{equation}
+M(\mathbf{p}) = \sum_{s=1}^N \lambda_s\phi(\vert\mathbf{p}-\mathbf{p}_s\vert)
+\end{equation}
+%
+where $\phi$ has been chosen as a multiquadric function $\phi(r)=\sqrt{1+(r/r_0)^2}$ with $r_0$ chosen as the mean euclidean distance between the points in the simulated grid $\mathbf{p}_s$.
+The constant coefficients $\lambda_s$ can be determined imposing the $N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which enforce the fact that the interpolation should be exact at the simulated points.
+The interpolation computations are conveniently performed using the Scipy library \citep{scipy}
 

### 2014-11-05 Paper_minkowski/paper.tex
added ray tracing simulations section

@@
 Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will serve the parameter inferences as in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
+
 \subsection{Ray Tracing Simulations}
 \label{raysim}
+The goal of this paragraph is to give an outline of our simulation pipeline; the fluctuations in the dark matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
+The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,w(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $w$ and two transverse coordinates $\mathbf{x}_\perp=w\pmb{\beta}$ using the flat sky approximation.
+Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
+We estimate the dark matter gravitational potential running $N$--body simulations (with $N=512^3$) with the public code Gadget2 \citep{Gadget2}, using a comoving box size of $240h^{-1}$Mpc.
+Using a similar procedure as in \citep{RayTracingJain,RayTracingHartlap}, the equation that governs the light ray deflections can be written in the form
+\begin{equation}
+\label{raytrajectory}
+\frac{d^2\mathbf{x}(w)}{dw^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(w),w)
+\end{equation}
+%
+where $\mathbf{x}(w)$ is the trajectory of a single light ray.
+Suppose that a light ray reaches the observer at an angular position $\pmb{\theta}$ on the sky: we want to know where this light ray originated, knowing it comes from a redshift $z_s$.
+To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$; for the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
+Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(w_s;\pmb{\theta}) = \partial \pmb{\beta}(w_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma_1,\gamma_2)$
+%
+\begin{equation}
+A(w_s;\pmb{\theta}) = (1-\kappa(w_s;\pmb{\theta}))\pmb{I} - \gamma_1(w_s;\pmb{\theta})\sigma_3 - \gamma_2(w_s;\pmb{\theta})\sigma_1
+\end{equation}  
+%
+where $\pmb{I}$ is the $2\times2$ identity and $\sigma_{1,3}$ are the first and third Pauli matrices.
+$\kappa$ is related to the source apparent magnification, while $(\gamma_1,\gamma_2)$ are related to the source apparent ellipticity, as seen from the observer.
 

### 2014-11-06 Paper_minkowski/paper.tex
add table with emu1 parameters

@@
 %
-We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in
-Figure \ref{designfig}.
+We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in Table \ref{designtable} and Figure \ref{designfig}.
+%
+\begin{table*}
+\begin{tabular}{c|ccc||c|ccc||c|ccc||c|ccc}
+$N$ & $\Omega_m$ & $w$ & $\sigma_8$ & $N$ & $\Omega_m$ & $w$ & $\sigma_8$ & $N$ & $\Omega_m$ & $w$ & $\sigma_8$ & $N$ & $\Omega_m$ & $w$ & $\sigma_8$ \\ \hline
+1 & 0.136 & -2.484 & 1.034 & 26 & 0.380 & -2.424 & 0.199 & 51 & 0.615 & -1.668 & 0.185 & 76 & 0.849 & -0.183 & 0.821 \\
+2 & 0.145 & -2.211 & 1.303 & 27 & 0.389 & -0.939 & 0.454 & 52 & 0.624 & -2.757 & 0.327 & 77 & 0.859 & -1.182 & 1.415 \\
+3 & 0.155 & -0.393 & 0.652 & 28 & 0.399 & -1.938 & 1.500 & 53 & 0.634 & -1.575 & 0.976 & 78 & 0.869 & -2.031 & 0.227 \\
+4 & 0.164 & -2.181 & 0.313 & 29 & 0.409 & -2.940 & 0.737 & 54 & 0.643 & -2.454 & 1.444 & 79 & 0.878 & -2.697 & 0.524 \\
+5 & 0.173 & -0.423 & 1.231 & 30 & 0.418 & -1.758 & 0.383 & 55 & 0.652 & -1.029 & 1.458 & 80 & 0.887 & -0.363 & 0.439 \\
+6 & 0.183 & -0.909 & 0.269 & 31 & 0.427 & -2.910 & 0.411 & 56 & 0.661 & -0.486 & 0.892 & 81 & 0.897 & -0.999 & 0.468 \\
+7 & 0.192 & -1.605 & 1.401 & 32 & 0.436 & -0.060 & 0.878 & 57 & 0.671 & -2.364 & 0.793 & 82 & 0.906 & -1.698 & 1.273 \\
+8 & 0.201 & -2.787 & 0.807 & 33 & 0.446 & -1.212 & 1.486 & 58 & 0.681 & -2.970 & 0.610 & 83 & 0.915 & -2.544 & 1.175 \\
+9 & 0.211 & -0.333 & 0.341 & 34 & 0.455 & -2.637 & 1.373 & 59 & 0.690 & -1.332 & 0.482 & 84 & 0.925 & -0.636 & 1.259 \\
+10 & 0.221 & -1.485 & 0.666 & 35 & 0.464 & -2.121 & 0.906 & 60 & 0.700 & -0.273 & 0.283 & 85 & 0.943 & -2.394 & 0.835 \\
+11 & 0.239 & -1.848 & 0.962 & 36 & 0.474 & -1.302 & 0.114 & 61 & 0.709 & -2.061 & 0.425 & 86 & 0.953 & -1.545 & 0.355 \\
+12 & 0.249 & -2.727 & 0.369 & 37 & 0.483 & -1.515 & 0.680 & 62 & 0.718 & -1.728 & 1.472 & 87 & 0.963 & -2.151 & 0.510 \\
+13 & 0.258 & -1.395 & 0.241 & 38 & 0.493 & -0.243 & 0.297 & 63 & 0.728 & -0.120 & 0.596 & 88 & 0.972 & -0.666 & 0.694 \\
+14 & 0.267 & -2.667 & 1.317 & 39 & 0.502 & -1.152 & 1.189 & 64 & 0.737 & -2.847 & 1.203 & 89 & 0.981 & -1.242 & 1.048 \\
+15 & 0.276 & -0.849 & 1.429 & 40 & 0.512 & -0.819 & 0.849 & 65 & 0.746 & -0.090 & 1.118 & 90 & 0.991 & -1.908 & 1.020 \\
+16 & 0.286 & -1.272 & 1.104 & 41 & 0.521 & -2.334 & 0.538 & 66 & 0.755 & -0.456 & 1.359 & 91 & 1.000 & -1.425 & 0.708 \\
+17 & 0.295 & -1.878 & 0.100 & 42 & 0.530 & 0.000 & 0.624 & 67 & 0.765 & -2.091 & 1.076 & -- & -- & -- & -- \\
+18 & 0.305 & -0.879 & 0.765 & 43 & 0.540 & -0.030 & 1.161 & 68 & 0.775 & -1.122 & 1.132 & -- & -- & -- & -- \\
+19 & 0.315 & -2.241 & 0.638 & 44 & 0.549 & -1.818 & 1.287 & 69 & 0.784 & -1.062 & 0.779 & -- & -- & -- & -- \\
+20 & 0.324 & -2.001 & 1.217 & 45 & 0.558 & -2.577 & 1.146 & 70 & 0.794 & -1.365 & 0.156 & -- & -- & -- & -- \\
+21 & 0.333 & -0.213 & 0.552 & 46 & 0.568 & -0.516 & 1.331 & 71 & 0.803 & -2.607 & 0.255 & -- & -- & -- & -- \\
+22 & 0.342 & -2.817 & 1.062 & 47 & 0.577 & -3.000 & 0.948 & 72 & 0.812 & -1.788 & 0.722 & -- & -- & -- & -- \\
+23 & 0.352 & -0.576 & 1.090 & 48 & 0.587 & -2.304 & 0.128 & 73 & 0.821 & -2.880 & 0.863 & -- & -- & -- & -- \\
+24 & 0.361 & -0.606 & 0.171 & 49 & 0.596 & -0.696 & 0.496 & 74 & 0.831 & -0.759 & 0.213 & -- & -- & -- & -- \\
+25 & 0.370 & -0.303 & 1.345 & 50 & 0.606 & -0.789 & 0.142 & 75 & 0.840 & -2.274 & 1.387 & -- & -- & -- & -- \\
+\end{tabular}
+\caption{List of the CFHTemu1 grid points in parameter space}
+\label{designtable}
+\end{table*}
 %

### 2014-11-18 Paper_minkowski/paper.tex
update paper and references

@@
 \begin{abstract}
-Weak lensing surveys have the potential... we consider CFHTLens \citep{CFHTFu}
+Weak lensing surveys have the potential... we consider CFHTLens \citep{CFHTKilbinger,CFHTFu}
 \end{abstract}
@@
 \subsection{CFHTLens data reduction}
+\label{cfhtdatareduction}
+%
+The CFHTLens survey covers four sky patches of 64,23,44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of the creation of a galaxy catalogue using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements with \textit{lensfit} \citep{cfht1,cfht2}.
+The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF).
+We apply the following cuts to the galaxy catalogue: mask$<1$, redshift $0.2 < z < 1.3$, fitclass = 0 (which requires the object to be a galaxy) and weight $w>0$ (with larger $w$ indicating smaller shear measurement uncertainty).
+Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ residual sky coverage, and average number density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
+The CFHTLens galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of eack galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
+Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps; these square subfield maps are pixelized according to a Gaussian gridding procedure
+\begin{equation}
+\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)w(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)w(\pmb{\theta}_i)[1+m(\pmb{\theta})]}
+\end{equation} 
+\begin{equation}
+\label{gausskernel}
+W_{\theta_G}(\pmb{\theta}) = \frac{1}{2\pi\theta_G^2}\exp{\left(-\frac{\pmb{\theta}^2}{2\theta_G^2}\right)}
+\end{equation}
+%
+where the smoothing kernel $W_{\theta_G}$ has been varied choosing from the set $(0.5,1.0,1.8,3.5,5.3,8.9)\,$arcmin; the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
+\begin{equation}
+\mathbf{e}^{obs} = (1+m)\mathbf{e}^{true} + c
+\end{equation}
+%
+Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we can perform a non--local Kaiser--Squires inversion to recover the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear field
+%
+\begin{equation}
+\kappa(\mathbf{l}) = \left(\frac{l_1^2-l_2^2}{l_1^2+l_2^2}\right)\gamma^1(\mathbf{l}) + 2\frac{l_1l_2}{l_1^2+l_2^2}\gamma^2(\mathbf{l})
+\end{equation}
+%
+The CFHTLens catalogues contain masked regions (mainly due to bright stars and incorrect PSF subtraction); these regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be masked out.
+We first create grided maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
+We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more throughout description of our data reduction procedure, we refer the reader to our companion paper \citep{Companion}.
 
@@
 In this paragraph we give a description of the method we used to sample the parameter space in our simulation effort.
-We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$: in order to do this we sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
+We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping fixed the other relevant parameters to $(h,\Omega_b,n_s)$ to their fiducial values (0.7,0.046,0.96).
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
 We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
@@
 The goal of this paragraph is to give an outline of our simulation pipeline; the fluctuations in the dark matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
-The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,w(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $w$ and two transverse coordinates $\mathbf{x}_\perp=w\pmb{\beta}$ using the flat sky approximation.
+The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,w(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $w$ (not to be confused with the weight factor in \S\ref{cfhtdatareduction}) and two transverse coordinates $\mathbf{x}_\perp=w\pmb{\beta}$ using the flat sky approximation.
 Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
@@
 %
-where $\mathbf{x}(w)$ is the trajectory of a single light ray.
+where $\mathbf{x}(w)$ is the trajectory of a single light ray, which we visualize schematically in Figure \ref{rayscheme}. 
+%
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.4]{Figures/rayscheme.eps}
+\end{center}
+\caption{Schematics of ray tracing with the lensing potential boosted by a factor of 50 for visualization purposes}
+\label{rayscheme}
+\end{figure*}
+%
 Suppose that a light ray reaches the observer at an angular position $\pmb{\theta}$ on the sky: we want to know where this light ray originated, knowing it comes from a redshift $z_s$.
 To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$; for the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
-Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(w_s;\pmb{\theta}) = \partial \pmb{\beta}(w_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma_1,\gamma_2)$
+Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(w_s;\pmb{\theta}) = \partial \pmb{\beta}(w_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
 %
 \begin{equation}
-A(w_s;\pmb{\theta}) = (1-\kappa(w_s;\pmb{\theta}))\pmb{I} - \gamma_1(w_s;\pmb{\theta})\sigma_3 - \gamma_2(w_s;\pmb{\theta})\sigma_1
+A(w_s;\pmb{\theta}) = (1-\kappa(w_s;\pmb{\theta}))\pmb{I} - \gamma^1(w_s;\pmb{\theta})\sigma^3 - \gamma^2(w_s;\pmb{\theta})\sigma^1
 \end{equation}  
 %
-where $\pmb{I}$ is the $2\times2$ identity and $\sigma_{1,3}$ are the first and third Pauli matrices.
-$\kappa$ is related to the source apparent magnification, while $(\gamma_1,\gamma_2)$ are related to the source apparent ellipticity, as seen from the observer.
+where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the first and third Pauli matrices.
+$\kappa$ is related to the source apparent magnification, while $(\gamma^1,\gamma^2)$ are related to the source apparent ellipticity, as seen from the observer.
+Given a source with intrinsic ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity as seen from an observer will be modified by the cosmic shear $\pmb{\gamma}=\gamma^1 + i\gamma^2$ following
+%
+\begin{equation}
+\mathbf{e} = 
+\begin{cases}
+\frac{\mathbf{e}_s+\mathbf{g}}{1+\mathbf{g}^*\mathbf{e}_s} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert \leq 1 \\ \\
+\frac{1+\mathbf{ge}_s^*}{\mathbf{e}_s^* + \mathbf{g}^*} \,\,\,\,\,\,\,\, \vert \mathbf{g}\vert > 1
+\end{cases}
+\end{equation}
+%
+where $\mathbf{g} = \pmb{\gamma}/1-\kappa$ is the reduced shear.
+For each simulated galaxy, we assign an intrinsic elliptic- ity by rotating the observed ellipticity for that galaxy by a random angle on the sky, while conserving its magnitude $\vert\mathbf{e}\vert$.
+To be consistent with the CFHTLenS analysis, we adopt the weak lensing limit ($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$),hence $\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx \mathbf{e}_s+\pmb{\gamma}$.
+We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$; like for the CFHTLens data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
+These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
 
@@
 \section{Statistical methods}
-The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameters triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a bayesian fashion in order to compute parameter confidence intervals.
+The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a bayesian fashion in order to compute parameter confidence intervals.
 
@@
 The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence random field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$.
-Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ images
+Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ images.
 %

### 2014-11-19 jia/WLanalysis.py
kSZ code backup

@@ -453,8 +453,13 @@ def azimuthalAverage(image, center = None, edges = None, logbins = True, bins = 
 	y, x = np.indices(image.shape)
 	if not center:
 		center = np.array([(x.max()-x.min())/2.0, (x.max()-x.min())/2.0])
-	if image.shape[0]%2 == 0:## added oct/31/2014, since nyquist freqnecy is not centered for even # mapsize
+	
+	## added below on oct/31/2014, 
+	## since nyquist freqnecy is not centered for even # mapsize
+
+	if image.shape[0]%2 == 0:
 		center+=0.5
+	
 	r = np.hypot(x - center[0], y - center[1])#distance to center pixel, for each pixel
 
 	# Get sorted radii

### 2014-11-19 jia/tSZxCFHT.py

@@ -7,27 +7,26 @@
 import numpy as np
 from scipy import *
 from pylab import *
-import os
+import os,sys
 import WLanalysis
 from scipy import interpolate
 
-freq = '545217GHzclean'#'857	GHz'#
-if freq == '545217GHzclean':
-	alpha = -0.00093959731543624692
-	#SNR 6bins -0.0024832214765100613#4bins -0.056124161073825493#6bins: -0.035928411633109614
-elif freq == '857GHz':
-	alpha = -2.0134228187919292e-05
-	#SNR 6 bins-0.00012080536912751662
-	#4bins -0.00056963087248322131
-	#6bins: -0.00035011185682326599
+freq_arr = ['2freqs', '545217GHzclean', '857GHz', 'dusty']#
+if int(sys.argv[1]):
+	freq = freq_arr[int(sys.argv[1])]
+else:
+	freq = freq_arr[0]
+print 'frequency:', freq
+
 ###################### knobs###########################
-plot_crosscorrelate_all = 1
-testCC = 0
-test_powspec = 0
+dusty = 0
+plot_crosscorrelate_all = 0
 create_noise_KS = 0
-cross_cov_mat = 0
+cross_cov_mat = 1
 powspec_without_ells_factor = 0
 clean_dust = 0
+testCC = 0
+test_powspec = 0
 #######################################################
 
 kSZ_dir = '/Users/jia/CFHTLenS/kSZ/newfil/'
@@ -38,11 +37,25 @@ kSZCoordsGen = lambda i: WLanalysis.readFits(kSZ_dir+'LGMCA_W%i_flipper8192_kSZf
 #noiseCoordsGen = lambda i: WLanalysis.readFits(kSZ_dir+'kSZ2_noise_W%i_ellmax3000.fit'%(i))
 #offsetCoordsGen = lambda i: WLanalysis.readFits(kSZ_dir+'kSZ2_W%i_ellmax3000_offset.fit'%(i))
 
+#CC_fcn = lambda Wx: kSZ_dir+'ptMask_Noise_convxkSZ_W%s.fit'%(Wx)# cross correlation file name for 500 sims
+CC_fcn = lambda Wx, freq: kSZ_dir+'convxkSZ_500sim_W%s_%s'%(Wx,freq)
[…]

### 2014-12-01 Paper_minkowski/paper.tex
updated paper

@@
 \usepackage{color}
+\usepackage{pbox}
+
 \hypersetup{
@@
 Because of this, throughout this work, we treat MF and LM as independent statistical descriptors.
-
+In addition to these two descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
+\begin{equation}
+\label{powerspectrum}
+\langle\tilde{\kappa}(\mathbf{l})\tilde{\kappa}(\mathbf{l}')\rangle=(2\pi)^2\delta_D(\mathbf{l}+\mathbf{l}')P_l
+\end{equation}  
+%
+where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function; while the use of this statistic is not a novelty, we want indeed to compare the results we get using MF and LM to the ones already present in the literature.
+A summary of the statistical descriptors we used is presented in Table \ref{desctable}
+%
+\begin{table}
+\begin{tabular}{c|c|c} \hline
+Descriptor & Details & $N_b$ \\ \hline
+$V_0,V_1,V_2$ (MF) & $\kappa_0\in[-0.04,0.12]$ & 50 \\
+Power Spectrum (PS) & $l \in [300,5000]$ & 50 \\
+Moments (LM) & -- & 9 \\
+\end{tabular}
+\caption{Summary of the descriptors we used, along with the specifications and the number of bins $N_b$ used}
+\label{desctable}
+\end{table}
+%
 \subsection{Cosmological parameter inferences}
@@
 \begin{equation}
+\label{datacov}
 C_{ij} = \frac{1}{R-1} \sum_{r=1}^R [M_i^r(\mathbf{p}_0)-M_i(\mathbf{p}_0)][M_j^r(\mathbf{p}_0)-M_j(\mathbf{p}_0)]
@@
 \begin{equation}
+\label{ennesigma}
 \int_{\mathcal{L}>c_N} \mathcal{L}_p(\mathbf{p}\vert D_i) d\mathbf{p} = \frac{1}{\sqrt{2\pi}}\int_{-N}^N dx e^{-x^2/2}
@@
 
+\subsection{Dimensionality reduction}
+\label{pcasection}
+%
+The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLens data; when the question on the accuracy of the $N\sigma$ contours is raised, particular attention should be given on the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
+It is known that the choice of the number of bins, $N_b$, can have a non--negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
+Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we know that the effective dimensionality of the feature space should be close to the number of parameters that are effectively varied (see \citep{coyote2}), 3 in our case; because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ that we choose originally.
+In order to compute the Principal Components of our feature space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
+Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$ subtracting the mean in each bin, and normalizing it by its variance; next we proceed in a SVD decomposition of $\mathbf{\tilde{M}}$
+\begin{equation}
+\label{svd}
+\mathbf{U}\Sigma \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}}
+\end{equation}   
+%
+where $\Sigma_{ij}=\Sigma_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $i$--th principal component of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
+To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\Sigma^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the feature covariance in (\ref{datacov}))
+\begin{equation}
+\frac{1}{N-1}\mathbf{\tilde{M}^T\tilde{M}} = \mathbf{V}\Sigma^2\mathbf{V}^T
+\end{equation} 
+%
+We follow the standard interpretation of PCA components, stating that the only meaningful components $V^T_i$ in the analysis (i.e.
+the ones that contain the relevant cosmological information) are the ones that correspond to the biggest eigenvalues $\Sigma^2_{i}$, with the smallest eigenvalues corresponding to noisy patterns in the model, due to numerical inaccuracies in the simulation pipeline.
+We expect the number of relevant components to be not too far from 3; using the fact that different Principal Components are orthogonal, we perform a PCA projection on our feature space by whitening the features and computing the dot product with the principal components, keeping only the first $n$ components
+\begin{equation}
+\label{pcaprojection}
+M(n)_{i}^r = V^T(n)_{ij}\tilde{M}_j^r \,\,\,\, ; \,\,\,\,  D(n)_i = V^T(n)_{ij}\tilde{D}_j
+\end{equation}
+%
+where we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows.
+The dimensional reduction comes from the fact that physical arguments justify a choice of $n\approx 3\ll N_{b}$.
+We want to stress the fact that, because we vary only 3 parameters in the CFHTemu1 simulations, we expect our feature space to be a 3--dimensional manifold embedded in a $N_b$ dimensional space: the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
+As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds: when curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
+We are allowed some flexibility on this flatness assumption by allowing the number of principal components to be slightly bigger than 3.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Results}
+In this section we outline our main results
+
+\subsection{Number of principal components}
+%
+The results of the PCA analysis are outlined in Figure \ref{pcafig}
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/pca_components.eps}
+\caption{Principal Components of the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $\Sigma_i^2$, the right plot shows their cumulative sum.
+A dashed black line has been drawn in correspondence of $n=3$ components}
+\label{pcafig}
+\end{figure*}
+
+\subsection{Cosmological constraints}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.55]{Figures/contours_3comp.png}
+\end{center}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane $w=-1.0$ (right panel)}
+\label{contours3comp}
+\end{figure*}
+
+\begin{table*}
+\begin{tabular}{c|c|c|c|c||c}
+Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
+$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLens data & Figure \ref{contours3comp} \\ \hline 
+$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{contours3comp} \\
+\end{tabular}
+\caption{Summary table of our results}
+\label{summarytable}
+\end{table*}
+
+\subsection{Robustness}
+
+\subsection{Combining statistics}
 

### 2014-12-01 Paper_minkowski/Figures/generate.py

@@ -1,0 +1,141 @@
+import sys,os,argparse,ConfigParser
+from lenstools.constraints import LikelihoodAnalysis
+import numpy as np
+import matplotlib.pyplot as plt
+from contours import ContourPlot
+
+root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
+brew_colors = ["red","green","blue","black","orange"]
+
+#Descriptor list
+descriptors=dict()
+descriptors["power_spectrum"]="Power spectrum"
+descriptors["minkowski_0"]=r"$V_0$"
+descriptors["minkowski_1"]=r"$V_1$"
+descriptors["minkowski_2"]=r"$V_2$"
+descriptors["moments"]="Moments"
+
+keys = descriptors.keys()
+keys.sort()
+
+
+def pca():
+
+	#Smoothing scales in arcmin
+	smoothing_scale=1.0
+
+	#Create figure
+	fig,ax = plt.subplots(1,2,figsize=(16,8))
+
+	#Cycle over descriptors to plot PCA eigenvalues
+	for n,descr in enumerate(keys):
+
+		#Unpickle the emulator
+		an = LikelihoodAnalysis.load(os.path.join(root_dir,"emulators","emulator_{0}--{1:.1f}.p".format(descr,smoothing_scale)))
+
+		#Compute PCA
+		pca = an.principalComponents()
+
+		#Plot the eigenvalues on the left and the cumulative sum on the right
+		ax[0].plot(pca.eigenvalues,label=descriptors[descr],color=brew_colors[n])
+		ax[1].plot(pca.eigenvalues.cumsum()/pca.eigenvalues.sum(),label=descriptors[descr],color=brew_colors[n])
+
+
+	#Draw a line at 3 components
+	ax[0].plot(3*np.ones(100),np.linspace(1.0e-10,1.0e2,100),color="black",linestyle="--")
+	ax[1].plot(3*np.ones(100),np.linspace(0.9,1.01,100),color="black",linestyle="--")
+	ax[1].set_ylim(0.9,1.01)
+
+	#Legend
+	ax[0].legend()
+
+	#Scale
+	ax[0].set_yscale("log")
+
+	#Labels
+	ax[0].set_xlabel(r"$i$",fontsize=18)
+	ax[1].set_xlabel(r"$n$",fontsize=18)
+	ax[0].set_ylabel(r"$\Sigma^2_i$",fontsize=18)
[…]

### 2014-12-01 andrea/convergence_map_analysis/contours.py
easy to fill contours now

@@ -355,7 +355,7 @@ class ContourPlot(object):
 	##############Plot the contours on top of the likelihood##############
 	######################################################################
 
-	def plotContours(self,colors=["red","green","blue"],display_percentages=True,display_maximum=True,fill=False):
+	def plotContours(self,colors=["red","green","blue"],display_percentages=True,display_maximum=True,fill=False,**kwargs):
 
 		"""
 		Display the confidence likelihood contours
@@ -381,12 +381,12 @@ class ContourPlot(object):
 			fmt[value] = "{0:.1f}%".format(self.computed_p_values[n]*100)
 
 		if fill:
-			self.contour = self.ax.contourf(likelihood,values,colors=colors,origin="lower",extent=extent,aspect="auto")
+			self.contour = self.ax.contourf(likelihood,values,colors=colors,origin="lower",extent=extent,aspect="auto",**kwargs)
 		else:
-			self.contour = self.ax.contour(likelihood,values,colors=colors,origin="lower",extent=extent,aspect="auto")
+			self.contour = self.ax.contour(likelihood,values,colors=colors,origin="lower",extent=extent,aspect="auto",**kwargs)
 
 		#Contour labels
-		self.ax.proxy += [ plt.Rectangle((0,0),1,1,fc=color) for color in colors ]
+		self.ax.proxy += [ plt.Rectangle((0,0),1,1,fc=color) for color in colors if color!="#eeeeee" ]
 		
 		if display_percentages:
 			plt.clabel(self.contour,fmt=fmt,inline=1,fontsize=9)

### 2014-12-01 jia/test_chisq_cube_MPI.py
full covariance bug fix

@@ -10,7 +10,7 @@ import WLanalysis
 from emcee.utils import MPIPool
 import sys
 
-nn = int(sys.argv[1])#range from 0 to 10 for idx_arr
+nn = 0#int(sys.argv[1])#range from 0 to 10 for idx_arr
 print nn
 
 fsky_all = 10.010646820070001
@@ -44,7 +44,8 @@ ps_avg0 = concatenate([np.load(test_dir+fn) for fn in ('PASS_ps_avg.npy','ALL_pk
 ####### 125:150 peak 53;
 ####### 150:200 all powspec
 #### 1) 2 smoothings + powspec
-idx_full = delete(arange(11,100), arange(50-12,50))
+#idx_full = arange(11,100)
+idx_full = delete(arange(11,100), arange(50-12,50)-11)
 #### 2) 2 smoothing
 idx_pk2 = arange(50,100)
 #### 3) 1.0 smoothing
@@ -67,7 +68,7 @@ idx_psAll7000 = arange(161,200-12)
 idx_arr = [idx_full, idx_pk2, idx_pk10, idx_pk18, idx_pk35, idx_pk53, idx_psPass, idx_psAll, idx_psPass7000, idx_psAll7000]
 fn_arr = ['idx_psPass7000_pk2smoothing', 'pk2smoothing', 'pk10', 'pk18', 'pk35', 'pk53', 'psPass', 'psAll', 'psPass7000', 'psAll7000']
 
-def return_interp_cosmo_for_idx (idx):
+def return_interp_cosmo_for_idx (idx, alpha = 0):
 	ps_CFHT_test = ps_CFHT0[idx]
 	idx = idx[where(ps_CFHT_test>0)[0]]#rid of zero bins
 	
@@ -80,16 +81,23 @@ def return_interp_cosmo_for_idx (idx):
 	spline_interps = list()
 	for ibin in range(ps_avg.shape[-1]):
 		ps_model = ps_avg[:,ibin]
-		iinterp = interpolate.Rbf(im, iw, s, ps_model)
+		if alpha:#for Sigma8 compute
+			iinterp = interpolate.Rbf((im/0.27)**alpha*s, iw, ps_model)
+		else:
+			iinterp = interpolate.Rbf(im, iw, s, ps_model)
 		spline_interps.append(iinterp)
 
-	def interp_cosmo (params, method = 'multiquadric'):
+	def interp_cosmo (params, method = 'multiquadric',alpha = alpha):
 		'''Interpolate the powspec for certain param.
[…]

### 2014-12-01 jia/test_chisq_cube_MPI.py
full covariance bug fix

@@ -10,7 +10,7 @@ import WLanalysis
 from emcee.utils import MPIPool
 import sys
 
-nn = 0#int(sys.argv[1])#range from 0 to 10 for idx_arr
+nn = int(sys.argv[1])#range from 0 to 10 for idx_arr
 print nn
 
 fsky_all = 10.010646820070001

### 2014-12-01 jia/test_chisq_cube_MPI.py
full covariance bug fix

@@ -125,10 +125,15 @@ def plot_heat_map_w (values):
 ############ operation ####################################
 ##########################################################
 pool=MPIPool()
+print 'boo'
 idx = idx_arr[nn]
+
 interp_cosmo, cov_mat, cov_inv, ps_CFHT = return_interp_cosmo_for_idx (idx)
+print 'boo2'
 values = [[w, idx, interp_cosmo, cov_inv, ps_CFHT] for w in w_arr]
+
 pool.map(plot_heat_map_w, values)
+
 cube = array([load('/home1/02977/jialiu/chisq_cube/test/chisqcube_%s_w%s.npy'%(fn_arr[nn], w)) for w in w_arr])
 
 save(test_dir+'covmat_%s.npy'%(fn_arr[nn]), cov_mat)

### 2014-12-02 Paper_minkowski/Figures/generate.py
update generate.py and paper.tex

@@ -2,7 +2,10 @@ import sys,os,argparse,ConfigParser
 from lenstools.constraints import LikelihoodAnalysis
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib import rc
 from contours import ContourPlot
+
+axes_facecolor = rc.func_globals["rcParams"]["axes.facecolor"]
 
 root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
 brew_colors = ["red","green","blue","black","orange"]
@@ -109,16 +112,19 @@ def contours():
 
 		#Marginalize
 		contour_marg.marginalize("w")
-		#Slice
-		contour_slice.slice("w",-1.0)
+		
+		#Slice on best fit for w
+		maximum = contour_slice.getMaximum()
+		print("Likelihood with {0} is maximum at {1}".format(descr,maximum))
+		contour_slice.slice("w",maximum["w"])
 
 		#Get levels
 		contour_marg.getLikelihoodValues(levels=levels)
 		contour_slice.getLikelihoodValues(levels=levels)
 
 		#Plot contours
-		contour_marg.plotContours(colors=[brew_colors[n],"#eeeeee"],fill=True,display_maximum=False,display_percentages=False,alpha=0.45)
-		contour_slice.plotContours(colors=[brew_colors[n],"#eeeeee"],fill=True,display_maximum=False,display_percentages=False,alpha=0.45)
+		contour_marg.plotContours(colors=[brew_colors[n],axes_facecolor],fill=True,display_maximum=False,display_percentages=False,alpha=0.45)
+		contour_slice.plotContours(colors=[brew_colors[n],axes_facecolor],fill=True,display_maximum=False,display_percentages=False,alpha=0.45)
 
 	
 	#Legend
@@ -128,7 +134,7 @@ def contours():
 	contour_slice.labels(None)
 
 	#Save
-	fig.savefig("contours_{0}comp.png".format(n_components))
+	fig.savefig("contours_{0}comp.pdf".format(n_components))
 
 
 

### 2014-12-02 andrea/convergence_map_analysis/contours.py
compute single parameter likelihoods

@@ -7,6 +7,7 @@ import logging
 import numpy as np
 from scipy import stats
 import matplotlib.pyplot as plt
+from matplotlib import rc
 
 #############################################################
 ##################ContourPlot class##########################
@@ -189,6 +190,28 @@ class ContourPlot(object):
 		self.extent = (self.min[self.remaining_parameters[0]],self.max[self.remaining_parameters[0]],self.min[self.remaining_parameters[1]],self.max[self.remaining_parameters[1]])
 		self.ax.set_xlim(self.extent[0],self.extent[1])
 		self.ax.set_ylim(self.extent[2],self.extent[3])
+
+
+	def marginal(self,parameter_name="w"):
+
+		"""
+		Marginalize the likelihood over all parameters but one
+
+		"""
+
+		assert hasattr(self,"likelihood"),"You have to load in the likelihood first!"
+		assert parameter_name in self.parameter_axes.keys(),"You are trying to compute a marginal likelihood of a parameter that does not exist!"
+
+		remaining_parameters = self.parameter_axes.keys()
+		remaining_parameters.pop(remaining_parameters.index(parameter_name))
+		remaining_parameter_axes = [ self.parameter_axes[par] for par in remaining_parameters ]
+
+		#Marginalize the likelihood
+		marginal_likelihood = self.likelihood.sum(axis=tuple(remaining_parameter_axes))
+
+		#Return the non-normalized single parameter likelihood
+		return np.linspace(self.min[parameter_name],self.max[parameter_name],self.npoints[parameter_name]),marginal_likelihood
+
 
 	def slice(self,parameter_name="w",parameter_value=-1.0):
 
@@ -386,7 +409,7 @@ class ContourPlot(object):
 			self.contour = self.ax.contour(likelihood,values,colors=colors,origin="lower",extent=extent,aspect="auto",**kwargs)
 
 		#Contour labels
-		self.ax.proxy += [ plt.Rectangle((0,0),1,1,fc=color) for color in colors if color!="#eeeeee" ]
+		self.ax.proxy += [ plt.Rectangle((0,0),1,1,fc=color) for color in colors if color!=rc.func_globals["rcParams"]["axes.facecolor"] ]
 		
 		if display_percentages:
 			plt.clabel(self.contour,fmt=fmt,inline=1,fontsize=9)

### 2014-12-02 andrea/convergence_map_analysis/contours.py
compute contours of 1D likelihood

@@ -6,8 +6,50 @@ import logging
 
 import numpy as np
 from scipy import stats
+from scipy import integrate
 import matplotlib.pyplot as plt
 from matplotlib import rc
+
+#############################################################
+############Find likelihood levels in 1D likelihood##########
+#############################################################
+
+def _1d_level_values(p,l,level=0.684,quantity=2):
+
+	"""
+	Find the parameter extremes that correspons to the likelihood Nsigma level
+
+	"""
+
+	#Find the maximum of the likelihood
+	maximum = np.where(l==l.max())[0][0]
+	parmax = p[maximum]
+
+	all_levels = np.zeros_like(l)
+	
+	for n in range(l.shape[0]):
+		all_levels[n] = l[l>=l[n]].sum() / l.sum()
+
+	#Find the closest level
+	closest = np.argmin(np.abs(all_levels - level))
+
+	#Find the n corresponding parameter values
+	ranks = stats.rankdata(np.abs(l-l[closest])).astype(np.int) - 1
+
+	par = list()
+	for n in range(quantity):
+		par.append(p[np.where(ranks==n)[0][0]])
+
+	#Sort parameters in order of closeness to the maximum
+	def _closest(x):
+		return np.abs(x-parmax)
+
+	par.sort(key=_closest)
+
+	return par
+
+	
+
 
 #############################################################
 ##################ContourPlot class##########################
@@ -192,7 +234,7 @@ class ContourPlot(object):
 		self.ax.set_ylim(self.extent[2],self.extent[3])
 
 
-	def marginal(self,parameter_name="w"):
+	def marginal(self,parameter_name="w",levels=None):
 
 		"""
 		Marginalize the likelihood over all parameters but one
@@ -207,10 +249,29 @@ class ContourPlot(object):
 		remaining_parameter_axes = [ self.parameter_axes[par] for par in remaining_parameters ]
 
 		#Marginalize the likelihood
+		parameter_range = np.linspace(self.min[parameter_name],self.max[parameter_name],self.npoints[parameter_name])
 		marginal_likelihood = self.likelihood.sum(axis=tuple(remaining_parameter_axes))
 
-		#Return the non-normalized single parameter likelihood
-		return np.linspace(self.min[parameter_name],self.max[parameter_name],self.npoints[parameter_name]),marginal_likelihood
+		#Compute the normalization
+		normalization = integrate.simps(marginal_likelihood,x=parameter_range)
+		marginal_likelihood /= normalization
+
[…]

### 2014-12-02 Paper_minkowski/paper.tex
update generate.py and paper.tex
update figures and paper

@@
 
+\subsection{Robustness}
+%
+The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e.
+they are reasonably stable once we consider an increasing number of Principal Components.
+These stability plots are shown in Figure
+
 \subsection{Cosmological constraints}
@@
 \begin{center}
-\includegraphics[scale=0.55]{Figures/contours_3comp.png}
+\includegraphics[scale=0.4]{Figures/contours_3comp.pdf}
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane $w=-1.0$ (right panel)}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane where $w$ corresponds to its best fit value (right panel)}
 \label{contours3comp}
@@
 \end{table*}
-
-\subsection{Robustness}
 

### 2014-12-02 Paper_minkowski/Figures/generate.py

@@ -9,6 +9,7 @@ axes_facecolor = rc.func_globals["rcParams"]["axes.facecolor"]
 
 root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
 brew_colors = ["red","green","blue","black","orange"]
+brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
 
 #Descriptor list
 descriptors=dict()
@@ -21,6 +22,7 @@ descriptors["moments"]="Moments"
 keys = descriptors.keys()
 keys.sort()
 
+##############################################################################################################################################
 
 def pca():
 
@@ -137,11 +139,87 @@ def contours():
 	fig.savefig("contours_{0}comp.pdf".format(n_components))
 
 
+##################################################################################################################################################
 
+def robustness():
+
+	#Smoothing scales in arcmin
+	smoothing_scale=1.0
+
+	#Likelihood levels
+	levels = [0.684]
+
+	#Descriptors
+	#descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
+	descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
+	descriptors_robustness.sort()
+
+	#Number of principal components to display
+	principal_components = dict()
+	for descr in descriptors_robustness:
+		principal_components[descr] = [3,4,5,6,8,10,20,30,40,50]
+
+	principal_components["moments--{0:.1f}"] = [3,4,5,6,8,9]
+
+	#Parameters of which we want to compute the confidence estimates
+	parameter_axes = {"Omega_m":0,"w":1,"sigma8":2}
+	cosmo_labels = {"Omega_m":r"$\Omega_m$","w":r"$w$","sigma8":r"$\sigma_8$"}
+	
+	#Parse command line options
+	parser = argparse.ArgumentParser(prog=sys.argv[0])
[…]

### 2014-12-02 andrea/convergence_map_analysis/test_load.py
added test_load to debug

@@ -1,0 +1,124 @@
+from __future__ import print_function,division,with_statement
+
+import os,sys
+import argparse
+import logging
+import time
+
+#################################################################################
+####################LensTools functionality######################################
+#################################################################################
+
+from lenstools.simulations import CFHTemu1,CFHTcov
+from lenstools.observations import CFHTLens
+from lenstools.constraints import LikelihoodAnalysis
+
+#################################################################################
+####################Borrow the FeatureLoader class from train####################
+#################################################################################
+
+from train import FeatureLoader
+from train import output_string
+
+#################################################################################
+####################Borrow the ContourPlot class from contours###################
+#################################################################################
+
+from contours import ContourPlot
+
+######################################################################
+###################Other functionality################################
+######################################################################
+
+import numpy as np
+from emcee.utils import MPIPool
+
+#######################################################################
+###################DEBUG_PLUS##########################################
+#######################################################################
+
+from train import DEBUG_PLUS
+
+######################################################################
+###################Main execution#####################################
+######################################################################
+
+def main():
+
+	#################################################
+	############Option parsing#######################
+	#################################################
+
+	#Parse command line options
+	parser = argparse.ArgumentParser()
+	parser.add_argument("-f","--file",dest="options_file",action="store",type=str,help="analysis options file")
+	parser.add_argument("-v","--verbose",dest="verbose",action="store_true",default=False,help="turn on verbosity")
+	parser.add_argument("-vv","--verbose_plus",dest="verbose_plus",action="store_true",default=False,help="turn on additional verbosity")
+	parser.add_argument("-m","--mask_scale",dest="mask_scale",action="store_true",default=False,help="scale peaks and power spectrum to unmasked area")
+	parser.add_argument("-c","--cut_convergence",dest="cut_convergence",action="store",default=None,help="select convergence values in (min,max) to compute the likelihood. Safe for single descriptor only!!")
[…]

### 2014-12-02 andrea/convergence_map_analysis/train.py
Prevent randomness in dictionary keys

@@ -174,7 +174,11 @@ class FeatureLoader(object):
 			#Construct one ensemble for each feature (with included smoothing scales) and load in the data
 			ensemble_subfield = list()
 			
-			for feature_type in self.features_to_measure.keys():
+			#Prevent randomness in dictionary keys
+			features_to_measure = self.features_to_measure.keys()
+			features_to_measure.sort()
+
+			for feature_type in features_to_measure:
 			
 				for smoothing_scale in self.features_to_measure[feature_type]:
 					

### 2014-12-02 Paper_minkowski/paper.tex
update paper and figures

@@
 they are reasonably stable once we consider an increasing number of Principal Components.
-These stability plots are shown in Figure
+These stability plots are shown in Figure \ref{robustnessfig}
+
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/robustness_pca.eps}
+\caption{Stability plot}
+\label{robustnessfig}
+\end{figure*}
 
@@
 $(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLens data & Figure \ref{contours3comp} \\ \hline 
-$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{contours3comp} \\
+$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{robustnessfig} \\
 \end{tabular}

### 2014-12-02 Paper_minkowski/Figures/generate.py

@@ -150,9 +150,14 @@ def robustness():
 	levels = [0.684]
 
 	#Descriptors
-	#descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
-	descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
-	descriptors_robustness.sort()
+	descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
+	descriptor_titles = dict()
+	descriptor_titles["minkowski_0--{0:.1f}"] = r"$V_0$"
+	descriptor_titles["minkowski_1--{0:.1f}"] = r"$V_1$"
+	descriptor_titles["minkowski_2--{0:.1f}"] = r"$V_2$"
+	descriptor_titles["minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}"] = r"$V_0 \times V_1 \times V_2$"
+	descriptor_titles["power_spectrum--{0:.1f}"] = r"$\mathrm{PS}$"
+	descriptor_titles["moments--{0:.1f}"] = r"$\mathrm{Moments}$"
 
 	#Number of principal components to display
 	principal_components = dict()
@@ -194,7 +199,6 @@ def robustness():
 
 			#Load the likelihood
 			likelihood_file = os.path.join(root_dir,"likelihoods","likelihoodmock_"+descr.format(smoothing_scale)+"_ncomp{0}.npy".format(n_components))
-			print(likelihood_file)
 			contour.getLikelihood(likelihood_file,parameter_axes=parameter_axes,parameter_labels=cosmo_labels)
 
 			#Set physical units
@@ -210,16 +214,70 @@ def robustness():
 			contour.plotContours(colors=[brew_colors_11[n]],fill=False,display_percentages=False,display_maximum=False)
 
[…]

### 2014-12-02 andrea/convergence_map_analysis/contours.py
modified title label font to 22

@@ -337,7 +337,7 @@ class ContourPlot(object):
 
 		self.ax.set_xlabel(self.parameter_labels[self.remaining_parameters[0]])
 		self.ax.set_ylabel(self.parameter_labels[self.remaining_parameters[1]])
-		self.ax.set_title(self.title_label)
+		self.ax.set_title(self.title_label,fontsize=22)
 
 		if contour_label is not None:
 			self.ax.legend(self.ax.proxy,contour_label)

### 2014-12-02 Paper_minkowski/paper.tex
update abstract and introduction

@@
 %\documentclass[11pt]{article}
-\documentclass[reprint,aps,prd,superscriptaddress,showkeys]{revtex4-1}
+\documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
 \usepackage{epsfig,amsmath,natbib}
@@
 
-\title{CFHTLens Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments}
+\title{CFHTLenS Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments}
 
@@
 \begin{abstract}
-Weak lensing surveys have the potential... we consider CFHTLens \citep{CFHTKilbinger,CFHTFu}
+Weak gravitational lensing has been proposed as an interesting probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; the fact that typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss some of the cosmological information contained in survey data.
+In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ from weak lensing Minkowski Functionals and Moments, using the publicly available data from the 154\,deg$^2$ CFHTLenS survey.
+We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise read from the CFHTLenS catalogs.
+We then build an emulator that interpolates the feature space with an accuracy of $\sim5\%$, and use it to compute the parameter likelihood, from which we derive the data constraints.
+We find that...
+
 \end{abstract}
@@
 \keywords{Weak Gravitational Lensing --- Data analysis --- Methods: analytical,numerical,statistical}
+\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}
 
@@
 \section{Introduction}
-In this work...
+In this work we use the publicly available CFHTLenS data, that consists of a catalog of $\approx$4.2 million galaxies, combined with a suite of ray-tracing simulations in 91 different cosmological models to constrain the cosmological parameters $\Omega_m$,$\sigma_8$ and the DE equation of state $w$.
+The paper is organized as follows; we first give an overview of the CFHTLenS catalogs we make use of, summarizing the data reduction techniques we adopted.
+Next, we give a description of our simulation pipeline, including the procedure to sample the parameter space and a broad description of the ray--tracing algorithm; after this we illustrate the statistical descriptors that we use to extract the cosmological information, complemented with a dimensional reduction and statistical inference framework.
+We then outline our results, with particular focus on the cosmological parameter constraints.
+To conclude, we discuss our findings and comment on possible future developments of this analysis.
 
@@
 
-\subsection{CFHTLens data reduction}
+\subsection{CFHTLenS data reduction}
 \label{cfhtdatareduction}
 %
-The CFHTLens survey covers four sky patches of 64,23,44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of the creation of a galaxy catalogue using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements with \textit{lensfit} \citep{cfht1,cfht2}.
+The CFHTLenS survey covers four sky patches of 64,23,44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of the creation of a galaxy catalogue using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements with \textit{lensfit} \citep{cfht1,cfht2}.
 The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF).
@@
 Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ residual sky coverage, and average number density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
-The CFHTLens galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of eack galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
+The CFHTLenS galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of eack galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
 Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps; these square subfield maps are pixelized according to a Gaussian gridding procedure
@@
 %
-The CFHTLens catalogues contain masked regions (mainly due to bright stars and incorrect PSF subtraction); these regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be masked out.
+The CFHTLenS catalogues contain masked regions (mainly due to bright stars and incorrect PSF subtraction); these regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be masked out.
 We first create grided maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
@@
 %
-For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLens shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
+For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLenS shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
 Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will serve the parameter inferences as in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
@@
 To be consistent with the CFHTLenS analysis, we adopt the weak lensing limit ($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$),hence $\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx \mathbf{e}_s+\pmb{\gamma}$.
-We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$; like for the CFHTLens data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
+We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$; like for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
 These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
@@
 If the $\kappa$ field was Gaussian, one could express all the Minkowski Functionals in terms of the LM2 moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones.
-In reality, weak lensing convergence fields, as the CFHTLens ones, are non--Gaussian and the MF and LM descriptors are in principle equivalent.
+In reality, weak lensing convergence fields, as the CFHTLenS ones, are non--Gaussian and the MF and LM descriptors are in principle equivalent.
 \citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order.
@@
 \label{cosmostats}
-In this paragraph we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLens observations; we make use of the MF and LM statistical descriptors outlined in the previous paragraph.
-We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLens data.
+In this paragraph we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations; we make use of the MF and LM statistical descriptors outlined in the previous paragraph.
+We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLenS data.
 In this notation, $i$ is an index that refers to the particular bin on which the descriptor is evaluated (for example $i$ can range from 0 to 9 for the LM statistic and from 0 to $N_b-1$ for a Minkowski Functional measured on $N_b$ different excursion sets).
@@
 is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model--independent; because of this the normalization constant in (\ref{datalikelihood}) is also model--independent.
-When computing parameter constraints from CFHTLens weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.
+When computing parameter constraints from CFHTLenS weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.
 Parameter inferences are made estimating the location of the maximum of the parameter likelihood in (\ref{parameterlikelihood}), which we call $\mathbf{p}_{ML}(D_i)$ as well as its confidence contours.
@@
 %
-The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLens data; when the question on the accuracy of the $N\sigma$ contours is raised, particular attention should be given on the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
+The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data; when the question on the accuracy of the $N\sigma$ contours is raised, particular attention should be given on the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
 It is known that the choice of the number of bins, $N_b$, can have a non--negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
@@
 where we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows.
-The dimensional reduction comes from the fact that physical arguments justify a choice of $n\approx 3\ll N_{b}$.
+The dimensional reduction comes from the fact that physical arguments justify a choice of $n\approx 3< N_{b}$.
 We want to stress the fact that, because we vary only 3 parameters in the CFHTemu1 simulations, we expect our feature space to be a 3--dimensional manifold embedded in a $N_b$ dimensional space: the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
 As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds: when curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
-We are allowed some flexibility on this flatness assumption by allowing the number of principal components to be slightly bigger than 3.
+We are allowed some flexibility on this flatness assumption by allowing the number of principal components to be bigger than 3.
 
@@
 Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
-$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLens data & Figure \ref{contours3comp} \\ \hline 
+$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLenS data & Figure \ref{contours3comp} \\ \hline 
 $(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{robustnessfig} \\

### 2014-12-02 Paper_minkowski/Figures/generate.py

@@ -8,7 +8,7 @@ from contours import ContourPlot
 axes_facecolor = rc.func_globals["rcParams"]["axes.facecolor"]
 
 root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
-brew_colors = ["red","green","blue","black","orange"]
+brew_colors = ["red","green","blue","black","orange","magenta","cyan"]
 brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
 
 #Descriptor list
@@ -150,7 +150,8 @@ def robustness():
 	levels = [0.684]
 
 	#Descriptors
-	descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
+	#descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
+	descriptors_robustness = ["minkowski_0--{0:.1f}","minkowski_1--{0:.1f}","minkowski_2--{0:.1f}","minkowski_012--{0:.1f}_power_spectrum--{0:.1f}","power_spectrum--{0:.1f}","moments--{0:.1f}"]
 	descriptor_titles = dict()
 	descriptor_titles["minkowski_0--{0:.1f}"] = r"$V_0$"
 	descriptor_titles["minkowski_1--{0:.1f}"] = r"$V_1$"
@@ -158,6 +159,7 @@ def robustness():
 	descriptor_titles["minkowski_0--{0:.1f}_minkowski_1--{0:.1f}_minkowski_2--{0:.1f}"] = r"$V_0 \times V_1 \times V_2$"
 	descriptor_titles["power_spectrum--{0:.1f}"] = r"$\mathrm{PS}$"
 	descriptor_titles["moments--{0:.1f}"] = r"$\mathrm{Moments}$"
[…]

### 2014-12-03 Paper_minkowski/paper.tex
take figure number from the command line

@@
 \includegraphics[scale=0.4]{Figures/design.eps}
-\caption{$(\Omega_m,w)$ and $(w,\sigma_8)$ projections of our the simulation design; the blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
+\caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of our the simulation design; the blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
 \label{designfig}
@@
 Where $A$ is the total area of the fields of view we have been using and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences.
-The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
+The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, $\partial V_0$ (which can be obtained by differentiation $\partial V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$), while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
 In addition to these topological descriptors, we consider a set of low order moments (LM) of the convergence field (two quadratic, three cubic and four quartic), which are defined in the following way
@@
 where we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows.
-The dimensional reduction comes from the fact that physical arguments justify a choice of $n\approx 3< N_{b}$.
+The dimensional reduction comes from the fact that physical arguments justify a choice of $n< N_{b}$.
 We want to stress the fact that, because we vary only 3 parameters in the CFHTemu1 simulations, we expect our feature space to be a 3--dimensional manifold embedded in a $N_b$ dimensional space: the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.

### 2014-12-03 Paper_minkowski/Figures/generate.py

@@ -1,5 +1,8 @@
 import sys,os,argparse,ConfigParser
+
 from lenstools.constraints import LikelihoodAnalysis
+from lenstools.simulations import Design
+
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import rc
@@ -8,23 +11,53 @@ from contours import ContourPlot
 axes_facecolor = rc.func_globals["rcParams"]["axes.facecolor"]
 
 root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
+design_points = "/Users/andreapetri/Documents/Cosmology_software/LensTools/lenstools/data/CFHTemu1_array.npy"
 brew_colors = ["red","green","blue","black","orange","magenta","cyan"]
 brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
+brew_colors_diverging = ["#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#ffff99","#b15928"]
 
 #Descriptor list
 descriptors=dict()
-descriptors["power_spectrum"]="Power spectrum"
+descriptors["power_spectrum"]=r"$\mathrm{PS}$"
 descriptors["minkowski_0"]=r"$V_0$"
 descriptors["minkowski_1"]=r"$V_1$"
 descriptors["minkowski_2"]=r"$V_2$"
-descriptors["moments"]="Moments"
+descriptors["moments"]=r"$\mathrm{Moments}$"
+
+#Number of principal components
+num_components = dict()
+num_components["power_spectrum"] = 3
+num_components["minkowski_0"] = 3
+num_components["minkowski_1"] = 3
+num_components["minkowski_2"] = 3
+num_components["moments"] = 3  
 
 keys = descriptors.keys()
 keys.sort()
 
+def design(cmd_args):
+
+	#Load the design
+	design = Design.load(design_points,[r"$\Omega_m$",r"$w$",r"$\sigma_8$"])
+
+	#Create the figure
+	fig,ax = plt.subplots(1,2,figsize=(16,8))
+
+	#Visualize the design
[…]

### 2014-12-03 Paper_minkowski/Figures/generate.py
generate more figures

@@ -10,8 +10,11 @@ from contours import ContourPlot
 
 axes_facecolor = rc.func_globals["rcParams"]["axes.facecolor"]
 
+#Locations
 root_dir = "/Users/andreapetri/Documents/Columbia/CFHTLens_analysis/andrea/convergence_map_analysis/cfht_masked_BAD_clipped"
 design_points = "/Users/andreapetri/Documents/Cosmology_software/LensTools/lenstools/data/CFHTemu1_array.npy"
+
+#Colors
 brew_colors = ["red","green","blue","black","orange","magenta","cyan"]
 brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
 brew_colors_diverging = ["#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#ffff99","#b15928"]
@@ -27,13 +30,43 @@ descriptors["moments"]=r"$\mathrm{Moments}$"
 #Number of principal components
 num_components = dict()
 num_components["power_spectrum"] = 3
-num_components["minkowski_0"] = 3
-num_components["minkowski_1"] = 3
-num_components["minkowski_2"] = 3
-num_components["moments"] = 3  
+num_components["minkowski_0"] = 5
+num_components["minkowski_1"] = 20
+num_components["minkowski_2"] = 20
+num_components["moments"] = 9 
+
+#Smoothing scales
+smoothing_scales = dict()
+smoothing_scales["power_spectrum"] = 1.0
+smoothing_scales["minkowski_0"] = 1.0
+smoothing_scales["minkowski_1"] = 1.0
+smoothing_scales["minkowski_2"] = 1.0 
+smoothing_scales["moments"] = 1.0
 
 keys = descriptors.keys()
 keys.sort()
+
+################################################################################################################################################
+################################################################################################################################################
+
+def _cross_name(*args):
+
+	names = list()
+	for arg in args:
+		names.append("{0}--{1:.1f}_ncomp{2}".format(arg,smoothing_scales[arg],num_components[arg]))
+
+	return "-".join(names) 
+
+def _cross_label(*args):
+
+	labels = list()
+	for arg in args:
+		labels.append(descriptors[arg]+r"$({0})$".format(num_components[arg]))
+
[…]

### 2014-12-08 Paper_minkowski/paper.tex
generated all figures

@@
 We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise read from the CFHTLenS catalogs.
-We then build an emulator that interpolates the feature space with an accuracy of $\sim5\%$, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We find that...
+We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
+We find that the constraint on $\Sigma_8$ is ...
 
@@
 %
-where the smoothing kernel $W_{\theta_G}$ has been varied choosing from the set $(0.5,1.0,1.8,3.5,5.3,8.9)\,$arcmin; the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
+where the smoothing scale $\theta_G$ has been fixed to 1.0\,arcmin; the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
 \begin{equation}
@@
 \section{Results}
-In this section we outline our main results
-
-\subsection{Number of principal components}
 %
-The results of the PCA analysis are outlined in Figure \ref{pcafig}
-\begin{figure*}
-\includegraphics[scale=0.4]{Figures/pca_components.eps}
-\caption{Principal Components of the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $\Sigma_i^2$, the right plot shows their cumulative sum.
-A dashed black line has been drawn in correspondence of $n=3$ components}
-\label{pcafig}
-\end{figure*}
+This section describes the results we have obtained in this work, and is organized as follows: we first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
+We then show the cosmological constraints from the CFHTLenS data.
+Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
+The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ and hence has a much smaller relative uncertainty.
+We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes; we also show the $\Sigma_8$ marginalized likelihood.
+We finally study the effect of combining different descriptors, in hope that this helps in tightening the constraints.
+A summary with the complete set of results, along with the relevant Figures, is shown in Table \ref{summarytable}.
 
@@
 The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e.
-they are reasonably stable once we consider an increasing number of Principal Components.
-These stability plots are shown in Figure \ref{robustnessfig}
-
+they are reasonably stable once we consider an large enough number $n$ of Principal Components.
+We show the PCA eigenvalues for the complete set of statistical descriptors in Figure \ref{pcafig}, as well as the contour stability plots in Figure \ref{robustnessfig}.
+%
 \begin{figure*}
-\includegraphics[scale=0.4]{Figures/robustness_pca.eps}
-\caption{Stability plot}
+\includegraphics[scale=0.4]{Figures/pca_components.eps}
+\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $\Sigma_i^2$, the right plot shows their cumulative sum.
+A dashed black line has been drawn in correspondence of $n=3$ components}
+\label{pcafig}
+\end{figure*}
+%
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/robustness_pca_Omega_m-sigma8.eps}
+\caption{PCA projection dependence of the $1\sigma$ contours in the $(\Omega_m,\sigma_8)$ plane obtained from a mock observation constructed with the CFHTcov simulations; the different panels refer to the descriptors (from left to right, top to bottom) $V_0$, $\partial V_0$(PDF), $V_1$, $V_2$, Power Spectrum and Moments}
 \label{robustnessfig}
 \end{figure*}
-
+%
 \subsection{Cosmological constraints}
+%
+We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figure \ref{contours3single} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
+Additionally we show the $\Sigma_8$ likelihood function (marginalized over $\Omega_m$ and $w$) in Figure \ref{likelihoodSi8single}.
 
@@
 \begin{center}
-\includegraphics[scale=0.4]{Figures/contours_3comp.pdf}
+\includegraphics[scale=0.45]{Figures/contoursOmega_m-sigma8_single.eps}
+\includegraphics[scale=0.45]{Figures/contoursmockOmega_m-sigma8_single.eps}
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the $V_0$ (red), $V_1$ (blue), $V_2$ (green), LM (black) and Power Spectrum (orange) statistics; the two panels are obtained marginalizing the parameter likelihood (\ref{parameterlikelihood}) over $w$ (left panel) and conditioning it on the plane where $w$ corresponds to its best fit value (right panel)}
-\label{contours3comp}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data (left panel) and from a mock observation constructed using the CFHTcov simulations as data (right panel).
+The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $w$.
+The parentheses near the descriptor label refer to the number of principal components.}
+\label{contours3single}
 \end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{Figures/contoursw-Sigma8Om055_single.eps}
+\end{center}
+\caption{$1\sigma$ constraints on the $(w,\Sigma_8)$ parameter doublet from the CFHTLenS data, obtained with the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data.
+The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $\Omega_m$.
+The parentheses near the descriptor label refer to the number of principal components.}
+\label{contours3singleRep}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{Figures/contoursSigma8Om055_single.eps}
+\end{center}
+\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; the likelihood has been marginalized over $\Omega_m$ and $w$.
+The parentheses near the descriptor label refer to the number of principal components.}
+\label{likelihoodSi8single}
+\end{figure}
 
@@
 Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
-$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask & $1\sigma$ contours from CFHTLenS data & Figure \ref{contours3comp} \\ \hline 
-$(\Omega_m,w,\sigma_8)$ & $V_0,V_1,V_2$, LM, PS & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ contours from simulations \\ for robustness test}  & Figure \ref{robustnessfig} \\
+$(\Omega_m,\sigma_8)$ & PS,$V_0,V_1,V_2$,LM & $1^\prime$ & BAD mask & Stability of contours & Figure \ref{robustnessfig} \\ \hline 
+$(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & Figures \ref{contours3single},\ref{contours3single}b \\ \hline
+$(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $1^\prime$ & BAD mask & contours from CFHTLenS & Figure \ref{contours3singleRep} \\ \hline 
+$\Sigma_8$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $1^\prime$ & BAD mask & $\mathcal{L}(\Sigma_8)$ from CFHTLenS & Figure \ref{likelihoodSi8single} \\ \hline
+$(\Omega_m,\sigma_8)$ & PS(3)$\times V_0(5)\times V_1(20)\times V_2(20)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & Figure \ref{contours3combined} \\ \hline
+$(w,\Sigma_8)$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & Figure \ref{contours3combined}b \\ \hline
+$\Sigma_8$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{$\mathcal{L}(\Sigma_8)$ from CFHTLenS \\ combining statistics} & Figure \ref{likelihoodSi8cross} \\ \hline
 \end{tabular}
@@
 \end{table*}
+%
+We discuss these results in \S~\ref{discussion}.
 
 \subsection{Combining statistics}
+%
+An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in our companion paper \citep{Companion}, where we combine the power spectrum and peak count statistics, as well as in the literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
+The procedure we adopt is the following: suppose we consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor; we compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ to keep in order for the constraints to be stable.
+We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector: this procedure allows us to take the cross covariance between different descriptors.
+We show in Figure \ref{contours3combined} the combined CFHTLenS constraints on the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
+We discuss our findings in the next section.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.45]{Figures/contoursOmega_m-sigma8_cross.eps}
+\includegraphics[scale=0.45]{Figures/contoursw-Sigma8Om055_cross.eps}
+\end{center}
+\caption{Combined $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ (left panel) and $(w,\Sigma_8)$ (right panel) doublets, using the MFs (red), MFs$\times$Power Spectrum (green) and MFs$\times$Power Spectrum$\times$Moments (blue).
+The likelihood function has been marginalized over $w$ (left panel) and $\Omega_m$ (right panel).
+The parentheses near the descriptor labels refer to the number of principal components.}
+\label{contours3combined}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.5]{Figures/contoursSigma8Om055_cross.eps}
+\end{center}
+\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the combinations of MFs (red), MFs$\times$Power Spectrum (green) and MFs$\times$Power Spectrum$\times$Moments (blue); the likelihood function has been marginalized over $\Omega_m$ and $w$.
+The parentheses near the descriptor label refer to the number of principal components.}
+\label{likelihoodSi8cross}
+\end{figure}
 
@@
 \section{Discussion}
+\label{discussion}
 

### 2014-12-08 Paper_minkowski/Figures/generate.py

@@ -52,7 +52,7 @@ keys.sort()
 ###################Consider these for the combinations###########################################
 #################################################################################################
 
-single = ["power_spectrum","minkowski_0"]
+single = ["power_spectrum","minkowski_0","minkowski_1","minkowski_2","moments"]
 multiple = [("minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2","moments")]
 all_descriptors = single + multiple
 
@@ -109,7 +109,7 @@ def pca(cmd_args):
 	fig,ax = plt.subplots(1,2,figsize=(16,8))
 
 	#Cycle over descriptors to plot PCA eigenvalues
-	for n,descr in enumerate(keys):
+	for n,descr in enumerate(single):
 
 		#Unpickle the emulator
 		an = LikelihoodAnalysis.load(os.path.join(root_dir,"emulators","emulator_{0}--{1:.1f}.p".format(descr,smoothing_scale)))
@@ -141,69 +141,6 @@ def pca(cmd_args):
 
 	#Save figure
 	fig.savefig("pca_components.{0}".format(cmd_args.type))
-
-
-##############################################################################################################################################
-
-def contours(cmd_args):
-
-	#Smoothing scales in arcmin
-	smoothing_scale=1.0
-	levels = [0.684,0.001]
-
-	#Parameters of which we want to compute the confidence estimates
-	parameter_axes = {"Omega_m":0,"w":1,"sigma8":2}
-	cosmo_labels = {"Omega_m":r"$\Omega_m$","w":r"$w$","sigma8":r"$\sigma_8$"}
-
-	#Parse options from configuration file
-	options = ConfigParser.ConfigParser()
-	with open(cmd_args.options_file,"r") as configfile:
-		options.readfp(configfile)
-
-	#Create figure
-	fig,ax = plt.subplots(1,2,figsize=(16,8))
-
-	#Cycle over descriptors
-	for n,descr in enumerate(keys):
-
-		#Instantiate contour plot
-		contour_marg = ContourPlot(fig=fig,ax=ax[0])
-		contour_slice = ContourPlot(fig=fig,ax=ax[1])
-
-		#Load the likelihood
[…]

### 2014-12-08 andrea/convergence_map_analysis/contours.py
fontsize set to 22

@@ -86,16 +86,6 @@ class ContourPlot(object):
 		self.npoints = dict()
 		self.unit = dict()
 
-	def close(self):
-
-		"""
-		Closes the figure
-
-		"""
-
-		plt.close(self.fig)
-	
-
 	def savefig(self,figname):
 
 		"""
@@ -387,16 +377,16 @@ class ContourPlot(object):
 		self.labels()
 		
 
-	def labels(self,contour_label=None):
+	def labels(self,contour_label=None,fontsize=22):
 
 		"""
 		Put the labels on the plot
 
 		"""
 
-		self.ax.set_xlabel(self.parameter_labels[self.remaining_parameters[0]])
-		self.ax.set_ylabel(self.parameter_labels[self.remaining_parameters[1]])
-		self.ax.set_title(self.title_label,fontsize=22)
+		self.ax.set_xlabel(self.parameter_labels[self.remaining_parameters[0]],fontsize=fontsize)
+		self.ax.set_ylabel(self.parameter_labels[self.remaining_parameters[1]],fontsize=fontsize)
+		self.ax.set_title(self.title_label,fontsize=fontsize)
 
 		if contour_label is not None:
 			self.ax.legend(self.ax.proxy,contour_label)

### 2014-12-08 jia/projectB_peakobs.py
projectB update all color in catalog

@@ -19,10 +19,12 @@ from scipy.integrate import quad
 plot_galn_vs_kappa_hist = 0
 list_peaks_cat = 0
 update_mag_i = 0
-do_hist_galn_magcut = 1
+update_mag_all = 1
+do_hist_galn_magcut = 0
 z_lo = 0.6
 z_hi = z_hi = '%s_hi'%(z_lo)
 ########### constants ######################
+obsPK_dir = '/Users/jia/CFHTLenS/obsPK/'
 plot_dir = '/Users/jia/weaklensing/CFHTLenS/plot/obsPK/'
 kmapGen = lambda i, z: WLanalysis.readFits('/Users/jia/CFHTLenS/obsPK/maps/W%i_KS_%s_sigmaG10.fit'%(i, z))
 # This is smoothed galn
@@ -360,3 +362,51 @@ if plot_galn_vs_kappa_hist:
 	savefig(plot_dir+'W%i_galn_peaks_%sarcmin_zlo%s_zhi%s.jpg'%(Wx,arcmin, z_lo, z_hi))
 	#savefig(plot_dir+'galn_peaks_%sarcmin_zlo%s_zhi%s.jpg'%(arcmin, z_lo, z_hi))
 	close()
+	
+if update_mag_all:
+	## 12/08/2014, code to: 
+	## (1) replace Mag_i = -99 items with Mag_y values
+	## (2) add ugriz bands to the catalogue
+	## (3) convert from MegaCam to SDSS AB system
+	color_cat = load(obsPK_dir+'CFHTdata_RA_DEC_ugriyz_2014-12-08T21-58-57.npy')
+	RA, DEC, star_flag, weight, MAG_u, MAG_g, MAG_r, MAG_i, MAG_y, MAG_z = color_cat.T
+	RADEC = RA+1.0j*DEC
+	# merge i and y band, rid of the 99 values
+	idx_badi = where(abs(MAG_i)==99)[0]
+	MAG_iy = MAG_i.copy()
+	MAG_iy[idx_badi]=MAG_y[idx_badi]
+	# test # of bad magnitude in i, y, and iy 
+	#array([sum(abs(arr)==99) for arr in (MAG_i, MAG_y, MAG_iy)])/7522546.0
+	#[963311, 6562757, 3523]
+	#[0.128, 0.872, 0.000468]
+	
+	### convert to SDSS ##############
+	### r_SDSS=r_Mega +0.011 (g_Mega - r_Mega)
[…]

### 2014-12-08 jia/test_chisq_cube_MPI.py

@@ -7,17 +7,19 @@ from scipy import *
 from scipy import interpolate
 import os
 import WLanalysis
-from emcee.utils import MPIPool
 import sys
 
-nn = int(sys.argv[1])#range from 0 to 10 for idx_arr
+#comment out if use on laptop
+#from emcee.utils import MPIPool
+nn = 0#int(sys.argv[1])#range from 0 to 10 for idx_arr
 print nn
+#test_dir = '/home1/02977/jialiu/chisq_cube/'
+
 
 fsky_all = 10.010646820070001
 fsky_pass= 7.6645622253410002
 
-#test_dir = '/Users/jia/Documents/weaklensing/CFHTLenS/emulator/test_ps_bug/'
-test_dir = '/home1/02977/jialiu/chisq_cube/'
+test_dir = '/Users/jia/Documents/weaklensing/CFHTLenS/emulator/test_ps_bug/'
 cosmo_params = genfromtxt(test_dir+'cosmo_params.txt')
 im, iw, s = cosmo_params.T
 
@@ -124,20 +126,20 @@ def plot_heat_map_w (values):
 ###########################################################
 ############ operation ####################################
 ##########################################################
-pool=MPIPool()
-print 'boo'
-idx = idx_arr[nn]
+#pool=MPIPool()
+#print 'boo'
+#idx = idx_arr[nn]
 
-interp_cosmo, cov_mat, cov_inv, ps_CFHT = return_interp_cosmo_for_idx (idx)
-print 'boo2'
-values = [[w, idx, interp_cosmo, cov_inv, ps_CFHT] for w in w_arr]
+#interp_cosmo, cov_mat, cov_inv, ps_CFHT = return_interp_cosmo_for_idx (idx)
+#print 'boo2'
+#values = [[w, idx, interp_cosmo, cov_inv, ps_CFHT] for w in w_arr]
 
-pool.map(plot_heat_map_w, values)
+#pool.map(plot_heat_map_w, values)
 
-cube = array([load('/home1/02977/jialiu/chisq_cube/test/chisqcube_%s_w%s.npy'%(fn_arr[nn], w)) for w in w_arr])
+#cube = array([load('/home1/02977/jialiu/chisq_cube/test/chisqcube_%s_w%s.npy'%(fn_arr[nn], w)) for w in w_arr])
 
[…]

### 2014-12-08 jia/projectB_peakobs.py
projectB update all color in catalog

@@ -6,7 +6,8 @@
 ### 1) find PDF for # gal within 2 arcmin as fcn of peak
 ### hights
 ### 2) the same, as 1) but for random direction
-### 3) future modification needed to include L-M conversion
+### 3) L-M conversion: L_k -> halo mass, using Vale&JPO06 (2014/12)
+### 4) kappa_proj assuming NFW (2014/12)
 
 import numpy as np
 from scipy import *

### 2014-12-09 Paper_minkowski/paper.tex
paper draft in pre-alpha stage

@@
 We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We find that the constraint on $\Sigma_8$ is ...
+We constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level.
 
@@
 where $\mathbf{g} = \pmb{\gamma}/1-\kappa$ is the reduced shear.
-For each simulated galaxy, we assign an intrinsic elliptic- ity by rotating the observed ellipticity for that galaxy by a random angle on the sky, while conserving its magnitude $\vert\mathbf{e}\vert$.
+For each simulated galaxy, we assign an intrinsic ellipticity by rotating the observed ellipticity for that galaxy by a random angle on the sky, while conserving its magnitude $\vert\mathbf{e}\vert$.
 To be consistent with the CFHTLenS analysis, we adopt the weak lensing limit ($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$),hence $\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx \mathbf{e}_s+\pmb{\gamma}$.
@@
 \begin{equation}
+\label{momentestimator}
 \begin{matrix}
@@
 where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function; while the use of this statistic is not a novelty, we want indeed to compare the results we get using MF and LM to the ones already present in the literature.
-A summary of the statistical descriptors we used is presented in Table \ref{desctable}
+A summary of the statistical descriptors we used is presented in Table \ref{desctable}.
 %
@@
 %
+When measuring statistical features on $\kappa$ maps, particular attention must be given to the effect of masked pixels: this does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with exception of the few pixels that are close to the mask boundaries.
+The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier Transforms and hence rely on the value of each pixel on the map.
+Although sophisticated interpolation approaches over the masked regions have been studied (see for example \citep{VplasInterpolation}), for the sake of simplicity we put a value of 0 in each masked pixel, arguing that, given the typical angular size of the masked regions we consider, this will have little effect on the Power Spectrum at the range of multipoles in Table \ref{desctable}.
+
 \subsection{Cosmological parameter inferences}
@@
 \label{pcasection}
-%
 The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data; when the question on the accuracy of the $N\sigma$ contours is raised, particular attention should be given on the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
@@
 
-\section{Results}
-%
-This section describes the results we have obtained in this work, and is organized as follows: we first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
-We then show the cosmological constraints from the CFHTLenS data.
-Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ and hence has a much smaller relative uncertainty.
-We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes; we also show the $\Sigma_8$ marginalized likelihood.
-We finally study the effect of combining different descriptors, in hope that this helps in tightening the constraints.
-A summary with the complete set of results, along with the relevant Figures, is shown in Table \ref{summarytable}.
-
-\subsection{Robustness}
-%
-The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e.
-they are reasonably stable once we consider an large enough number $n$ of Principal Components.
-We show the PCA eigenvalues for the complete set of statistical descriptors in Figure \ref{pcafig}, as well as the contour stability plots in Figure \ref{robustnessfig}.
 %
@@
 %
+
+\section{Results}
+\label{results}
+This section describes the results we have obtained in this work, and is organized as follows: we first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
+We then show the cosmological constraints from the CFHTLenS data.
+Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
+The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ and hence has a much smaller relative uncertainty.
+We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes; we also show the $\Sigma_8$ marginalized likelihood.
+We finally study the effect of combining different descriptors, in hope that this helps in tightening the constraints.
+A summary with the complete set of results, along with the relevant Figures, is shown in Table \ref{summarytable}.
+
+\subsection{Robustness}
+%
+The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e.
+they are reasonably stable once we consider an large enough number $n$ of Principal Components.
+We show the PCA eigenvalues for the complete set of statistical descriptors in Figure \ref{pcafig}, as well as the contour stability plots in Figure \ref{robustnessfig}.
 \subsection{Cosmological constraints}
@@
 \begin{table*}
-\begin{tabular}{c|c|c|c|c||c}
-Parameters & Descriptors & $\theta_G$ & Additional details & Short description & Relevant Figures/Tables \\ \hline \hline
-$(\Omega_m,\sigma_8)$ & PS,$V_0,V_1,V_2$,LM & $1^\prime$ & BAD mask & Stability of contours & Figure \ref{robustnessfig} \\ \hline 
-$(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) & $1^\prime$ & BAD mask &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & Figures \ref{contours3single},\ref{contours3single}b \\ \hline
-$(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $1^\prime$ & BAD mask & contours from CFHTLenS & Figure \ref{contours3singleRep} \\ \hline 
-$\Sigma_8$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $1^\prime$ & BAD mask & $\mathcal{L}(\Sigma_8)$ from CFHTLenS & Figure \ref{likelihoodSi8single} \\ \hline
-$(\Omega_m,\sigma_8)$ & PS(3)$\times V_0(5)\times V_1(20)\times V_2(20)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & Figure \ref{contours3combined} \\ \hline
-$(w,\Sigma_8)$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & Figure \ref{contours3combined}b \\ \hline
-$\Sigma_8$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & $1^\prime$ & BAD mask & \pbox{20cm}{$\mathcal{L}(\Sigma_8)$ from CFHTLenS \\ combining statistics} & Figure \ref{likelihoodSi8cross} \\ \hline
+\begin{tabular}{c|c|c||c}
+Parameters & Descriptors & Short description & Relevant Figures \\ \hline \hline
+$(\Omega_m,\sigma_8)$ & PS,$V_0,V_1,V_2$,LM & Stability of contours & \ref{robustnessfig} \\ \hline 
+$(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
+$(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & contours from CFHTLenS & \ref{contours3singleRep} \\ \hline 
+$\Sigma_8$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $\mathcal{L}(\Sigma_8)$ from CFHTLenS & \ref{likelihoodSi8single} \\ \hline
+$(\Omega_m,\sigma_8)$ & PS(3)$\times V_0(5)\times V_1(20)\times V_2(20)\times$LM(9) & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & \ref{contours3combined} \\ \hline
+$(w,\Sigma_8)$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & \ref{contours3combined}b \\ \hline 
+$\Sigma_8$ & PS(3)$\times V_0(10)\times V_1(10)\times V_2(10)\times$LM(9) & \pbox{20cm}{$\mathcal{L}(\Sigma_8)$ from CFHTLenS \\ combining statistics} & \ref{likelihoodSi8cross} \\ \hline
 \end{tabular}
@@
 We discuss these results in \S~\ref{discussion}.
-
-\subsection{Combining statistics}
-%
-An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in our companion paper \citep{Companion}, where we combine the power spectrum and peak count statistics, as well as in the literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
-The procedure we adopt is the following: suppose we consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor; we compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ to keep in order for the constraints to be stable.
-We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector: this procedure allows us to take the cross covariance between different descriptors.
-We show in Figure \ref{contours3combined} the combined CFHTLenS constraints on the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
-We discuss our findings in the next section.
 
@@
 \begin{center}
-\includegraphics[scale=0.5]{Figures/contoursSigma8Om055_cross.eps}
+\includegraphics[scale=0.45]{Figures/contoursSigma8Om055_cross.eps}
 \end{center}
@@
 
+\subsection{Combining statistics}
+An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in our companion paper \citep{Companion}, where we combine the power spectrum and peak count statistics, as well as in the literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
+The procedure we adopt is the following: suppose we consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor; we compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ to keep in order for the constraints to be stable.
+We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector: this procedure allows us to take the cross covariance between different descriptors.
+We show in Figure \ref{contours3combined} the combined CFHTLenS constraints on the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
+We discuss our findings in the next section.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+In this section we discuss the results outlined in section \S~\ref{results}, with particular focus on the constraints on cosmology.
+As pointed out in \S~\ref{pcasection}, the choice of the number of bins, $N_b$, is an important point on which one should be careful; in order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our feature spaces.
+In the left panel of Figure \ref{pcafig} we see that the PCA eigenvalues for our descriptors decrease about 4 orders of magnitude from $n=1$ to $n=3$, and looking at the right panel we see that we capture more than 99\% of the feature variance even if we cut the PCA projection to the first 3 components.
+This does not mean that all the cosmological information is captured by the first 3 PCA components, and this is why we make a stability check by plotting the $1\sigma$ contour sizes as a function of $n$ in Figure \ref{robustnessfig}.
+Looking at the plot we can observe that, while the first 3 components capture essentially all the information contained in the Power Spectrum, this is not true for the remaining set of statistics.
+In particular we find that at least 5 components are necessary for $V_0$, and at least 20 components for $V_1,V_2$, in order for the $(\Omega_m,\sigma_8)$ contours to be stable at a $\sim$5\% level.
+All the 9 components are necessary for the Moments contours to be stable.
+Matters are slightly different when we study the $(w,\Sigma_8)$ constraints: in this case we find that the optimal choice for the three MFs, $(V_0,V_1,V_2)$, is $n=10$, while the Power Spectrum and Moments components can be kept fixed, at respectively 3 and 9.
+
+We now discuss the main scientific findings of this work.
+In Figure \ref{contours3single} we show the $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data: we can see that the MFs constraints are heavily biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
+We believe that this is due to uncorrected systematics in the CFHTLenS data, since when we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
+We also see that the moments give the best constraint on these model parameters.
+The bias in the $(\Omega_m,\sigma_8)$ constraints is only worse by the cosmological degeneracy of these parameters; to mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
+In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but on the other hand it does a good job in nailing the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
+
+We next studied whether the combination of different statistical descriptors can help in tightening the cosmological constraints; we show the effects of some of these combinations in Figures \ref{contours3combined} and \ref{likelihoodSi8cross}.
+The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, unfortunately this does not help in reducing the inherent parameter bias.
+In the right panel of Figure \ref{contours3combined} we can see that even with these statistics combinations, $w$ remains essentially unconstrained.
+Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained with either the MFs alone, without the need of combining different descriptors.
+
+\newpage 
 %%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusions}
+
+In this final section we summarize the main conclusions of this work:
+\begin{itemize}
+\item Although weak lensing surveys are a promising technique to constrain the DE equation of state $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.
+\item When studying the cosmological information contained in the CFHTLenS data, one must pay special attention to the correction of residual systematics; while it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected for to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
+\item The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level. 
+\end{itemize}
+
+Possible future developments of this work include simulating higher dimensional parameter spaces (possibly including varying Hubble parameter $H_0$ and the running of the DE equation of state $w_1$), and combining constraints from different cosmological probes (data from Planck for example), that can help in breaking the $\Omega_m,\sigma_8$ degeneracy.
 

### 2014-12-09 Paper_minkowski/Figures/generate.py

@@ -221,7 +221,7 @@ def robustness(cmd_args,parameter_axes={"Omega_m":0,"w":1,"sigma8":2},cosmo_labe
 			else:
 
 				#Plot the likelihood
-				p,l = contour.marginal(select)
+				p,l,pmax = contour.marginal(select)
 				ax_flat[d].plot(p,l,color=brew_colors_diverging[n],label=r"$n={0}$".format(n_components))
 
 		#Labels
@@ -341,7 +341,8 @@ def contours_combine(cmd_args,descriptors_in_plot=multiple,parameter_axes={"Omeg
 
 		else:
 			
-			p,l = contour.marginal(select)
+			p,l,pmax,p0 = contour.marginal(select,levels=[0.684])
+			print(pmax,p0)
 			ax.plot(p,l,color=brew_colors[n],label=contour_labels[-1])		
 			
 

### 2014-12-16 Paper_minkowski/paper.tex
changed author order
implemented part of zoltan's comments

@@
 
+\author{Morgan May}
+\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}
+
 \author{Lam Hui}
@@
 \affiliation{Astrophysics and Cosmology Research Unit, University of KwaZulu-Natal, Westville, Durban 4000, South Africa}
-
-\author{Morgan May}
-\affiliation{Physics Department, Brookhaven National Laboratory, Upton, NY 11973, USA}
 
@@
 We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level.
+We find that dimensionality reduction techniques such as Principal Component Analysis help in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
+Using our full set of statistical descriptors, we constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
+We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a marginal bias, the Moments provide a tight unbiased bound on the former parameters.
 
 \end{abstract}
+
+%AP: Re-worded the abstract
 
@@
 The CFHTLenS survey covers four sky patches of 64,23,44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of the creation of a galaxy catalogue using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements with \textit{lensfit} \citep{cfht1,cfht2}.
-The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF).
+The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF); additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using the skewness as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
 We apply the following cuts to the galaxy catalogue: mask$<1$, redshift $0.2 < z < 1.3$, fitclass = 0 (which requires the object to be a galaxy) and weight $w>0$ (with larger $w$ indicating smaller shear measurement uncertainty).
 Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ residual sky coverage, and average number density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
-The CFHTLenS galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of eack galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
+The CFHTLenS galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
 Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps; these square subfield maps are pixelized according to a Gaussian gridding procedure
+
+%AP: added references and fixed typo. Is there a problem with the galaxy density I reported? (I took it from Jia's paper) 
 \begin{equation}
@@
 We first create grided maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
-We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more throughout description of our data reduction procedure, we refer the reader to our companion paper \citep{Companion}.
+We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more in--depth description of our data reduction procedure, we refer the reader to our companion paper \citep{Companion}.
+
+%AP: throughout --> in--depth
 
@@
 We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping fixed the other relevant parameters to $(h,\Omega_b,n_s)$ to their fiducial values (0.7,0.046,0.96).
-We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is necessary, given our limited computing resources: a regular parameter grid with the same average spacing between models would require in fact a prohibitively large number of samples.
 We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
@@
 Following \citep{coyote2}, we choose our optimal design as the minimum of the cost function
+
+%AP: Justified irregular parameter sampling
 
@@
 The goal of this paragraph is to give an outline of our simulation pipeline; the fluctuations in the dark matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
-The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,w(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $w$ (not to be confused with the weight factor in \S\ref{cfhtdatareduction}) and two transverse coordinates $\mathbf{x}_\perp=w\pmb{\beta}$ using the flat sky approximation.
+The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
 Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
@@
 \label{raytrajectory}
-\frac{d^2\mathbf{x}(w)}{dw^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(w),w)
+\frac{d^2\mathbf{x}(\chi)}{d\chi^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(\chi),\chi)
 \end{equation}
 %
-where $\mathbf{x}(w)$ is the trajectory of a single light ray, which we visualize schematically in Figure \ref{rayscheme}. 
-%
-\begin{figure*}
-\begin{center}
-\includegraphics[scale=0.4]{Figures/rayscheme.eps}
-\end{center}
-\caption{Schematics of ray tracing with the lensing potential boosted by a factor of 50 for visualization purposes}
-\label{rayscheme}
-\end{figure*}
-%
+where $\mathbf{x}(\chi)$ is the trajectory of a single light ray.
 Suppose that a light ray reaches the observer at an angular position $\pmb{\theta}$ on the sky: we want to know where this light ray originated, knowing it comes from a redshift $z_s$.
 To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$; for the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
-Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(w_s;\pmb{\theta}) = \partial \pmb{\beta}(w_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
+Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(\chi_s;\pmb{\theta}) = \partial \pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
 %
 \begin{equation}
-A(w_s;\pmb{\theta}) = (1-\kappa(w_s;\pmb{\theta}))\pmb{I} - \gamma^1(w_s;\pmb{\theta})\sigma^3 - \gamma^2(w_s;\pmb{\theta})\sigma^1
+A(\chi_s;\pmb{\theta}) = (1-\kappa(\chi_s;\pmb{\theta}))\pmb{I} - \gamma^1(\chi_s;\pmb{\theta})\sigma^3 - \gamma^2(\chi_s;\pmb{\theta})\sigma^1
 \end{equation}  
@@
 To be consistent with the CFHTLenS analysis, we adopt the weak lensing limit ($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$),hence $\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx \mathbf{e}_s+\pmb{\gamma}$.
-We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$; like for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
+We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$.
+We note that the observed ellipticity for a particular galaxy already contains information from the lensing from Large Scale Structure, but the random angle rotation makes this contribution second order in $\kappa$: consistently with the weak lensing approximation, the lensing singal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
+Like for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
 These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
+
+%AP: changed comoving distance symbol to chi; knocked out the ray tracing figure; clarified the signal double counting issue
 
@@
 Such perturbative series, however, have been shown not to converge in \citep{Petri2013} unless the weak lensing fields are smoothed with windows of size comparable to $\sim 15^\prime$.
-Because of this, throughout this work, we treat MF and LM as independent statistical descriptors.
+Because of this, throughout this work, we treat MF and LM as separate statistical descriptors.
 In addition to these two descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
@@
 \end{equation}  
+%
+%AP: independent --> separate
 %
@@
 When measuring statistical features on $\kappa$ maps, particular attention must be given to the effect of masked pixels: this does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with exception of the few pixels that are close to the mask boundaries.
+Masking effects on Minkowski Functionals constraints with CFHTLenS have been studies extensively by \citep{CFHTMasato}.
 The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier Transforms and hence rely on the value of each pixel on the map.
 Although sophisticated interpolation approaches over the masked regions have been studied (see for example \citep{VplasInterpolation}), for the sake of simplicity we put a value of 0 in each masked pixel, arguing that, given the typical angular size of the masked regions we consider, this will have little effect on the Power Spectrum at the range of multipoles in Table \ref{desctable}.
+We nevertheless believe that the way we deal with masked sky regions is very robust, because we apply the same masks to our simulations.
+
+%AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki
 
@@
 The constant coefficients $\lambda_s$ can be determined imposing the $N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which enforce the fact that the interpolation should be exact at the simulated points.
-The interpolation computations are conveniently performed using the Scipy library \citep{scipy}
+The interpolation computations are conveniently performed using the Scipy library \citep{scipy}.
+We studied the accuracy of emulator, built with the CFHTemu1 simulations, by interpolating the convergence features to the fiducial parameter setting $(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to the one expected from the CFHTcov simulations.
+Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator is at least 10\% accurate for the lower multipoles, and this accuracy can even be comparable with 1\% for the higher multipoles.
+The Minkowski Functionals emulator has a good, $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates with numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next paragraph.
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.45]{Figures/emulator_accuracy.eps}
+\end{center}
+\caption{Accuracy of the emulator based on the CFHTemu1 simulations: we show the difference between the interpolated feature at the fiducial parameter setting and the expected feature from the CFHTcov simulations, in units of the standard deviation in each bin $i$ (determined from the diagonal elements of the CFHTcov covariance matrix).
+We show the accuracy results for the Power Spectrum (red) and Minkowski Functionals $V_0$ (green), $V_1$ (blue) and $V_2$ (black).}
+\label{emulatorAccuracy}
+\end{figure}
 
@@
 It is known that the choice of the number of bins, $N_b$, can have a non--negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
-Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we know that the effective dimensionality of the feature space should be close to the number of parameters that are effectively varied (see \citep{coyote2}), 3 in our case; because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ that we choose originally.
+Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular feature) is contained in a fixed limited number of linear combinations of its binning.
+In the framework adopted by \citep{coyote2}, for example, the authors find that the majority of the cosmological information in the matter Power Spectrum is contained in only 5 selected linear combinations of the multipoles.
+Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ that we choose originally.
 In order to compute the Principal Components of our feature space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
-Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$ subtracting the mean in each bin, and normalizing it by its variance; next we proceed in a SVD decomposition of $\mathbf{\tilde{M}}$
+Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$, defined by subtracting the mean in each bin, and normalizing it by its variance; next we proceed in a SVD decomposition of $\mathbf{\tilde{M}}$
 \begin{equation}
@@
 the ones that contain the relevant cosmological information) are the ones that correspond to the biggest eigenvalues $\Sigma^2_{i}$, with the smallest eigenvalues corresponding to noisy patterns in the model, due to numerical inaccuracies in the simulation pipeline.
-We expect the number of relevant components to be not too far from 3; using the fact that different Principal Components are orthogonal, we perform a PCA projection on our feature space by whitening the features and computing the dot product with the principal components, keeping only the first $n$ components
+We expect our constraints to be stable with respect to the number of components, once enough components have been included.
+Using the fact that different Principal Components are orthogonal, we perform a PCA projection on our feature space by whitening the features and computing the dot product with the principal components, keeping only the first $n$ components
 \begin{equation}
@@
 where we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows.
-The dimensional reduction comes from the fact that physical arguments justify a choice of $n< N_{b}$.
-We want to stress the fact that, because we vary only 3 parameters in the CFHTemu1 simulations, we expect our feature space to be a 3--dimensional manifold embedded in a $N_b$ dimensional space: the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
+The dimensionality reduction comes from the fact that we expect most of the cosmological information to be contained in a number of components $n<N_{b}$.
+Looking at the dimensionality issue from a more geometrical perspective, we expect our feature space to be a 3 dimensional manifold embedded in a $N_b$--dimensional space.
+The dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
 As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds: when curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
-We are allowed some flexibility on this flatness assumption by allowing the number of principal components to be bigger than 3.
+We are allowed flexibility on this flatness assumption because we allow the number of principal components to be bigger than 3.
+
+%AP: Addressed dimensionality issues
 
@@
 We then show the cosmological constraints from the CFHTLenS data.
-Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ and hence has a much smaller relative uncertainty.
+Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8(\alpha)=\sigma_8(\Omega_m/0.27)^\alpha$.
+The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8(\alpha)$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ for a suitable choice of $\alpha$, and hence has a much smaller relative uncertainty.
+We can derive this optimal value of $\alpha$ from the full three dimensional likelihood $\mathcal{L}(\Omega_m,w,\sigma_8)$, from which we can compute the expectation values
+\begin{equation}
+\mathds{E}(\alpha) = \langle\Sigma_8(\alpha)\rangle \,\,\, ; \,\,\, \mathds{V}(\alpha) = \langle(\Sigma_8(\alpha)-\mathds{E}(\alpha))^2\rangle
+\end{equation}
+%
+and minimizing the ratio $\mathds{E}/\sqrt{\mathds{V}}$ with respect to $\alpha$.
+This procedure yields a value $\alpha\approx0.55$ for the statistical descriptors that we consider, consistent to what can be found in the literature.
 We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes; we also show the $\Sigma_8$ marginalized likelihood.
@@
 A summary with the complete set of results, along with the relevant Figures, is shown in Table \ref{summarytable}.
+
+%AP: Justified value of alpha=0.55
 
@@
 they are reasonably stable once we consider an large enough number $n$ of Principal Components.
-We show the PCA eigenvalues for the complete set of statistical descriptors in Figure \ref{pcafig}, as well as the contour stability plots in Figure \ref{robustnessfig}.
+Figure \ref{pcafig} shows the PCA eigenvalues that result from the SVD decomposition of our feature spaces, as well as the cumulative sum of these eigenvalues, normalized to 1.
+Figure \ref{robustnessfig} shows the dependence of the $(\Omega_m,\sigma_8)$ constraints on the number of principal components $n$, and clearly indicates that we only need a limited number of components in order to capture the cosmological information contained in our descriptors.
+The number of components to keep, however, depends on the particular descriptor considered.
+
+%AP: Added inline description of the figures
+
 \subsection{Cosmological constraints}
@@
 Additionally we show the $\Sigma_8$ likelihood function (marginalized over $\Omega_m$ and $w$) in Figure \ref{likelihoodSi8single}.
+We discuss these results in \S~\ref{discussion}.
 
@@
 %
-We discuss these results in \S~\ref{discussion}.
 

### 2014-12-16 Paper_minkowski/Figures/generate.py

@@ -1,7 +1,9 @@
 #!/usr/bin/env python
+from __future__ import division,print_function
 
 import sys,os,argparse,ConfigParser
 
+from lenstools import Ensemble
 from lenstools.constraints import LikelihoodAnalysis
 from lenstools.simulations import Design
 
@@ -111,6 +113,33 @@ def design(cmd_args):
 
 	#Save the figure 
 	fig.savefig("design.{0}".format(cmd_args.type))
+
+################################################################################################################################################
+
+def emulatorAccuracy(cmd_args,descriptors_in_plot=single[:-1]):
+
+	#Smoothing scale
+	smoothing_scale = 1.0
+
+	#Ready to plot
+	fig,ax = plt.subplots(figsize=(8,8))
+	for n,descr in enumerate(descriptors_in_plot):
+
+		predicted = np.load(os.path.join(root_dir,"troubleshoot","fiducial_from_interpolator_{0}--{1:.1f}.npy".format(descr,smoothing_scale)))
+		measured = np.load(os.path.join(root_dir,"troubleshoot","fiducial_{0}--{1:.1f}.npy".format(descr,smoothing_scale)))
+		covariance = np.load(os.path.join(root_dir,"troubleshoot","covariance_{0}--{1:.1f}.npy".format(descr,smoothing_scale)))
+
+		ax.plot(np.abs(measured-predicted)/np.sqrt(covariance.diagonal()),color=brew_colors[n],label=descriptors[descr])
+
+	#Plot labels
+	ax.set_xlabel(r"$i$",fontsize=22)
+	ax.set_ylabel(r"$(E-M)/\sqrt{C_{MM}}$")
+	ax.set_yscale("log")
+	ax.legend(loc="lower left")
+
+	#Save the figure
+	fig.savefig("emulator_accuracy.{0}".format(cmd_args.type))
+
 
 
 ##############################################################################################################################################
@@ -567,7 +596,9 @@ def Si8_likelihood_moments(cmd_args):
 
 
 figure_method = dict()
-figure_method["2"] = design
+
+figure_method["1"] = design
+figure_method["2"] = emulatorAccuracy
 figure_method["3"] = pca
 figure_method["4"] = robustness
 figure_method["4s"] = robustness_1d

### 2014-12-17 Paper_minkowski/paper.tex
update paper and figures

@@
 Using our full set of statistical descriptors, we constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a marginal bias, the Moments provide a tight unbiased bound on the former parameters.
+We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a marginal bias, the Moments provide a tight unbiased bound on the former parameters, with the main contribution coming from quartic moments of gradients.
 
@@
 \begin{equation}
-\frac{1}{N-1}\mathbf{\tilde{M}^T\tilde{M}} = \mathbf{V}\Sigma^2\mathbf{V}^T
+\frac{1}{N-1}\mathbf{\tilde{M}}^T\mathbf{\tilde{M}} = \mathbf{V}\Sigma^2\mathbf{V}^T
 \end{equation} 
@@
 \begin{center}
+\includegraphics[scale=0.45]{Figures/contours_momentsOmega_m-sigma8.eps}
+\end{center}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments; we start by considering only the combination of the quadratic moments and the skewness, and add the remaining one by one.
+The colors are shown in the legend.}
+\label{contoursMoments}
+\end{figure}
+
+\begin{figure}
+\begin{center}
 \includegraphics[scale=0.45]{Figures/contoursw-Sigma8Om055_single.eps}
@@
 $(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
+$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments}  & \ref{contoursMoments} \\ \hline
 $(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & contours from CFHTLenS & \ref{contours3singleRep} \\ \hline 
@@
 \end{center}
-\caption{Combined $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ (left panel) and $(w,\Sigma_8)$ (right panel) doublets, using the MFs (red), MFs$\times$Power Spectrum (green) and MFs$\times$Power Spectrum$\times$Moments (blue).
+\caption{Combined $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ (left panel) and $(w,\Sigma_8)$ (right panel) doublets, using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange).
 The likelihood function has been marginalized over $w$ (left panel) and $\Omega_m$ (right panel).
@@
 \end{center}
-\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the combinations of MFs (red), MFs$\times$Power Spectrum (green) and MFs$\times$Power Spectrum$\times$Moments (blue); the likelihood function has been marginalized over $\Omega_m$ and $w$.
+\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange); the likelihood function has been marginalized over $\Omega_m$ and $w$.
 The parentheses near the descriptor label refer to the number of principal components.}
@@
 We discuss our findings in the next section.
+
+%AP: Added the statistics combinations Zoltan suggested
 
@@
 We believe that this is due to uncorrected systematics in the CFHTLenS data, since when we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
-We also see that the moments give the best constraint on these model parameters.
-The bias in the $(\Omega_m,\sigma_8)$ constraints is only worse by the cosmological degeneracy of these parameters; to mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
+It is important to say, however, that the mock observation to which the right panel of Figure \ref{contours3single} refers, was build with the mean of $R=1000$ realizations of the CFHTcov simulations.
+We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner,even if the likelihood of this happening is very small ($\lesssim1\%$).
+We also see that the moments give the best constraint on these model parameters; in order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
+Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higer order moments to the feature set: because we are focusing on 3 parameters, we start by considering the set of the three moments $(\sigma_0^2,\sigma_1^2,S_0)$ and then we add the remaining 6 one by one.
+We see that the biggest improvement on the parameter bounds comes from including quartic moments of gradients (i.e.
+$K_i$ with $i\ge1$) in the feature set.
+This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding the skewness to quadratic statistics, since the main improvement comes from higer moments of $\kappa$ derivatives.
+This result agrees with what \citep{BhuvKurtosis} in their previous work, in which they state that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
+
+The bias in the $(\Omega_m,\sigma_8)$ constraints is made worse by the cosmological degeneracy of these parameters; to mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
 In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but on the other hand it does a good job in nailing the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
+Our results are in accordance with what already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
+In accordance with the same work, we found that the LM statistic is the less biased one and hence is the ideal tool to detect cosmological information in CFHTLenS.
 
@@
 \begin{itemize}
+\item When constraining the $(\Omega_m,\sigma_8)$ doublet with the CFHTLenS survey, we find that the Moments of the $\kappa$ field provide the tighest constraint on the former parameters; this constraint has also the advantage of being unbiased.
+We found that the biggest improvement on these parameter bounds is achieved when we include the quartic moments of gradients in the feature set.
 \item Although weak lensing surveys are a promising technique to constrain the DE equation of state $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.

### 2014-12-17 Paper_minkowski/Figures/generate.py

@@ -30,7 +30,7 @@ descriptors["minkowski_0"]=r"$V_0$"
 descriptors["minkowski_1"]=r"$V_1$"
 descriptors["minkowski_2"]=r"$V_2$"
 descriptors["moments"]=r"$\mathrm{Moments}$"
-descriptors["moments_q12_s1"]=r"$\sigma_0^2\times\sigma_1^2\times S_0$"
+descriptors["moments_q12_s1"]=r"$\sigma_0^2$ $\times$ $\sigma_1^2$ $\times$ $S_0$"
 descriptors["moments_q12_s12"]=r"$\mathrm{Add}$ $S_1$"
 descriptors["moments_q12_s123"]=r"$\mathrm{Add}$ $S_2$"
 descriptors["moments_q12_s123_k1"]=r"$\mathrm{Add}$ $K_0$"
@@ -41,9 +41,9 @@ descriptors["moments_q12_s123_k1234"]=r"$\mathrm{Add}$ $K_3$"
 #Number of principal components
 num_components = dict()
 num_components["power_spectrum"] = 3
-num_components["minkowski_0"] = 10
-num_components["minkowski_1"] = 10
-num_components["minkowski_2"] = 10
+num_components["minkowski_0"] = 5
+num_components["minkowski_1"] = 20
+num_components["minkowski_2"] = 20
 num_components["moments"] = 9 
 
 #Smoothing scales
@@ -69,7 +69,7 @@ keys.sort()
 #################################################################################################
 
 single = ["power_spectrum","minkowski_0","minkowski_1","minkowski_2","moments"]
-multiple = [("minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2","moments")]
+multiple = [("power_spectrum","moments"),("minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2"),("power_spectrum","minkowski_0","minkowski_1","minkowski_2","moments")]
 all_descriptors = single + multiple
 moment_list = ["moments_q12_s1","moments_q12_s12","moments_q12_s123","moments_q12_s123_k1","moments_q12_s123_k12","moments_q12_s123_k123","moments_q12_s123_k1234"]
 
[…]

### 2014-12-17 andrea/convergence_map_analysis/contours.py
tunable legend sizes in contours

@@ -390,7 +390,7 @@ class ContourPlot(object):
 		self.labels()
 		
 
-	def labels(self,contour_label=None,fontsize=22):
+	def labels(self,contour_label=None,fontsize=22,**kwargs):
 
 		"""
 		Put the labels on the plot
@@ -402,7 +402,7 @@ class ContourPlot(object):
 		self.ax.set_title(self.title_label,fontsize=fontsize)
 
 		if contour_label is not None:
-			self.ax.legend(self.ax.proxy,contour_label)
+			self.ax.legend(self.ax.proxy,contour_label,**kwargs)
 
 	def point(self,coordinate_x,coordinate_y,color="green",marker="o"):
 

### 2014-12-18 Paper_minkowski/paper.tex
updated paper for round 2

@@
 %
-where the smoothing scale $\theta_G$ has been fixed to 1.0\,arcmin; the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
+where the smoothing scale $\theta_G$ has been fixed to 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests); the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
 \begin{equation}
@@
 
+%AP: what kind of quantitative test should I implement?
+We can use Anderson-Darling to check how gaussian the pdf in each bin is, but this doesn't tell anything on the bin correlations.
+Also which bins shall I choose?
+There is a problem if the likelihood is non-Gaussian: we don't know what to do.
+Basically this is the only functional form with which we can model the PDF and bin correlations analytically, and compute the parameter likelihood semi-analytically, otherwise we need to dig into more sophisticated non--parametric methods in which I am not that proficient yet.
+
 \begin{equation}
@@
 %
-We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figure \ref{contours3single} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
+We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figures \ref{contours3single},\ref{contoursMoments} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
 Additionally we show the $\Sigma_8$ likelihood function (marginalized over $\Omega_m$ and $w$) in Figure \ref{likelihoodSi8single}.
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments; we start by considering only the combination of the quadratic moments and the skewness, and add the remaining one by one.
-The colors are shown in the legend.}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments, with different colors corresponding to different moment combinations: we show the results obtained using the one--point moments $\sigma_0^2,S_0,K_0$ (black) and using the one--point moments combined at $(1.0,3.0,5.8)$\,arcmin smoothing (gray scale).
+We also show the improvements that we get when we add the quadratic (green), cubic (red) and quartic (moments) of gradients.
+The yellow contour refers to the whole set of 9 Moments}
 \label{contoursMoments}
@@
 $(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
-$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments}  & \ref{contoursMoments} \\ \hline
+$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments \\ combined ad different $\theta_G$}  & \ref{contoursMoments} \\ \hline
 $(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & contours from CFHTLenS & \ref{contours3singleRep} \\ \hline 
@@
 We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner,even if the likelihood of this happening is very small ($\lesssim1\%$).
-We also see that the moments give the best constraint on these model parameters; in order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
-Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higer order moments to the feature set: because we are focusing on 3 parameters, we start by considering the set of the three moments $(\sigma_0^2,\sigma_1^2,S_0)$ and then we add the remaining 6 one by one.
+
+We observe that the Moments give the best constraint on $(\Omega_m,\sigma_8)$; in order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
+Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higer order moments to the feature set: because we are focusing on 3 parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then we add the remaining six moments of gradients one by one, starting from the quadratic ones.
 We see that the biggest improvement on the parameter bounds comes from including quartic moments of gradients (i.e.
@@
 This result agrees with what \citep{BhuvKurtosis} in their previous work, in which they state that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
+We also observe that the improvement we obtain combining the one--point moments at different smoothing scales $\theta_G$, is not as good as the one that we get considering the moments of gradients.
 
@@
 In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but on the other hand it does a good job in nailing the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
-Our results are in accordance with what already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
+The numerical value that we find for $\Sigma_8$ agrees with the one previously published by the CFHTLenS collaboration in \citep{CFHTKilbinger}.
+Regarding the parameter biases, our results are in accordance with what already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
 In accordance with the same work, we found that the LM statistic is the less biased one and hence is the ideal tool to detect cosmological information in CFHTLenS.
@@
 \item When constraining the $(\Omega_m,\sigma_8)$ doublet with the CFHTLenS survey, we find that the Moments of the $\kappa$ field provide the tighest constraint on the former parameters; this constraint has also the advantage of being unbiased.
-We found that the biggest improvement on these parameter bounds is achieved when we include the quartic moments of gradients in the feature set.
+We found that the biggest improvement on these parameter bounds is achieved when we include the quartic moments of gradients in the feature set; this improvement cannot be obtained by combining one--point moments at different smoothing scales
 \item Although weak lensing surveys are a promising technique to constrain the DE equation of state $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.
 \item When studying the cosmological information contained in the CFHTLenS data, one must pay special attention to the correction of residual systematics; while it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected for to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
-\item The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level. 
+\item The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
+Some tensions with Planck \citep{PlanckXVI2013} still remain.
 \end{itemize}

### 2014-12-18 Paper_minkowski/Figures/generate.py

@@ -2,6 +2,7 @@
 from __future__ import division,print_function
 
 import sys,os,argparse,ConfigParser
+import ast
 
 from lenstools import Ensemble
 from lenstools.constraints import LikelihoodAnalysis
@@ -22,6 +23,7 @@ design_points = "/Users/andreapetri/Documents/Cosmology_software/LensTools/lenst
 brew_colors = ["red","green","blue","black","orange","magenta","cyan"]
 brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
 brew_colors_diverging = ["#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#ffff99","#b15928"]
+brew_colors_moments = ["black","#bdbdbd","#636363","green","#e34a33","#b30000","#74a9cf","#2b8cbe","yellow"]
 
 #Descriptor list
 descriptors=dict()
@@ -30,13 +32,16 @@ descriptors["minkowski_0"]=r"$V_0$"
 descriptors["minkowski_1"]=r"$V_1$"
 descriptors["minkowski_2"]=r"$V_2$"
 descriptors["moments"]=r"$\mathrm{Moments}$"
-descriptors["moments_q12_s1"]=r"$\sigma_0^2$ $\times$ $\sigma_1^2$ $\times$ $S_0$"
-descriptors["moments_q12_s12"]=r"$\mathrm{Add}$ $S_1$"
-descriptors["moments_q12_s123"]=r"$\mathrm{Add}$ $S_2$"
-descriptors["moments_q12_s123_k1"]=r"$\mathrm{Add}$ $K_0$"
-descriptors["moments_q12_s123_k12"]=r"$\mathrm{Add}$ $K_1$"
-descriptors["moments_q12_s123_k123"]=r"$\mathrm{Add}$ $K_2$"
-descriptors["moments_q12_s123_k1234"]=r"$\mathrm{Add}$ $K_3$"
+descriptors["moments_q1_s1_k1"]=r"$\sigma_{0}^2,S_0,K_0$"
+descriptors["moments_q12_s1_k1"]=r"$\sigma_{0,1}^2,S_0,K_0$"
[…]

### 2014-12-18 jia/junk_projectB_peakobs.py
cluster counts plotting

@@ -248,3 +248,8 @@ cat_gen_junk = lambda Wx: np.load('/Users/jia/CFHTLenS/obsPK/W%s_cat_z0213_ra_de
 
 		#savefig(obsPK_dir+'plot/sample2_contribute_vs_Mhalo_%s.jpg'%(i))
 		#close()
+		
+noise_arr = np.load (obsPK_dir+'Halos_IDziM_DistContri_k4_kB_zcut%s_R%s_noise%s.npy'%(zcut, R, True))
+noiseIDs, noisez_arr, noiseMAGi_arr, noiseMhalo_arr, noised_arr, \
+	noisecontri_arr, noisekappaP_arr, noisekappaConv_arr = \
+	noise_arr[:, idxcuts(noise_arr)]

### 2014-12-18 jia/projectB_peakobs.py

@@ -14,21 +14,23 @@ from scipy import *
 from pylab import *
 import os
 import WLanalysis
-from scipy import interpolate
+from scipy import interpolate,stats
 from scipy.integrate import quad
 import scipy.optimize as op
 import sys
 
 ######## for stampede #####
-from emcee.utils import MPIPool
-obsPK_dir = '/home1/02977/jialiu/obsPK/'
+#from emcee.utils import MPIPool
+#obsPK_dir = '/home1/02977/jialiu/obsPK/'
 
 ######## for laptop #####
-#obsPK_dir = '/Users/jia/CFHTLenS/obsPK/'
-#plot_dir = obsPK_dir+'plot/'
+obsPK_dir = '/Users/jia/CFHTLenS/obsPK/'
+plot_dir = obsPK_dir+'plot/'
 
+cluster_counts = 0
+halo_plots = 1
 list_peaks_cat = 0 #! generate a list of galaxies for all peaks
-project_mass = 1
+project_mass = 0
 #junk routines below
 update_mag_i = 0
 plot_galn_vs_kappa_hist = 0
@@ -374,17 +376,146 @@ def MassProj (gridofdata, zcut, R = 3.0, sigmaG=1.0):
 ################################################
 ################ operations ####################
 ################################################
+zcenters = arange(0.225, 1.3, 0.05)#center of z bins from CFHT
+zbins = linspace(0.2,1.3,23)#edges
+zPDF = array([ 0.45445094,  0.80881598,  0.93470199,  0.76456038,  1.10499822,
+        0.8803627 ,  1.1195881 ,  1.50167501,  1.48711827,  1.60911659,
+        1.47213078,  1.31645756,  1.2022788 ,  1.76004064,  1.00095837,
+        1.08889524,  0.97712418,  0.91611398,  0.57378752,  0.31843705,
+        0.53337544,  0.17501226])# = dP/dz, normed in between z=0.2-1.3
 
+zPDF_normed = lambda zcut: zPDF[:where(zcenters<=zcut)[0][-1]+1]/sum(zPDF[:where(zcenters<=zcut)[0][-1]+1])
+
+	
+def Nhalo_vs_kappa (icontri_arr, iz_arr, izPDF):#iMhalo_arr
[…]

### 2014-12-22 Paper_minkowski/paper.tex
updated with round 2 edits

@@
 
-\title{CFHTLenS Weak Lensing Emulator and Cosmological Constraints from the Minkowski Functionals and Moments}
+\title{Moments and Minkowski Functionals constrain cosmology: applying a weak lensing emulator to CFHTLenS data}
 
@@
 \begin{abstract}
-Weak gravitational lensing has been proposed as an interesting probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; the fact that typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss some of the cosmological information contained in survey data.
+Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; the fact that typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss some of the cosmological information contained in survey data.
 In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ from weak lensing Minkowski Functionals and Moments, using the publicly available data from the 154\,deg$^2$ CFHTLenS survey.
-We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise read from the CFHTLenS catalogs.
+We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise in the CFHTLenS catalogs.
 We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
@@
 %
-The CFHTLenS survey covers four sky patches of 64,23,44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of the creation of a galaxy catalogue using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements with \textit{lensfit} \citep{cfht1,cfht2}.
+The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of a galaxy catalogue created using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements using \textit{lensfit} \citep{cfht1,cfht2}.
 The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF); additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using the skewness as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
@@
 Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ residual sky coverage, and average number density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
+The catalogue is further reduced by $\sim25\%$ when one leaves out galaxies with non--negligible star--galaxy correlations.
+These spurious correlations are due to imperfect PSF removal, and do not contain cosmological signal.
 The CFHTLenS galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
@@
 We first create grided maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
-We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more in--depth description of our data reduction procedure, we refer the reader to our companion paper \citep{Companion}.
+We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more in--depth description of our data reduction procedure, we refer the reader to \citep{Companion}.
 
@@
 \subsection{Simulation design}
-In this paragraph we give a description of the method we used to sample the parameter space in our simulation effort.
+In this section we give a description of the method we used to sample the parameter space in our simulation effort.
 We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping fixed the other relevant parameters to $(h,\Omega_b,n_s)$ to their fiducial values (0.7,0.046,0.96).
-We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is necessary, given our limited computing resources: a regular parameter grid with the same average spacing between models would require in fact a prohibitively large number of samples.
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require in fact a prohibitively large number of samples.
 We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
@@
 \label{raysim}
-The goal of this paragraph is to give an outline of our simulation pipeline; the fluctuations in the dark matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
-The fluctuations in the dark matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
+The goal of this section is to give an outline of our simulation pipeline; the fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
+The fluctuations in the matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
 Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
@@
 We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$.
-We note that the observed ellipticity for a particular galaxy already contains information from the lensing from Large Scale Structure, but the random angle rotation makes this contribution second order in $\kappa$: consistently with the weak lensing approximation, the lensing singal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
-Like for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
+We note that the observed ellipticity for a particular galaxy already contains information from the lensing by Large Scale Structure, but the random angle rotation makes this contribution second order in $\kappa$: consistently with the weak lensing approximation, the lensing signal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
+Just as for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
 These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
@@
 \section{Statistical methods}
-The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a bayesian fashion in order to compute parameter confidence intervals.
+The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian fashion in order to compute parameter confidence intervals.
 
@@
 \label{cosmostats}
-In this paragraph we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations; we make use of the MF and LM statistical descriptors outlined in the previous paragraph.
+
+In this section we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations; we make use of the MF and LM statistical descriptors outlined in the previous section.
 We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLenS data.
 In this notation, $i$ is an index that refers to the particular bin on which the descriptor is evaluated (for example $i$ can range from 0 to 9 for the LM statistic and from 0 to $N_b-1$ for a Minkowski Functional measured on $N_b$ different excursion sets).
-Once we make an assumption for the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ and for the parameter priors $\Pi(\mathbf{p})$, we can use the Bayes theorem to compute the parameter likelihood $\mathcal{L}_p$ as follows
+Once we make an assumption for the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ and for the parameter priors $\Pi(\mathbf{p})$, we can use Bayes theorem to compute the parameter likelihood $\mathcal{L}_p$ as follows
 
@@
 Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator is at least 10\% accurate for the lower multipoles, and this accuracy can even be comparable with 1\% for the higher multipoles.
-The Minkowski Functionals emulator has a good, $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates with numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next paragraph.
+The Minkowski Functionals emulator has a good, $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates with numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
 
@@
 %
-The purpose of this paragraph is to convince the reader that the cosmological constraints we show in this paper are numerically robust, i.e.
+The purpose of this section is to demonstrate that the cosmological constraints we show in this paper are numerically robust, i.e.
 they are reasonably stable once we consider an large enough number $n$ of Principal Components.
@@
 \subsection{Combining statistics}
-An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in our companion paper \citep{Companion}, where we combine the power spectrum and peak count statistics, as well as in the literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
+An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in \citep{Companion}, where the authors combine the power spectrum and peak count statistics, as well as in previous literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
 The procedure we adopt is the following: suppose we consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor; we compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ to keep in order for the constraints to be stable.
@@
 We believe that this is due to uncorrected systematics in the CFHTLenS data, since when we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
-It is important to say, however, that the mock observation to which the right panel of Figure \ref{contours3single} refers, was build with the mean of $R=1000$ realizations of the CFHTcov simulations.
+It is important to say, however, that the mock observation to which the right panel of Figure \ref{contours3single} refers, was built with the mean of $R=1000$ realizations of the CFHTcov simulations.
 We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner,even if the likelihood of this happening is very small ($\lesssim1\%$).
 
-We observe that the Moments give the best constraint on $(\Omega_m,\sigma_8)$; in order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
+We observe that the Moments give the tightest constraint on $(\Omega_m,\sigma_8)$; this constraint is also unbiased in the sense that it includes the accepted values for these parameters within 1$\sigma$.
+The fact that the Moments are useful in terms of deriving unbiased cosmological constraints has been confirmed in previous work, such as \citep{PetriSpurious}.
+In order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
 Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higer order moments to the feature set: because we are focusing on 3 parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then we add the remaining six moments of gradients one by one, starting from the quadratic ones.
@@
 The bias in the $(\Omega_m,\sigma_8)$ constraints is made worse by the cosmological degeneracy of these parameters; to mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but on the other hand it does a good job in nailing the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
+In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but it does a good job in determining the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
 The numerical value that we find for $\Sigma_8$ agrees with the one previously published by the CFHTLenS collaboration in \citep{CFHTKilbinger}.
-Regarding the parameter biases, our results are in accordance with what already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
+Regarding the parameter biases, our results are in accordance with what was already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
 In accordance with the same work, we found that the LM statistic is the less biased one and hence is the ideal tool to detect cosmological information in CFHTLenS.
@@
 The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, unfortunately this does not help in reducing the inherent parameter bias.
-In the right panel of Figure \ref{contours3combined} we can see that even with these statistics combinations, $w$ remains essentially unconstrained.
-Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained with either the MFs alone, without the need of combining different descriptors.
+In the right panel of Figure \ref{contours3combined} we can see that even with these statistics combined, $w$ remains essentially unconstrained.
+Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained with the MFs alone, without the need of combining different descriptors.
 
@@
 \begin{itemize}
-\item When constraining the $(\Omega_m,\sigma_8)$ doublet with the CFHTLenS survey, we find that the Moments of the $\kappa$ field provide the tighest constraint on the former parameters; this constraint has also the advantage of being unbiased.
+\item When constraining the $(\Omega_m,\sigma_8)$ doublet with the CFHTLenS survey, we find that the Moments of the $\kappa$ field provide the tighest constraint on the former parameters; this constraint has also the advantage of being unbiased (further evidence in the unbiased nature of constraints from the Moments has been found in \citep{PetriSpurious}).
 We found that the biggest improvement on these parameter bounds is achieved when we include the quartic moments of gradients in the feature set; this improvement cannot be obtained by combining one--point moments at different smoothing scales

### 2014-12-22 andrea/convergence_map_analysis/contours_pca.py
replaced contour plotting with the lenstools one

@@ -8,7 +8,7 @@ import numpy as np
 from scipy import stats
 import matplotlib.pyplot as plt
 
-from contours import ContourPlot
+from lenstools.contours import ContourPlot
 
 def main():
 

### 2014-12-23 jia/junk_projectB_peakobs.py
organize obsPK files

@@ -707,3 +707,49 @@ def MassProj (gridofdata, zcut, R = 3.0, sigmaG=1.0):
 		ikappa = sum(icontribute[idx_nonzero])
 		icontribute/=ikappa
 		return idx_dist[idx_fore[idx_nonzero]], icontribute[idx_nonzero], ikappa*ones(len(idx_nonzero))
+
+cat_gen_old = lambda Wx: np.load(obsPK_dir+'W%s_cat_z0213_ra_dec_weight_z_ugriz_SDSSr_SDSSz.npy'%(Wx)) #columns: ra, dec, z_peak, weight, MAG_u, MAG_g, MAG_r, MAG_iy, MAG_z, r_SDSS, z_SDSS
+def Mhalo_gen (Wx):
+	print Wx
+	ra, dec, z_arr, weight, MAG_u, MAG_g, MAG_r, MAG_iy, MAG_z, r_SDSS, z_SDSS = cat_gen_old(Wx).T
+	idx = where( (abs(r_SDSS)!=99)&(abs(z_SDSS)!=99) )[0]#rid of the mag=99 ones
+	SDSSr_rest = M_rest_fcn(r_SDSS[idx], z_arr[idx])
+	SDSSz_rest = M_rest_fcn(z_SDSS[idx], z_arr[idx])
+	#MAG_z_rest = M_rest_fcn(MAG_z[idx], z_arr[idx])
+	MAG_i_rest = M_rest_fcn(MAG_iy[idx], z_arr[idx])
+	rminusz = SDSSr_rest - SDSSz_rest
+	M_arr = Minterp(SDSSz_rest, rminusz)
+	M100 = M_arr[where(~isnan(M_arr))[0]]
+	idx_new = idx[where(~isnan(M_arr))[0]]
+	Mvir = M100/1.227
+	Rvir_arr = Rvir_fcn(Mvir, z_arr[idx_new])
+	DL_arr = DL_interp(z_arr[idx_new])	
+	new_cat = array([ra[idx_new], dec[idx_new], z_arr[idx_new], weight[idx_new], MAG_iy[idx_new], Mvir, Rvir_arr, DL_arr]).T
+	save(obsPK_dir+'W%s_cat_z0213_ra_dec_redshift_weight_MAGi_Mvir_Rvir_DL.npy'%(Wx), new_cat)
+map(Mhalo_gen, range(1,5))
+
[…]

### 2014-12-23 jia/projectB_peakobs.py

@@ -27,6 +27,7 @@ import sys
 obsPK_dir = '/Users/jia/CFHTLenS/obsPK/'
 plot_dir = obsPK_dir+'plot/'
 
+make_kappa_predict = 1
 cluster_counts = 0
 halo_plots = 0
 list_peaks_cat = 0 #! generate a list of galaxies for all peaks
@@ -66,8 +67,9 @@ kmapGen = lambda Wx, zcut, sigmaG: WLanalysis.readFits('/Users/jia/CFHTLenS/obsP
 
 bmodeGen = lambda Wx, zcut, sigmaG: WLanalysis.readFits('/Users/jia/CFHTLenS/obsPK/maps/W%i_Bmode_%s_sigmaG%02d.fit'%(Wx, zcut, sigmaG))*maskGen(Wx, zcut, sigmaG)
 
-cat_gen = lambda Wx: np.load(obsPK_dir+'W%s_cat_z0213_ra_dec_weight_z_ugriz_SDSSr_SDSSz.npy'%(Wx)) #columns: ra, dec, z_peak, weight, MAG_u, MAG_g, MAG_r, MAG_iy, MAG_z, r_SDSS, z_SDSS
-
+cat_gen = lambda Wx: np.load(obsPK_dir+'W%s_cat_z0213_ra_dec_redshift_weight_MAGi_Mvir_Rvir_DL.npy'%(Wx))
+#columns: ra, dec, redshift, weight, i, Mhalo, Rvir, DL
+	
 
 ########## cosmologies #######################
 # growth factor
@@ -80,6 +82,12 @@ DL_arr = array([DL(z) for z in z_arr])
 DL_interp = interpolate.interp1d(z_arr, DL_arr)
 # find the rest magnitude at the galaxy, from observed magnitude cut
 M_rest_fcn = lambda M_obs, z: M_obs - 5.0*log10(DL_interp(z)) - 25.0
+
+
+##################### MAG_z to M100 ##########
+datagrid_VO = np.load(obsPK_dir+'Mhalo_interpolator_VO.npy')#Mag_z, r-z, M100, residual
+Minterp = interpolate.CloughTocher2DInterpolator(datagrid_VO[:,:2],datagrid_VO[:,2])
+#usage: Minterp(MAGz_arr, r-z_arr)
 
 
[…]

### 2014-12-23 jia/junk_projectB_peakobs.py
organize obsPK files

@@ -1,3 +1,14 @@
+cluster_counts = 0
+halo_plots = 0
+list_peaks_cat = 0 #! generate a list of galaxies for all peaks
+project_mass = 0
+#junk routines below
+update_mag_i = 0
+plot_galn_vs_kappa_hist = 0
+do_hist_galn_magcut = 0
+update_mag_all = 0 #! make a list of galaxie catagues with useful quantities
+
+
 #cNFW_fcn = lambda zM: 9.0/(1.0+zM[0])*(zM[1]/1.3e13)**(-0.13)#Bullock2001
 #cNFW_fcn = lambda zM: 10.0/(1.0+zM[0])*(zM[1]/1e13)**(-0.2)#Takada&Jain2003
 #cNFW_fcn = lambda zM: 11.0/(1.0+zM[0])*(zM[1]/1e13)**(-0.13)#Lin&Kilbinger2014

### 2014-12-23 jia/projectB_peakobs.py

@@ -28,15 +28,7 @@ obsPK_dir = '/Users/jia/CFHTLenS/obsPK/'
 plot_dir = obsPK_dir+'plot/'
 
 make_kappa_predict = 1
-cluster_counts = 0
-halo_plots = 0
-list_peaks_cat = 0 #! generate a list of galaxies for all peaks
-project_mass = 0
-#junk routines below
-update_mag_i = 0
-plot_galn_vs_kappa_hist = 0
-do_hist_galn_magcut = 0
-update_mag_all = 0 #! make a list of galaxie catagues with useful quantities
+
 ########### constants ######################
 z_lo = 0.6
 z_hi = '%s_hi'%(z_lo)
@@ -139,39 +131,65 @@ def Gx_fcn (x, cNFW=5.0):
 	return out
 
 f = 1.043
-def kappa_proj (Mvir, Rvir, z_fore, ra_fore, dec_fore, DL_fore, cNFW=5.0):#(Mvir, Rvir, z_fore, ra_fore, dec_fore, DL_fore, z_back, ra_back, dec_back, DL_back, cNFW=5.0, f = 1.043):
+def kappa_proj (Mvir, Rvir, z_fore, x_fore, y_fore, DL_fore, z_back, x_back, y_back, DL_back, cNFW=5.0):
 	'''return a function, for certain foreground halo, 
 	calculate the projected mass between a foreground halo and a background galaxy pair.
 	'''
 	#f = 1.043#=1.0/(log(1+cNFW)-cNFW/(1+cNFW)) with cNFW=5.0
-	#Mvir = M100/1.227#cNFW = 5, M100/Mvir = 1.227
-	#Rvir = Rvir_fcn(Mvir, z)#cm
 	two_rhos_rs = Mvir*M_sun*f*cNFW**2/(2*pi*Rvir**2)#cgs, see LK2014 footnote
-	xy_fcn = WLanalysis.gnom_fun((ra_fore, dec_fore))
 	Dl = DL_fore/(1+z_fore)**2
 	Dl_cm = 3.08567758e24*Dl # D_angular = D_luminosity/(1+z)**2
-	theta_vir = Rvir/Dl_cm
-	def kappa_proj_fcn (z_back, ra_back, dec_back, DL_back):
-		Ds = DL_back/(1+z_back)**2
-		Dls = Ds - Dl
[…]

### 2015-01-09 Paper_minkowski/paper.tex
incorporated round 3 edits

@@
 Using our full set of statistical descriptors, we constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a marginal bias, the Moments provide a tight unbiased bound on the former parameters, with the main contribution coming from quartic moments of gradients.
+We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the Moments provide a tight unbiased bound on the former parameters, with the main contribution coming from quartic moments of gradients.
 
@@
 In this section we give a description of the method we used to sample the parameter space in our simulation effort.
-We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping fixed the other relevant parameters to $(h,\Omega_b,n_s)$ to their fiducial values (0.7,0.046,0.96).
+We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7, 0.046, 0.96).
 We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require in fact a prohibitively large number of samples.
@@
 The statistical descriptors we consider on this work are the Minkowski Functionals (MFs) and the low order moments (LM) of the convergence field.
-The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence random field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$.
+The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$.
 Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ images.
@@
 %
-If the $\kappa$ field was Gaussian, one could express all the Minkowski Functionals in terms of the LM2 moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones.
-In reality, weak lensing convergence fields, as the CFHTLenS ones, are non--Gaussian and the MF and LM descriptors are in principle equivalent.
+If the $\kappa$ field were Gaussian, one could express all the Minkowski Functionals in terms of the LM$_2$ moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones.
+In reality, weak lensing convergence fields, as the CFHTLenS ones, are non--Gaussian and the MF and LM descriptors are not guaranteed to be equivalent.
 \citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order.
@@
 Because of this, throughout this work, we treat MF and LM as separate statistical descriptors.
+The LM we consider are restricted to the ones that appear in the perturbatice expansion of the Minkowski functionals.
+The LM$_4$ moments which include derivatives of the $\kappa$ field ($K_{1,2,3}$) each emphasize a different set of trispectrum quadrileteral shapes.
+For example, $K_2$ emphasizes shapes where one side of the quadrilateral is large and $K_4$ emphasizes shapes close to rectangular.
+There are other moments which include derivatives besides the ones we have considered.
+In the future we will investigate whether there is additional constraining power in quartic moments not considered here.
+
 In addition to these two descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
@@
 %
-and minimizing the ratio $\mathds{E}/\sqrt{\mathds{V}}$ with respect to $\alpha$.
+and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect to $\alpha$.
 This procedure yields a value $\alpha\approx0.55$ for the statistical descriptors that we consider, consistent to what can be found in the literature.
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data (left panel) and from a mock observation constructed using the CFHTcov simulations as data (right panel).
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data (left panel) and from a mock observation constructed using the mean of 1000 realizations in CFHTcov simulations as data (right panel).
 The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $w$.
@@
 
-\newpage 
+%\newpage 
 %%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Acknowledgements}
-We thank the Stampede cluster who saved our day
+The simulations referenced in this work were performed at the NSF Extreme Science and Engineering Discovery Environment (XSEDE), supported by grant number ACI-1053575, and at the New York Center for Computational Sciences, a cooperative effort between Brookhaven National Laboratory and Stony Brook University, supported in part by the State of New York.
+This work was supported in part by the U.S.
+Department of Energy under Contract No.
+DE-AC02-98CH10886 and Contract No.
+DE-SC0012704.
 

### 2015-01-30 Paper_minkowski/paper.tex
update abstract

@@
 \begin{abstract}
-Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; the fact that typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss some of the cosmological information contained in survey data.
-In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ from weak lensing Minkowski Functionals and Moments, using the publicly available data from the 154\,deg$^2$ CFHTLenS survey.
-We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise in the CFHTLenS catalogs.
-We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We find that dimensionality reduction techniques such as Principal Component Analysis help in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
-Using our full set of statistical descriptors, we constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the Moments provide a tight unbiased bound on the former parameters, with the main contribution coming from quartic moments of gradients.
+Weak gravitational lensing is a powerful cosmological probe, with
+non--Gaussian features potentially containing the majority of the
+information. We examine constraints on the parameter triplet
+$(\Omega_m,w,\sigma_8)$ from high--order moments and Minkowski
+Functionals (non-Gaussian ``features'') of the weak lensing
+convergence field, using publicly available data from the 154\,deg$^2$
+CFHTLenS survey. We utilize a suite of ray--tracing N-body simulations
+spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space,
+replicating the galaxy sky positions, redshifts and shape noise in the
+CFHTLenS catalogs. We then build an emulator that interpolates the
+simulated features as a function of $(\Omega_m,w,\sigma_8)$, and use
+it to compute the likelihood function and parameter constraints. We
+employ a principal component analysis to reduce dimensionality and to
+help stabilize the constraints with respect to the number of bins used
+to construct each convergence statistics. Using the full set of
+statistics, we find
+$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
+C.L.), in agreement with previous values. We find that constraints on
+the $(\Omega_m,\sigma_8)$ doublet from the Minkowski Functionals
+suffer a strong bias. However, high-order moments break the
+$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
+these parameters with no apparent bias.  The main contribution comes
+from quartic moments of gradients.
 

### 2015-02-17 Paper_minkowski/paper.tex
incorporated edits round 3

--- 2015-01-09 Paper_minkowski/paper.tex
@@
 
+%MM edited wording
+
 \begin{abstract}
-Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; the fact that typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss some of the cosmological information contained in survey data.
-In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ from weak lensing Minkowski Functionals and Moments, using the publicly available data from the 154\,deg$^2$ CFHTLenS survey.
+Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
+In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ derived from weak lensing Minkowski Functionals and Moments, using publicly available data from the 154\,deg$^2$ CFHTLenS survey.
 We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise in the CFHTLenS catalogs.
 We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We find that dimensionality reduction techniques such as Principal Component Analysis help in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
-Using our full set of statistical descriptors, we constrain the $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the Moments provide a tight unbiased bound on the former parameters, with the main contribution coming from quartic moments of gradients.
+We find that the dimensionality reduction technique Principal Component Analysis helps in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
+Using our full set of statistical descriptors, we constrain $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
+We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the Moments provide a tight unbiased bound on the parameters, with a substantial contribution coming from quartic moments of gradients.
 
@@
 \section{Introduction}
-In this work we use the publicly available CFHTLenS data, that consists of a catalog of $\approx$4.2 million galaxies, combined with a suite of ray-tracing simulations in 91 different cosmological models to constrain the cosmological parameters $\Omega_m$,$\sigma_8$ and the DE equation of state $w$.
-The paper is organized as follows; we first give an overview of the CFHTLenS catalogs we make use of, summarizing the data reduction techniques we adopted.
-Next, we give a description of our simulation pipeline, including the procedure to sample the parameter space and a broad description of the ray--tracing algorithm; after this we illustrate the statistical descriptors that we use to extract the cosmological information, complemented with a dimensional reduction and statistical inference framework.
-We then outline our results, with particular focus on the cosmological parameter constraints.
-To conclude, we discuss our findings and comment on possible future developments of this analysis.
+%
+
+Weak gravitational lensing is emerging as a promising technique to constrain cosmology.
+Techniques have been developed to construct cosmic shear fields with shape measurements in large galaxy catalogues; although the shear two--point function (2PCF) serves as a main cosmological probe (see \citep{CFHTKilbinger} for example), alternative statistics have been shown to increase the amount of cosmological information one can extract from weak lensing fields.
+Among these, higher moments (\citep{moments1,moments2,moments3,moments4,moments5,moments6}), three--point functions (\citep{3pcf1,3pcf2}), bispectra (\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts (\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski Functionals (\citep{MinkJan,Petri2013}) have shown to improve cosmological constraints in weak lensing analyses.
+In this work we use the publicly available CFHTLenS data, consisting of a catalog of $\approx$4.2 million galaxies, combined with a suite of ray-tracing simulations in 91 different cosmological models to constrain the cosmological parameters $\Omega_m$,$\sigma_8$ and the DE equation of state $w$.
+The paper is organized as follows; we first give an overview of the CFHTLenS catalogs, summarizing the data reduction techniques adopted.
+Next, we give a description of our simulation pipeline, including the procedure used to sample the parameter space and outline the ray--tracing algorithm.
+We call the weak lensing statistical observables - the Power Spectrum, Minkowski Functionals and Moments - "descriptors" or "features" interchangeably throughout the paper.
+We discuss the calculation of the statistical descriptors, the dimensional reduction method, and the statistical inference framework used.
+We then outline our results, and the the cosmological parameter constraints obtained.
+To conclude, we discuss our findings and comment on possible future extensions of this analysis.
+
+% "descriptors" or "features" are used interchangeably throughout the paper. It may be sufficient to state this here, but it might be clearer to use only "descriptors" Morgan 2/16/2015
 
@@
 %
-The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data roughly consist of a galaxy catalogue created using SExtractor \citep{SExtractor}, a photometric redshift estimation with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements using \textit{lensfit} \citep{cfht1,cfht2}.
-The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the two point correlation function (2PCF); additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using the skewness as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
-We apply the following cuts to the galaxy catalogue: mask$<1$, redshift $0.2 < z < 1.3$, fitclass = 0 (which requires the object to be a galaxy) and weight $w>0$ (with larger $w$ indicating smaller shear measurement uncertainty).
-Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ residual sky coverage, and average number density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
-The catalogue is further reduced by $\sim25\%$ when one leaves out galaxies with non--negligible star--galaxy correlations.
-These spurious correlations are due to imperfect PSF removal, and do not contain cosmological signal.
-The CFHTLenS galaxy catalogue provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}),m(\pmb{\theta})$.
+The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data consist of a galaxy catalog created using SExtractor \citep{SExtractor}, a photometric redshift estimated with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements made using \textit{lensfit} \citep{cfht1,cfht2}.
+The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF; additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using the skewness as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
+We apply the following cuts to the galaxy catalog: mask$<1$, redshift $0.2 < z < 1.3$, fitclass = 0 (which requires the object to be a galaxy) and weight $w>0$ (with larger $w$ indicating smaller shear measurement uncertainty).
+Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ sky coverage, and average galaxy density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
+The catalog is further reduced by $\sim25\%$ when one rejects fields with non--negligible star--galaxy correlations.
+These spurious correlations are likely due to imperfect PSF removal, and do not contain cosmological signal.
+The CFHTLenS galaxy catalog provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}), m(\pmb{\theta})$.
 Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps; these square subfield maps are pixelized according to a Gaussian gridding procedure
@@
 %
-where the smoothing scale $\theta_G$ has been fixed to 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests); the multiplicative and additive corrections $m,c$ related the observed and true ellipticities of the galaxies in the catalogue
+where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests); the multiplicative and additive corrections $m,c$ relate the observed and true ellipticities of the galaxies in the catalog
 \begin{equation}
@@
 %
-Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we can perform a non--local Kaiser--Squires inversion to recover the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear field
+Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we can perform a non--local Kaiser--Squires inversion \citep{KS} to recover the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear field
 %
@@
 %
-The CFHTLenS catalogues contain masked regions (mainly due to bright stars and incorrect PSF subtraction); these regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be masked out.
-We first create grided maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
-We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}); for a more in--depth description of our data reduction procedure, we refer the reader to \citep{Companion}.
+The CFHTLenS catalogs contain masked regions ( rejected fields, regions around bright stars etc.).
+We first create gridded maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
+We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}).
+Regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be removed.
+For a more in--depth description of our data reduction procedure, we refer the reader to \citep{Companion}.
 
@@
 In this section we give a description of the method we used to sample the parameter space in our simulation effort.
-We wish to investigate the non--linear dependency of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7, 0.046, 0.96).
-We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require in fact a prohibitively large number of samples.
+We wish to investigate the non--linear dependence of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7, 0.046, 0.96).
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require a prohibitively large number of samples.
 We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
@@
 \begin{enumerate}
-\item We start from the diagonal design $\mathcal{D}_0$: $x_i^d\equiv i/(N-1)$
+\item We start from the diagonal design $\mathcal{D}_0$:
+
+$x_i^d\equiv i/(N-1)$
 \item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$ where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$
@@
 For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLenS shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
-Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will serve the parameter inferences as in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
+Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will be used for the parameter inferences in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
 
@@
 \label{raysim}
-The goal of this section is to give an outline of our simulation pipeline; the fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays travelling from the source to the observer.
-The fluctuations in the matter field are described by their gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can trade the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
+The goal of this section is to give an outline of our simulation pipeline; the fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays traveling from the source to the observer.
+The fluctuations in the matter field are described by the gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can replace the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
 Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
@@
 To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$; for the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
-Once we know the details of the light ray trajectories, we can easily infer the weak lensing interesting quantities by taking the angular derivatives of the ray deflections $A(\chi_s;\pmb{\theta}) = \partial \pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
+Once we know the details of the light ray trajectories, we can easily infer the interesting weak lensing  quantities by taking the angular derivatives of the ray deflections $A(\chi_s;\pmb{\theta}) = \partial \pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
 %
@@
 where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the first and third Pauli matrices.
-$\kappa$ is related to the source apparent magnification, while $(\gamma^1,\gamma^2)$ are related to the source apparent ellipticity, as seen from the observer.
-Given a source with intrinsic ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity as seen from an observer will be modified by the cosmic shear $\pmb{\gamma}=\gamma^1 + i\gamma^2$ following
+$\kappa$ is related to the source apparent magnification, while $(\gamma^1,\gamma^2)$ are related to the source apparent ellipticity, as seen by the observer.
+Given a source with intrinsic ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity as seen by an observer will be modified by the cosmic shear $\pmb{\gamma}=\gamma^1 + i\gamma^2$ following
 %
@@
 %
-where $\mathbf{g} = \pmb{\gamma}/1-\kappa$ is the reduced shear.
+where $\mathbf{g} = \pmb{\gamma}/(1-\kappa)$ is the reduced shear.
 For each simulated galaxy, we assign an intrinsic ellipticity by rotating the observed ellipticity for that galaxy by a random angle on the sky, while conserving its magnitude $\vert\mathbf{e}\vert$.
@@
 We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$.
-We note that the observed ellipticity for a particular galaxy already contains information from the lensing by Large Scale Structure, but the random angle rotation makes this contribution second order in $\kappa$: consistently with the weak lensing approximation, the lensing signal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
-Just as for the CFHTLenS data, we proceed in constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
+We note that the observed ellipticity for a particular galaxy already contains information from the lensing by large scale structure, but the random angle rotation makes this contribution second order in $\kappa$.
+Consistent with the weak lensing approximation, the lensing signal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
+We analyze the simulations in the same way as we analyzed CFHTLenS data, constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
 These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
@@
 \section{Statistical methods}
-The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian fashion in order to compute parameter confidence intervals.
+The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian framework in order to compute parameter confidence intervals.
 
 \subsection{Descriptors}
-The statistical descriptors we consider on this work are the Minkowski Functionals (MFs) and the low order moments (LM) of the convergence field.
+The statistical descriptors we consider in this work are the Minkowski Functionals (MFs) and the low order moments (LM) of the convergence field.
 The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$.
-Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ images.
+Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ maps.
 %
@@
 %
-Where $A$ is the total area of the fields of view we have been using and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences.
+Where $A$ is the total area of the fields of view and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences.
 The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, $\partial V_0$ (which can be obtained by differentiation $\partial V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$), while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
@@
 %
+
 If the $\kappa$ field were Gaussian, one could express all the Minkowski Functionals in terms of the LM$_2$ moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones.
-In reality, weak lensing convergence fields, as the CFHTLenS ones, are non--Gaussian and the MF and LM descriptors are not guaranteed to be equivalent.
-\citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order.
-Such perturbative series, however, have been shown not to converge in \citep{Petri2013} unless the weak lensing fields are smoothed with windows of size comparable to $\sim 15^\prime$.
+In reality, weak lensing convergence fields are non--Gaussian and the MF and LM descriptors are not guaranteed to be equivalent.
+\citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the $\kappa$ field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order.
+Such perturbative series, however, have been shown not to converge \citep{Petri2013} unless the weak lensing fields are smoothed with windows of size $\geq 15^\prime$.
 Because of this, throughout this work, we treat MF and LM as separate statistical descriptors.
-The LM we consider are restricted to the ones that appear in the perturbatice expansion of the Minkowski functionals.
-The LM$_4$ moments which include derivatives of the $\kappa$ field ($K_{1,2,3}$) each emphasize a different set of trispectrum quadrileteral shapes.
+The LM we consider are restricted to the ones that appear in the perturbative expansion of the Minkowski functionals.
+The LM$_4$ moments which include derivatives of the $\kappa$ field ($K_{1,2,3}$) each emphasize a different set of trispectrum quadrilateral shapes.
 For example, $K_2$ emphasizes shapes where one side of the quadrilateral is large and $K_4$ emphasizes shapes close to rectangular.
@@
 
-In addition to these two descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
+In addition to the MF and LM descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
 \begin{equation}
@@
 %
-where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function; while the use of this statistic is not a novelty, we want indeed to compare the results we get using MF and LM to the ones already present in the literature.
-A summary of the statistical descriptors we used is presented in Table \ref{desctable}.
+where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function.
+While the use of this statistic is not a novelty, we want to compare the results we get using MF and LM to ones already present in the literature which are based on the power spectrum.
+A summary of the statistical descriptors used is presented in Table \ref{desctable}.
 %
@@
 %
-When measuring statistical features on $\kappa$ maps, particular attention must be given to the effect of masked pixels: this does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with exception of the few pixels that are close to the mask boundaries.
+
+When measuring statistical features on $\kappa$ maps, particular attention must be given to the effect of masked pixels.
+This does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with the exception of the few pixels that are close to the mask boundaries.
 Masking effects on Minkowski Functionals constraints with CFHTLenS have been studies extensively by \citep{CFHTMasato}.
-The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier Transforms and hence rely on the value of each pixel on the map.
+The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier transforms and hence rely on the value of every pixel in the map.
 Although sophisticated interpolation approaches over the masked regions have been studied (see for example \citep{VplasInterpolation}), for the sake of simplicity we put a value of 0 in each masked pixel, arguing that, given the typical angular size of the masked regions we consider, this will have little effect on the Power Spectrum at the range of multipoles in Table \ref{desctable}.
-We nevertheless believe that the way we deal with masked sky regions is very robust, because we apply the same masks to our simulations.
+We believe that the way we deal with masked sky regions is very robust, since we apply the same masks to our simulations.
 
@@
 
-In this section we give a brief outline of the statistical framework we adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations; we make use of the MF and LM statistical descriptors outlined in the previous section.
+In this section we give a brief outline of the statistical framework adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations.
+We make use of the MF and LM statistical descriptors outlined in the previous section.
 We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLenS data.
@@
 %
-where $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that ensures the proper normalization for $\mathcal{L}_p$; we make the usual assumption that the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ is a Gaussian
+where $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that ensures the proper normalization for $\mathcal{L}_p$; we make the usual assumption that the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ is Gaussian
 
@@
 \mathcal{L}_d(D_i\vert \mathbf{p}) = ((2\pi)^{N_b}\det{\mathbf{C}})^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})} \\ \\
-\chi^2(D_i\vert \mathbf{p}) = \mathbf{(D - M(p))C^{-1}(D-M(p))}
+\chi^2(D_i\vert \mathbf{p}) = \mathbf{(D - M(p))C^{-1}(D-M(p))}.
 \end{matrix}
@@
 %
+
 The simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
 \begin{equation}
-M_i(\mathbf{p}) = \frac{1}{R}\sum_{r=1}^R M_i^r 
+M_i(\mathbf{p}) = \frac{1}{R}\sum_{r=1}^R M_i^r .
 \end{equation}
 %
-and the covariance matrix 
+The covariance matrix 
 \begin{equation}
@@
 %
-is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model--independent; because of this the normalization constant in (\ref{datalikelihood}) is also model--independent.
+is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model-independent.
+Thus the normalization constant in (\ref{datalikelihood}) is also model--independent.
 When computing parameter constraints from CFHTLenS weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.
@@
 \label{ennesigma}
-\int_{\mathcal{L}>c_N} \mathcal{L}_p(\mathbf{p}\vert D_i) d\mathbf{p} = \frac{1}{\sqrt{2\pi}}\int_{-N}^N dx e^{-x^2/2}
+\int_{\mathcal{L}>c_N} \mathcal{L}_p(\mathbf{p}\vert D_i) d\mathbf{p} = \frac{1}{\sqrt{2\pi}}\int_{-N}^N dx e^{-x^2/2}.
 \end{equation}
 %
+
 Given the low dimensionality of the parameter space we consider $(N_p=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on a finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$, and hence we are able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.
-We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M_(\mathbf{p})$ at an arbitrary intermediate point; we decided to use a Radial Basis Function (RBF) interpolation scheme.
+We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M_(\mathbf{p})$ to an arbitrary intermediate point.
+We use a Radial Basis Function (RBF) interpolation scheme.
 We approximate the model descriptor as
@@
 %
-where $\phi$ has been chosen as a multiquadric function $\phi(r)=\sqrt{1+(r/r_0)^2}$ with $r_0$ chosen as the mean euclidean distance between the points in the simulated grid $\mathbf{p}_s$.
+where $\phi$ has been chosen as a multiquadric function $\phi(r)=\sqrt{1+(r/r_0)^2}$ with $r_0$ chosen as the mean Euclidean distance between the points in the simulated grid $\mathbf{p}_s$.
 The constant coefficients $\lambda_s$ can be determined imposing the $N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which enforce the fact that the interpolation should be exact at the simulated points.
 The interpolation computations are conveniently performed using the Scipy library \citep{scipy}.
+
 We studied the accuracy of emulator, built with the CFHTemu1 simulations, by interpolating the convergence features to the fiducial parameter setting $(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to the one expected from the CFHTcov simulations.
-Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator is at least 10\% accurate for the lower multipoles, and this accuracy can even be comparable with 1\% for the higher multipoles.
-The Minkowski Functionals emulator has a good, $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates with numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
+Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator has accuracy better than 10\% for the lower multipoles and comparable to 1\% for the higher multipoles.
+The Minkowski Functionals emulator has accuracy $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due to numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
 
@@
 \label{pcasection}
-The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data; when the question on the accuracy of the $N\sigma$ contours is raised, particular attention should be given on the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
-It is known that the choice of the number of bins, $N_b$, can have a non--negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
-Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular feature) is contained in a fixed limited number of linear combinations of its binning.
+The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data.
+When the question on the accuracy of the $N\sigma$ contours is considered, particular attention must be paid to the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
+It is known that the choice of the number of bins, $N_b$, can have a non-negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
+Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular feature) is contained in a limited number of linear combinations of its binning.
 In the framework adopted by \citep{coyote2}, for example, the authors find that the majority of the cosmological information in the matter Power Spectrum is contained in only 5 selected linear combinations of the multipoles.
-Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ that we choose originally.
+Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ originally chosen.
+
 In order to compute the Principal Components of our feature space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
-Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$, defined by subtracting the mean in each bin, and normalizing it by its variance; next we proceed in a SVD decomposition of $\mathbf{\tilde{M}}$
+Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$, defined by subtracting the mean in each bin, and normalizing it by its variance.
+Next we proceed with a singular value decomposition (SVD) of $\mathbf{\tilde{M}}$
 \begin{equation}
 \label{svd}
-\mathbf{U}\Sigma \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}}
+\mathbf{U}\mathbf{S} \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}}
 \end{equation}   
 %
-where $\Sigma_{ij}=\Sigma_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $i$--th principal component of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
-To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\Sigma^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the feature covariance in (\ref{datacov}))
+where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $i$--th principal component of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
+
+To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\mathbf{S}^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the feature covariance in (\ref{datacov}))
 \begin{equation}
-\frac{1}{N-1}\mathbf{\tilde{M}}^T\mathbf{\tilde{M}} = \mathbf{V}\Sigma^2\mathbf{V}^T
+\frac{1}{N-1}\mathbf{\tilde{M}}^T\mathbf{\tilde{M}} = \mathbf{V}\mathbf{S}^2\mathbf{V}^T.
 \end{equation} 
@@
 We follow the standard interpretation of PCA components, stating that the only meaningful components $V^T_i$ in the analysis (i.e.
-the ones that contain the relevant cosmological information) are the ones that correspond to the biggest eigenvalues $\Sigma^2_{i}$, with the smallest eigenvalues corresponding to noisy patterns in the model, due to numerical inaccuracies in the simulation pipeline.
+the ones that contain the relevant cosmological information) are those corresponding to the largest eigenvalues $S^2_{i}$, with the smallest eigenvalues corresponding to noise in the model, due to numerical inaccuracies in the simulation pipeline.
 We expect our constraints to be stable with respect to the number of components, once enough components have been included.
@@
 The dimensionality reduction comes from the fact that we expect most of the cosmological information to be contained in a number of components $n<N_{b}$.
-Looking at the dimensionality issue from a more geometrical perspective, we expect our feature space to be a 3 dimensional manifold embedded in a $N_b$--dimensional space.
+
+Looking at the dimensionality issue from a more geometric perspective, we expect our feature space to be a 3-dimensional manifold embedded in a $N_b$--dimensional space.
 The dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
-As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds: when curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
-We are allowed flexibility on this flatness assumption because we allow the number of principal components to be bigger than 3.
+As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds.
+When curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
+We have flexibility on the flatness assumption because we allow the number of principal components to be greater than 3.
 
@@
 \includegraphics[scale=0.4]{Figures/pca_components.eps}
-\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $\Sigma_i^2$, the right plot shows their cumulative sum.
+\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
 A dashed black line has been drawn in correspondence of $n=3$ components}
@@
 \label{results}
-This section describes the results we have obtained in this work, and is organized as follows: we first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
+This section describes the results we have obtained and is organized as follows.
+We first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
 We then show the cosmological constraints from the CFHTLenS data.
-Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints: this is why, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8(\alpha)=\sigma_8(\Omega_m/0.27)^\alpha$.
-The reason for this is that, while $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8(\alpha)$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ for a suitable choice of $\alpha$, and hence has a much smaller relative uncertainty.
+Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints.
+To mitigate the effect of degeneracies, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8(\alpha)=\sigma_8(\Omega_m/0.27)^\alpha$.
+While $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8(\alpha)$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ for a suitable choice of $\alpha$, and hence has a much smaller relative uncertainty.
 We can derive this optimal value of $\alpha$ from the full three dimensional likelihood $\mathcal{L}(\Omega_m,w,\sigma_8)$, from which we can compute the expectation values
@@
 and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect to $\alpha$.
-This procedure yields a value $\alpha\approx0.55$ for the statistical descriptors that we consider, consistent to what can be found in the literature.
-We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes; we also show the $\Sigma_8$ marginalized likelihood.
-We finally study the effect of combining different descriptors, in hope that this helps in tightening the constraints.
-A summary with the complete set of results, along with the relevant Figures, is shown in Table \ref{summarytable}.
+This procedure yields a value $\alpha\approx0.55$ for the statistical descriptors that we consider, consistent  with what is found in the literature.
+
+We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes.
+We also show the $\Sigma_8$ marginalized likelihood.
+We finally study the effect of combining different descriptors, tightening the constraints.
+A summary with the complete set of results, along with the relevant Ffgures, is shown in Table \ref{summarytable}.
 
@@
 %
-The purpose of this section is to demonstrate that the cosmological constraints we show in this paper are numerically robust, i.e.
-they are reasonably stable once we consider an large enough number $n$ of Principal Components.
+Here we give evidence that the cosmological constraints derived in this paper are numerically robust, i.e.
+they are reasonably stable once we consider a large enough number $n$ of Principal Components.
 Figure \ref{pcafig} shows the PCA eigenvalues that result from the SVD decomposition of our feature spaces, as well as the cumulative sum of these eigenvalues, normalized to 1.
 Figure \ref{robustnessfig} shows the dependence of the $(\Omega_m,\sigma_8)$ constraints on the number of principal components $n$, and clearly indicates that we only need a limited number of components in order to capture the cosmological information contained in our descriptors.
-The number of components to keep, however, depends on the particular descriptor considered.
+The number of components with significant information content depends on the particular descriptor considered.
+This also addresses the inaccuracy of the MF emulator at high thresholds pointed out in Figure \ref{emulatorAccuracy}.
+By keeping a limited number of principal components we are able to prevent the inaccurate high--threshold bins, that have a low constraining power, from contributing to the parameter confidence levels.
 
@@
 %
-We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figures \ref{contours3single},\ref{contoursMoments} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
+We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figures \ref{contours3single}, \ref{contoursMoments} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
 Additionally we show the $\Sigma_8$ likelihood function (marginalized over $\Omega_m$ and $w$) in Figure \ref{likelihoodSi8single}.
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
 \includegraphics[scale=0.45]{Figures/contours_momentsOmega_m-sigma8.eps}
+\includegraphics[scale=0.45]{Figures/contours_momentsOmega_m-sigma8smooth.eps}
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments, with different colors corresponding to different moment combinations: we show the results obtained using the one--point moments $\sigma_0^2,S_0,K_0$ (black) and using the one--point moments combined at $(1.0,3.0,5.8)$\,arcmin smoothing (gray scale).
-We also show the improvements that we get when we add the quadratic (green), cubic (red) and quartic (moments) of gradients.
-The yellow contour refers to the whole set of 9 Moments}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments, with different colors corresponding to different moment combinations: we show the results obtained using the one--point moments $\sigma_0^2,S_0,K_0$ (black, left and right panels).
+In the left panel we show the constraints obtained adding moments of gradients to the one--point moments, while in the right panel we combine the one--point momente measured at different smoothing scales.}
 \label{contoursMoments}
-\end{figure}
+\end{figure*}
 
@@
 $(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
-$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments \\ combined ad different $\theta_G$}  & \ref{contoursMoments} \\ \hline
+$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments \\ combined at different $\theta_G$}  & \ref{contoursMoments},\ref{contoursMoments}b \\ \hline
 $(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & contours from CFHTLenS & \ref{contours3singleRep} \\ \hline 
@@
 \subsection{Combining statistics}
-An important point of this work is trying to address is whether the combination of different statistics can help in tighening the constraints on cosmology; some work in this direction has already been done in \citep{Companion}, where the authors combine the power spectrum and peak count statistics, as well as in previous literature (see \citep{CFHTFu}) where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
-The procedure we adopt is the following: suppose we consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor; we compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ to keep in order for the constraints to be stable.
-We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector: this procedure allows us to take the cross covariance between different descriptors.
-We show in Figure \ref{contours3combined} the combined CFHTLenS constraints on the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
+Combinating of different statistics can tighten the constraints on cosmology.
+Previous work in this direction includes \citep{Companion}, where the authors combine the power spectrum and peak count statistics and  \citep{CFHTFu} where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
+
+The procedure we adopt is the following:  Consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor.
+We compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ needed for the constraints to be stable.
+We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector.
+This procedure allows us to take the cross covariance between different descriptors.
+We show in Figure \ref{contours3combined} the combined CFHTLenS constraints in the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
 We discuss our findings in the next section.
@@
 In this section we discuss the results outlined in section \S~\ref{results}, with particular focus on the constraints on cosmology.
-As pointed out in \S~\ref{pcasection}, the choice of the number of bins, $N_b$, is an important point on which one should be careful; in order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our feature spaces.
+
+As pointed out in \S~\ref{pcasection}, the choice of the number of bins, $N_b$, is an important issue.
+In order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our feature spaces.
 In the left panel of Figure \ref{pcafig} we see that the PCA eigenvalues for our descriptors decrease about 4 orders of magnitude from $n=1$ to $n=3$, and looking at the right panel we see that we capture more than 99\%  of the feature variance even if we cut the PCA projection to the first 3 components.
+
 This does not mean that all the cosmological information is captured by the first 3 PCA components, and this is why we make a stability check by plotting the $1\sigma$ contour sizes as a function of $n$ in Figure \ref{robustnessfig}.
@@
 All the 9 components are necessary for the Moments contours to be stable.
-Matters are slightly different when we study the $(w,\Sigma_8)$ constraints: in this case we find that the optimal choice for the three MFs, $(V_0,V_1,V_2)$, is $n=10$, while the Power Spectrum and Moments components can be kept fixed, at respectively 3 and 9.
+
+Matters are slightly different when we study the $(w,\Sigma_8)$ constraints: in this case we find that the optimal choice for the three MFs, $(V_0,V_1,V_2)$, is $n=10$, while the Power Spectrum and Moments components remain at, respectively, 3 and 9 (figures supporting this choice not shown).
 
 We now discuss the main scientific findings of this work.
-In Figure \ref{contours3single} we show the $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data: we can see that the MFs constraints are heavily biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
-We believe that this is due to uncorrected systematics in the CFHTLenS data, since when we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
-It is important to say, however, that the mock observation to which the right panel of Figure \ref{contours3single} refers, was built with the mean of $R=1000$ realizations of the CFHTcov simulations.
-We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner,even if the likelihood of this happening is very small ($\lesssim1\%$).
+In Figure \ref{contours3single} we show the $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data.
+The MF constraints are heavily biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
+The best current values of $(\Omega_m,\sigma_8)$  \citep{PlanckXVI2013} lie beyond the 99\% likelihood contours (not shown).
+This may be due to uncorrected systematics in the CFHTLenS data, amplified by the $(\Omega_m,\sigma_8)$ degeneracy.
+When we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
+It is important to note, however, that the mock observations to which the right panel of Figure \ref{contours3single} refers, were built with the mean of $R=1000$ realizations of the CFHTcov simulations.
+We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner, though the likelihood of this happening is very small ($\lesssim1\%$).
 
-We observe that the Moments give the tightest constraint on $(\Omega_m,\sigma_8)$; this constraint is also unbiased in the sense that it includes the accepted values for these parameters within 1$\sigma$.
-The fact that the Moments are useful in terms of deriving unbiased cosmological constraints has been confirmed in previous work, such as \citep{PetriSpurious}.
-In order to understand what are the features responsible for such tight bounds, we studied the individual contributions of each of the moments to the constraining power.
-Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higer order moments to the feature set: because we are focusing on 3 parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then we add the remaining six moments of gradients one by one, starting from the quadratic ones.
+%Added that  the reason we think MFs are biased is that the best current values of Om, s8 lie beyond the 99% likelihood contours for MFs.
+Changed "We believe that this is due to uncorrected systematics" to "This may be due to"  .
+Added that bias is amplified by degeneracy.
+Morgan 2/16/2015
+
+We observe that the Moments give the tightest constraint on $(\Omega_m,\sigma_8)$.
+This constraint is also unbiased in the sense that it includes the best current values for these parameters within 1$\sigma$.
+The fact that the Moments are useful for deriving unbiased cosmological constraints has been noted in previous work  \citep{PetriSpurious}.
+
+In order to determine the origin of the tight bounds derived from moments, we studied the individual contributions of each of the moments to the constraining power.
+Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higher order moments to the feature set.
+Since we are constraining  3 cosmological parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then add the remaining six moments of gradients one by one, starting from the quadratic moments.
 We see that the biggest improvement on the parameter bounds comes from including quartic moments of gradients (i.e.
 $K_i$ with $i\ge1$) in the feature set.
-This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding the skewness to quadratic statistics, since the main improvement comes from higer moments of $\kappa$ derivatives.
-This result agrees with what \citep{BhuvKurtosis} in their previous work, in which they state that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
-We also observe that the improvement we obtain combining the one--point moments at different smoothing scales $\theta_G$, is not as good as the one that we get considering the moments of gradients.
+This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding the skewness to quadratic statistics, since the main improvement comes from higher moments of $\kappa$ derivatives.
+Our result agrees with  \citep{moments4}  which found that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
+We also observe that the improvement obtained by combining the one--point moments at different smoothing scales $\theta_G$, is not as large as that obtained by considering the moments of gradients.
 
-The bias in the $(\Omega_m,\sigma_8)$ constraints is made worse by the cosmological degeneracy of these parameters; to mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-In Figure \ref{likelihoodSi8single} we show the $1\sigma$ constraints on the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data: we can see that this survey is not sufficient to constrain $w$, but it does a good job in determining the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$, using either of the MFs.
-The numerical value that we find for $\Sigma_8$ agrees with the one previously published by the CFHTLenS collaboration in \citep{CFHTKilbinger}.
-Regarding the parameter biases, our results are in accordance with what was already found in \citep{PetriSpurious}, who found that unaccounted systematics result in larger parameter biases when the contstraints come from the MFs.
-In accordance with the same work, we found that the LM statistic is the less biased one and hence is the ideal tool to detect cosmological information in CFHTLenS.
+The bias in the $(\Omega_m,\sigma_8)$ constraints is amplified by the cosmological degeneracy of these parameters.
+To mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non-degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
+Figure \ref{likelihoodSi8single} shows the $1\sigma$ constraints for the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data.
+The CFHTLenS survey is not sufficient to constrain $w$, but it does well in determining the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in agreement with values previously published by the CFHTLenS collaboration \citep{CFHTKilbinger}.
+
+%"using either of the MFs" changed to using the full descriptor set Morgan 2/16/2015
+
+Regarding the parameter biases, our results are in accordance with  \citep{PetriSpurious}, namely, that unaccounted systematics result in larger parameter biases when the constraints are derived from the MFs, and that the LM statistic is less biased.
+However, for the CFHTLenS data the MFs can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated (Figure \ref{likelihoodSi8single}).
+
+%MF constraints on Om, s8 are biased. However MFs can effectively constrain the non-degenerate direction, S8 for CFHTLenS
 
 We next studied whether the combination of different statistical descriptors can help in tightening the cosmological constraints; we show the effects of some of these combinations in Figures \ref{contours3combined} and \ref{likelihoodSi8cross}.
-The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, unfortunately this does not help in reducing the inherent parameter bias.
+The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, it does not help in reducing the inherent parameter bias.
 In the right panel of Figure \ref{contours3combined} we can see that even with these statistics combined, $w$ remains essentially unconstrained.
-Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained with the MFs alone, without the need of combining different descriptors.
+Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained by any of the descriptors alone, without the need of combining different descriptors.
 
@@
 \begin{itemize}
-\item When constraining the $(\Omega_m,\sigma_8)$ doublet with the CFHTLenS survey, we find that the Moments of the $\kappa$ field provide the tighest constraint on the former parameters; this constraint has also the advantage of being unbiased (further evidence in the unbiased nature of constraints from the Moments has been found in \citep{PetriSpurious}).
-We found that the biggest improvement on these parameter bounds is achieved when we include the quartic moments of gradients in the feature set; this improvement cannot be obtained by combining one--point moments at different smoothing scales
-\item Although weak lensing surveys are a promising technique to constrain the DE equation of state $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.
-\item When studying the cosmological information contained in the CFHTLenS data, one must pay special attention to the correction of residual systematics; while it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected for to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
-\item The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
+\item We find that the Moments of the $\kappa$ field provide the tightest constraint on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS survey data.
+Evidence of the unbiased nature of constraints from the Moments has been found in \citep{PetriSpurious}.
+We find that the biggest improvement in bounds on these parameter is achieved when we include the quartic moments of gradients in the feature set.
+This improvement cannot be obtained by combining one-point moments at different smoothing scales
+\item Although weak lensing surveys are a promising technique to constrain the DE equation of state parameter $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.
+\item When studying the cosmological information contained in the CFHTLenS data, special attention must be paid to the effect of residual systematic biases.
+While it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
+\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
 Some tensions with Planck \citep{PlanckXVI2013} still remain.
@@
 
-Possible future developments of this work include simulating higher dimensional parameter spaces (possibly including varying Hubble parameter $H_0$ and the running of the DE equation of state $w_1$), and combining constraints from different cosmological probes (data from Planck for example), that can help in breaking the $\Omega_m,\sigma_8$ degeneracy.
+Possible future extensions of this work include simulating higher dimensional parameter spaces (possibly including varying Hubble parameter $H_0$ and the running of the DE equation of state $w_1$), and combining constraints from different cosmological probes (data from Planck for example), that can help in breaking the $\Omega_m,\sigma_8$ degeneracy, and application of our analysis to larger survey data sets.
 

### 2015-02-17 Paper_minkowski/Figures/generate.py

@@ -23,7 +23,7 @@ design_points = "/Users/andreapetri/Documents/Cosmology_software/LensTools/lenst
 brew_colors = ["red","green","blue","black","orange","magenta","cyan"]
 brew_colors_11 = ["#a50026","#d73027","#f46d43","#fdae61","#fee08b","#ffffbf","#d9ef8b","#a6d96a","#66bd63","#1a9850","#006837"]
 brew_colors_diverging = ["#a6cee3","#1f78b4","#b2df8a","#33a02c","#fb9a99","#e31a1c","#fdbf6f","#ff7f00","#cab2d6","#6a3d9a","#ffff99","#b15928"]
-brew_colors_moments = ["black","#bdbdbd","#636363","green","#e34a33","#b30000","#74a9cf","#2b8cbe","yellow"]
+brew_colors_moments = ["black","green","#e34a33","#b30000","#74a9cf","#2b8cbe","yellow"]
 
 #Descriptor list
 descriptors=dict()
@@ -58,7 +58,7 @@ smoothing_scales["minkowski_0"] = 1.0
 smoothing_scales["minkowski_1"] = 1.0
 smoothing_scales["minkowski_2"] = 1.0 
 smoothing_scales["moments"] = 1.0
-smoothing_scales["moments_q1_s1_k1"] = "1.0+[1.0,1.8]+[1.0,1.8,3.5]"
+smoothing_scales["moments_q1_s1_k1"] = 1.0
 smoothing_scales["moments_q12_s1_k1"]=1.0
 smoothing_scales["moments_q12_s12_k1"]=1.0
 smoothing_scales["moments_q12_s1"]=1.0
@@ -317,7 +317,7 @@ def robustness_reparametrize(cmd_args):
 ##################################################################################################################################################
 ##################################################################################################################################################
 
-def contours_combine(cmd_args,descriptors_in_plot=["power_spectrum"]+multiple,parameter_axes={"Omega_m":0,"w":1,"sigma8":2},cosmo_labels={"Omega_m":r"$\Omega_m$","w":r"$w$","sigma8":r"$\sigma_8$"},select="w",marginalize_over="me",mock=False,cross_label="cross"):
[…]

### 2015-02-26 Paper_minkowski/paper.tex
new updates on paper

@@
 \begin{abstract}
-Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the Dark Energy (DE) equation of state $w$; since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
-In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ derived from weak lensing Minkowski Functionals and Moments, using publicly available data from the 154\,deg$^2$ CFHTLenS survey.
+Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the dark energy (DE) equation of state $w$; since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
+In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ derived from weak lensing Minkowski functionals and moments, using publicly available data from the 154\,deg$^2$ CFHTLenS survey.
 We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise in the CFHTLenS catalogs.
-We then build an emulator that interpolates the simulated feature spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
+We then build an emulator that interpolates the simulated descriptor spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
 We find that the dimensionality reduction technique Principal Component Analysis helps in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
-Using our full set of statistical descriptors, we constrain $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ at the $1\sigma$ significance level, well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski Functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the Moments provide a tight unbiased bound on the parameters, with a substantial contribution coming from quartic moments of gradients.
+Using our full set of statistical descriptors, we constrain $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ ($1\sigma$), well in agreement with the values already quoted in the literature.
+We find that, while the Minkowski functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the moments provide a tight unbiased bound on the parameters, with a substantial contribution coming from quartic moments of gradients.
 
@@
 Next, we give a description of our simulation pipeline, including the procedure used to sample the parameter space and outline the ray--tracing algorithm.
-We call the weak lensing statistical observables - the Power Spectrum, Minkowski Functionals and Moments - "descriptors" or "features" interchangeably throughout the paper.
+We call the weak lensing statistical observables - the Power Spectrum, Minkowski Functionals and Moments - "descriptors" throughout the paper.
 We discuss the calculation of the statistical descriptors, the dimensional reduction method, and the statistical inference framework used.
-We then outline our results, and the the cosmological parameter constraints obtained.
+We then outline our results, and the cosmological parameter constraints obtained.
 To conclude, we discuss our findings and comment on possible future extensions of this analysis.
 
-% "descriptors" or "features" are used interchangeably throughout the paper. It may be sufficient to state this here, but it might be clearer to use only "descriptors" Morgan 2/16/2015
+% "features" or "descriptors" are used interchangeably throughout the paper. It may be sufficient to state this here, but it might be clearer to use only "descriptors" Morgan 2/16/2015
 
@@
 The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data consist of a galaxy catalog created using SExtractor \citep{SExtractor}, a photometric redshift estimated with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements made using \textit{lensfit} \citep{cfht1,cfht2}.
-The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF; additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using the skewness as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
-We apply the following cuts to the galaxy catalog: mask$<1$, redshift $0.2 < z < 1.3$, fitclass = 0 (which requires the object to be a galaxy) and weight $w>0$ (with larger $w$ indicating smaller shear measurement uncertainty).
+The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF; additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using three--point correlations as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
+The cosmological constraints obtained in this work are based on an irregular--grid sampling of the parameter space, which is an improvement on the Fisher matrix formalism adopted by \citep{CFHTMasato}.
+
+We apply the following cuts to the galaxy catalog: mask$<1$ (see Table B2 in \citep{SExtractor}), redshift $0.2 < z < 1.3$ (see \citep{cfht1}), fitclass = 0 (which requires the object to be a galaxy) and weight $\mathrm{w}>0$ (with larger $\mathrm{w}$ indicating smaller shear measurement uncertainty).
 Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ sky coverage, and average galaxy density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
@@
 These spurious correlations are likely due to imperfect PSF removal, and do not contain cosmological signal.
+These cuts are consistent with the ones adopted by the CFHTLenS collaboration (see \citep{CFHTFu}).
 The CFHTLenS galaxy catalog provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}), m(\pmb{\theta})$.
@@
 \begin{equation}
-\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)w(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)w(\pmb{\theta}_i)[1+m(\pmb{\theta})]}
+\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[1+m(\pmb{\theta})]}
 \end{equation} 
@@
 %
-where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests); the multiplicative and additive corrections $m,c$ relate the observed and true ellipticities of the galaxies in the catalog
-\begin{equation}
-\mathbf{e}^{obs} = (1+m)\mathbf{e}^{true} + c
-\end{equation}
-%
+where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests) and $m,c$ refer to the multiplicative and additive corrections of the galaxies in the catalog.
 Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we can perform a non--local Kaiser--Squires inversion \citep{KS} to recover the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear field
@@
 %
-The CFHTLenS catalogs contain masked regions ( rejected fields, regions around bright stars etc.).
-We first create gridded maps of the same size and resolution as the $\kappa$ maps, but with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
+The $\kappa$ maps we consider are $12\mathrm{deg}^2$ in size and have a resolution of $512\times512$ pixel.
+The CFHTLenS catalogs contain masked regions (among which rejected fields and regions around bright stars).
+We first create gridded maps of the same size and resolution of the $\kappa$ maps, with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
 We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}).
@@
 \label{costfunction}
-d(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}
+\mathcal{C}(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}
 \end{equation} 
@@
 
-$x_i^d\equiv i/(N-1)$
+$x_i^d\equiv i/(N-1)$ for $d=1...D$
 \item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$ where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$
@@
 %
+%AP: Inspector Gadget was never published
+%
 \begin{equation}
@@
 Where $A$ is the total area of the fields of view and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences.
-The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, $\partial V_0$ (which can be obtained by differentiation $\partial V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$), while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
-In addition to these topological descriptors, we consider a set of low order moments (LM) of the convergence field (two quadratic, three cubic and four quartic), which are defined in the following way
+The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
+The one--point PDF of the $\kappa$ field, $\partial V_0$, can be obtained by differentiation $\partial V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$.
+In addition to these topological descriptors, we consider a set of low order moments (LM) of the convergence field (two quadratic, three cubic and four quartic).
+We choose these moments to be the minimal set of LM necessary to build a perturbative expansion of the MF up to $O(\sigma_0^2)$ (see \citep{Munshi12,Matsubara10}).
+We adopt the following definitions
 %
@@
 
-If the $\kappa$ field were Gaussian, one could express all the Minkowski Functionals in terms of the LM$_2$ moments, as expected from the fact that, for a Gaussian field, the only meaningful statistics are the quadratic ones.
+If the $\kappa$ field were Gaussian, one could express all the Minkowski Functionals in terms of the LM$_2$ moments, as expected from the fact that, for a Gaussian field, the only non--trivial statistics are the quadratic ones.
 In reality, weak lensing convergence fields are non--Gaussian and the MF and LM descriptors are not guaranteed to be equivalent.
@@
 Because of this, throughout this work, we treat MF and LM as separate statistical descriptors.
-The LM we consider are restricted to the ones that appear in the perturbative expansion of the Minkowski functionals.
-The LM$_4$ moments which include derivatives of the $\kappa$ field ($K_{1,2,3}$) each emphasize a different set of trispectrum quadrilateral shapes.
-For example, $K_2$ emphasizes shapes where one side of the quadrilateral is large and $K_4$ emphasizes shapes close to rectangular.
+
+The LM that contain gradients are sensitive to different shapes of the $\kappa$ multispectra $P_{\kappa}^n(\mathbf{l}_1,...,\mathbf{l}_n)$ because a particular $\mathrm{LM}_n$ has the general form
+%
+\begin{equation}
+\mathrm{LM}_n = \int d\mathbf{l}_1...d\mathbf{l}_n \rho(\mathbf{l}_{1...n})P^n_{\kappa}(\mathbf{l}_{1...n})
+\end{equation}
+%
+where $\rho$ is a polynomial of order $n$ in the $\mathbf{l}$'s.
+For example for $K_2$ we have $\rho(\mathbf{l}_{1234})=l_4^2$ and this moment emphasizes quadrilateral shapes in which where one sides is much larger than the others.
+On the other hand, for $K_4$ we have $\rho(\mathbf{l}_{1234})=(\mathbf{l}_1\cdot\mathbf{l}_2)(\mathbf{l}_3\cdot\mathbf{l}_4)$ and this moment is most sensitive to trispectrum shapes that are close to rectangular.
 There are other moments which include derivatives besides the ones we have considered.
@@
 
-In addition to the MF and LM descriptors, we consider the $\kappa$ angular power spectrum $P_l$ defined as
+In addition to the MF and LM descriptors, we consider the $\kappa$ angular power spectrum $P_l\equiv P^2_l$ defined as
 \begin{equation}
@@
 where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function.
-While the use of this statistic is not a novelty, we want to compare the results we get using MF and LM to ones already present in the literature which are based on the power spectrum.
+While the use of this statistic is not a novelty, we want to compare the results we get using MF and LM to ones already present in the literature which are based on the use of quadratic statistics (see for example \citep{CFHTKilbinger}).
 A summary of the statistical descriptors used is presented in Table \ref{desctable}.
@@
 
-When measuring statistical features on $\kappa$ maps, particular attention must be given to the effect of masked pixels.
+When measuring statistical descriptors on $\kappa$ maps, particular attention must be given to the effect of masked pixels.
 This does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with the exception of the few pixels that are close to the mask boundaries.
-Masking effects on Minkowski Functionals constraints with CFHTLenS have been studies extensively by \citep{CFHTMasato}.
+Masking effects on Minkowski Functionals constraints with CFHTLenS have been studied extensively by \citep{CFHTMasato}.
 The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier transforms and hence rely on the value of every pixel in the map.
@@
 %AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki 
+%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and Moments are well defined also in the presence of masked pixels, while the PS estimator is not
 
@@
 %
-
+We assume that the covariance matrix $\mathbf{C}$ that appears in (\ref{datalikelihood}) is $\mathbf{p}$--independent and coincides with $\mathbf{C}(\mathbf{p}_0)$.
+For this reason, the normalization constant in (\ref{datalikelihood}) is also model--independent.
 The simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
@@
 %
-is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$ and is assumed to be model-independent.
-Thus the normalization constant in (\ref{datalikelihood}) is also model--independent.
-When computing parameter constraints from CFHTLenS weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.
+is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$.
+We should mention that, while (\ref{datacov}) is an unbiased estimator of the covariance matrix, its inverse is not an unbiased estimator of $\mathbf{C}^{-1}$ as seen in \citep{RayTracingHartlap}.
+Given that in our case $R\gg N_b$, we can safely neglect the correction factor needed to make the estimator for $\mathbf{C}^{-1}$ unbiased.
+
+When computing parameter constraints from CFHTLenS weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$ and we reserve the possibility of a more general prior for future work.
 Parameter inferences are made estimating the location of the maximum of the parameter likelihood in (\ref{parameterlikelihood}), which we call $\mathbf{p}_{ML}(D_i)$ as well as its confidence contours.
@@
 
-Given the low dimensionality of the parameter space we consider $(N_p=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on a finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$, and hence we are able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.
-We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M_(\mathbf{p})$ to an arbitrary intermediate point.
+Using equation (\ref{rbfinterpolation}) and given the low dimensionality of the parameter space we consider $(D=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on $100^3$ different combinations of the cosmological parameters $p$, arranged in finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$.
+We are hence able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.
+We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation irregular grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M(\mathbf{p})$ to an arbitrary intermediate point.
 We use a Radial Basis Function (RBF) interpolation scheme.
@@
 \begin{equation}
+\label{rbfinterpolation}
 M(\mathbf{p}) = \sum_{s=1}^N \lambda_s\phi(\vert\mathbf{p}-\mathbf{p}_s\vert)
@@
 The constant coefficients $\lambda_s$ can be determined imposing the $N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which enforce the fact that the interpolation should be exact at the simulated points.
-The interpolation computations are conveniently performed using the Scipy library \citep{scipy}.
+The interpolation computations are conveniently performed using the \texttt{interpolate.Rbf} routine contained in Scipy library \citep{scipy}.
 
-We studied the accuracy of emulator, built with the CFHTemu1 simulations, by interpolating the convergence features to the fiducial parameter setting $(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to the one expected from the CFHTcov simulations.
+We studied the accuracy of emulator, built with the CFHTemu1 simulations, by interpolating the convergence descriptors to the fiducial parameter setting $(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to the one expected from the CFHTcov simulations.
 Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator has accuracy better than 10\% for the lower multipoles and comparable to 1\% for the higher multipoles.
@@
 \end{center}
-\caption{Accuracy of the emulator based on the CFHTemu1 simulations: we show the difference between the interpolated feature at the fiducial parameter setting and the expected feature from the CFHTcov simulations, in units of the standard deviation in each bin $i$ (determined from the diagonal elements of the CFHTcov covariance matrix).
+\caption{Accuracy of the emulator based on the CFHTemu1 simulations: we show the difference between the interpolated descriptor at the fiducial parameter setting and the expected descriptor from the CFHTcov simulations, in units of the standard deviation in each bin $i$ (determined from the diagonal elements of the CFHTcov covariance matrix).
 We show the accuracy results for the Power Spectrum (red) and Minkowski Functionals $V_0$ (green), $V_1$ (blue) and $V_2$ (black).}
@@
 It is known that the choice of the number of bins, $N_b$, can have a non-negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
-Our main physical motivation for this approach is that, albeit we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular feature) is contained in a limited number of linear combinations of its binning.
+Our main physical motivation for this approach is that, even though we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular descriptor) is contained in a limited number of linear combinations of its binning.
 In the framework adopted by \citep{coyote2}, for example, the authors find that the majority of the cosmological information in the matter Power Spectrum is contained in only 5 selected linear combinations of the multipoles.
-Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering constraints that are independent on the number of bins $N_b$ originally chosen.
+Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering accurate cosmological constraints using only a limited number of descriptor degrees of freedom.
 
-In order to compute the Principal Components of our feature space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
+In order to compute the Principal Components of our descriptor space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
 Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$, defined by subtracting the mean in each bin, and normalizing it by its variance.
@@
 %
-where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $i$--th principal component of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
+where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $j$--th coordinate ($j=1...N_b$) of $i$--th principal component ($i=1...\mathrm{min}(N_b,N)$) of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
+By construction, $\mathbf{V}$ is $\mathbf{p}$--independent.
 
-To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\mathbf{S}^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the feature covariance in (\ref{datacov}))
+To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\mathbf{S}^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the descriptor covariance in (\ref{datacov}))
 \begin{equation}
@@
 We expect our constraints to be stable with respect to the number of components, once enough components have been included.
-Using the fact that different Principal Components are orthogonal, we perform a PCA projection on our feature space by whitening the features and computing the dot product with the principal components, keeping only the first $n$ components
+Using the fact that different Principal Components are orthogonal, we perform a PCA projection on our descriptor space by whitening the descriptors and computing the dot product with the principal components, keeping only the first $n$ components
 \begin{equation}
@@
 %
-where we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows.
+where we suppressed the first index of $M(n)$ for notational simplicity and we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows (i.e.
+$i$ can now range from $1$ to $n$).
 The dimensionality reduction comes from the fact that we expect most of the cosmological information to be contained in a number of components $n<N_{b}$.
+We will describe in detail below the choice we make for $n$, and how our results are sensitive to it.
 
-Looking at the dimensionality issue from a more geometric perspective, we expect our feature space to be a 3-dimensional manifold embedded in a $N_b$--dimensional space.
-The dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this feature manifold.
-As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat feature manifolds.
+Looking at the dimensionality issue from a more geometric perspective, we expect our descriptor space to be a 3-dimensional manifold embedded in a $N_b$--dimensional space.
+The dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this descriptor manifold.
+As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat descriptor manifolds.
 When curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
@@
 \includegraphics[scale=0.4]{Figures/pca_components.eps}
-\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) feature spaces; the left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
-A dashed black line has been drawn in correspondence of $n=3$ components}
+\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) descriptor spaces; the left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
+A dashed black line has been drawn corresponding to $n=3$ components}
 \label{pcafig}
 \end{figure*}
+%
+%AP: 3 is the dimensionality of our parameter space which may, or may not tell us something about the number of principal components
 %
@@
 We then show the cosmological constraints from the CFHTLenS data.
-Because of the relatively small size of this survey, degeneracy in the parameters can have undesired effect on the constraints.
+Because of the relatively small size of this survey, degeneracy in the parameters can have undesirable effect on the constraints.
 To mitigate the effect of degeneracies, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8(\alpha)=\sigma_8(\Omega_m/0.27)^\alpha$.
@@
 %
+The cosmological constraints should in principle be insensitive to $N_b$, but an inaccurate covariance (due to a limited number of realizations) can introduce a $N_b$ dependence.
 Here we give evidence that the cosmological constraints derived in this paper are numerically robust, i.e.
 they are reasonably stable once we consider a large enough number $n$ of Principal Components.
-Figure \ref{pcafig} shows the PCA eigenvalues that result from the SVD decomposition of our feature spaces, as well as the cumulative sum of these eigenvalues, normalized to 1.
+Figure \ref{pcafig} shows the PCA eigenvalues that result from the SVD decomposition of our descriptor spaces, as well as the cumulative sum of these eigenvalues, normalized to 1.
 Figure \ref{robustnessfig} shows the dependence of the $(\Omega_m,\sigma_8)$ constraints on the number of principal components $n$, and clearly indicates that we only need a limited number of components in order to capture the cosmological information contained in our descriptors.
@@
 \subsection{Combining statistics}
-Combinating of different statistics can tighten the constraints on cosmology.
+Combining of different statistics can tighten the constraints on cosmology.
 Previous work in this direction includes \citep{Companion}, where the authors combine the power spectrum and peak count statistics and  \citep{CFHTFu} where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
@@
 We compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ needed for the constraints to be stable.
-We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined feature vector.
+We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined descriptor vector.
 This procedure allows us to take the cross covariance between different descriptors.
+An analogous procedure can be used to combine multiple descriptors.
 We show in Figure \ref{contours3combined} the combined CFHTLenS constraints in the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
@@
 As pointed out in \S~\ref{pcasection}, the choice of the number of bins, $N_b$, is an important issue.
-In order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our feature spaces.
-In the left panel of Figure \ref{pcafig} we see that the PCA eigenvalues for our descriptors decrease about 4 orders of magnitude from $n=1$ to $n=3$, and looking at the right panel we see that we capture more than 99\%  of the feature variance even if we cut the PCA projection to the first 3 components.
+In order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our descriptor spaces.
+In the left panel of Figure \ref{pcafig} we see that the PCA eigenvalues for our descriptors decrease about 4 orders of magnitude from $n=1$ to $n=3$, and looking at the right panel we see that we capture more than 99\%  of the descriptor variance even if we cut the PCA projection to the first 3 components.
 
@@
 In Figure \ref{contours3single} we show the $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data.
-The MF constraints are heavily biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
+The MF constraints appear to be biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
+Here and throughout the rest of the paper, we refer to "biased"("unbiased") as a best fit which is incompatible(compatible) with the accepted fiducial values at $1\sigma$.
 The best current values of $(\Omega_m,\sigma_8)$  \citep{PlanckXVI2013} lie beyond the 99\% likelihood contours (not shown).
@@
 In order to determine the origin of the tight bounds derived from moments, we studied the individual contributions of each of the moments to the constraining power.
-Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higher order moments to the feature set.
+Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higher order moments to the descriptor set.
 Since we are constraining  3 cosmological parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then add the remaining six moments of gradients one by one, starting from the quadratic moments.
 We see that the biggest improvement on the parameter bounds comes from including quartic moments of gradients (i.e.
-$K_i$ with $i\ge1$) in the feature set.
+$K_i$ with $i\ge1$) in the descriptor set.
 This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding the skewness to quadratic statistics, since the main improvement comes from higher moments of $\kappa$ derivatives.
 Our result agrees with  \citep{moments4}  which found that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
+We show that considering quartic moments of gradients further helps in breaking this degeneracy.
 We also observe that the improvement obtained by combining the one--point moments at different smoothing scales $\theta_G$, is not as large as that obtained by considering the moments of gradients.
@@
 To mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non-degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-Figure \ref{likelihoodSi8single} shows the $1\sigma$ constraints for the $(w,\Sigma_8)$ doublet, as well as the marginalized $\Sigma_8$ likelihood from the CFHTLenS data.
+Figure \ref{contours3singleRep} shows the $1\sigma$ constraints for the $(w,\Sigma_8)$ doublet, while Figure \ref{likelihoodSi8single} the marginalized $\Sigma_8$ likelihood from the CFHTLenS data.
 The CFHTLenS survey is not sufficient to constrain $w$, but it does well in determining the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in agreement with values previously published by the CFHTLenS collaboration \citep{CFHTKilbinger}.
@@
 \begin{itemize}
-\item We find that the Moments of the $\kappa$ field provide the tightest constraint on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS survey data.
+\item We find that the Power Spectrum combined with the Moments of the $\kappa$ field provides the tightest constraint on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS survey data.
+The tightness of these constraints comes mainly from the moments.
 Evidence of the unbiased nature of constraints from the Moments has been found in \citep{PetriSpurious}.
-We find that the biggest improvement in bounds on these parameter is achieved when we include the quartic moments of gradients in the feature set.
+We find that the biggest improvement in bounds on these parameter is achieved when we include the quartic moments of gradients in the descriptor set.
 This improvement cannot be obtained by combining one-point moments at different smoothing scales
@@
 While it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
-\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski Functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
+\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
 Some tensions with Planck \citep{PlanckXVI2013} still remain.
@@
 DE-AC02-98CH10886 and Contract No.
-DE-SC0012704.
+DE-SC0012704, and by the NSF Grant No.
+AST-1210877 (to Z.H.) and by the Research Opportunities and Approaches to Data Science (ROADS) program at the Institute for Data Sciences and Engineering at Columbia University.
 

### 2015-02-26 Paper_minkowski/Figures/generate.py

@@ -139,10 +139,17 @@ def emulatorAccuracy(cmd_args,descriptors_in_plot=single[:-1]):
 
 		ax.plot(np.abs(measured-predicted)/np.sqrt(covariance.diagonal()),color=brew_colors[n],label=descriptors[descr])
 
+		#Plot also the predicted descriptors in another cosmology
+		emulator = LikelihoodAnalysis.load(os.path.join(root_dir,"emulators","emulator_{0}--{1:.1f}.p".format(descr,smoothing_scale)))
+		predictedOther = emulator.predict(np.array([0.8,-1.0,0.5]))
+
+		ax.plot(np.abs(measured-predictedOther)/np.sqrt(covariance.diagonal()),color=brew_colors[n],linestyle="--")
+
 	#Plot labels
 	ax.set_xlabel(r"$i$",fontsize=22)
 	ax.set_ylabel(r"$(E-M)/\sqrt{C_{MM}}$",fontsize=22)
 	ax.set_yscale("log")
+	ax.set_ylim(1.0e-3,10.0)
 	ax.legend(loc="lower left")
 
 	#Save the figure

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -21,7 +21,7 @@ mask_arr =  array([WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask
 def createPDF(sfr):
 	sf, r = sfr
 	print sf, r
-	y, x, e1, e2, w, m = yxewm_arr [Wx-1]
+	y, x, e1, e2, w, m = yxewm_arr [sf-1]
 	kappa = KSgen(r, sf).T[0]
 	kmap, galn = WLanalysis.coords2grid(x, y, array([kappa,]))
 	kmap_smooth = WLanalysis.weighted_smooth(kmap, galn, sigmaG=1.0)

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -14,9 +14,9 @@ cosmo = 'cfhtcov-512b240_Om0.260_Ol0.740_w-1.000_ns0.960_si0.800'
 
 KSgen = lambda r, sf: WLanalysis.readFits('/scratch/02977/jialiu/cat/%s/emulator_subfield%i_WL-only_%s_4096xy_%04dr.fit'%(cosmo, sf, cosmo, r))
 
-yxewm_arr = array([ WLanalysis.readFits('/home1/02977/jialiu/KSsim/yxewm_subfield%i_zcut0213.fit'%(sf)).T] for sf in range(1,14))
+yxewm_arr = array([ WLanalysis.readFits('/home1/02977/jialiu/KSsim/yxewm_subfield%i_zcut0213.fit'%(sf)).T for sf in range(1,14)])
 
-mask_arr =  array([WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask_ngal5_sigma10_subfield%02d.fits'%(sf))] for sf in range(1,14))
+mask_arr =  array([WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask_ngal5_sigma10_subfield%02d.fits'%(sf)) for sf in range(1,14)])
 
 def createPDF(sfr):
 	sf, r = sfr

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -32,7 +32,7 @@ def createPDF(sfr):
 	return PDF_normed
 
 pool = MPIPool()
-PDF_arr = pool.map(createPDF, [[sf, r] for sf in arange(1,14) for r in arange(1,1001)])
+PDF_arr = array(pool.map(createPDF, [[sf, r] for sf in arange(1,14) for r in arange(1,1001)]))
 #np.save('/home1/02977/jialiu/KSsim/PDF_noiseless/PDF_noiseless_50bins_sf%i_%s.npy'%(sf, cosmo), PDF_arr)
 PDF_reshaped = PDF_arr.reshape(13, 1000, 50)
 fsky_all = array([0.839298248291,0.865875244141,0.809467315674,

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -41,7 +41,7 @@ fsky_all = array([0.839298248291,0.865875244141,0.809467315674,
 		  0.761451721191,0.691867828369,0.711254119873,
 		  0.745429992676])
 
-PDF_sum = sum(fsky_all.reshape(-1,1,1)*all_PDF,axis=0)/sum(fsky_all)
+PDF_sum = sum(fsky_all.reshape(-1,1,1)*PDF_reshaped,axis=0)/sum(fsky_all)
 
 save('PDF_noiseless_%s.npy'%(cosmo), PDF_sum)
 print 'done done done'

### 2015-03-03 jia/batch_filegen.py
regular update

@@ -1,0 +1,23 @@
+#!python
+N = 1
+n = N*16
+def write_file(errfn, program_name, variable):
+	f = open('/home1/02977/jialiu/batch/batch_{0}_{1}'.format(errfn, variable), 'w')
+	content = 	'''#!/bin/bash
+	#SBATCH -J {0}{2}    # Job name
+	#SBATCH -o {0}{2}.e%j # Name of stdout output file
+	#SBATCH -e {0}{2}.e%j # Name of stderr output file
+	#SBATCH -p normal       # Submit to the 'normal' or 'development' queue
+	#SBATCH -N {3}           # Total number of nodes requested (16 cores/node)
+	#SBATCH -n {4}           # Total number of mpi tasks requested
+	#SBATCH -t 0:30:00      # Run time (hh:mm:ss)
+	#SBATCH -A TG-AST140041
+
+	ibrun python /home1/02977/jialiu/CFHTLens_analysis/jia/{1} {2}'''.format(errfn, program_name, variable, N, n)
+	f.write(content)
+	f.close()
+
+errfn = 'noiselessPDF'
+program_name = 'stampede_noiseless_PDF.py'
+for variable in range(1,14):
+	write_file(errfn, program_name, variable)

### 2015-03-03 jia/batch_filegen.py
regular update

@@ -3,17 +3,17 @@ N = 1
 n = N*16
 def write_file(errfn, program_name, variable):
 	f = open('/home1/02977/jialiu/batch/batch_{0}_{1}'.format(errfn, variable), 'w')
-	content = 	'''#!/bin/bash
-	#SBATCH -J {0}{2}    # Job name
-	#SBATCH -o {0}{2}.e%j # Name of stdout output file
-	#SBATCH -e {0}{2}.e%j # Name of stderr output file
-	#SBATCH -p normal       # Submit to the 'normal' or 'development' queue
-	#SBATCH -N {3}           # Total number of nodes requested (16 cores/node)
-	#SBATCH -n {4}           # Total number of mpi tasks requested
-	#SBATCH -t 0:30:00      # Run time (hh:mm:ss)
-	#SBATCH -A TG-AST140041
+	content = '''#!/bin/bash
+#SBATCH -J {0}{2}    # Job name
+#SBATCH -o {0}{2}.e%j # Name of stdout output file
+#SBATCH -e {0}{2}.e%j # Name of stderr output file
+#SBATCH -p normal       # Submit to the 'normal' or 'development' queue
+#SBATCH -N {3}           # Total number of nodes requested (16 cores/node)
+#SBATCH -n {4}           # Total number of mpi tasks requested
+#SBATCH -t 0:30:00      # Run time (hh:mm:ss)
+#SBATCH -A TG-AST140041
 
-	ibrun python /home1/02977/jialiu/CFHTLens_analysis/jia/{1} {2}'''.format(errfn, program_name, variable, N, n)
+ibrun python /home1/02977/jialiu/CFHTLens_analysis/jia/{1} {2}'''.format(errfn, program_name, variable, N, n)
 	f.write(content)
 	f.close()
 

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -4,7 +4,7 @@ import numpy as np
 from scipy import *
 from emcee.utils import MPIPool
 import sys
-#sf = int(sys.argv[1])
+sf = int(sys.argv[1])
 PPA512 = 2.4633625
 edges = linspace(-0.05,0.15,51)
 #cosmo = 'emu1-512b240_Om0.483_Ol0.517_w-1.515_ns0.960_si0.680'
@@ -12,36 +12,43 @@ cosmo = 'cfhtcov-512b240_Om0.260_Ol0.740_w-1.000_ns0.960_si0.800'
 
 #KSgen = lambda r: WLanalysis.readFits('/home1/02977/jialiu/cov_cat/emulator_subfield%i_WL-only_cfhtcov-512b240_Om0.260_Ol0.740_w-1.000_ns0.960_si0.800_4096xy_%04dr.fit'%(sf, r))
 
-KSgen = lambda r, sf: WLanalysis.readFits('/scratch/02977/jialiu/cat/%s/emulator_subfield%i_WL-only_%s_4096xy_%04dr.fit'%(cosmo, sf, cosmo, r))
+KSgen = lambda r: WLanalysis.readFits('/scratch/02977/jialiu/cat/%s/emulator_subfield%i_WL-only_%s_4096xy_%04dr.fit'%(cosmo, sf, cosmo, r))
 
-yxewm_arr = array([ WLanalysis.readFits('/home1/02977/jialiu/KSsim/yxewm_subfield%i_zcut0213.fit'%(sf)).T for sf in range(1,14)])
+#yxewm_arr = array([ WLanalysis.readFits('/home1/02977/jialiu/KSsim/yxewm_subfield%i_zcut0213.fit'%(sf)).T for sf in range(1,14)])
 
-mask_arr =  array([WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask_ngal5_sigma10_subfield%02d.fits'%(sf)) for sf in range(1,14)])
+#mask_arr =  array([WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask_ngal5_sigma10_subfield%02d.fits'%(sf)) for sf in range(1,14)])
 
-def createPDF(sfr):
-	sf, r = sfr
+#y, x, e1, e2, w, m = yxewm_arr [sf-1]
+
[…]

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -3,7 +3,7 @@ import WLanalysis
 import numpy as np
 from scipy import *
 from emcee.utils import MPIPool
-import sys
+import sys, os
 sf = int(sys.argv[1])
 PPA512 = 2.4633625
 edges = linspace(-0.05,0.15,51)

### 2015-03-03 jia/stampede_noiseless_PDF.py
regular update

@@ -26,7 +26,7 @@ mask = WLanalysis.readFits('/home1/02977/jialiu/KSsim/mask/CFHT_mask_ngal5_sigma
 
 def createPDF(r):
 	print sf, r
-	kappa = KSgen(r, sf).T[0]
+	kappa = KSgen(r).T[0]
 	kmap, galn = WLanalysis.coords2grid(x, y, array([kappa,]))
 	kmap_smooth = WLanalysis.weighted_smooth(kmap, galn, sigmaG=1.0)
 	all_kappa = kmap_smooth[where(mask>0)]

### 2015-03-03 Paper_minkowski/paper.tex
latest edits

@@
 \begin{abstract}
-Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the dark energy (DE) equation of state $w$; since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
+Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the dark energy (DE) equation of state $w$.
+Since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
 In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ derived from weak lensing Minkowski functionals and moments, using publicly available data from the 154\,deg$^2$ CFHTLenS survey.
@@
 Weak gravitational lensing is emerging as a promising technique to constrain cosmology.
-Techniques have been developed to construct cosmic shear fields with shape measurements in large galaxy catalogues; although the shear two--point function (2PCF) serves as a main cosmological probe (see \citep{CFHTKilbinger} for example), alternative statistics have been shown to increase the amount of cosmological information one can extract from weak lensing fields.
+Techniques have been developed to construct cosmic shear fields with shape measurements in large galaxy catalogues.
+Although the shear two--point function (2PCF) serves as a main cosmological probe (see \citep{CFHTKilbinger} for example), alternative statistics have been shown to increase the amount of cosmological information one can extract from weak lensing fields.
 Among these, higher moments (\citep{moments1,moments2,moments3,moments4,moments5,moments6}), three--point functions (\citep{3pcf1,3pcf2}), bispectra (\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts (\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski Functionals (\citep{MinkJan,Petri2013}) have shown to improve cosmological constraints in weak lensing analyses.
 In this work we use the publicly available CFHTLenS data, consisting of a catalog of $\approx$4.2 million galaxies, combined with a suite of ray-tracing simulations in 91 different cosmological models to constrain the cosmological parameters $\Omega_m$,$\sigma_8$ and the DE equation of state $w$.
-The paper is organized as follows; we first give an overview of the CFHTLenS catalogs, summarizing the data reduction techniques adopted.
+The paper is organized as follows: we first give an overview of the CFHTLenS catalogs, summarizing the data reduction techniques adopted.
 Next, we give a description of our simulation pipeline, including the procedure used to sample the parameter space and outline the ray--tracing algorithm.
@@
 %
-The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$; the publicly released data consist of a galaxy catalog created using SExtractor \citep{SExtractor}, a photometric redshift estimated with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements made using \textit{lensfit} \citep{cfht1,cfht2}.
-The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF; additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using three--point correlations as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
+The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$.
+The publicly released data consist of a galaxy catalog created using SExtractor \citep{SExtractor}, a photometric redshift estimated with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements made using \textit{lensfit} \citep{cfht1,cfht2}.
+The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF.
+Additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using three--point correlations as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
 The cosmological constraints obtained in this work are based on an irregular--grid sampling of the parameter space, which is an improvement on the Fisher matrix formalism adopted by \citep{CFHTMasato}.
@@
 The CFHTLenS galaxy catalog provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}), m(\pmb{\theta})$.
-Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps; these square subfield maps are pixelized according to a Gaussian gridding procedure
+Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps.
+These square subfield maps are pixelized according to a Gaussian gridding procedure
 
@@
 We wish to investigate the non--linear dependence of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7, 0.046, 0.96).
-We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}; the irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require a prohibitively large number of samples.
-We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side; we want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
+The irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require a prohibitively large number of samples.
+We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side.
+We want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
 Let a \textit{design} $\mathcal{D}$ be the set of this irregularly spaced $N$ points: we wish to find an optimal design, in which the points are spread as uniformly as possible inside the box.
@@
 %
-We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$; once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in Table \ref{designtable} and Figure \ref{designfig}.
+We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$.
+Once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in Table \ref{designtable} and Figure \ref{designfig}.
 %
@@
 \includegraphics[scale=0.4]{Figures/design.eps}
-\caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of our the simulation design; the blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
+\caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of our the simulation design.
+The blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
 \label{designfig}
@@
 %
-For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLenS shear catalogs; this set of simulations will be called CFHTemu1 throughout the rest of this work.
-Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will be used for the parameter inferences in \S-\ref{cosmostats}; this set of simulations will be called CFHTcov throughout the rest of this work.
+For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLenS shear catalogs: this set of simulations will be called CFHTemu1 throughout the rest of this work.
+Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will be used for the parameter inferences in \S-\ref{cosmostats}: this set of simulations will be called CFHTcov throughout the rest of this work.
 
@@
 \label{raysim}
-The goal of this section is to give an outline of our simulation pipeline; the fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays traveling from the source to the observer.
+The goal of this section is to give an outline of our simulation pipeline. 
+The fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays traveling from the source to the observer.
 The fluctuations in the matter field are described by the gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can replace the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
@@
 Suppose that a light ray reaches the observer at an angular position $\pmb{\theta}$ on the sky: we want to know where this light ray originated, knowing it comes from a redshift $z_s$.
-To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$; for the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
+To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$.
+For the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
 Once we know the details of the light ray trajectories, we can easily infer the interesting weak lensing  quantities by taking the angular derivatives of the ray deflections $A(\chi_s;\pmb{\theta}) = \partial \pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
@@
 \section{Statistical methods}
-The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$; we measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian framework in order to compute parameter confidence intervals.
+The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
+We measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian framework in order to compute parameter confidence intervals.
 
@@
 Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator has accuracy better than 10\% for the lower multipoles and comparable to 1\% for the higher multipoles.
-The Minkowski Functionals emulator has accuracy $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due to numerical noise for the remaining 20 bins; we take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
+The Minkowski Functionals emulator has accuracy $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due to numerical noise for the remaining 20 bins.
+We take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
+Nevertheless, we do not expect these inaccuracies to affect our conclusions as Figure \ref{emulatorAccuracy} clearly show that our emulator is able to distinguish a non--fiducial model from the fiducial one within numerical errors.
 
@@
 \caption{Accuracy of the emulator based on the CFHTemu1 simulations: we show the difference between the interpolated descriptor at the fiducial parameter setting and the expected descriptor from the CFHTcov simulations, in units of the standard deviation in each bin $i$ (determined from the diagonal elements of the CFHTcov covariance matrix).
-We show the accuracy results for the Power Spectrum (red) and Minkowski Functionals $V_0$ (green), $V_1$ (blue) and $V_2$ (black).}
+We show the accuracy results for the Power Spectrum (red) and Minkowski Functionals $V_0$ (green), $V_1$ (blue) and $V_2$ (black).
+We also show, using dashed lines, the difference between the expected CFHTcov descriptors and the interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$}
 \label{emulatorAccuracy}
@@
 When the question on the accuracy of the $N\sigma$ contours is considered, particular attention must be paid to the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
-It is known that the choice of the number of bins, $N_b$, can have a non-negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets); in order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
+It is known that the choice of the number of bins, $N_b$, can have a non-negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets).
+In order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
 Our main physical motivation for this approach is that, even though we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular descriptor) is contained in a limited number of linear combinations of its binning.
@@
 
-Looking at the dimensionality issue from a more geometric perspective, we expect our descriptor space to be a 3-dimensional manifold embedded in a $N_b$--dimensional space.
-The dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of this descriptor manifold.
+Looking at PCA from a geometrical perspective, the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of the descriptor manifold.
 As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat descriptor manifolds.
 When curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
-We have flexibility on the flatness assumption because we allow the number of principal components to be greater than 3.
 
@@
 \includegraphics[scale=0.4]{Figures/pca_components.eps}
-\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) descriptor spaces; the left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
+\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) descriptor spaces.
+The left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
 A dashed black line has been drawn corresponding to $n=3$ components}
@@
 \includegraphics[scale=0.4]{Figures/robustness_pca_Omega_m-sigma8.eps}
-\caption{PCA projection dependence of the $1\sigma$ contours in the $(\Omega_m,\sigma_8)$ plane obtained from a mock observation constructed with the CFHTcov simulations; the different panels refer to the descriptors (from left to right, top to bottom) $V_0$, $\partial V_0$(PDF), $V_1$, $V_2$, Power Spectrum and Moments}
+\caption{PCA projection dependence of the $1\sigma$ contours in the $(\Omega_m,\sigma_8)$ plane obtained from a mock observation constructed with the CFHTcov simulations.
+The different panels refer to the descriptors (from left to right, top to bottom) $V_0$, $\partial V_0$(PDF), $V_1$, $V_2$, Power Spectrum and Moments}
 \label{robustnessfig}
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data (left panel) and from a mock observation constructed using the mean of 1000 realizations in CFHTcov simulations as data (right panel).
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (green), $V_1$ (blue), $V_2$ (black) and Moments (orange) statistics.
+We show the constraints from the data (left panel) and from a mock observation constructed using the mean of 1000 realizations in CFHTcov simulations as data (right panel).
 The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $w$.
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(w,\Sigma_8)$ parameter doublet from the CFHTLenS data, obtained with the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; we show the constraints from the data.
+\caption{$1\sigma$ constraints on the $(w,\Sigma_8)$ parameter doublet from the CFHTLenS data, obtained with the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics.
+We show the constraints from the data.
 The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $\Omega_m$.
@@
 \end{center}
-\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics; the likelihood has been marginalized over $\Omega_m$ and $w$.
+\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics.
+The likelihood has been marginalized over $\Omega_m$ and $w$.
 The parentheses near the descriptor label refer to the number of principal components.}
@@
 \end{center}
-\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange); the likelihood function has been marginalized over $\Omega_m$ and $w$.
+\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange).
+The likelihood function has been marginalized over $\Omega_m$ and $w$.
 The parentheses near the descriptor label refer to the number of principal components.}
@@
 $K_i$ with $i\ge1$) in the descriptor set.
-This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding the skewness to quadratic statistics, since the main improvement comes from higher moments of $\kappa$ derivatives.
-Our result agrees with  \citep{moments4}  which found that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
+This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding three point correlations to quadratic statistics, since the main improvement comes from higher moments of $\kappa$ derivatives.
+\citep{CFHTFu} consider one--point third order moments where multiple smoothing scales are combined.
+Figure \ref{contoursMoments} however shows that smoothing scale combinations are not as effective as moments of gradients in costraining the $(\Omega_m,\sigma_8)$ doublet.
+Our results agree with  \citep{moments4}  which found that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
 We show that considering quartic moments of gradients further helps in breaking this degeneracy.
-We also observe that the improvement obtained by combining the one--point moments at different smoothing scales $\theta_G$, is not as large as that obtained by considering the moments of gradients.
 
@@
 Figure \ref{contours3singleRep} shows the $1\sigma$ constraints for the $(w,\Sigma_8)$ doublet, while Figure \ref{likelihoodSi8single} the marginalized $\Sigma_8$ likelihood from the CFHTLenS data.
-The CFHTLenS survey is not sufficient to constrain $w$, but it does well in determining the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in agreement with values previously published by the CFHTLenS collaboration \citep{CFHTKilbinger}.
+The CFHTLenS survey constrains the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in agreement with values previously published by the CFHTLenS collaboration \citep{CFHTKilbinger}.
+The current dataset is not sufficient to constrain $w$ to a reasonable precision, even if Figure \ref{contours3combined} right panel shows that the Moments are able to confine $w$ to isolated regions in parameter space.
+At the current stage of our analysis, $w=-1$ seems to be excluded at the $1\sigma$ level.
 
@@
 Regarding the parameter biases, our results are in accordance with  \citep{PetriSpurious}, namely, that unaccounted systematics result in larger parameter biases when the constraints are derived from the MFs, and that the LM statistic is less biased.
-However, for the CFHTLenS data the MFs can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated (Figure \ref{likelihoodSi8single}).
+However, for the CFHTLenS data the MFs can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$ (Figure \ref{likelihoodSi8single}).
 
@@
 
-We next studied whether the combination of different statistical descriptors can help in tightening the cosmological constraints; we show the effects of some of these combinations in Figures \ref{contours3combined} and \ref{likelihoodSi8cross}.
+We next studied whether the combination of different statistical descriptors can help in tightening the cosmological constraints.
+We show the effects of some of these combinations in Figures \ref{contours3combined} and \ref{likelihoodSi8cross}.
 The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, it does not help in reducing the inherent parameter bias.
@@
 While it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
-\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level; this agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
+\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level.
+This agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
 Some tensions with Planck \citep{PlanckXVI2013} still remain.

### 2015-03-19 Paper_minkowski/paper.tex
zoltan's version

@@
 
-\title{Moments and Minkowski Functionals constrain cosmology: applying a weak lensing emulator to CFHTLenS data}
+%ZH: changed title a bit
+\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from Moments and Minkowski Functionals}
 
@@
 
-%MM edited wording
-
+%ZH: I reworded the abstract
 \begin{abstract}
-Weak gravitational lensing is a potentially powerful probe for cosmology, and in particular for the dark energy (DE) equation of state $w$.
-Since typical weak lensing fields are non--Gaussian in nature, quadratic statistics, such as angular power spectra, can miss significant cosmological information contained in survey data.
-In this work we examine constraints on the parameter triplet $(\Omega_m,w,\sigma_8)$ derived from weak lensing Minkowski functionals and moments, using publicly available data from the 154\,deg$^2$ CFHTLenS survey.
-We utilize a new suite of ray--tracing N-body simulations spanning 91 points in the $(\Omega_m,w,\sigma_8)$ parameter space, replicating the galaxy sky positions, redshift and shape noise in the CFHTLenS catalogs.
-We then build an emulator that interpolates the simulated descriptor spaces, and use it to compute the parameter likelihood, from which we derive the data constraints.
-We find that the dimensionality reduction technique Principal Component Analysis helps in stabilizing the constraints with respect to the number of bins used to construct the convergence statistics.
-Using our full set of statistical descriptors, we constrain $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$ to a value of $0.75\pm0.04$ ($1\sigma$), well in agreement with the values already quoted in the literature.
-We find that, while the Minkowski functionals constraints on the $(\Omega_m,\sigma_8)$ doublet suffer from a bias, the moments provide a tight unbiased bound on the parameters, with a substantial contribution coming from quartic moments of gradients.
-
+Weak gravitational lensing is a powerful cosmological probe, with
+non--Gaussian features potentially containing the majority of the
+information. We examine constraints on the parameter triplet
+$(\Omega_m,w,\sigma_8)$ from non-Gaussian features of the weak lensing
+convergence field, including a set of moments (up to $4^{\rm th}$
+order) and Minkowski Functionals, using publicly available data from
+the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
+N-body simulations spanning 91 points in $(\Omega_m,w,\sigma_8)$
+parameter space, replicating the galaxy sky positions, redshifts and
+shape noise in the CFHTLenS catalogs. We then build an emulator that
+interpolates the simulated features as a function of
+$(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
+and parameter constraints. We employ a principal component analysis to
+reduce dimensionality and to help stabilize the constraints with
+respect to the number of bins used to construct each statistic. Using
+the full set of statistics, we find
+$\Sigma_8\equiv\sigma_8(\Omega_m/0.27)^{0.55}=0.75\pm0.04$ (68\%
+C.L.), in agreement with previous values. We find that constraints on
+the $(\Omega_m,\sigma_8)$ doublet from the Minkowski Functionals
+suffer a strong bias. However, high-order moments break the
+$(\Omega_m,\sigma_8)$ degeneracy and provide a tight constraint on
+these parameters with no apparent bias.  The main contribution comes
+from quartic moments of gradients.
 \end{abstract}
-
-%AP: Re-worded the abstract
 
@@
 
-Weak gravitational lensing is emerging as a promising technique to constrain cosmology.
-Techniques have been developed to construct cosmic shear fields with shape measurements in large galaxy catalogues.
-Although the shear two--point function (2PCF) serves as a main cosmological probe (see \citep{CFHTKilbinger} for example), alternative statistics have been shown to increase the amount of cosmological information one can extract from weak lensing fields.
-Among these, higher moments (\citep{moments1,moments2,moments3,moments4,moments5,moments6}), three--point functions (\citep{3pcf1,3pcf2}), bispectra (\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts (\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski Functionals (\citep{MinkJan,Petri2013}) have shown to improve cosmological constraints in weak lensing analyses.
-In this work we use the publicly available CFHTLenS data, consisting of a catalog of $\approx$4.2 million galaxies, combined with a suite of ray-tracing simulations in 91 different cosmological models to constrain the cosmological parameters $\Omega_m$,$\sigma_8$ and the DE equation of state $w$.
-The paper is organized as follows: we first give an overview of the CFHTLenS catalogs, summarizing the data reduction techniques adopted.
-Next, we give a description of our simulation pipeline, including the procedure used to sample the parameter space and outline the ray--tracing algorithm.
-We call the weak lensing statistical observables - the Power Spectrum, Minkowski Functionals and Moments - "descriptors" throughout the paper.
-We discuss the calculation of the statistical descriptors, the dimensional reduction method, and the statistical inference framework used.
-We then outline our results, and the cosmological parameter constraints obtained.
-To conclude, we discuss our findings and comment on possible future extensions of this analysis.
-
-% "features" or "descriptors" are used interchangeably throughout the paper. It may be sufficient to state this here, but it might be clearer to use only "descriptors" Morgan 2/16/2015
+Weak gravitational lensing (hereafter WL) is emerging as a promising
+technique to constrain cosmology. Techniques have been developed to
+construct cosmic shear fields with shape measurements in large galaxy
+catalogues. Although the shear two--point function (2PCF) is the most
+widely studied cosmological probe (see, e.g. \citep{CFHTKilbinger}),
+alternative statistics have been shown to increase the amount of
+cosmological information one can extract from weak lensing
+fields. Among these, high--order moments
+(\citep{moments1,moments2,moments3,moments4,moments5,moments6}),
+three--point functions (\citep{3pcf1,3pcf2}), bispectra
+(\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts
+(\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski
+Functionals (\citep{MinkJan,Petri2013}) have been shown to improve
+cosmological constraints in weak lensing analyses.
+
+In this work, we use the publicly available CFHTLenS data, consisting
+of a catalog of $\approx$4.2 million galaxies, combined with a suite
+of ray-tracing simulations in 91 different cosmological models to
+derive constraints on the cosmological parameters $\Omega_m$,
+$\sigma_8$ and the dark energy (DE) equation of state $w$.  The
+statistics we consider in this work are the Minkowski Functionals
+(MFs) and the low--order moments (LM) of the convergence field.
+%ZH: I moved this here from the simulation section. Fits better here.
+Cosmological parameter inferences from CFHTLenS have been obtained
+using the 2PCF~\citep{CFHTKilbinger}, and a number of authors have
+investigated the constraining power of CFHTLenS using statistics that
+go beyond the usual quadratic ones. Fu et al.~\citep{CFHTFu} used
+three--point correlations as an additional probe for cosmology, and
+found modest ($10-20\%$) improvements over the 2PCF.  Liu et
+al.~\citep{Companion} have found a more significant ($50-60\%$)
+tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
+abundance of WL peaks.
+%ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
+Finally, closest to the present paper, Shirasaki \&
+Yoshida~\citep{CFHTMasato} investigated constraints from Minkowski
+Functionals, including systematic errors.  Our study represents two
+major improvements over previous work.  First, constraints from the
+MFs in~ref.~\citep{CFHTMasato} were obtained through the Fisher matrix
+formalism, assuming linear dependence on cosmological parameters. Our
+study utilizes a suite of simulations sampling the cosmological
+parameter space, mapping out the non-linear parameter-dependence of
+each descriptor.  Second, we include the LMs as a set of new
+descriptors; these yield to the tightest and least biased constraints.
+
+This paper is organized as follows: we first give an overview of the
+CFHTLenS catalogs, and summarize the adopted data reduction
+techniques. Next, we give a description of our simulation pipeline,
+including the ray--tracing algorithm, and the procedure used to sample
+the parameter space. We call the statistical weak lensing observables
+-- the Power Spectrum, Minkowski Functionals, and Moments --
+"descriptors" throughout the paper. We discuss the calculation of the
+descriptors, including dimensional reduction using a principal
+component analysis, and the statistical inference framework we
+used. We then describe our main results, i.e. the cosmological
+parameter constraints. To conclude, we then discuss our findings and
+comment on possible future extensions of this analysis.
 
@@
 %
-The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23 deg$^2$ area, for a total of 154 deg$^2$.
-The publicly released data consist of a galaxy catalog created using SExtractor \citep{SExtractor}, a photometric redshift estimated with a Bayesian photometric redshift code \citep{PhotoCode} and galaxy shape measurements made using \textit{lensfit} \citep{cfht1,cfht2}.
-The cosmological parameter inferences have been obtained in \citep{CFHTKilbinger} using the 2PCF.
-Additionally a number of authors investigated the CFHTLenS constraining power using statistics that go beyond the usual quadratic ones: \citep{CFHTFu} investigated the effect of using three--point correlations as an additional probe for cosmology, while \citep{CFHTMasato} investigated CFHT cosmological constraints and systematic errors using the Minkowski Functionals.
-The cosmological constraints obtained in this work are based on an irregular--grid sampling of the parameter space, which is an improvement on the Fisher matrix formalism adopted by \citep{CFHTMasato}.
-
-We apply the following cuts to the galaxy catalog: mask$<1$ (see Table B2 in \citep{SExtractor}), redshift $0.2 < z < 1.3$ (see \citep{cfht1}), fitclass = 0 (which requires the object to be a galaxy) and weight $\mathrm{w}>0$ (with larger $\mathrm{w}$ indicating smaller shear measurement uncertainty).
-Applying these cuts leaves us 4.2$\times10^6$ galaxies, 124.7 deg$^2$ sky coverage, and average galaxy density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$.
-The catalog is further reduced by $\sim25\%$ when one rejects fields with non--negligible star--galaxy correlations.
-These spurious correlations are likely due to imperfect PSF removal, and do not contain cosmological signal.
-These cuts are consistent with the ones adopted by the CFHTLenS collaboration (see \citep{CFHTFu}).
-The CFHTLenS galaxy catalog provides us with the sky position $\pmb{\theta}$, the redshift $z(\pmb{\theta})$ and ellipticity $\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual weight factors $w(\pmb{\theta})$ and additive and multiplicative ellipticity corrections $c(\pmb{\theta}), m(\pmb{\theta})$.
-Because the CFHTLenS fields are irregularly shaped, we first divide them into 13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size of our simulated maps.
-These square subfield maps are pixelized according to a Gaussian gridding procedure
-
-%AP: added references and fixed typo. Is there a problem with the galaxy density I reported? (I took it from Jia's paper) 
-\begin{equation}
-\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[1+m(\pmb{\theta})]}
+
+%ZH: Added lead-in sentence, and moved the last sentence up here:
+In this section, we briefly summarize our treatment of the public
+CFHTLenS data.  For a more in--depth description of our data reduction
+procedure, we refer the reader to \citep{Companion}.
+
+The CFHTLenS survey covers four sky patches of 64, 23, 44 and 23
+deg$^2$ area, for a total of 154 deg$^2$. The publicly released data
+consist of a galaxy catalog created using SExtractor
+\citep{SExtractor}, and includes photometric redshifts estimated with
+a Bayesian photometric redshift code \citep{PhotoCode} and galaxy
+shape measurements using \textit{lensfit} \citep{cfht1,cfht2}.
+
+We apply the following cuts to the galaxy catalog: \texttt{mask} $<1$ (see
+Table B2 in \citep{SExtractor}), redshift $0.2 < z < 1.3$ (see
+\citep{cfht1}), \texttt{fitclass} = 0 (which requires the object to be a
+galaxy) and weight $\mathrm{w}>0$ (with larger $\mathrm{w}$ indicating
+smaller shear measurement uncertainty). Applying these cuts leaves us
+4.2$\times10^6$ galaxies, 124.7 deg$^2$ sky coverage, and average
+galaxy density $n_{gal} \approx 9.3\,\mathrm{arcmin}^{-2}$. The
+catalog is further reduced by $\sim25\%$ when one rejects fields with
+non--negligible star--galaxy correlations. These spurious correlations
+are likely due to imperfect PSF removal, and do not contain
+cosmological signal. These cuts are consistent with the ones adopted
+by the CFHTLenS collaboration (see \citep{CFHTFu}).
+
+The CFHTLenS galaxy catalog provides us with the sky position
+$\pmb{\theta}$, redshift $z(\pmb{\theta})$ and ellipticity
+$\mathbf{e}(\pmb{\theta})$ of each galaxy, as well as the individual
+weight factors $w(\pmb{\theta})$ and additive and multiplicative
+ellipticity corrections $c(\pmb{\theta}), m(\pmb{\theta})$. Because
+the CFHTLenS fields are irregularly shaped, we first divide them into
+13 squares (subfields) to match the shape and $\approx12$ deg$^2$ size
+of our simulated maps (see below). These square-shaped subfield maps
+are pixelized according to a Gaussian gridding procedure
+
+\begin{equation}
+\bar{\mathbf{e}}(\pmb{\theta}) = \frac{\sum_{i=1}^{N_s} W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[\mathbf{e}^{obs}(\pmb{\theta}_i)-c(\pmb{\theta}_i)]}{\sum_{i=1}^{N_s}W(\vert\pmb{\theta}-\pmb{\theta}_i\vert)\mathrm{w}(\pmb{\theta}_i)[1+m(\pmb{\theta})]},
 \end{equation} 
@@
 \label{gausskernel}
-W_{\theta_G}(\pmb{\theta}) = \frac{1}{2\pi\theta_G^2}\exp{\left(-\frac{\pmb{\theta}^2}{2\theta_G^2}\right)}
-\end{equation}
-%
-where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin (and occasionally varied to 1.8 and 3.5\,arcmin for isolated tests) and $m,c$ refer to the multiplicative and additive corrections of the galaxies in the catalog.
-Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we can perform a non--local Kaiser--Squires inversion \citep{KS} to recover the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear field
-%
-\begin{equation}
-\kappa(\mathbf{l}) = \left(\frac{l_1^2-l_2^2}{l_1^2+l_2^2}\right)\gamma^1(\mathbf{l}) + 2\frac{l_1l_2}{l_1^2+l_2^2}\gamma^2(\mathbf{l})
-\end{equation}
-%
-The $\kappa$ maps we consider are $12\mathrm{deg}^2$ in size and have a resolution of $512\times512$ pixel.
-The CFHTLenS catalogs contain masked regions (among which rejected fields and regions around bright stars).
-We first create gridded maps of the same size and resolution of the $\kappa$ maps, with each pixel containing the number of galaxies ($n_{gal}$) falling within its window.
-We then smooth this galaxy surface density map with the same Gaussian window function as equation (\ref{gausskernel}) and we remove regions where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see \citep{CFHTMasato}).
-Regions with low galaxy number density can induce large errors in the cosmological parameter inferences, hence they need to be removed.
-For a more in--depth description of our data reduction procedure, we refer the reader to \citep{Companion}.
-
-%AP: throughout --> in--depth
+W_{\theta_G}(\pmb{\theta}) = \frac{1}{2\pi\theta_G^2}\exp{\left(-\frac{\pmb{\theta}^2}{2\theta_G^2}\right)},
+\end{equation}
+%
+where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin
+(but varied occasionally to 1.8 and 3.5\,arcmin for specific tests
+described below) and $m,c$ refer to the multiplicative and additive
+corrections of the galaxies in the catalog.
+
+Using the ellipticity grid $\bar{\mathbf{e}}(\pmb{\theta})$ as an
+estimator for the cosmic shear $\gamma^{1,2}(\pmb{\theta})$, we
+perform a non--local Kaiser--Squires inversion \citep{KS} to recover
+the convergence $\kappa(\pmb{\theta})$ from the $E$--mode of the shear
+field,
+%
+\begin{equation}
+\kappa(\mathbf{l}) = \left(\frac{l_1^2-l_2^2}{l_1^2+l_2^2}\right)\gamma^1(\mathbf{l}) + 2\frac{l_1l_2}{l_1^2+l_2^2}\gamma^2(\mathbf{l}).
+\end{equation}
+%
+The simulated $\kappa$ maps we create below are $12~\mathrm{deg}^2$ in
+size and have a resolution of $512\times512$ pixels. The CFHTLenS
+catalogs contain masked regions (which include the rejected fields and
+the regions around bright stars). We first create gridded versions of
+the observed $\kappa$ maps matching the size and pixel resolution of
+our simulated maps, with each pixel containing the number of galaxies
+($n_{gal}$) falling within its window.  
+%ZH: I paraphrased the above sentence, because it was ambiguous.  Please check that this is what you meant to say.
+We then smooth this galaxy surface density map with the same Gaussian
+window function as equation (\ref{gausskernel}) and remove regions
+where $n_{gal} < 5 \,\mathrm{arcmin}^{−2}$ (see
+\citep{CFHTMasato}). Regions with low galaxy number density can induce
+large errors in the cosmological parameter inferences.
 
 \subsection{Simulation design}
-In this section we give a description of the method we used to sample the parameter space in our simulation effort.
-We wish to investigate the non--linear dependence of cosmological probes (in this work Minkowski Functionals and Moments of the $\kappa$ field) on the parameter triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7, 0.046, 0.96).
-We sampled the $D$--dimensional ($D=3$ in this case) parameter space using an irregularly spaced grid, designed with a method similar to \citep{coyote2}.
-The irregular grid design is more efficient, given the available computing resources: a regular parameter grid with the same average spacing between models would require a prohibitively large number of samples.
-We limit the parameter sampling in a box of corners $\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$ and we map this sampling box $\Pi$ into an hypercube of unit side.
-We want to contruct an irregularly spaced grid consisting of $N$ points $\mathbf{x}_i\in[0,1]^D$.
-Let a \textit{design} $\mathcal{D}$ be the set of this irregularly spaced $N$ points: we wish to find an optimal design, in which the points are spread as uniformly as possible inside the box.
-Following \citep{coyote2}, we choose our optimal design as the minimum of the cost function
-
-%AP: Justified irregular parameter sampling
+
+We next give a description of our method to sample the parameter space
+with a suite of N--body simulations. We wish to investigate the
+non--linear dependence of the descriptors (in this work, Minkowski
+Functionals and moments of the $\kappa$ field) on the parameter
+triplet $\mathbf{p}=(\Omega_m,w,\sigma_8)$, while keeping the other
+relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
+0.046, 0.96). 
+%ZH: cite WMAP9 paper here for the parameter choices.
+We sampled the $D$--dimensional ($D=3$ in this case) parameter space
+using an irregularly spaced grid. The grid was designed with a method
+similar to that used to construct an emulator for the matter power
+spectrum in the \texttt{Coyote} simulation suite \citep{coyote2}.
+Given fixed available computing resources, the irregular grid design
+is more efficient than a parameter grid with regular spacings: to
+achieve the same average spacing between models in the latter approach
+would require a prohibitively large number of simulations.
+
+We limit the parameter sampling to a box whose sides range over
+$\Omega_m\in[0.07,1],\,w\in[-3.0,0],\,\sigma_8\in[0.1,1.5]$.  These
+are large ranges, with most of the corresponding 3D parameter volume
+ruled out by other cosmological experiments. However, our focus in
+this work is to quantify the constraints from CFHTLenS alone, which,
+by itself has strong parameter degeneracies.
+%ZH: Added justification of large ranges above.
+We next map this sampling box $\Pi$ into a hypercube of unit side. We
+want to construct an irregularly spaced grid consisting of $N$ points
+$\mathbf{x}_i\in[0,1]^D$. Let a \textit{design} $\mathcal{D}$ be the
+set of this irregularly spaced $N$ points. Our goal is to find an
+optimal design, in which the points are spread as uniformly as
+possible inside the box. Following ref.~\citep{coyote2}, we choose our
+optimal design as the minimum of the cost function
 
@@
 \label{costfunction}
-\mathcal{C}(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}
-\end{equation} 
-%
-This problem is mathematically equivalent to the minimization of the Coulomb potential energy of $N$ unit charges in a unit box, which will make sure that the charges are as evenly spread as possible throughout the confining volume.
-Finding the optimal design $\mathcal{D}_m$ that minimized (\ref{costfunction}) can be computationally very demanding, and hence we decided to use a simplified approach that, although approximate, serves our purposes for the grid design.
-We use an iterative procedure:
+\mathcal{C}(\mathcal{D}) = \frac{2D^{1/2}}{N(N-1)}\sum_{i<j}^N\frac{1}{\vert\mathbf{x}_i-\mathbf{x}_j\vert}.
+\end{equation} 
+%
+This problem is mathematically equivalent to the minimization of the
+Coulomb potential energy of $N$ unit charges in a unit box, which
+corresponds to spreading the charges as evenly as possible.
+%, which will make sure that the charges are as evenly spread as possible throughout the confining volume.
+Finding the optimal design $\mathcal{D}_m$ that minimizes
+(\ref{costfunction}) can be computationally very demanding, and hence
+we decided to use a simplified approach. Although approximate, the
+following iterative procedure gives satisfactory accuracy for our purposes:
+
 \begin{enumerate}
 \item We start from the diagonal design $\mathcal{D}_0$:
-
-$x_i^d\equiv i/(N-1)$ for $d=1...D$
-\item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$ where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$
-\item We pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$
-\item We compute the new cost function, if this is less than the previous step, we keep the exchange, otherwise we revert the coordinate swap
-\item We repeat steps 3 and 4 until the relative cost function change is less than a chosen accuracy parameter $\epsilon$ 
+$x_i^d\equiv i/(N-1)$ for $d=1...D$.
+\item We shuffle the coordinates of the particles in each dimension independently $x_i^d = \mathcal{P}_d\left(\frac{1}{N-1},\frac{2}{N-1},...,1\right)$, where $\mathcal{P}_1,...,\mathcal{P}_D$ are random independent permutations of $(1,2,...,N)$.
+\item We pick a random particle pair $(i,j)$ and a random coordinate $d\in\{1,...,D\}$ and swap $x_i^d\leftrightarrow x_j^d$.
+\item We compute the new cost function. If the value is less than in the previous step, we keep the exchange, otherwise we revert the coordinate swap.
+\item We repeat steps 3 and 4 until the relative cost function change is less than a chosen accuracy parameter $\epsilon$.
 \end{enumerate}
 %
-We found that for $N=91$ grid points, order of $10^5$ iterations are sufficient to reach an accuracy of $\epsilon\sim10^{-4}$.
-Once the optimal design $\mathcal{D}_m$ has been found, we can invert the mapping $\Pi\rightarrow[0,1]^3$ to find our simulation parameter sampling $\mathbf{p}_s$, which we show in Table \ref{designtable} and Figure \ref{designfig}.
+
+We have found that for $N=91$ grid points O($10^5$) iterations are
+sufficient to reach an accuracy of $\epsilon\sim10^{-4}$. Once the
+optimal design $\mathcal{D}_m$ has been determined, we invert the
+mapping $\Pi\rightarrow[0,1]^3$ to arrive at our simulation parameter
+sampling $\mathbf{p}_s$. We show the final list of grid points in
+Table~\ref{designtable} and Figure~\ref{designfig}.
+
 %
@@
 \end{tabular}
-\caption{List of the CFHTemu1 grid points in parameter space}
+\caption{List of the \texttt{CFHTemu1} grid points in the 3D cosmological parameter space.}
 \label{designtable}
@@
 \includegraphics[scale=0.4]{Figures/design.eps}
-\caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of our the simulation design.
-The blue points correspond to the CFHTemu1 simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the CFHTcov simulation set, which is based on 50 independent $N$--body simulations}
+\caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of the final simulation design.
+The blue points correspond to the \texttt{CFHTemu1} simulation set, which consists of one $N$--body simulation per point, while the red point corresponds to the \texttt{CFHTcov} simulation set, which is based on 50 independent $N$--body simulations.}
 \label{designfig}
@@
 %
-For each parameter point on the grid $\mathbf{p}_s$ we run one $N$--body simulation and perform ray tracing through it, as described in \S~\ref{raysim}, to simulate CFHTLenS shear catalogs: this set of simulations will be called CFHTemu1 throughout the rest of this work.
-Additionally, we run 50 independent $N$--body simulations with a \textit{fiducial} parameter choice $\mathbf{p}_0=(0.26,-1.0,0.8)$ for the purpose of measuring accurately the covariance matrices which will be used for the parameter inferences in \S-\ref{cosmostats}: this set of simulations will be called CFHTcov throughout the rest of this work.
-
-\subsection{Ray Tracing Simulations}
+
+For each parameter point on the grid $\mathbf{p}_s$ we then run an
+$N$--body simulation and perform ray tracing, as described in
+\S~\ref{raysim}, to simulate CFHTLenS shear catalogs.  Throughout the
+rest of this paper, we refer to this set of simulations as
+\texttt{CFHTemu1}.  Additionally, we have run 50 independent $N$--body
+simulations with a \textit{fiducial} parameter choice
+$\mathbf{p}_0=(0.26,-1.0,0.8)$, for the purpose of accurately
+measuring the covariance matrices, needed for the parameter inferences
+in \S\ref{cosmostats}. This additional suite of 50 simulations will
+be referred to as \texttt{CFHTcov}.
+
+\subsection{Ray--Tracing Simulations}
 \label{raysim}
-The goal of this section is to give an outline of our simulation pipeline. 
-The fluctuations in the matter density field between a source at redshift $z$ and an observer located on Earth will cause small deflections to the trajectories of light rays traveling from the source to the observer.
-The fluctuations in the matter field are described by the gravitational potential $\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can replace the physical coordinates $\mathrm{x}$ with the comoving distance from the observer $\chi$ and two transverse coordinates $\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky approximation.
-Here $\pmb{\beta}$ refers to the angular coordinate on the sky of a physical point $\mathbf{x}$, as seen from the observer.
-We estimate the dark matter gravitational potential running $N$--body simulations (with $N=512^3$) with the public code Gadget2 \citep{Gadget2}, using a comoving box size of $240h^{-1}$Mpc.
-Using a similar procedure as in \citep{RayTracingJain,RayTracingHartlap}, the equation that governs the light ray deflections can be written in the form
+
+The goal of this section is to outline our simulation pipeline.  The
+fluctuations in the matter density field between a source at redshift
+$z$ and an observer located on Earth will cause small deflections in
+the trajectories of light rays traveling from the source to the
+observer. 
+%ZH: I don't think this low-level description is necessary here:
+%
+%The fluctuations in the matter field are described by the
+%gravitational potential
+%$\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can
+%replace the physical coordinates $\mathrm{x}$ with the comoving
+%distance from the observer $\chi$ and two transverse coordinates
+%$\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky
+%approximation. Here $\pmb{\beta}$ refers to the angular coordinate on
+%the sky of a physical point $\mathbf{x}$, as seen from the
+%observer. 
+We estimate the dark matter gravitational potential running $N$--body
+simulations with $N=512^3$ particles, using the public code Gadget2
+\citep{Gadget2}. We adopted a comoving box size of $240h^{-1}$Mpc,
+corresponding to a mass resolution of $7.4\times10^9h^{-1}M_\odot$.
+%ZH: Instead, I added this:
+The simulations include dark matter only, and the initial conditions
+were generated with \texttt{N-GenIC} at $z=100$, based on the linear
+matter power spectrum created with the Einstein-Boltzmann code CAMB
+\cite{CAMB}. Data cubes were output at redshift intervals
+corresponding to $80h^{-1}$ (comoving) Mpc.
+
+Using a procedure similar to
+refs.~\citep{RayTracingJain,RayTracingHartlap}, the equation that
+governs the light ray deflections can be written in the form
 \begin{equation}
 \label{raytrajectory}
-\frac{d^2\mathbf{x}(\chi)}{d\chi^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(\chi),\chi)
-\end{equation}
-%
-where $\mathbf{x}(\chi)$ is the trajectory of a single light ray.
-Suppose that a light ray reaches the observer at an angular position $\pmb{\theta}$ on the sky: we want to know where this light ray originated, knowing it comes from a redshift $z_s$.
-To answer this question we need to integrate equation (\ref{raytrajectory}) with the initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$, $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance $w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$.
-For the light ray trajectory solver, based on equation (\ref{raytrajectory}), we use our proprietary implementation Inspector Gadget.
-Once we know the details of the light ray trajectories, we can easily infer the interesting weak lensing  quantities by taking the angular derivatives of the ray deflections $A(\chi_s;\pmb{\theta}) = \partial \pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing the usual spin decomposition to infer the convergence $\kappa$ and the shear components $(\gamma^1,\gamma^2)$
-%
-%AP: Inspector Gadget was never published
+\frac{d^2\mathbf{x}(\chi)}{d\chi^2} = -\frac{2}{c^2}\nabla_{\mathbf{x}_\perp}\Phi(\mathbf{x}_\perp(\chi),\chi),
+\end{equation}
+%
+where $\chi$ is the radial comoving distance,
+$\mathbf{x}_\perp=\chi\pmb{\beta}$ refers to two transverse
+coordinates (with $\pmb{\beta}$ the angular sky coordinates, using the
+flat sky approximation)a, $\mathbf{x}(\chi)$ is the trajectory of a
+single light ray, and $\Phi$ is the gravitational potential.
+
+Suppose that a light ray reaches the observer at an angular position
+$\pmb{\theta}$ on the sky: we want to know where this light ray
+originated, knowing it comes from a redshift $z_s$. To answer this
+question we need to integrate equation (\ref{raytrajectory}) with the
+initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$,
+$\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance
+%$w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$. 
+%ZH: any reason to switch from chi to w ?   I switched back.
+$\chi_s=\chi(z_s)$ to obtain the source angular position
+$\pmb{\beta}(\chi_s;\pmb{\theta})$. We use our proprietary
+implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
+for the light ray trajectories based on equation
+(\ref{raytrajectory}).
+
+Once we obtain the light ray trajectories, we infer the relevant weak
+lensing quantities by taking angular derivatives of the ray
+deflections $A(\chi_s;\pmb{\theta}) = \partial
+\pmb{\beta}(\chi_s;\pmb{\theta})/\partial\pmb{\theta}$ and performing
+the usual spin decomposition to infer the convergence $\kappa$ and the
+shear components $(\gamma^1,\gamma^2)$,
+%
+%AP: Inspector Gadget was never published.
+%ZH: Yes.  That's a pity.  I added the reference to Jan's first paper instead.
 %
@@
 %
-where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the first and third Pauli matrices.
-$\kappa$ is related to the source apparent magnification, while $(\gamma^1,\gamma^2)$ are related to the source apparent ellipticity, as seen by the observer.
-Given a source with intrinsic ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity as seen by an observer will be modified by the cosmic shear $\pmb{\gamma}=\gamma^1 + i\gamma^2$ following
+where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
+first and third Pauli matrices. The convergence $\kappa$ is related to
+the magnification, while the two components of the complex shear
+$\pmb{\gamma}=\gamma^1 + i\gamma^2$ are related to the apparent
+ellipticity of the source. Given a source with intrinsic complex
+ellipticity $\mathbf{e}_s=e^1_s + ie^2_s$, its observed ellipticity
+will be modified to
 %
@@
 %
-where $\mathbf{g} = \pmb{\gamma}/(1-\kappa)$ is the reduced shear.
-For each simulated galaxy, we assign an intrinsic ellipticity by rotating the observed ellipticity for that galaxy by a random angle on the sky, while conserving its magnitude $\vert\mathbf{e}\vert$.
-To be consistent with the CFHTLenS analysis, we adopt the weak lensing limit ($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$),hence $\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx \mathbf{e}_s+\pmb{\gamma}$.
-We also add the multiplicative shear corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$.
-We note that the observed ellipticity for a particular galaxy already contains information from the lensing by large scale structure, but the random angle rotation makes this contribution second order in $\kappa$.
-Consistent with the weak lensing approximation, the lensing signal from the simulations is first order in $\kappa$ and hence the randomly rotated observed ellipticities can be effectively considered as intrinsic ellipticities.
-We analyze the simulations in the same way as we analyzed CFHTLenS data, constructing the simulated $\kappa$ maps as explained in \S\ref{cfhtdatareduction}.
-These final simulation products are then processed together with the $\kappa$ maps obtained from the data to calculate the confidence intervals on the parameter triplet $(\Omega_m,w,\sigma_8)$.
-
-%AP: changed comoving distance symbol to chi; knocked out the ray tracing figure; clarified the signal double counting issue
+where $\mathbf{g} \equiv \pmb{\gamma}/(1-\kappa)$ is the reduced shear.
+
+For each simulated galaxy, we assign an intrinsic ellipticity by
+rotating the observed ellipticity for that galaxy by a random angle on
+the sky, while conserving its magnitude $\vert\mathbf{e}\vert$. To be
+consistent with the CFHTLenS analysis, we adopt the weak lensing limit
+($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$), i.e.
+$\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx
+\mathbf{e}_s+\pmb{\gamma}$. We also add the multiplicative shear
+corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$. We
+note that the observed ellipticity for a particular galaxy already
+contains the lensing shear by large scale structure, but the random
+rotation makes this contribution second order in $\kappa$. Consistent
+with the weak lensing approximation, the lensing signal from the
+simulations is first order in $\kappa$ and hence the randomly rotated
+observed ellipticities can be safely considered as intrinsic
+ellipticities.
+
+We analyze the simulations in the same way as we analyzed the CFHTLenS
+data -- constructing the simulated $\kappa$ maps as explained in
+\S\ref{cfhtdatareduction}. These final simulation products are then
+processed together with the $\kappa$ maps obtained from the data to
+compute confidence intervals on the parameter triplet
+$(\Omega_m,w,\sigma_8)$.
 
@@
 \section{Statistical methods}
-The goal of this section is to describe the framework in which we combine the CFHT data and our simulations in order to derive the constraints on the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$.
-We measure a set of statistical descriptors from the data and the simulations, which will then be compared in a Bayesian framework in order to compute parameter confidence intervals.
+
+The goal of this section is to describe the framework to combine the
+CFHT data and our simulations, and to derive the constraints on the
+cosmological parameter triplet $(\Omega_m,w,\sigma_8)$. Briefly, we
+measure the same set of statistical descriptors from the data and from the
+simulations; these are then compared in a Bayesian framework in
+order to compute parameter confidence intervals.
 
 \subsection{Descriptors}
-The statistical descriptors we consider in this work are the Minkowski Functionals (MFs) and the low order moments (LM) of the convergence field.
-The three MFs $(V_0,V_1,V_2)$ are topological descriptors of the convergence field $\kappa(\pmb{\theta})$, which probe respectively the area, perimeter and genus characteristic of the $\kappa$ excursion sets $\Sigma_{\kappa_0}$, defined as $\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$.
-Following \citep{Petri2013,MinkJan} we use the following local estimators to measure the MFs from the $\kappa$ maps.
+
+The statistical descriptors we consider in this work are the Minkowski
+Functionals (MFs) and the low--order moments (LMs) of the convergence
+field. The three MFs $(V_0,V_1,V_2)$ are topological descriptors of
+the convergence field $\kappa(\pmb{\theta})$, probing the area,
+perimeter and genus characteristic of the $\kappa$ excursion sets
+$\Sigma_{\kappa_0}$, defined as
+$\Sigma_{\kappa_0}=\{\kappa>\kappa_0\}$. Following
+refs.~\citep{Petri2013,MinkJan} we use the following local estimators
+to measure the MFs from the $\kappa$ maps:
 %
@@
 %
-Where $A$ is the total area of the fields of view and the notation $\kappa_{x,y}$ indicates gradients of the $\kappa$ field, which we evaluate using finite differences.
-The first Minkowski functional, $V_0$, is equivalent to the cumulative one--point PDF of the $\kappa$ field, while $V_1,V_2$ are sensitive to the correlations between nearby pixels.
-The one--point PDF of the $\kappa$ field, $\partial V_0$, can be obtained by differentiation $\partial V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$.
-In addition to these topological descriptors, we consider a set of low order moments (LM) of the convergence field (two quadratic, three cubic and four quartic).
-We choose these moments to be the minimal set of LM necessary to build a perturbative expansion of the MF up to $O(\sigma_0^2)$ (see \citep{Munshi12,Matsubara10}).
-We adopt the following definitions
+Here $A$ is the total area of the field of view and $\kappa_{x,y}$
+denotes gradients of the $\kappa$ field, which we evaluate using
+finite differences. The first Minkowski functional, $V_0$, is
+equivalent to the cumulative one--point PDF of the $\kappa$ field,
+while $V_1,V_2$ are sensitive to the correlations between nearby
+pixels. The one--point PDF of the $\kappa$ field, $\partial V_0$, can
+be obtained by differentiation $\partial
+V_0(\kappa_0)=dV_0(\kappa_0)/d\kappa_0$.
+
+In addition to these topological descriptors, we consider a set of
+low--order moments of the convergence field (two quadratic, three
+cubic and four quartic). We choose these moments to be the minimal set
+of LMs necessary to build a perturbative expansion of the MFs up to
+$O(\sigma_0^2)$ (see \citep{Munshi12,Matsubara10}). We adopt the
+following definitions
 %
@@
 
-If the $\kappa$ field were Gaussian, one could express all the Minkowski Functionals in terms of the LM$_2$ moments, as expected from the fact that, for a Gaussian field, the only non--trivial statistics are the quadratic ones.
-In reality, weak lensing convergence fields are non--Gaussian and the MF and LM descriptors are not guaranteed to be equivalent.
-\citep{Munshi12,Matsubara10} studied a perturbative expansion of the MF descriptors in powers of the $\kappa$ field standard deviation $\sigma_0$, which, when truncated at order $O(\sigma_0^2)$, can be expressed completely in terms of the LM up to quartic order.
-Such perturbative series, however, have been shown not to converge \citep{Petri2013} unless the weak lensing fields are smoothed with windows of size $\geq 15^\prime$.
-Because of this, throughout this work, we treat MF and LM as separate statistical descriptors.
-
-The LM that contain gradients are sensitive to different shapes of the $\kappa$ multispectra $P_{\kappa}^n(\mathbf{l}_1,...,\mathbf{l}_n)$ because a particular $\mathrm{LM}_n$ has the general form
+If the $\kappa$ field were Gaussian, one could express the MFs in
+terms of the LM$_2$ moments, which are the only independent moments
+for a Gaussian random field. In reality, weak lensing convergence
+fields are non--Gaussian and the MF and LM descriptors are not
+guaranteed to be equivalent. Refs.~\citep{Munshi12,Matsubara10}
+studied a perturbative expansion of the MFs in powers of the standard
+deviation $\sigma_0$ of the $\kappa$ field. When truncated at order
+$O(\sigma_0^2)$, this can be expressed completely in terms of the LMs
+up to quartic order. Such perturbative series, however, have been
+shown not to converge \citep{Petri2013} unless the weak lensing fields
+are smoothed with windows of size $\geq 15^\prime$. Because of this,
+throughout this work, we treat MF and LM as separate statistical
+descriptors.
+
+We note that this choice is somewhat ad-hoc. In general, the LMs that
+contain gradients are sensitive to different shapes of the $\kappa$
+multispectra $P_{\kappa}^n(\mathbf{l}_1,...,\mathbf{l}_n)$ because a
+particular $\mathrm{LM}_n$ has the general form
 %
@@
 %
-where $\rho$ is a polynomial of order $n$ in the $\mathbf{l}$'s.
-For example for $K_2$ we have $\rho(\mathbf{l}_{1234})=l_4^2$ and this moment emphasizes quadrilateral shapes in which where one sides is much larger than the others.
-On the other hand, for $K_4$ we have $\rho(\mathbf{l}_{1234})=(\mathbf{l}_1\cdot\mathbf{l}_2)(\mathbf{l}_3\cdot\mathbf{l}_4)$ and this moment is most sensitive to trispectrum shapes that are close to rectangular.
-There are other moments which include derivatives besides the ones we have considered.
-In the future we will investigate whether there is additional constraining power in quartic moments not considered here.
-
-In addition to the MF and LM descriptors, we consider the $\kappa$ angular power spectrum $P_l\equiv P^2_l$ defined as
+where $\rho$ is a polynomial of order $n$ in the $\mathbf{l}$'s. For
+example for $K_2$ we have $\rho(\mathbf{l}_{1234})=l_4^2$ and this
+moment emphasizes quadrilateral shapes for which one side is much
+larger than the others. On the other hand, for $K_4$ we have
+$\rho(\mathbf{l}_{1234})=(\mathbf{l}_1\cdot\mathbf{l}_2)(\mathbf{l}_3\cdot\mathbf{l}_4)$
+and this moment is most sensitive to trispectrum shapes that are close
+to rectangular. There are moments which include derivatives in
+addition to those included in Eq.~\ref{momentestimator}. In the
+future, we will investigate whether there is additional constraining
+power in these additional quartic moments.
+
+In addition to the MFs and LMs, we consider the angular power spectrum
+$P_l\equiv P^2_l$ of $\kappa$, defined as
 \begin{equation}
 \label{powerspectrum}
-\langle\tilde{\kappa}(\mathbf{l})\tilde{\kappa}(\mathbf{l}')\rangle=(2\pi)^2\delta_D(\mathbf{l}+\mathbf{l}')P_l
-\end{equation}  
-%
-%AP: independent --> separate
-%
-where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the $\kappa$ field and $\delta_D$ is the usual Dirac delta function.
-While the use of this statistic is not a novelty, we want to compare the results we get using MF and LM to ones already present in the literature which are based on the use of quadratic statistics (see for example \citep{CFHTKilbinger}).
-A summary of the statistical descriptors used is presented in Table \ref{desctable}.
+\langle\tilde{\kappa}(\mathbf{l})\tilde{\kappa}(\mathbf{l}')\rangle=(2\pi)^2\delta_D(\mathbf{l}+\mathbf{l}')P_l,
+\end{equation}  
+%
+where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the
+$\kappa$ field and $\delta_D$ is the usual Dirac delta
+function. Previous works have studied cosmological constraints from
+the convergence power spectrum extensively.  Here our purpose is to
+compare the constraints we obtain from the MFs and LMs to ones present
+in the literature, which are based on the use of quadratic statistics
+(see for example \citep{CFHTKilbinger}). The statistical descriptors
+used in this work are summarized in Table \ref{desctable}.
 %
@@
 \end{tabular}
-\caption{Summary of the descriptors we used, along with the specifications and the number of bins $N_b$ used}
+\caption{Summary of the descriptors we used, together with the specifications and the number of bins $N_b$ in each case.}
 \label{desctable}
@@
 
-When measuring statistical descriptors on $\kappa$ maps, particular attention must be given to the effect of masked pixels.
-This does not pose a particular problem for the MFs and LM statistics, since the estimators in (\ref{v1meas}) and (\ref{momentestimator}) are well defined over all the non--masked region, with the exception of the few pixels that are close to the mask boundaries.
-Masking effects on Minkowski Functionals constraints with CFHTLenS have been studied extensively by \citep{CFHTMasato}.
-The situation is more complicated for the Power Spectrum measurements, that require the evaluations of Fourier transforms and hence rely on the value of every pixel in the map.
-Although sophisticated interpolation approaches over the masked regions have been studied (see for example \citep{VplasInterpolation}), for the sake of simplicity we put a value of 0 in each masked pixel, arguing that, given the typical angular size of the masked regions we consider, this will have little effect on the Power Spectrum at the range of multipoles in Table \ref{desctable}.
-We believe that the way we deal with masked sky regions is very robust, since we apply the same masks to our simulations.
+When measuring statistical descriptors on $\kappa$ maps, particular
+attention must be paid to the effect of masked pixels. The MFs and LMs
+remain well--defined in the presence of masks, since the estimators in
+equations~(\ref{v1meas}) and (\ref{momentestimator}) are defined
+locally, and can be computed in the non--masked regions (with the
+exception of the few pixels that are close to the mask
+boundaries). The situation is more complicated for power spectrum
+measurements, which require the evaluations of Fourier transforms and
+hence rely on the value of every pixel in the map. Although
+sophisticated schemes to interpolate over the masked regions have been
+studied (see for example \citep{VplasInterpolation}), for the sake of
+simplicity, we here insert the value $\kappa=0$ in each masked pixel.
+Given the typical angular size of the masked regions we consider, this
+will have little effect on the power spectrum at the range of
+multipoles in Table \ref{desctable}. 
+%ZH: can you be more specific above and say what you mean by the angular scales?  Masks are much smaller than
+%    the scales over which moments are defined?   Or much bigger?
+Likewise, we believe that the way we deal with masked sky regions --
+essentially ignoring them -- is robust for the MFs and LMs. Since we
+apply the same masks to our simulations and the data, they are
+unlikely to introduce biases in the resulting constraints.  Masks, of
+course, can still affect the sensitivity and weaken constraints. The
+impact of the masks and their treatment has been evaluated for the
+MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}.
+%ZH:  I think we need to state here something on what they found.
 
@@
 %AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and Moments are well defined also in the presence of masked pixels, while the PS estimator is not
+%ZH:  OK, I rewrote above to say this.  I think what you mean to say here is that our results will not be biased,
+%     since we apply the same masking to the data and the sims.   But there's still a separate question of loosing
+%     sensitivity, which I noted above.
 
@@
 
-In this section we give a brief outline of the statistical framework adopted for computing the cosmological parameter confidence levels from the CFHTLenS observations.
-We make use of the MF and LM statistical descriptors outlined in the previous section.
-We refer to $M_i^r(\mathbf{p})$ as the measured descriptor from a realization $r$ of one of our simulations with a choice of cosmological parameters $\mathbf{p}$, and to $D_i$ as the measured descriptor from the CFHTLenS data.
-In this notation, $i$ is an index that refers to the particular bin on which the descriptor is evaluated (for example $i$ can range from 0 to 9 for the LM statistic and from 0 to $N_b-1$ for a Minkowski Functional measured on $N_b$ different excursion sets).
-Once we make an assumption for the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ and for the parameter priors $\Pi(\mathbf{p})$, we can use Bayes theorem to compute the parameter likelihood $\mathcal{L}_p$ as follows
+In this section, we briefly outline of the statistical framework
+adopted for computing cosmological parameter confidence levels.  We
+make use of the MFs and LMs, as well as the power spectrum, as
+discussed in the previous section. We refer to $M_i^r(\mathbf{p})$ as
+the descriptor measured from a realization $r$ of one of our
+simulations with a choice of cosmological parameters $\mathbf{p}$
+(i.e. from one of the $R=1000$ maps in this cosmology), and to $D_i$
+as the descriptor measured from the CFHTLenS data.
+%ZH: Important: we never describe that we have R=1000 realization of
+%    each model, by random rotations and shifts of the single N-body run.
+%    This should be added above, where the simulations and the ray-tracing is discussed.
+In this notation, $i$ is an index that refers to the particular bin on
+which the descriptor is evaluated (for example $i$ can range from 0 to
+9 for the LM statistic and from 0 to $N_b-1$ for a MF measured in
+$N_b$ different $\kappa$ bins).
+%on $N_b$ different excursion sets.
+%ZH: Similarly: we should insert 2-3 sentence above, where we discuss the descriptors,
+%    to state what binning we used (and indicate the actual kappa values of the bin boundaries).
+
+Once we make an assumption for the data likelihood
+$\mathcal{L}_d(D_i\vert \mathbf{p})$ and for the parameter priors
+$\Pi(\mathbf{p})$, we can use Bayes' theorem to compute the parameter
+likelihood $\mathcal{L}_p$,
 
@@
 \label{parameterlikelihood}
-\mathcal{L}_p(\mathbf{p}\vert D_i) = \frac{\mathcal{L}_d(D_i\vert \mathbf{p})\Pi(\mathbf{p})}{N_{\mathcal{L}}}
-\end{equation}
-%
-where $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that ensures the proper normalization for $\mathcal{L}_p$; we make the usual assumption that the data likelihood $\mathcal{L}_d(D_i\vert \mathbf{p})$ is Gaussian
+\mathcal{L}_p(\mathbf{p}\vert D_i) = \frac{\mathcal{L}_d(D_i\vert \mathbf{p})\Pi(\mathbf{p})}{N_{\mathcal{L}}}.
+\end{equation}
+%
+Here $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that
+ensures the proper normalization for $\mathcal{L}_p$. We make the
+usual assumption that the data likelihood $\mathcal{L}_d(D_i\vert
+\mathbf{p})$ is Gaussian~\footnote{In principle, this assumption could
+  be relaxed, by measuring joint probability distributions of the
+  descriptors in our simulations.  In practice, characterizing
+  non-Gaussianities and folding them into the likelihood analysis
+  requires significant analysis, which we postpone to future work.}
 
@@
 Basically this is the only functional form with which we can model the PDF and bin correlations analytically, and compute the parameter likelihood semi-analytically, otherwise we need to dig into more sophisticated non--parametric methods in which I am not that proficient yet.
+%
+%ZH: OK, I added a footnote along these lines.  It's just tempting to try to do this using the sims, since in principle, we could relax the assumption. I agree in practice it will be a lot of work.
 
@@
 \begin{matrix}
-\mathcal{L}_d(D_i\vert \mathbf{p}) = ((2\pi)^{N_b}\det{\mathbf{C}})^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})} \\ \\
-\chi^2(D_i\vert \mathbf{p}) = \mathbf{(D - M(p))C^{-1}(D-M(p))}.
+\mathcal{L}_d(D_i\vert \mathbf{p}) = [(2\pi)^{N_b}\det{\mathbf{C}}]^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})}, \\ \\
+\chi^2(D_i\vert \mathbf{p}) = \mathbf{[D - M(p)]C^{-1}[D-M(p)]}.
 \end{matrix}
@@
 %
-We assume that the covariance matrix $\mathbf{C}$ that appears in (\ref{datalikelihood}) is $\mathbf{p}$--independent and coincides with $\mathbf{C}(\mathbf{p}_0)$.
-For this reason, the normalization constant in (\ref{datalikelihood}) is also model--independent.
-The simulated descriptors $\mathbf{M(p)}$ are measured from an average over realizations
+We assume, for simplicity, that the covariance matrix $\mathbf{C}$ in
+equation~(\ref{datalikelihood}) is $\mathbf{p}$--independent and
+coincides with $\mathbf{C}(\mathbf{p}_0)$. For this reason, the
+normalization constant in equation~(\ref{parameterlikelihood}) is also
+model--independent. The simulated descriptors $\mathbf{M(p)}$ are
+measured from an average over the $R=1000$ realizations
 \begin{equation}
@@
 %
-is measured from a simulation set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$.
-We should mention that, while (\ref{datacov}) is an unbiased estimator of the covariance matrix, its inverse is not an unbiased estimator of $\mathbf{C}^{-1}$ as seen in \citep{RayTracingHartlap}.
-Given that in our case $R\gg N_b$, we can safely neglect the correction factor needed to make the estimator for $\mathbf{C}^{-1}$ unbiased.
-
-When computing parameter constraints from CFHTLenS weak lensing data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$ and we reserve the possibility of a more general prior for future work.
-Parameter inferences are made estimating the location of the maximum of the parameter likelihood in (\ref{parameterlikelihood}), which we call $\mathbf{p}_{ML}(D_i)$ as well as its confidence contours.
-A $N\sigma$--confidence contour of $\mathcal{L}_p(\mathbf{p}\vert D_i)$ is defined to be the subset of points in parameter space on which the likelihood has a constant value $c_N$ and
+is measured from the independent \texttt{CFHTcov} simulation suite.
+% set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$
+While eq.~(\ref{datacov}) gives an unbiased estimator of the
+covariance matrix, its inverse is not an unbiased estimator of
+$\mathbf{C}^{-1}$ (e.g. ref.~\citep{RayTracingHartlap}). Given that in
+our case $R\gg N_b$, we can safely neglect the correction factor
+needed to make the estimator for $\mathbf{C}^{-1}$ unbiased.
+
+When computing parameter constraints from the CFHTLenS weak lensing
+data alone, we make a flat prior assumption for $\Pi(\mathbf{p})$.  We
+postpone using different priors, incorporating external data, for
+future work. Parameter inferences are made estimating the location of
+the maximum of the parameter likelihood in
+eq.~(\ref{parameterlikelihood}), which we call $\mathbf{p}_{ML}(D_i)$,
+as well as its confidence contours. The $N\sigma$--confidence contour
+of $\mathcal{L}_p(\mathbf{p}\vert D_i)$ is defined to be the subset of
+points in parameter space on which the likelihood has a constant value
+$c_N$ and
 \begin{equation}
@@
 
-Using equation (\ref{rbfinterpolation}) and given the low dimensionality of the parameter space we consider $(D=3)$ we are able to evaluate the parameter likelihood (\ref{parameterlikelihood}) on $100^3$ different combinations of the cosmological parameters $p$, arranged in finely spaced $100\times100\times100$ mesh within the prior window $\Pi(\mathbf{p})$.
-We are hence able to evaluate the likelihood maximum $\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ directly without the need to use more sophisticated MCMC methods.
-We know how to evaluate the data likelihood (\ref{datalikelihood}) on the simulation irregular grid $\mathbf{p}_s$, but more work needs to be done to interpolate $M(\mathbf{p})$ to an arbitrary intermediate point.
-We use a Radial Basis Function (RBF) interpolation scheme.
-We approximate the model descriptor as
+Using equation (\ref{rbfinterpolation}) below, and given the low
+dimensionality of the parameter space we consider $(D=3)$, we are able
+to directly compute the parameter likelihood
+eq.~(\ref{parameterlikelihood}) for $100^3$ different combinations of
+the cosmological parameters $p$, arranged in a finely spaced
+$100\times100\times100$ mesh within the prior window
+$\Pi(\mathbf{p})$. We directly compute the maximum likelihood
+$\mathbf{p}_{ML}(D_i)$ and the contour levels $c_N$ without the need
+for more sophisticated MCMC methods.
+
+The data likelihood is directly available for parameter combinations
+on the simulated irregular grid $\mathbf{p}_s$.  We use a Radial Basis
+Function (RBF) scheme to interpolate $M(\mathbf{p})$ to arbitrary
+intermediate points.  We approximate the model descriptor as
 \begin{equation}
@@
 %
-where $\phi$ has been chosen as a multiquadric function $\phi(r)=\sqrt{1+(r/r_0)^2}$ with $r_0$ chosen as the mean Euclidean distance between the points in the simulated grid $\mathbf{p}_s$.
-The constant coefficients $\lambda_s$ can be determined imposing the $N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which enforce the fact that the interpolation should be exact at the simulated points.
-The interpolation computations are conveniently performed using the \texttt{interpolate.Rbf} routine contained in Scipy library \citep{scipy}.
-
-We studied the accuracy of emulator, built with the CFHTemu1 simulations, by interpolating the convergence descriptors to the fiducial parameter setting $(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to the one expected from the CFHTcov simulations.
-Figure \ref{emulatorAccuracy} shows that our Power Spectrum emulator has accuracy better than 10\% for the lower multipoles and comparable to 1\% for the higher multipoles.
-The Minkowski Functionals emulator has accuracy $\lesssim$10\% for the first 30 bins (which correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due to numerical noise for the remaining 20 bins.
-We take care of these inaccuracies in our dimensionality reduction framework, which we explain in the next section.
-Nevertheless, we do not expect these inaccuracies to affect our conclusions as Figure \ref{emulatorAccuracy} clearly show that our emulator is able to distinguish a non--fiducial model from the fiducial one within numerical errors.
+where $\phi$ has been chosen as a multi-quadric function
+$\phi(r)=\sqrt{1+(r/r_0)^2}$, with $r_0$ chosen as the mean Euclidean
+distance between the points in the simulated grid $\mathbf{p}_s$. The
+constant coefficients $\lambda_s$ can be determined by imposing the
+$N$ constraints $M(\mathbf{p}=\mathbf{p}_s)=M(\mathbf{p_s})$, which
+enforce exact results at the simulated points. The interpolation
+computations are conveniently performed using the
+\texttt{interpolate.Rbf} routine contained in a Scipy library~\citep{scipy}.
+
+We studied the accuracy of the emulator, built with the
+\texttt{CFHTemu1} simulations, by interpolating the convergence
+descriptors to the fiducial parameter setting
+$(\Omega_m,w,\sigma_8)=(0.26,-1.0,0.8)$ and comparing the result to
+the one expected from the \texttt{CFHTcov}
+simulations. Figure~\ref{emulatorAccuracy} shows that our power
+spectrum emulator has accuracy better than 10\% for the lower
+multipoles, and comparable to 1\% for the higher multipoles. The MF
+emulator has accuracy $\lesssim$10\% for the first 30 bins (which
+correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
+to numerical noise for the remaining 20 bins. We eliminate the
+residual impact of these inaccuracies using a dimensionality reduction
+framework, which we explain in the next section. Nevertheless, we do
+not expect these inaccuracies to affect our
+conclusions. Figure~\ref{emulatorAccuracy} demonstrates that our
+emulator is able to distinguish a non--fiducial model from the
+fiducial one within numerical errors.  We thus found no need to
+implement a more sophisticated interpolation
+scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented
+  with interpolations using a Gaussian Process, but did not find a
+  significant improvement in accuracy over the much simpler polynomial
+  scheme; this is in agreement with earlier results.}.
+%ZH: we should add citation of Lloyd Knox's paper http://adsabs.harvard.edu/abs/2011ApJ...728..137S
+%    which said GP is not worth the hassle....
 
@@
 \end{center}
-\caption{Accuracy of the emulator based on the CFHTemu1 simulations: we show the difference between the interpolated descriptor at the fiducial parameter setting and the expected descriptor from the CFHTcov simulations, in units of the standard deviation in each bin $i$ (determined from the diagonal elements of the CFHTcov covariance matrix).
-We show the accuracy results for the Power Spectrum (red) and Minkowski Functionals $V_0$ (green), $V_1$ (blue) and $V_2$ (black).
-We also show, using dashed lines, the difference between the expected CFHTcov descriptors and the interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$}
+%ZH:  It would be really nice to show ``kappa'' and ``ell'' instead (or in addition) to ``i'' on the x axis.
+%     Maybe use the top of the figure to label kappa's and ell's?  Or at least state the kappa and ell ranges in words.
+\caption{Accuracy of the emulator based on the \texttt{CFHTemu1}
+  simulations. The figure shows the difference between the descriptor
+  interpolated at the fiducial parameter setting, and the descriptor
+  expected from the \texttt{CFHTcov} simulations. The descriptors are
+  shown in units of the standard deviation in each bin $i$ (determined
+  from the diagonal elements of the \texttt{CFHTcov} covariance
+  matrix). We show the accuracy results for the power spectrum (red)
+  and the three Minkowski Functionals $V_0$ (green), $V_1$ (blue) and
+  $V_2$ (black). For reference, we also show, using dashed lines, the
+  difference between the expected \texttt{CFHTcov} descriptors and the
+  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.}
+%ZH: This last one is chosen to lie along our 1 (or 2?) sigma contour, right?
+%    We should then state this, and make the point that this is the interpolation accuracy we care about,
+%    and our accuracy is indeed better than this.
 \label{emulatorAccuracy}
@@
 \label{pcasection}
-The main goal of this work is constraining the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data.
-When the question on the accuracy of the $N\sigma$ contours is considered, particular attention must be paid to the effect of binning choices on contour sizes computed with equations (\ref{parameterlikelihood})--(\ref{ennesigma}).
-It is known that the choice of the number of bins, $N_b$, can have a non-negligible effect on the contour sizes (see \citep{Petri2013} for an example with simulated datasets).
-In order for our results to be robust under this effect, we adopt a Principal Component Analysis (PCA) approach.
-Our main physical motivation for this approach is that, even though we need to specify $N_b$ numbers in order to fully characterize a binned descriptor, we suspect that the majority of the constraining information (of a particular descriptor) is contained in a limited number of linear combinations of its binning.
-In the framework adopted by \citep{coyote2}, for example, the authors find that the majority of the cosmological information in the matter Power Spectrum is contained in only 5 selected linear combinations of the multipoles.
-Because of this, we believe that dimensionality reduction techniques such as PCA can help in delivering accurate cosmological constraints using only a limited number of descriptor degrees of freedom.
-
-In order to compute the Principal Components of our descriptor space, we consider the CFHTemu1 simulations, which sample the cosmological parameter space at the $N=91$ points outlined in Table \ref{designtable} and allow us to compute the $N\times N_b$ model matrix $M_{pi}=M_i(\mathbf{p})$.
-Following a standard procedure (see \citep{astroMLText} for example), we then derive the whitened model matrix $\tilde{M}_{pi}$, defined by subtracting the mean in each bin, and normalizing it by its variance.
-Next we proceed with a singular value decomposition (SVD) of $\mathbf{\tilde{M}}$
+
+The main goal of this work is constraining the cosmological parameter
+triplet $(\Omega_m,w,\sigma_8)$ using the CFHTLenS data.  Once the
+$N\sigma$ contours have been obtained, using the procedure and
+equations (\ref{parameterlikelihood})--(\ref{ennesigma}) outlined
+above, one may ask whether the choice of binning affects these
+contours.  Indeed, in our previous work, we have found that the number
+of bins, $N_b$, can have a non-negligible effect on the contour sizes
+(see \citep{Petri2013} for an example with simulated datasets).
+
+In order to ensure that are results are robust with respect to binning
+choices, we have implemented a Principal Component Analysis (PCA)
+approach. Our physical motivation for this approach is that, even
+though we need to specify $N_b$ numbers in order to fully characterize
+a binned descriptor, we suspect that the majority of the constraining
+information (of a particular descriptor) is contained in a limited
+number of linear combinations of its binning. In the framework adopted
+by \citep{coyote2}, for example, the authors find that the majority of
+the cosmological information in the matter power spectrum is contained
+in only 5 different linear combinations of the multipoles. Because of
+this, we believe that dimensionality reduction techniques such as PCA
+can help deliver accurate cosmological constraints using only a
+limited number of descriptor degrees of freedom.
+
+In order to compute the principal components of our descriptor space,
+we use the \texttt{CFHTemu1} simulations, which sample the
+cosmological parameters at the $N=91$ points listed in Table
+\ref{designtable}, and allow us to compute the $N\times N_b$ model
+matrix $M_{pi}=M_i(\mathbf{p})$. Note that this is a rectangular
+(non-square) matrix. Following a standard procedure (see, e.g.,
+ref.~\citep{astroMLText}), we derive the {\it whitened} model matrix
+$\tilde{M}_{pi}$, defined by subtracting the mean (over the $R=1000$
+realizations) of each matrix element,
+%ZH: you wrote ``bin'' here, but I changed it to matrix element. All NxN_bin entries are whitened, presumably.
+and normalizing it by its variance. Next we proceed with a singular
+value decomposition (SVD) of $\mathbf{\tilde{M}}$,
 \begin{equation}
 \label{svd}
-\mathbf{U}\mathbf{S} \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}}
-\end{equation}   
-%
-where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is the $j$--th coordinate ($j=1...N_b$) of $i$--th principal component ($i=1...\mathrm{min}(N_b,N)$) of $\mathbf{\tilde{M}}$, with the index $j$ ranging from $0$ to $N_b-1$.
-By construction, $\mathbf{V}$ is $\mathbf{p}$--independent.
-
-To rank the Principal Components $V^T$ in order of importance, we note that the diagonal matrix $\mathbf{S}^2$ is nothing more than the diagonalization of the model covariance (not to be confused with the descriptor covariance in (\ref{datacov}))
+\mathbf{U}\mathbf{S} \mathbf{V}^T=\frac{\mathbf{\tilde{M}}}{\sqrt{N-1}},
+\end{equation}   
+%
+where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is
+the $j$--th coordinate ($j=1...N_b$) of the $i$--th principal
+component ($i=1...\mathrm{min}[N_b,N]$) of $\mathbf{\tilde{M}}$, with
+the index $j$ ranging from $0$ to $N_b-1$. By construction,
+$\mathbf{V}$ is $\mathbf{p}$--independent.
+
+To rank the Principal Components $V^T$ in order of importance, we note
+that the diagonal matrix $\mathbf{S}^2$ is simply the diagonalization
+of the model covariance (not to be confused with the descriptor
+covariance in eq.~\ref{datacov}),
 \begin{equation}
@@
 %
-We follow the standard interpretation of PCA components, stating that the only meaningful components $V^T_i$ in the analysis (i.e.
-the ones that contain the relevant cosmological information) are those corresponding to the largest eigenvalues $S^2_{i}$, with the smallest eigenvalues corresponding to noise in the model, due to numerical inaccuracies in the simulation pipeline.
-We expect our constraints to be stable with respect to the number of components, once enough components have been included.
-Using the fact that different Principal Components are orthogonal, we perform a PCA projection on our descriptor space by whitening the descriptors and computing the dot product with the principal components, keeping only the first $n$ components
+We follow the standard interpretation of PCA components, stating that
+the only meaningful components $V^T_i$ in the analysis (i.e. the ones
+that contain the relevant cosmological information) are those
+corresponding to the largest eigenvalues $S^2_{i}$, with the smallest
+eigenvalues corresponding to noise in the model, due to numerical
+inaccuracies in the simulation pipeline. We expect our constraints to
+be stable with respect to the number of components, once a sufficient
+number of components have been included. Using the fact that different
+principal components are orthogonal, we perform a PCA projection on
+our descriptor space by whitening the descriptors and computing the
+dot product with the principal components, keeping only the first $n$
+components
 \begin{equation}
 \label{pcaprojection}
-M(n)_{i}^r = V^T(n)_{ij}\tilde{M}_j^r \,\,\,\, ; \,\,\,\,  D(n)_i = V^T(n)_{ij}\tilde{D}_j
-\end{equation}
-%
-where we suppressed the first index of $M(n)$ for notational simplicity and we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$ rows (i.e.
-$i$ can now range from $1$ to $n$).
-The dimensionality reduction comes from the fact that we expect most of the cosmological information to be contained in a number of components $n<N_{b}$.
-We will describe in detail below the choice we make for $n$, and how our results are sensitive to it.
-
-Looking at PCA from a geometrical perspective, the dimensionality reduction problem is equivalent to the accurate reconstruction of the coordinate chart of the descriptor manifold.
-As outlined in \citep{astroMLText}, the coordinate chart constructed with the PCA projection in (\ref{pcaprojection}) is accurate for reasonably flat descriptor manifolds.
-When curvature effects become important, more advanced projection techniques (such as Locally Linear Embedding) have to be employed.
-
-%AP: Addressed dimensionality issues
+M(n)_{i}^r = V^T(n)_{ij}\tilde{M}_j^r \,\,\,\, ; \,\,\,\,  D(n)_i = V^T(n)_{ij}\tilde{D}_j.
+\end{equation}
+%
+Here we suppressed the first index of $M(n)$ for notational simplicity
+and we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$
+rows (i.e. $i$ can now range from $1$ to $n$). As described above, the
+expectation is that most of the cosmological information is contained
+in a small number of components $n<N_{b}$. We will describe in detail
+below the choice we make for $n$, together with the sensitivity of our
+results to this choice.
+
+Looking at PCA from a geometrical perspective, the dimensionality
+reduction problem is equivalent to the accurate reconstruction of the
+coordinate chart of the descriptor manifold. As outlined in
+ref.~\citep{astroMLText}, the coordinate chart constructed with the
+PCA projection in eq.~(\ref{pcaprojection}) is accurate for reasonably
+flat descriptor manifolds. When curvature becomes important, more
+advanced projection techniques (such as Locally Linear Embedding) have
+to be employed.  We postpone an investigation of such improvements to
+future work.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%
-\begin{figure*}
-\includegraphics[scale=0.4]{Figures/pca_components.eps}
-\caption{Principal Components of the Power Spectrum(red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange) descriptor spaces.
-The left plot shows the magnitudes of the PCA eigenvalues $S_i^2$, the right plot shows their cumulative sum.
-A dashed black line has been drawn corresponding to $n=3$ components}
-\label{pcafig}
-\end{figure*}
-%
-%AP: 3 is the dimensionality of our parameter space which may, or may not tell us something about the number of principal components
-%
-\begin{figure*}
-\includegraphics[scale=0.4]{Figures/robustness_pca_Omega_m-sigma8.eps}
-\caption{PCA projection dependence of the $1\sigma$ contours in the $(\Omega_m,\sigma_8)$ plane obtained from a mock observation constructed with the CFHTcov simulations.
-The different panels refer to the descriptors (from left to right, top to bottom) $V_0$, $\partial V_0$(PDF), $V_1$, $V_2$, Power Spectrum and Moments}
-\label{robustnessfig}
-\end{figure*}
-%
 
@@
 \label{results}
-This section describes the results we have obtained and is organized as follows.
-We first use our simulations to perform a robustness analysis of the parameter confidence intervals with respect to the number of PCA components used in the projection.
-We then show the cosmological constraints from the CFHTLenS data.
-Because of the relatively small size of this survey, degeneracy in the parameters can have undesirable effect on the constraints.
-To mitigate the effect of degeneracies, in addition to the usual $(\Omega_m,w,\sigma_8)$ parametrization, we consider a slightly different one, built with the parameter triplet $(\Omega_m,w,\Sigma_8)$ with $\Sigma_8(\alpha)=\sigma_8(\Omega_m/0.27)^\alpha$.
-While $\Omega_m$ and $\sigma_8$ are poorly constrained by CFHTLenS due to degeneracies, the $\Sigma_8(\alpha)$ combination lies on the smallest variance direction of $\mathcal{L}(\Omega_m,\sigma_8)$ for a suitable choice of $\alpha$, and hence has a much smaller relative uncertainty.
-We can derive this optimal value of $\alpha$ from the full three dimensional likelihood $\mathcal{L}(\Omega_m,w,\sigma_8)$, from which we can compute the expectation values
+
+This section describes our main results, and is organized as follows.
+We begin by showing the cosmological constraints from the CFHTLenS
+data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
+alternative parameterization, $(\Sigma_8,\alpha,w)$, with
+$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$.  We then use
+our simulations to perform a robustness analysis of the parameter
+confidence intervals with respect to the number of PCA components used
+in the projection.
+%We first use our simulations to perform a robustness analysis
+%of the parameter confidence intervals with respect to the number of
+%PCA components used in the projection. We then show the cosmological
+%constraints from the CFHTLenS data.
+%ZH: I reversed the order of the above two.  
+%    It is better to first show the constraints,  and only THEN we can discuss their robustness.
+%    Also I moved the discussion of \Sigma_8 down below.
+We finally study whether the constraints can be tightened by combining
+different descriptors. A summary with the complete set of results,
+along with the relevant Figures, is shown in Table \ref{summarytable}.
+
+%AP: Justified value of alpha=0.55
+
+%AP: Added inline description of the figures
+
+%ZH: I reversed the order of this and the next subsection
+\subsection{Cosmological constraints}
+%
+We first make use of equations
+(\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$
+constraints on cosmological parameters, using the triplet
+$(\Omega_m,\sigma_8,w)$.  Figures \ref{contours3single} shows the
+constraints in the $(\Omega_m,\sigma_8)$ plane, marginalized over $w$,
+for both the CFHTLenS data, as well as from the mock data in our
+simulations.  In Figure~\ref{contoursMoments}, we examine constraints
+from different sets of moments, as well as using different smoothing
+scales.  Figure~\ref{contours3singleRep} shows the confidence contours
+in the $(w,\Sigma_8)$ plane, marginalized over $\Omega_m$. As this
+figure shows, and as discussed further below, no meaningful
+constraints were found on $w$ from CFHTLenS alone.
+
+%ZH: I moved this here -- fits better:
+Because of the relatively small size of this survey, degeneracies
+among the parameters can have undesirable effects on the constraints.
+The well-known strong degeneracy between $\Omega_m$ and $\sigma_8$ is
+evident in the long ``banana'' shaped contours in Figures
+\ref{contours3single} and \ref{contoursMoments}.  To mitigate the
+effect of this degeneracy, in addition to the usual triplet
+$(\Omega_m,\sigma_8,w)$, we consider an alternative parameterization,
+built with the triplet $(\alpha,\Sigma_8,w)$ where $\alpha$ is a
+constant, and
+$\Sigma_8(\alpha)\equiv\sigma_8(\Omega_m/0.27)^\alpha$. While
+$\Omega_m$ and $\sigma_8$ are poorly constrained due to degeneracies,
+the $\Sigma_8(\alpha)$ combination lies in the direction perpendicular
+to the error ``banana'' at the pivot point $\Omega_m=0.27$.  
+%ZH:  added above, about the pivot point.  Please check this is OK (or modify).
+%     It depends on how you computed alpha (see below).
+This is the direction of the lowest variance
+$\mathcal{L}(\Omega_m,\sigma_8)$ for a suitable choice of $\alpha$,
+and hence has a much smaller relative uncertainty. We can derive the
+optimal value of $\alpha$ from the full three dimensional likelihood
+$\mathcal{L}(\Omega_m,w,\sigma_8)$, from which we can compute the
+expectation values
 \begin{equation}
@@
 %
-and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect to $\alpha$.
-This procedure yields a value $\alpha\approx0.55$ for the statistical descriptors that we consider, consistent  with what is found in the literature.
-
-We show the constraints in both the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes.
-We also show the $\Sigma_8$ marginalized likelihood.
-We finally study the effect of combining different descriptors, tightening the constraints.
-A summary with the complete set of results, along with the relevant Ffgures, is shown in Table \ref{summarytable}.
-
-%AP: Justified value of alpha=0.55
+and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect
+to $\alpha$. 
+%ZH: Is this done at fixed Omega_m=0.27, or is the averaging above over all Omega_m and sigma8 (and w) ?
+%    Let's make it clear.
+%    I think either is fine (as long as we make it clear), but I think usually, people fix Omega_m.
+%    This could make a difference in the best-fit alpha values.
+%    Also, which descriptor is being used?  Let's make that clear, too.
+This procedure yields a value $\alpha\approx0.55$ for the
+statistical descriptors that we consider, 
+%ZH: which statistical descriptor do you mean here?   Or is alpha the same for all?
+%    it would also be nice to show an error bar on alpha, if it isn't too much work to compute it (in 
+%    principle, the minimization procedure above, done over the 1000 realizations, must give an error bar).
+%    and also to give an indication of (A) how much alpha varies for different descriptors, and (B) how much
+%    it depends on Omega_m, sigma8, and w.
+consistent with what is found in the literature.
+%ZH:  We should give references, if we say the above.
+We show the probability distribution of the best-constrained parameter
+$\Sigma_8$ (marginalized over $\Omega_m$ and $w$) in Figure
+\ref{likelihoodSi8single}.
+
+We discuss the results of this section in \S~\ref{discussion} below.
 
 \subsection{Robustness}
-%
-The cosmological constraints should in principle be insensitive to $N_b$, but an inaccurate covariance (due to a limited number of realizations) can introduce a $N_b$ dependence.
-Here we give evidence that the cosmological constraints derived in this paper are numerically robust, i.e.
-they are reasonably stable once we consider a large enough number $n$ of Principal Components.
-Figure \ref{pcafig} shows the PCA eigenvalues that result from the SVD decomposition of our descriptor spaces, as well as the cumulative sum of these eigenvalues, normalized to 1.
-Figure \ref{robustnessfig} shows the dependence of the $(\Omega_m,\sigma_8)$ constraints on the number of principal components $n$, and clearly indicates that we only need a limited number of components in order to capture the cosmological information contained in our descriptors.
-The number of components with significant information content depends on the particular descriptor considered.
-This also addresses the inaccuracy of the MF emulator at high thresholds pointed out in Figure \ref{emulatorAccuracy}.
-By keeping a limited number of principal components we are able to prevent the inaccurate high--threshold bins, that have a low constraining power, from contributing to the parameter confidence levels.
-
-%AP: Added inline description of the figures
-
-\subsection{Cosmological constraints}
-%
-We make use of equations (\ref{parameterlikelihood})-(\ref{ennesigma}) to compute the $1\sigma$ constraints on different combinations of cosmological parameters: in Figures \ref{contours3single}, \ref{contoursMoments} we show the constraints in the $(\Omega_m,\sigma_8)$ plane, in Figure \ref{contours3singleRep} we focus on the $(w,\Sigma_8)$ plane.
-Additionally we show the $\Sigma_8$ likelihood function (marginalized over $\Omega_m$ and $w$) in Figure \ref{likelihoodSi8single}.
-We discuss these results in \S~\ref{discussion}.
+
+% ZH: we need to state somewhere above, clearly, the actual fiducial
+%binnings we used (and maybe recap it here, too)
+The cosmological constraints should in principle be insensitive to
+$N_b$, once a sufficient number of bins are used, but inaccuracies in
+the covariance (due to a limited number of realizations) can introduce
+an $N_b$ dependence.  Here we show that the cosmological constraints
+derived in this paper are numerically robust, i.e. they are reasonably
+stable, once we consider a large enough number $n$ of Principal
+Components.
+
+Figure~\ref{pcafig} shows the PCA eigenvalues from the SVD
+decomposition of our binned descriptor spaces (following the
+discussion in \S~\ref{pcasection}), as well as the cumulative sum of
+these eigenvalues, normalized to unity. Figure \ref{robustnessfig}
+shows the dependence of the $(\Omega_m,\sigma_8)$ constraints on the
+number of principal components $n$.
+
+These figures clearly indicate that we only need a limited number of
+components in order to capture the cosmological information contained
+in our descriptors. The eigenvalues diminish rapidly with $n$, and, in
+particular, the confidence contours converge to good ($\lesssim 10\%$)
+accuracy typically for $n=5-10$ (depending on the descriptor).
+%ZH: I added above.  I see later you quote larger n for V1 an V2, for 5% accuracy.
+This finding also addresses the inaccuracy of the MF emulator at high
+thresholds, pointed out in Figure~\ref{emulatorAccuracy}. By keeping a
+limited number of principal components, we are able to prevent the
+inaccurate high--threshold bins, which have a low constraining power,
+from contributing to the parameter confidence levels.
 
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Power Spectrum (red), $V_0$ (green), $V_1$ (blue), $V_2$ (black) and Moments (orange) statistics.
-We show the constraints from the data (left panel) and from a mock observation constructed using the mean of 1000 realizations in CFHTcov simulations as data (right panel).
-The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $w$.
-The parentheses near the descriptor label refer to the number of principal components.}
+\caption{$1\sigma$ (68\% CL) constraints on the $(\Omega_m,\sigma_8)$
+  parameter doublet using the power spectrum (red), the three
+  Minkowski Functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
+  the Moments (orange). We show the constraints from the data (left
+  panel) and from a mock observation constructed using the mean of
+  1000 realizations in the \texttt{CFHTcov} simulation suite (right
+  panel). The contours are calculated from the parameter likelihood
+  function $\mathcal{L}$ marginalized over $w$. The parentheses near
+  the descriptor label refer to the number of principal components
+  included.}
 \label{contours3single}
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ parameter doublet using the Moments, with different colors corresponding to different moment combinations: we show the results obtained using the one--point moments $\sigma_0^2,S_0,K_0$ (black, left and right panels).
-In the left panel we show the constraints obtained adding moments of gradients to the one--point moments, while in the right panel we combine the one--point momente measured at different smoothing scales.}
+\caption{$1\sigma$ (68\% CL) constraints on the $(\Omega_m,\sigma_8)$
+  parameter doublet using Moments, with different colors corresponding
+  to different moment combinations (see eq.~\ref{momentestimator} for
+  their definitions). We show the results from the one--point moments
+  $\sigma_0^2,S_0,K_0$ (black curves; both left and right panels). In
+  the left panel, we also show constraints obtained adding moments of
+  gradients to the one--point moments. In the right panel, we combine
+  one--point moments measured at different smoothing scales. }
 \label{contoursMoments}
@@
 \end{center}
-\caption{$1\sigma$ constraints on the $(w,\Sigma_8)$ parameter doublet from the CFHTLenS data, obtained with the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics.
-We show the constraints from the data.
-The contours are calculated from the parameter likelihood function $\mathcal{L}$ marginalized over $\Omega_m$.
-The parentheses near the descriptor label refer to the number of principal components.}
+\caption{$1\sigma$ (68\% C.L.) constraints on the $(w,\Sigma_8)$
+  parameter doublet from the CFHTLenS data, obtained with the power
+  spectrum (red), the three Minkowski Functionals ($V_0$: green,
+  $V_1$: blue, $V_2$: black) and the Moments (orange).
+%ZH: You had V0=blue and V1=green here, but the figure label shows the opposite. 
+%  I assume figure label was correct, but please double-check:
+%%%% $V_0$ (blue), $V_1$ (green), $V_2$ (black) and
+%  Moments (orange) statistics. 
+   The contours are calculated from the parameter likelihood function
+   $\mathcal{L}$ marginalized over $\Omega_m$, and the parentheses
+   near the descriptor label refer to the number of principal
+   components.}
 \label{contours3singleRep}
@@
 \end{center}
-\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the Power Spectrum (red), $V_0$ (blue), $V_1$ (green), $V_2$ (black) and Moments (orange) statistics.
-The likelihood has been marginalized over $\Omega_m$ and $w$.
-The parentheses near the descriptor label refer to the number of principal components.}
+\caption{The likelihood of the best-constrained parameter combination
+  $\Sigma_8(\alpha)\equiv\sigma_8(\Omega_m/0.27)^\alpha$ from the
+  CFHTLenS data, obtained with the power spectrum (red), the three
+  Minkowski Functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
+  the Moments (orange).
+%ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
+%  I assume figure label was correct, but please double-check:
+%%%%  the Power Spectrum (red), $V_0$ (blue), $V_1$ (green),
+%%%%  $V_2$ (black) and Moments (orange) statistics. 
+  The likelihood was computed with a constant optimized $\alpha=0.55$,
+  but marginalized over both $\Omega_m$ and $w$. 
+%ZH: so we should make clear what we did - I think you fixed alpha, but marginalized over Omega and w
+%    (technically, the best-fit alpha is a function of Omega and w, but this was not included in your
+%     calculation, right?)
+  The parentheses near the descriptor label refer to the number of
+  principal components.}
 \label{likelihoodSi8single}
@@
 Parameters & Descriptors & Short description & Relevant Figures \\ \hline \hline
-$(\Omega_m,\sigma_8)$ & PS,$V_0,V_1,V_2$,LM & Stability of contours & \ref{robustnessfig} \\ \hline 
 $(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
@@
 $\Sigma_8$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & $\mathcal{L}(\Sigma_8)$ from CFHTLenS & \ref{likelihoodSi8single} \\ \hline
+- & PS,$V_0,V_1,V_2$,LM & PCA eigenvalues  & \ref{pcafig} \\ \hline
+$(\Omega_m,\sigma_8)$ & PS,$V_0,V_1,V_2$,LM & Stability of contours & \ref{robustnessfig} \\ \hline 
 $(\Omega_m,\sigma_8)$ & PS(3)$\times V_0(5)\times V_1(20)\times V_2(20)\times$LM(9) & \pbox{20cm}{constraints from CFHTLenS \\ combining statistics} & \ref{contours3combined} \\ \hline
@@
 \end{tabular}
-\caption{Summary table of our results}
+\caption{Summary of our results and related figures.}
+%ZH: this is basically a list of figures.  It's a bit unusual to have such a table, but let's leave it in.
+%    I actually think it's quite useful.
+%    However: I suggest to make the rows be in the same order as the figures
+%    (start with Figures 3a,b, which are the main result). And, add the missing figures 7 and 8 for completeness.
 \label{summarytable}
@@
 %
+
+%--------------------------------------------------------
+%ZH: Also changed the order of the Figures
+%
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/pca_components.eps}
+%ZH: The right panel figure is mostly wasted, since it just shows ``1''.
+%    You should either cut the figure and restrict it to n<10 or n<15,
+%    or else maybe make the x axis logarithmic, to show the n<5 points better.
+\caption{Results from the Principal Components Analysis (PCA) of the
+  binned power spectrum (red), the three Minkowski Functionals ($V_0$:
+  green, $V_1$: blue, $V_2$: black) and the Moments (orange).
+%ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
+%  I assume figure label was correct, but please double-check:
+%%% the Power Spectrum(red), $V_0$
+%%%  (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange)
+  The left panel shows the magnitudes of the PCA eigenvalues $S_i^2$
+  and the right panel shows their cumulative sum, normalized to
+  unity. A dashed vertical (black) line has marks $n=3$ for
+  reference.}
+\label{pcafig}
+\end{figure*}
+%
+%AP: 3 is the dimensionality of our parameter space which may, or may not tell us something about the number of principal components
+%
+\begin{figure*}
+\includegraphics[scale=0.4]{Figures/robustness_pca_Omega_m-sigma8.eps}
+\caption{The dependence of the $1\sigma$ contours in the
+  $(\Omega_m,\sigma_8)$ plane on the number of PCA components,
+  obtained from a mock observation constructed with the
+  \texttt{CFHTcov} simulations. The different panels refer to the
+  different descriptors (from left to right, top to bottom) $V_0$,
+  $\partial V_0$(PDF), $V_1$, $V_2$, power spectrum and Moments.  The
+  labels in each panel show the number of PCA components included to
+  obtain contour with different colors.}
+\label{robustnessfig}
+\end{figure*}
+%
+
+%--------------------------------------------------------
 
@@
 \end{center}
-\caption{Combined $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ (left panel) and $(w,\Sigma_8)$ (right panel) doublets, using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange).
-The likelihood function has been marginalized over $w$ (left panel) and $\Omega_m$ (right panel).
-The parentheses near the descriptor labels refer to the number of principal components.}
+\caption{$1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ (left
+  panel) and $(w,\Sigma_8)$ (right panel) doublets, using the power
+  spectrum (PS) alone (red), the MFs alone (blue), as well as using
+  different combinations of descriptors: PS$\times$Moments (green),
+  PS$\times$MFs (black) and PS$\times$MFs$\times$Moments (orange). The
+  likelihood function has been marginalized over $w$ (left panel) and
+  $\Omega_m$ (right panel). The parentheses next to each descriptor
+  label refers to the number of PCA components included.}
 \label{contours3combined}
@@
 \end{center}
-\caption{$\Sigma_8$ parameter likelihood calculated from the CFHTLenS data using the PS (red), PS$\times$Moments (green), MFs (blue), MFs$\times$Power Spectrum (black) and MFs$\times$Power Spectrum$\times$Moments (orange).
-The likelihood function has been marginalized over $\Omega_m$ and $w$.
-The parentheses near the descriptor label refer to the number of principal components.}
+\caption{The probability distribution of the best-constrained
+  parameter $\Sigma_8$ from the CFHTLenS data, using the power
+  spectrum (PS) alone (red), the MFs alone (blue), as well as using
+  different combinations of descriptors: PS$\times$Moments (green),
+  PS$\times$MFs (black) and PS$\times$MFs$\times$Moments (orange).
+  The likelihood function has been marginalized over $\Omega_m$ and
+  $w$. The parentheses next to each descriptor label refers to the
+  number of PCA components.}
 \label{likelihoodSi8cross}
@@
 \subsection{Combining statistics}
-Combining of different statistics can tighten the constraints on cosmology.
-Previous work in this direction includes \citep{Companion}, where the authors combine the power spectrum and peak count statistics and  \citep{CFHTFu} where the authors combine quadratic statistics with the skewness of the CFHTLenS $\kappa$ fields.
-
-The procedure we adopt is the following:  Consider two descriptors, $d_{1,i},d_{2,i}$ where the index $i$ corresponds to the bin number of the particular descriptor.
-We compute the single descriptor constraints as in Figure \ref{robustnessfig} and we decide which is the minimum number of principal components $n_{1,2}$ needed for the constraints to be stable.
-We then construct the vector $d_{1\times2} = (d_1(n_1),d_2(n_2))$ and consider this as the combined descriptor vector.
-This procedure allows us to take the cross covariance between different descriptors.
-An analogous procedure can be used to combine multiple descriptors.
-We show in Figure \ref{contours3combined} the combined CFHTLenS constraints in the $(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes, and in Figure \ref{likelihoodSi8cross} the combined $\Sigma_8$ likelihood.
-We discuss our findings in the next section.
+
+Different statistics can include complementary cosmological
+information, allowing their combinations to tighten the
+constraints. Previous work using multiple lensing descriptors in
+CFHTLenS alone included combining the power spectrum and peak
+counts~\citep{Companion}, and combining quadratic (2PCF) statistics
+with the skewness of the CFHTLenS $\kappa$ field~\citep{CFHTFu}.
+%ZH: This was on the 3PCF, not the skewness -- right?  And didn't Shirasaki+Yoshida also combine PS+MF ?
+%    Please check and fix/complete these citations as necessary.
+
+The procedure we adopt here is as follows. Consider two binned
+descriptors, $d_{1,i},d_{2,j}$ where the indices $i,j$ correspond to
+bin numbers.  We first compute each single--descriptor constraint as a
+function of the number of PCA components, as in Figure
+\ref{robustnessfig}. We then determine the minimum number of PCA
+components $n_{1,2}$ needed for the constraints to be stable. We next
+construct the vector $d_{1\times2} = \{d_1(n_1),d_2(n_2)\}$ and
+consider this as the combined ($n_1+n_2$)--dimensional descriptor
+vector. This procedure naturally allows us to account for the
+cross--covariance between different binned descriptors. An analogous
+procedure can be used to combine multiple (three or more)
+descriptors.
+
+We show constraints from different descriptor combinations in the
+$(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes in Figure
+\ref{contours3combined}, and on the best-constrained parameter
+$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. We discuss these
+findings in the next section.
 
@@
 
-In this section we discuss the results outlined in section \S~\ref{results}, with particular focus on the constraints on cosmology.
-
-As pointed out in \S~\ref{pcasection}, the choice of the number of bins, $N_b$, is an important issue.
-In order for our results to be insensitive to $N_b$, we adopt a PCA projection technique to reduce the dimensionality of our descriptor spaces.
-In the left panel of Figure \ref{pcafig} we see that the PCA eigenvalues for our descriptors decrease about 4 orders of magnitude from $n=1$ to $n=3$, and looking at the right panel we see that we capture more than 99\%  of the descriptor variance even if we cut the PCA projection to the first 3 components.
-
-This does not mean that all the cosmological information is captured by the first 3 PCA components, and this is why we make a stability check by plotting the $1\sigma$ contour sizes as a function of $n$ in Figure \ref{robustnessfig}.
-Looking at the plot we can observe that, while the first 3 components capture essentially all the information contained in the Power Spectrum, this is not true for the remaining set of statistics.
-In particular we find that at least 5 components are necessary for $V_0$, and at least 20 components for $V_1,V_2$, in order for the $(\Omega_m,\sigma_8)$ contours to be stable at a $\sim$5\% level.
-All the 9 components are necessary for the Moments contours to be stable.
-
-Matters are slightly different when we study the $(w,\Sigma_8)$ constraints: in this case we find that the optimal choice for the three MFs, $(V_0,V_1,V_2)$, is $n=10$, while the Power Spectrum and Moments components remain at, respectively, 3 and 9 (figures supporting this choice not shown).
-
-We now discuss the main scientific findings of this work.
-In Figure \ref{contours3single} we show the $1\sigma$ constraints on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data.
-The MF constraints appear to be biased towards the low--$\sigma_8$, high--$\Omega_m$ region.
-Here and throughout the rest of the paper, we refer to "biased"("unbiased") as a best fit which is incompatible(compatible) with the accepted fiducial values at $1\sigma$.
-The best current values of $(\Omega_m,\sigma_8)$  \citep{PlanckXVI2013} lie beyond the 99\% likelihood contours (not shown).
-This may be due to uncorrected systematics in the CFHTLenS data, amplified by the $(\Omega_m,\sigma_8)$ degeneracy.
-When we try to constrain mock observations based on simulations (shown in the left panel of Figure \ref{contours3single}), we recover the correct position of the $1\sigma$ contours.
-It is important to note, however, that the mock observations to which the right panel of Figure \ref{contours3single} refers, were built with the mean of $R=1000$ realizations of the CFHTcov simulations.
-We found that it is possible to find some realizations for which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right corner, though the likelihood of this happening is very small ($\lesssim1\%$).
+In this section we discuss the results shown in \S~\ref{results}
+above, with particular focus on the constraints on cosmology.
+
+As pointed out in \S~\ref{pcasection}, the choice of the number of
+bins, $N_b$, is an important issue. In order to ensure that our
+results are insensitive to $N_b$, we adopted a PCA projection
+technique to reduce the dimensionality of our descriptor spaces. The
+left panel of Figure~\ref{pcafig} shows that the PCA eigenvalues for
+all of our descriptors decrease by about 4 orders of magnitude from
+$n=1$ to $n=3$. The right panel of this figure shows that more than
+99\% of the descriptor variances are captured by including only the
+first $n=3$ components.
+
+%ZH: I added explanation:
+This does not necessarily mean, however, that the cosmological
+information is captured by the first 3 PCA components: in principle,
+one of the higher-$n$ PCA components could have an unusually strong
+cosmology-dependence, and could impact the confidence levels.  To
+address this possibility, we determined the $1\sigma$ contour sizes as
+a function of $n$ in Figure~\ref{robustnessfig}.  This figure shows
+that the first 3 components indeed capture essentially all the
+information contained in the power spectrum. However, this is not true
+for the other descriptors. In particular, we find that $n\geq5$
+components are necessary for $V_0$, and $n\geq20$ components for $V_1$
+and $V_2$, in order for the $(\Omega_m,\sigma_8)$ contours to be
+stable at the $\sim$5\% level. All nine moments need to be included
+for the Moments contours to be stable to this accuracy.
+
+These results are slightly different when we study the $(w,\Sigma_8)$
+constraints (with $\alpha$ fixed at $\alpha=0.55$ as discussed
+above). In this case we find that the optimal choice for all three MFs
+is $n=10$, while the number of components required for the PS and
+Moments remain at $n=3$ and $n=9$, respectively. (These results are
+not shown, but obtained analogously to the Figures above.)
+% (in order to figures supporting this choice not shown).
+
+We now discuss the main scientific findings of this work. In
+Figure~\ref{contours3single}, we show the $1\sigma$ constraints on the
+$(\Omega_m,\sigma_8)$ doublet from the CFHTLenS data. The MF
+constraints appear to be biased towards the low--$\sigma_8$,
+high--$\Omega_m$ region. Here and throughout the remainder of this
+paper, by "biased" (or "unbiased") we refer to being incompatible (or
+compatible) with the concordance fiducial values at $1\sigma$ obtained
+in other experiments. For example, the current best-fit values of
+$(\Omega_m,\sigma_8)=(...,...)$ from cosmic microwave background
+anisotropies measured by the Planck
+%ZH: Let's give the actual numbers here.  I would also quote WMAP9
+%    for these numbers -- there's currently a sigma8-discrepancy that
+%    needs to be resolved between these two (and my suspicion is that WMAP is correct :)
+satellite~\citep{PlanckXVI2013} lie beyond the 99\% likelihood
+contours obtained from the three MFs (not shown).
+
+This discrepancy may be due to uncorrected systematics in the CFHTLenS
+data, amplified by the $(\Omega_m,\sigma_8)$ degeneracy.  As a test of
+our analysis pipeline, when we try to constrain mock observations
+based on simulations (shown in the
+%left
+%ZH: changed left->right
+right panel of Figure \ref{contours3single}), we recover the correct
+input position of the $1\sigma$ contours.  It is important to note,
+however, that the mock observations to which the right panel of Figure
+\ref{contours3single} refers, were built with the mean of $R=1000$
+realizations of the \texttt{CFHTcov} simulations. We found that it is
+possible to find some rare (10 out of the 1,000) realizations for
+which the best fit for $(\Omega_m,\sigma_8)$ lies in the lower right
+corner, near the location of the best-fit from the data. While this
+could provide an alternative explanation of the bias from the MFs, the
+likelihood of this happening is very small ($\lesssim1\%$).
 
@@
 
-We observe that the Moments give the tightest constraint on $(\Omega_m,\sigma_8)$.
-This constraint is also unbiased in the sense that it includes the best current values for these parameters within 1$\sigma$.
-The fact that the Moments are useful for deriving unbiased cosmological constraints has been noted in previous work  \citep{PetriSpurious}.
-
-In order to determine the origin of the tight bounds derived from moments, we studied the individual contributions of each of the moments to the constraining power.
-Figure \ref{contoursMoments} shows the evolution of the $(\Omega_m,\sigma_8)$ constraints as we add higher order moments to the descriptor set.
-Since we are constraining  3 cosmological parameters, we start by considering the set of the three one--point moments $(\sigma_0^2,S_0,K_0)$ and then add the remaining six moments of gradients one by one, starting from the quadratic moments.
-We see that the biggest improvement on the parameter bounds comes from including quartic moments of gradients (i.e.
-$K_i$ with $i\ge1$) in the descriptor set.
-This might explain why \citep{CFHTFu} find only unimpressive ($\sim10\%$) contour tightening when adding three point correlations to quadratic statistics, since the main improvement comes from higher moments of $\kappa$ derivatives.
-\citep{CFHTFu} consider one--point third order moments where multiple smoothing scales are combined.
-Figure \ref{contoursMoments} however shows that smoothing scale combinations are not as effective as moments of gradients in costraining the $(\Omega_m,\sigma_8)$ doublet.
-Our results agree with  \citep{moments4}  which found that the kurtosis of the shear field can help in breaking degeneracies between $\Omega_m$ and $\sigma_8$.
-We show that considering quartic moments of gradients further helps in breaking this degeneracy.
-
-The bias in the $(\Omega_m,\sigma_8)$ constraints is amplified by the cosmological degeneracy of these parameters.
-To mitigate this effect, we consider the combination of $\Omega_m$ and $\sigma_8$ that lies along the non-degenerate direction, namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$.
-Figure \ref{contours3singleRep} shows the $1\sigma$ constraints for the $(w,\Sigma_8)$ doublet, while Figure \ref{likelihoodSi8single} the marginalized $\Sigma_8$ likelihood from the CFHTLenS data.
-The CFHTLenS survey constrains the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in agreement with values previously published by the CFHTLenS collaboration \citep{CFHTKilbinger}.
-The current dataset is not sufficient to constrain $w$ to a reasonable precision, even if Figure \ref{contours3combined} right panel shows that the Moments are able to confine $w$ to isolated regions in parameter space.
-At the current stage of our analysis, $w=-1$ seems to be excluded at the $1\sigma$ level.
+We observe that the Moments give the tightest constraint on
+$(\Omega_m,\sigma_8)$.  Furthermore, this constraint is unbiased, in
+the sense defined above: it includes the current concordance values
+for these parameters within 1$\sigma$.  This leads us to conclude that
+the bias in the constraints from the MFs is due to systematic errors,
+rather than the rare statistical fluctuations found above.
+%ZH:  I guess the natural question: if you look at those ~10 realizations which give biased best-fits from the MFs,
+%     do they also give biased fits from the Moments?  I would guess so.
+The fact that the Moments are useful for deriving unbiased
+cosmological constraints has been noted in previous work, which
+examined the biases caused by spurious shear
+errors~\citep{PetriSpurious}.
+
+In order to determine the origin of the tight bounds derived from
+moments, we studied the contribution of each individual moment to the
+constraints. Figure \ref{contoursMoments} shows the evolution of the
+$(\Omega_m,\sigma_8)$ constraints as we add increasingly higher-order
+moments to the descriptor set. Since we are constraining 3
+cosmological parameters, we start by considering the set of the three
+traditional one--point moments which do not involve gradients,
+i.e. the variance, skewness, and kurtosis $(\sigma_0^2,S_0,K_0)$. We
+then add the remaining six moments of gradients one by one, starting
+from the quadratic moments.
+
+Figure \ref{contoursMoments} shows that the biggest improvement on the
+parameter bounds comes from including quartic moments of gradients
+(i.e. $K_i$ with $i\ge1$) in the descriptor set. This might explain
+why \citep{CFHTFu} find only relatively weak contour tightening
+($\sim10\%$) when adding three--point correlations to quadratic
+statistics, since the main improvement comes from higher moments of
+$\kappa$ derivatives. Ref.~\citep{CFHTFu} consider one--point,
+third--order moments, combined for multiple smoothing scales. Figure
+\ref{contoursMoments} explicitly shows, however, that smoothing scale
+combinations are not as effective as moments of gradients in
+constraining the $(\Omega_m,\sigma_8)$ doublet. Our results agree with
+an early prediction \citep{moments4} that the kurtosis of the shear
+field can help in breaking degeneracies between $\Omega_m$ and
+$\sigma_8$.  Here we found that considering quartic moments of
+gradients further helps in breaking this degeneracy.
+
+As noted above, the bias in the $(\Omega_m,\sigma_8)$ constraints is
+amplified by the cosmological degeneracy of these parameters. To
+mitigate this effect, we consider the combination of $\Omega_m$ and
+$\sigma_8$ that lies orthogonal to the most degenerate direction,
+namely $\Sigma_8=\sigma_8(\Omega_m/0.27)^{0.55}$. Figure
+\ref{contours3singleRep} shows the $1\sigma$ constraints for the
+$(w,\Sigma_8)$ doublet, while Figure \ref{likelihoodSi8single} shows
+the marginalized $\Sigma_8$ likelihood from the CFHTLenS data. The
+CFHTLenS survey constrains the $\Sigma_8$ combination to a value of
+$\Sigma_8=0.75\pm0.04(1\sigma)$ using the full descriptor set, in
+agreement with values previously published by the CFHTLenS
+collaboration \citep{CFHTKilbinger}.
+
+These figures also show that the current dataset is insufficient to
+constrain $w$ to a reasonable precision.
+%ZH: Added this.  And I think it's nice that we could clarify the origin of the w=-2 best-fit...
+This is consistent with the previous analyses of
+CFHTLenS~\citep{CFHTKilbinger,CFHTFu,Companion,CFHTMasato}.  We also
+note that ref.~\citep{CFHTMasato} obtained the best-fit value of
+$w\approx -2$ (but with large errors that include $w=-1$ at
+1$\sigma$).  We found a similar result when using a Fisher matrix to
+compute confidence levels.  We thus attribute this bias to the
+assumption of linear cosmology-parameter dependence of the
+descriptors.  
+%
+Although the right panel in Figure
+\ref{contours3combined} shows that the Moments confine $w$ to isolated
+regions in parameter space, we note that $w=-1$, the value favored by
+several other existing experiments, is excluded at the $1\sigma$
+level. The $2\sigma$ contours (not shown in the figure) close, and
+include $w=-1$.
+%ZH: Added above.  OK?
 
@@
 
-Regarding the parameter biases, our results are in accordance with  \citep{PetriSpurious}, namely, that unaccounted systematics result in larger parameter biases when the constraints are derived from the MFs, and that the LM statistic is less biased.
-However, for the CFHTLenS data the MFs can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$ (Figure \ref{likelihoodSi8single}).
+Regarding the parameter biases, our results overall are in accordance
+with \citep{PetriSpurious}, namely, that unaccounted systematics
+result in larger parameter biases when the constraints are derived
+from the MFs, and that the LM statistic is less biased. However, for
+the CFHTLenS data the MFs can still effectively constrain the
+non-degenerate direction in parameter space, $\Sigma_8$ (Figure
+\ref{likelihoodSi8single}).
 
@@
 
-We next studied whether the combination of different statistical descriptors can help in tightening the cosmological constraints.
-We show the effects of some of these combinations in Figures \ref{contours3combined} and \ref{likelihoodSi8cross}.
-The left panel of Figure \ref{contours3combined} shows that, although combining the Power Spectrum with the Minkowski Functionals and Moments helps in shrinking the $(\Omega_m,\sigma_8)$ constraints, it does not help in reducing the inherent parameter bias.
-In the right panel of Figure \ref{contours3combined} we can see that even with these statistics combined, $w$ remains essentially unconstrained.
-Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is already well constrained by any of the descriptors alone, without the need of combining different descriptors.
+Finally, we studied whether the combination of different statistical
+descriptors can help in tightening the cosmological constraints. We
+show the effects of some of these combinations in Figures
+\ref{contours3combined} and \ref{likelihoodSi8cross}. The left panel
+of Figure \ref{contours3combined} shows that, although combining the
+power spectrum with the Minkowski Functionals and Moments helps
+tighten the $(\Omega_m,\sigma_8)$ constraints, it does not help in
+reducing the inherent parameter bias. The right panel of Figure
+\ref{contours3combined} shows that even with these statistics
+combined, $w$ remains essentially unconstrained. Figure
+\ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
+already well constrained by any of the descriptors alone, without the
+need of combining different descriptors.
+%ZH: added this
+This further clarifies that the non-quadratic descriptor mainly help
+to break degeneracies, tightening contours along the
+degenerate direction.
 
@@
 In this final section we summarize the main conclusions of this work:
+
 \begin{itemize}
-\item We find that the Power Spectrum combined with the Moments of the $\kappa$ field provides the tightest constraint on the $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS survey data.
-The tightness of these constraints comes mainly from the moments.
-Evidence of the unbiased nature of constraints from the Moments has been found in \citep{PetriSpurious}.
-We find that the biggest improvement in bounds on these parameter is achieved when we include the quartic moments of gradients in the descriptor set.
-This improvement cannot be obtained by combining one-point moments at different smoothing scales
-\item Although weak lensing surveys are a promising technique to constrain the DE equation of state parameter $w$, reasonable constraints cannot be obtained with the CFHTLenS survey alone, even when using additional sets of descriptors that go beyond the standard quadratic statistics.
-\item When studying the cosmological information contained in the CFHTLenS data, special attention must be paid to the effect of residual systematic biases.
-While it seems these residual systematics are not important when constraining cosmology with the Power Spectrum alone, we find that these systematics need to be corrected to obtain sensible constraints on the $(\Omega_m,\sigma_8)$ doublet using the Minkowski Functionals.
-\item For the CFHTLenS data set, Minkowski functionals can effectively constrain the non-degenerate direction in parameter space, $\Sigma_8$, where the amplifying effects of degeneracy are mitigated.The Minkowski functionals alone are sufficient to constrain the $\Sigma_8$ combination to a value of $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level.
-This agrees with the value previously published by the CFHTLenS collaboration within $1\sigma$.
-Some tensions with Planck \citep{PlanckXVI2013} still remain.
+
+\item We find that the power spectrum, combined with the Moments of
+  the $\kappa$ field provides the tightest constraint on the
+  $(\Omega_m,\sigma_8)$ doublet from the CFHTLenS survey data. The
+  tightness of these constraints comes mainly from the
+  Moments. Evidence of the unbiased nature of constraints from the
+  Moments has been found in \citep{PetriSpurious}. We further find
+  that the largest improvement on parameter bounds is achieved when we
+  include the quartic moments of gradients in the descriptor set. This
+  level of improvement cannot be achieved by combining one-point
+  moments at different smoothing scales.
+
+\item Although weak lensing surveys are a promising technique to
+  constrain the DE equation of state parameter $w$, reasonable
+  constraints cannot be obtained with the CFHTLenS survey alone, even
+  when using additional sets of descriptors that go beyond the
+  standard quadratic statistics.
+
+\item When studying the cosmological information contained in the
+  CFHTLenS data, special attention must be paid to the effect of
+  residual systematic biases. While these residual systematics are
+  found to be unimportant when constraining cosmology with the power
+  spectrum alone, we find that these systematics need to be corrected
+  to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
+  using the Minkowski Functionals.
+
+\item For the CFHTLenS data set, Minkowski functionals can effectively
+  constrain the non-degenerate direction in parameter space,
+  $\Sigma_8$, where the amplifying effects of degeneracy are
+  mitigated.The Minkowski functionals alone are sufficient to
+  constrain the $\Sigma_8$ combination to a value of
+  $\Sigma_8=0.75\pm0.04$ at $1\sigma$ significance level. This agrees
+  with the value previously published by the CFHTLenS collaboration
+  within $1\sigma$. Some tensions with Planck \citep{PlanckXVI2013}
+  still remain.
+
 \end{itemize}
 
-Possible future extensions of this work include simulating higher dimensional parameter spaces (possibly including varying Hubble parameter $H_0$ and the running of the DE equation of state $w_1$), and combining constraints from different cosmological probes (data from Planck for example), that can help in breaking the $\Omega_m,\sigma_8$ degeneracy, and application of our analysis to larger survey data sets.
+Possible future extensions of this work include simulating
+higher--dimensional parameter spaces (including, for example, the
+Hubble constant $H_0$, and allowing a tilt in the power spectrum or a
+time-dependence of the DE equation of state $w$), and combining the
+CFHTLenS constraints with different cosmological probes from
+large-scales structures and the CMB. The latter can help in breaking
+the $\Omega_m,\sigma_8$ degeneracy, and allow improvements in the the
+constraints on $w$.  The techniques developed here can be applied to
+larger, soon-forthcoming survey data sets.
+%ZH: we should cite the dark energy survey (DES), and Subaru, and maybe also WFIRST and LSST here.
 
@@
 \section*{Acknowledgements}
-The simulations referenced in this work were performed at the NSF Extreme Science and Engineering Discovery Environment (XSEDE), supported by grant number ACI-1053575, and at the New York Center for Computational Sciences, a cooperative effort between Brookhaven National Laboratory and Stony Brook University, supported in part by the State of New York.
-This work was supported in part by the U.S.
-Department of Energy under Contract No.
-DE-AC02-98CH10886 and Contract No.
-DE-SC0012704, and by the NSF Grant No.
-AST-1210877 (to Z.H.) and by the Research Opportunities and Approaches to Data Science (ROADS) program at the Institute for Data Sciences and Engineering at Columbia University.
+
+The simulations in this work were performed at the NSF Extreme Science
+and Engineering Discovery Environment (XSEDE), supported by grant
+number ACI-1053575, at the Yeti computing cluster at Columbia
+University,
+%ZH: added Yeti
+and at the New York Center for Computational Sciences, a cooperative
+effort between Brookhaven National Laboratory and Stony Brook
+University, supported in part by the State of New York. This work was
+supported in part by the U.S. Department of Energy under Contract
+Nos. DE-AC02-98CH10886 and DE-SC0012704, and by the NSF Grant
+No. AST-1210877 (to Z.H.) and by the Research Opportunities and
+Approaches to Data Science (ROADS) program at the Institute for Data
+Sciences and Engineering at Columbia University.
 

### 2015-03-19 Paper_minkowski/Figures/generate.py

@@ -183,7 +183,8 @@ def pca(cmd_args):
 	#Draw a line at 3 components
 	ax[0].plot(3*np.ones(100),np.linspace(1.0e-10,1.0e2,100),color="black",linestyle="--")
 	ax[1].plot(3*np.ones(100),np.linspace(0.9,1.01,100),color="black",linestyle="--")
-	ax[1].set_ylim(0.9,1.01)
+	ax[1].set_ylim(0.98,1.001)
+	ax[1].set_xscale("log")
 
 	#Legend
 	ax[0].legend()
@@ -198,6 +199,7 @@ def pca(cmd_args):
 	ax[1].set_ylabel(r"$\Sigma_{i=0}^n\Sigma^2_i/\Sigma^2_{tot}$",fontsize=18)
 
 	#Save figure
+	fig.tight_layout()
 	fig.savefig("pca_components.{0}".format(cmd_args.type))
 
 ##################################################################################################################################################

### 2015-04-16 jia/stampede_peakpeak.py
regular update

@@ -90,31 +90,31 @@ def single_corr(iRcosmosigmaG, edges = edges):
 
 pool = MPIPool()
 
-#cosmosigmaG_arr = [[cosmo, sigmaG] for sigmaG in sigmaG_arr[::-1] for cosmo in cosmo_arr]
-#def create_peakpeak_arr (cosmosigmaG):
-	#cosmo, sigmaG = cosmosigmaG
-	#fn_kappa = peaks_corr_dir+'sum/Corr_kappa_sigma%02d_%s.npy'%(sigmaG*10, cosmo)
-	#fn_counts = peaks_corr_dir+'sum/Corr_counts_sigma%02d_%s.npy'%(sigmaG*10, cosmo)
-	#if os.path.isfile(fn_kappa) and os.path.isfile(fn_counts):
-		#return None
-	#else:
-		#RcosmosigmaG = [[R, cosmo, sigmaG] for R in R_arr]
-		#peakpeak_arr = array(map(single_corr, RcosmosigmaG))
-		#save(fn_kappa, peakpeak_arr[:,0,:])
-		#save(fn_counts, peakpeak_arr[:,1,:])
-		#return None
-#pool.map(create_peakpeak_arr, cosmosigmaG_arr)
+cosmosigmaG_arr = [[cosmo, sigmaG] for sigmaG in sigmaG_arr[::-1] for cosmo in cosmo_arr]
+def create_peakpeak_arr (cosmosigmaG):
+	cosmo, sigmaG = cosmosigmaG
+	fn_kappa = peaks_corr_dir+'sum/Corr_kappa_sigma%02d_%s.npy'%(sigmaG*10, cosmo)
+	fn_counts = peaks_corr_dir+'sum/Corr_counts_sigma%02d_%s.npy'%(sigmaG*10, cosmo)
+	if os.path.isfile(fn_kappa) and os.path.isfile(fn_counts):
+		return None
+	else:
+		RcosmosigmaG = [[R, cosmo, sigmaG] for R in R_arr]
+		peakpeak_arr = array(map(single_corr, RcosmosigmaG))
+		save(fn_kappa, peakpeak_arr[:,0,:])
+		save(fn_counts, peakpeak_arr[:,1,:])
+		return None
+pool.map(create_peakpeak_arr, cosmosigmaG_arr)
 
-for cosmo in cosmo_arr:
-	for sigmaG in (1.0,):#sigmaG_arr:
[…]

### 2015-04-16 jia/stampede_peakpeak.py
regular update

@@ -41,6 +41,8 @@ maskGen = lambda i, sigmaG: WLanalysis.readFits(backup_dir+'mask/CFHT_mask_ngal5
 
 ipeaklist_fn = lambda cosmo, R, sigmaG: peaks_corr_dir+'peaks_corr_single/%s/sigma%02d/Peaklist_sigma%02d_%s_%04dr.npy'%(cosmo, sigmaG*10, sigmaG*10, cosmo, R)
 
+icorr_fn = lambda cosmo, R, sigmaG: peaks_corr_dir+'peaks_corr_single/%s/sigma%02d/Corrlist_sigma%02d_%s_%04dr.npy'%(cosmo, sigmaG*10, sigmaG*10, cosmo, R)
+
 mask_all_arr = array([[maskGen(i, sigmaG) for sigmaG in sigmaG_arr]for i in i_arr])
 #i, R, cosmo, sigmaG = 1, 99, cosmo_arr[5], 8.9
 def single_peaklist(i, cosmo, R, sigmaG):
@@ -73,19 +75,35 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	'''	
 	R, cosmo, sigmaG = iRcosmosigmaG
 	
-	fn = ipeaklist_fn(cosmo, R, sigmaG)
+	fn = icorr_fn(cosmo, R, sigmaG)
 	if not os.path.isfile(fn):
-		ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
-		save(fn, ipeaklist)
+		if not ipeaklist_fn(cosmo, R, sigmaG):
+			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
+			save(fn, ipeaklist)
+		else:
+			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
+		out_DDRR = zeros(len(edges)-1)
+		out_Corr = zeros(len(edges)-1)
+		for i in range(len(edges)-1):
+			idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
+			out_DDRR[i] = len(idx)
+			out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
+		save(fn, [out_Corr, out_DDRR])
 	else:
-		ipeaklist = load(fn)
[…]

### 2015-04-16 jia/stampede_peakpeak.py
regular update

@@ -77,7 +77,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	
 	fn = icorr_fn(cosmo, R, sigmaG)
 	if not os.path.isfile(fn):
-		if not ipeaklist_fn(cosmo, R, sigmaG):
+		if not os.path.isfile(ipeaklist_fn(cosmo, R, sigmaG)):
 			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
 			save(fn, ipeaklist)
 		else:

### 2015-04-16 Paper_minkowski/Figures/generate.py
sigma --> S

@@ -216,8 +216,8 @@ def pca(cmd_args):
 	#Labels
 	ax[0].set_xlabel(r"$i$",fontsize=18)
 	ax[1].set_xlabel(r"$n$",fontsize=18)
-	ax[0].set_ylabel(r"$\Sigma^2_i$",fontsize=18)
-	ax[1].set_ylabel(r"$\Sigma_{i=0}^n\Sigma^2_i/\Sigma^2_{tot}$",fontsize=18)
+	ax[0].set_ylabel(r"$S^2_i$",fontsize=18)
+	ax[1].set_ylabel(r"$\Sigma_{i=0}^n S^2_i/S^2_{tot}$",fontsize=18)
 
 	#Save figure
 	fig.tight_layout()

### 2015-04-16 Paper_minkowski/Submission/reply/reply_referee.tex
added submission files

\documentclass[11pt]{article}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hyperref}

\addtolength{\hoffset}{-2.5cm}
\addtolength{\textwidth}{4.5cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textheight}{4.5cm}

\begin{document}

\title{Reply to referee's comments, DC11786/Petri}
\author{}
\date{}

\maketitle

\noindent
We thank the referee for the interesting and insightful comments, which we address in this document.

\section*{General comments}

\begin{itemize}
\item \textit{Some cited papers do not match the description}: the desctiptions and references have been updated. The suggested references have been added.
\item \textit{Missing reference to Simon et. al.}: the reference has been added.
\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Caucky problem well defined. The appropriate explanation has been added to the text.

\item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
\item \textit{Cubic and quartic moments notations}: we are aware that the definitions of $S_i,K_i$ we adopt are different than the ones provided in [38,39]. Within our statistical framework, these definition mismatches do not matter as they are related to each other via a constant lineat transformation that drops out in the likelihood calculations. The typo $K_4\leftrightarrow K_3$ has been corrected. 
\item \textit{Confusion between $R=1000$ and the 50 independent $N$--body runs in \texttt{CFHTcov}}: the covariance matrices are always estimated from the $R=1000$ lensing field realizations. We believe that the $R$ realizations in the \texttt{CFHTcov} ensemble are more independen than the ones in the \texttt{CFHTemu1} ensemble due to the fact that \texttt{CFHTcov} is bases on 50 independent $N$--body runs. An appropriate explanation has been added to the text. 
\item \textit{Equation (15) (now equation (16)}: here, as throughout the paper, $R=1000$. We added the appropriate clarification
\item \textit{"For this reason, the normalization constant in equation (12) is also model–independent"}: the sentence has been deleted
\item \textit{Accuracy vs relative error}: the wording "accuracy" has been changed to "relative error". The relative error of the PS emulator at low $l$ has been correctly updated to 20\%
\item \textit{Confusion deriving from the $p$ index suppression}: the $p$ index in equation (21) has been reinstated. The sentence "we suppressed the first index of $M(n)$ for notational simplicity" has been deleted

\item \textit{Comment of the large number of components needed in the PCA}: the referee is correct, one of the reasons why large numbers of PCA components are needed might be due to how the PCA is performed. Taking into account the correlation between errors in different bins (i.e. including the covariance matrix due to cosmic variance) will likely reduce the number of components needed. Unfortunately the standard PCA formalism does not allow for such generality. We are currently exploring different extensions to the PCA formalism, whose results will be included in future work

\item \textit{Citation to Heymans et al. (2013) for tomographic lensing constraints}: the citation has been addded

\item \textit{Logic and context of the sentence "We thus attribute this bias to the assumption of linear cosmology-parameter dependence"}: the Fisher matrix formalism is the linear order approximation of our emulator. Using the Fisher matrix in our case would be an oversimplification. A clarifying sentence has been added in the appropriate section

\end{itemize}

\section*{Typos}

\begin{itemize}
\item \textit{"Section III-B first sentence: no 'of'"}: fixed
\item \textit{"eq. (13) 2nd line: the first vector should be transposed"}: fixed
\item \textit{"page 7: thW N = 91 models"}: fixed
\item \textit{"page 8: Odd expression 'In the latter'"}: changed with "in the next section"
\item \textit{"Fig. 7: Labels on y-axes should probably be small sigma"}: $\Sigma_i$ has been replaced with $S_i$

\end{itemize}

\end{document}

### 2015-04-16 Paper_minkowski/Submission/paper.tex
added submission files

--- 2015-03-19 Paper_minkowski/paper.tex
@@
-%\documentclass[useAMS, usenatbib,usegraphicx,letter]{mn2e}
-%\documentclass[11pt]{article}
 \documentclass[reprint,aps,prd,superscriptaddress,showkeys,showpacs]{revtex4-1}
@@
 }
-% \usepackage{graphicx}
-% \usepackage{epstopdf}
-% \usepackage{natbib}
 
@@
 
-%ZH: changed title a bit
-\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from Moments and Minkowski Functionals}
+\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from moments and Minkowski functionals}
 
@@
 
-%ZH: I reworded the abstract
 \begin{abstract}
@@
 convergence field, including a set of moments (up to $4^{\rm th}$
-order) and Minkowski Functionals, using publicly available data from
+order) and Minkowski functionals, using publicly available data from
 the 154\,deg$^2$ CFHTLenS survey. We utilize a suite of ray--tracing
@@
 shape noise in the CFHTLenS catalogs. We then build an emulator that
-interpolates the simulated features as a function of
+interpolates the simulated descriptors as a function of
 $(\Omega_m,w,\sigma_8)$, and use it to compute the likelihood function
@@
 C.L.), in agreement with previous values. We find that constraints on
-the $(\Omega_m,\sigma_8)$ doublet from the Minkowski Functionals
+the $(\Omega_m,\sigma_8)$ doublet from the Minkowski functionals
 suffer a strong bias. However, high-order moments break the
@@
 these parameters with no apparent bias.  The main contribution comes
-from quartic moments of gradients.
+from quartic moments of derivatives.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
-%
 
@@
 fields. Among these, high--order moments
-(\citep{moments1,moments2,moments3,moments4,moments5,moments6}),
-three--point functions (\citep{3pcf1,3pcf2}), bispectra
+(\citep{moments1,moments2,moments3,moments4,moments5}),
+three--point functions (\citep{3pcf1,3pcf2,3pcf3}), bispectra
 (\citep{bispectrum1,bispectrum2,bispectrum3,bispectrum4}), peak counts
-(\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6}) and Minkowski
+(\citep{peaks1,peaks2,peaks3,peaks4,peaks5,peaks6,peaks7,peaks8}) and Minkowski
 Functionals (\citep{MinkJan,Petri2013}) have been shown to improve
@@
 $\sigma_8$ and the dark energy (DE) equation of state $w$.  The
-statistics we consider in this work are the Minkowski Functionals
+statistics we consider in this work are the Minkowski functionals
 (MFs) and the low--order moments (LM) of the convergence field.
-%ZH: I moved this here from the simulation section. Fits better here.
 Cosmological parameter inferences from CFHTLenS have been obtained
@@
 three--point correlations as an additional probe for cosmology, and
-found modest ($10-20\%$) improvements over the 2PCF.  Liu et
-al.~\citep{Companion} have found a more significant ($50-60\%$)
+found modest ($10-20\%$) improvements over the 2PCF. \textbf{These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.
+
+Liu et al.~\citep{Companion} have found a more significant ($50-60\%$)
 tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
-abundance of WL peaks.
-%ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
+abundance of WL peaks. Cosmological constraints using WL peaks in CFHTLenS Stripe82 data
+have also been investigated by Liu et. al.~\citep{Stripe82}. 
 Finally, closest to the present paper, Shirasaki \&
@@
 each descriptor.  Second, we include the LMs as a set of new
-descriptors; these yield to the tightest and least biased constraints.
+descriptors; these yield the tightest and least biased constraints.
 
@@
 the parameter space. We call the statistical weak lensing observables
--- the Power Spectrum, Minkowski Functionals, and Moments --
+-- the power spectrum, Minkowski functionals, and moments --
 "descriptors" throughout the paper. We discuss the calculation of the
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%% DATA AND SIMULATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Data and simulations}
@@
 \label{cfhtdatareduction}
-%
-
-%ZH: Added lead-in sentence, and moved the last sentence up here:
+
 In this section, we briefly summarize our treatment of the public
@@
 \end{equation}
-%
 where the smoothing scale $\theta_G$ has been fixed at 1.0\,arcmin
@@
 field,
-%
 \begin{equation}
@@
 \end{equation}
-%
 The simulated $\kappa$ maps we create below are $12~\mathrm{deg}^2$ in
@@
 ($n_{gal}$) falling within its window.  
-%ZH: I paraphrased the above sentence, because it was ambiguous.  Please check that this is what you meant to say.
 We then smooth this galaxy surface density map with the same Gaussian
@@
 relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
-0.046, 0.96). 
-%ZH: cite WMAP9 paper here for the parameter choices.
+0.046, 0.96) (see \citep{WMAP9}).
 We sampled the $D$--dimensional ($D=3$ in this case) parameter space
@@
 by itself has strong parameter degeneracies.
-%ZH: Added justification of large ranges above.
 We next map this sampling box $\Pi$ into a hypercube of unit side. We
@@
 \end{equation} 
-%
 This problem is mathematically equivalent to the minimization of the
@@
 corresponds to spreading the charges as evenly as possible.
-%, which will make sure that the charges are as evenly spread as possible throughout the confining volume.
 Finding the optimal design $\mathcal{D}_m$ that minimizes
@@
 \end{enumerate}
-%
 
@@
 
-%
 \begin{table*}
@@
 \end{table*}
-%
 \begin{figure*}
 \begin{center}
-\includegraphics[scale=0.4]{Figures/design.eps}
+\includegraphics[scale=0.4]{design.eps}
 \caption{$(\Omega_m,w)$ and $(\Omega_m,\sigma_8)$ projections of the final simulation design.
@@
 \end{figure*}
-%
 
@@
 observer. 
-%ZH: I don't think this low-level description is necessary here:
-%
-%The fluctuations in the matter field are described by the
-%gravitational potential
-%$\Phi(\mathbf{x},z)=\Phi(\mathbf{x}_\perp,\chi(z))$, where we can
-%replace the physical coordinates $\mathrm{x}$ with the comoving
-%distance from the observer $\chi$ and two transverse coordinates
-%$\mathbf{x}_\perp=\chi\pmb{\beta}$ using the flat sky
-%approximation. Here $\pmb{\beta}$ refers to the angular coordinate on
-%the sky of a physical point $\mathbf{x}$, as seen from the
-%observer. 
 We estimate the dark matter gravitational potential running $N$--body
@@
 corresponding to a mass resolution of $7.4\times10^9h^{-1}M_\odot$.
-%ZH: Instead, I added this:
 The simulations include dark matter only, and the initial conditions
@@
 \end{equation}
-%
 where $\chi$ is the radial comoving distance,
@@
 question we need to integrate equation (\ref{raytrajectory}) with the
-initial conditions $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$,
-$\dot{\pmb{\beta}}(0;\pmb{\theta})=0$ up to a distance
-%$w_s=w(z_s)$ to obtain the source angular position $\pmb{\beta}(w_s;\pmb{\theta})$. 
-%ZH: any reason to switch from chi to w ?   I switched back.
+initial condition $\pmb{\beta}(0;\pmb{\theta})=\pmb{\theta}$ up to a distance
 $\chi_s=\chi(z_s)$ to obtain the source angular position
-$\pmb{\beta}(\chi_s;\pmb{\theta})$. We use our proprietary
-implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
-for the light ray trajectories based on equation
-(\ref{raytrajectory}).
-
+$\pmb{\beta}(\chi_s;\pmb{\theta})$.
+\textbf{Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$.
+We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.}
+%
+We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
+for the light ray trajectories based \textbf{on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
+Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).}
+%
 Once we obtain the light ray trajectories, we infer the relevant weak
@@
 shear components $(\gamma^1,\gamma^2)$,
-%
-%AP: Inspector Gadget was never published.
-%ZH: Yes.  That's a pity.  I added the reference to Jan's first paper instead.
-%
 \begin{equation}
@@
 \end{equation}  
-%
 where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
-first and third Pauli matrices. The convergence $\kappa$ is related to
+first and third Pauli matrices.
+\textbf{We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{(from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{(from the \texttt{CFHTcov} simulations)} of our descriptors.
+\textbf{Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}
+
+The convergence $\kappa$ is related to
 the magnification, while the two components of the complex shear
@@
 will be modified to
-%
 \begin{equation}
@@
 \end{equation}
-%
 where $\mathbf{g} \equiv \pmb{\gamma}/(1-\kappa)$ is the reduced shear.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Statistical methods}
@@
 to measure the MFs from the $\kappa$ maps:
-%
 \begin{equation*}
@@
 \label{v1meas}
-V_1(\kappa_0)=\frac{1}{4A}\int_A\delta(\kappa(\pmb{\theta})-\kappa_0)\sqrt{\kappa_x^2+\kappa_y^2}d\pmb{\theta},
+V_1(\kappa_0)=\frac{1}{4A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\sqrt{\kappa_x^2+\kappa_y^2}d\pmb{\theta},
 \end{equation}
@@
 \label{v2meas}
-V_2(\kappa_0)=\frac{1}{2\pi A}\int_A\delta(\kappa(\pmb{\theta})-\kappa_0)\frac{2\kappa_x\kappa_y\kappa_{xy}-\kappa_x^2\kappa_{yy}-\kappa_y^2\kappa_{xx}}{\kappa_x^2+\kappa_y^2}d\pmb{\theta}.
+V_2(\kappa_0)=\frac{1}{2\pi A}\int_A\delta_D(\kappa(\pmb{\theta})-\kappa_0)\frac{2\kappa_x\kappa_y\kappa_{xy}-\kappa_x^2\kappa_{yy}-\kappa_y^2\kappa_{xx}}{\kappa_x^2+\kappa_y^2}d\pmb{\theta}.
 \end{equation*}
-%
 Here $A$ is the total area of the field of view and $\kappa_{x,y}$
 denotes gradients of the $\kappa$ field, which we evaluate using
-finite differences. The first Minkowski functional, $V_0$, is
+finite differences. \textbf{In this notation $\Theta(x)$ is the Heaviside function}
+%
+\begin{equation}
+\Theta(x) = 
+\begin{cases}
+1 \,\,\,\,\,\,\,\, x\geq0 \\ \\
+0 \,\,\,\,\,\,\,\, \mathrm{otherwise}
+\end{cases}
+\end{equation}
+%
+\textbf{and $\delta_D(x)$ is the Dirac delta function.}
+The first Minkowski functional, $V_0$, is
 equivalent to the cumulative one--point PDF of the $\kappa$ field,
@@
 following definitions
-%
 \begin{equation}
@@
 \end{equation}
-%
 
@@
 particular $\mathrm{LM}_n$ has the general form
-%
 \begin{equation}
@@
 \end{equation}
-%
 where $\rho$ is a polynomial of order $n$ in the $\mathbf{l}$'s. For
@@
 moment emphasizes quadrilateral shapes for which one side is much
-larger than the others. On the other hand, for $K_4$ we have
+larger than the others. On the other hand, for $K_3$ we have
 $\rho(\mathbf{l}_{1234})=(\mathbf{l}_1\cdot\mathbf{l}_2)(\mathbf{l}_3\cdot\mathbf{l}_4)$
@@
 \end{equation}  
-%
 where $\tilde{\kappa}(\mathbf{l})$ is the Fourier transform of the
-$\kappa$ field and $\delta_D$ is the usual Dirac delta
-function. Previous works have studied cosmological constraints from
+$\kappa$ field. Previous works have studied cosmological constraints from
 the convergence power spectrum extensively.  Here our purpose is to
@@
 used in this work are summarized in Table \ref{desctable}.
-%
 \begin{table}
 \begin{tabular}{c|c|c} \hline
-Descriptor & Details & $N_b$ \\ \hline
+Descriptor & Details & $N_b$ (linear spacing) \\ \hline
 $V_0,V_1,V_2$ (MF) & $\kappa_0\in[-0.04,0.12]$ & 50 \\
@@
 \end{table}
-%
 
@@
 simplicity, we here insert the value $\kappa=0$ in each masked pixel.
-Given the typical angular size of the masked regions we consider, this
-will have little effect on the power spectrum at the range of
-multipoles in Table \ref{desctable}. 
-%ZH: can you be more specific above and say what you mean by the angular scales?  Masks are much smaller than
-%    the scales over which moments are defined?   Or much bigger?
+Given the uniform spatial distribution of the masked regions in the data, we expect that masks have a little effect on the power spectrum at the range of
+multipoles in Table \ref{desctable}, except for an overall normalization which will be the same both in the data and the simulations.  
 Likewise, we believe that the way we deal with masked sky regions --
@@
 impact of the masks and their treatment has been evaluated for the
-MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}.
-%ZH:  I think we need to state here something on what they found.
-
-%AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki 
-%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and Moments are well defined also in the presence of masked pixels, while the PS estimator is not
-%ZH:  OK, I rewrote above to say this.  I think what you mean to say here is that our results will not be biased,
-%     since we apply the same masking to the data and the sims.   But there's still a separate question of loosing
-%     sensitivity, which I noted above.
+MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}, in which the authors find that the masked regions 
+are not a dominant source of systematic effects in the CFHTLenS data.
 
@@
 
-In this section, we briefly outline of the statistical framework
+In this section, we briefly outline the statistical framework
 adopted for computing cosmological parameter confidence levels.  We
@@
 simulations with a choice of cosmological parameters $\mathbf{p}$
-(i.e. from one of the $R=1000$ maps in this cosmology), and to $D_i$
+(i.e. from one of the $R=1000$ map realizations in this cosmology), and to $D_i$
 as the descriptor measured from the CFHTLenS data.
-%ZH: Important: we never describe that we have R=1000 realization of
-%    each model, by random rotations and shifts of the single N-body run.
-%    This should be added above, where the simulations and the ray-tracing is discussed.
 In this notation, $i$ is an index that refers to the particular bin on
@@
 9 for the LM statistic and from 0 to $N_b-1$ for a MF measured in
-$N_b$ different $\kappa$ bins).
-%on $N_b$ different excursion sets.
-%ZH: Similarly: we should insert 2-3 sentence above, where we discuss the descriptors,
-%    to state what binning we used (and indicate the actual kappa values of the bin boundaries).
+$N_b$ different, linearly spaced $\kappa$ bins, as indicated in Table \ref{desctable}).
 
@@
 \end{equation}
-%
 Here $N_{\mathcal{L}}$ is a $\mathbf{p}$--independent constant that
@@
 
-%AP: what kind of quantitative test should I implement?
-We can use Anderson-Darling to check how gaussian the pdf in each bin is, but this doesn't tell anything on the bin correlations.
-Also which bins shall I choose?
-There is a problem if the likelihood is non-Gaussian: we don't know what to do.
-Basically this is the only functional form with which we can model the PDF and bin correlations analytically, and compute the parameter likelihood semi-analytically, otherwise we need to dig into more sophisticated non--parametric methods in which I am not that proficient yet.
-%
-%ZH: OK, I added a footnote along these lines.  It's just tempting to try to do this using the sims, since in principle, we could relax the assumption. I agree in practice it will be a lot of work.
-
 \begin{equation}
@@
 \mathcal{L}_d(D_i\vert \mathbf{p}) = [(2\pi)^{N_b}\det{\mathbf{C}}]^{-1/2} e^{-\frac{1}{2}\chi^2(D_i\vert \mathbf{p})}, \\ \\
-\chi^2(D_i\vert \mathbf{p}) = \mathbf{[D - M(p)]C^{-1}[D-M(p)]}.
+\chi^2(D_i\vert \mathbf{p}) = \mathbf{[D - M(p)]}^T\mathbf{C^{-1}[D-M(p)]}.
 \end{matrix}
 \end{equation} 
-%
 We assume, for simplicity, that the covariance matrix $\mathbf{C}$ in
 equation~(\ref{datalikelihood}) is $\mathbf{p}$--independent and
-coincides with $\mathbf{C}(\mathbf{p}_0)$. For this reason, the
-normalization constant in equation~(\ref{parameterlikelihood}) is also
-model--independent. The simulated descriptors $\mathbf{M(p)}$ are
-measured from an average over the $R=1000$ realizations
+coincides with $\mathbf{C}(\mathbf{p}_0)$. The simulated descriptors $\mathbf{M(p)}$ are
+measured from an average over the $R=1000$ realizations \textbf{in the \texttt{CFHTemu1} ensemble}  
 \begin{equation}
@@
 \end{equation}
-%
 The covariance matrix 
@@
 \end{equation}
-%
-is measured from the independent \texttt{CFHTcov} simulation suite.
-% set based on 50 independent $N$--body simulations with parameters $\mathbf{p}_0=(0.26,-1.0,0.8)$
+is measured from the \textbf{$R=1000$} realizations \textbf{in the \texttt{CFHTcov} ensemble}.
 While eq.~(\ref{datacov}) gives an unbiased estimator of the
@@
 \end{equation}
-%
 where $\phi$ has been chosen as a multi-quadric function
@@
 simulations. Figure~\ref{emulatorAccuracy} shows that our power
-spectrum emulator has accuracy better than 10\% for the lower
-multipoles, and comparable to 1\% for the higher multipoles. The MF
-emulator has accuracy $\lesssim$10\% for the first 30 bins (which
+spectrum emulator has a \textbf{relative error} smaller than 20\% for the lower
+multipoles ($l<500$), and comparable to 1\% for the higher multipoles. The MF
+emulator has a \textbf{relative error} $\lesssim$10\% for the first 30 bins (which
 correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
@@
 implement a more sophisticated interpolation
-scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented
-  with interpolations using a Gaussian Process, but did not find a
-  significant improvement in accuracy over the much simpler polynomial
-  scheme; this is in agreement with earlier results.}.
-%ZH: we should add citation of Lloyd Knox's paper http://adsabs.harvard.edu/abs/2011ApJ...728..137S
-%    which said GP is not worth the hassle....
-
-\begin{figure}
+scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in \textbf{relative error} over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
+
+\begin{figure*}
 \begin{center}
-\includegraphics[scale=0.45]{Figures/emulator_accuracy.eps}
+\includegraphics[scale=0.4]{emulator_accuracy.eps}
 \end{center}
-%ZH:  It would be really nice to show ``kappa'' and ``ell'' instead (or in addition) to ``i'' on the x axis.
-%     Maybe use the top of the figure to label kappa's and ell's?  Or at least state the kappa and ell ranges in words.
 \caption{Accuracy of the emulator based on the \texttt{CFHTemu1}
-  simulations. The figure shows the difference between the descriptor
+  simulations. The figure shows the absolute difference between the descriptor
   interpolated at the fiducial parameter setting, and the descriptor
-  expected from the \texttt{CFHTcov} simulations. The descriptors are
+  expected from the \texttt{CFHTcov} simulations (these are the absoulte values of differences which oscillate around zero). The descriptors are
   shown in units of the standard deviation in each bin $i$ (determined
@@
   matrix). We show the accuracy results for the power spectrum (red)
-  and the three Minkowski Functionals $V_0$ (green), $V_1$ (blue) and
+  and the three Minkowski functionals $V_0$ (green), $V_1$ (blue) and
   $V_2$ (black). For reference, we also show, using dashed lines, the
   difference between the expected \texttt{CFHTcov} descriptors and the
-  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.}
-%ZH: This last one is chosen to lie along our 1 (or 2?) sigma contour, right?
-%    We should then state this, and make the point that this is the interpolation accuracy we care about,
-%    and our accuracy is indeed better than this.
+  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.
+This non--fiducial point lies beyond the LM $1\sigma$ contour from the simulations shown in Figure \ref{contours3single} right panel, and corresponds to the target accuracy we wish to achieve}
 \label{emulatorAccuracy}
-\end{figure}
+\end{figure*}
 
@@
 ref.~\citep{astroMLText}), we derive the {\it whitened} model matrix
-$\tilde{M}_{pi}$, defined by subtracting the mean (over the $R=1000$
-realizations) of each matrix element,
-%ZH: you wrote ``bin'' here, but I changed it to matrix element. All NxN_bin entries are whitened, presumably.
-and normalizing it by its variance. Next we proceed with a singular
+$\tilde{M}_{pi}$, defined by subtracting the mean (over the $N=91$ models) of each bin,
+and normalizing it by its variance (always over the $N=91$ models). Next we proceed with a singular
 value decomposition (SVD) of $\mathbf{\tilde{M}}$,
@@
 \end{equation}   
-%
 where $S_{ij}=S_i\delta_{ij}$ is a diagonal matrix and $V^T_{ij}$ is
@@
 component ($i=1...\mathrm{min}[N_b,N]$) of $\mathbf{\tilde{M}}$, with
-the index $j$ ranging from $0$ to $N_b-1$. By construction,
+the index $j$ ranging from $1$ to $N_b$. By construction,
 $\mathbf{V}$ is $\mathbf{p}$--independent.
@@
 of the model covariance (not to be confused with the descriptor
-covariance in eq.~\ref{datacov}),
+covariance in eq.~(\ref{datacov})),
 \begin{equation}
@@
 \end{equation} 
-%
 We follow the standard interpretation of PCA components, stating that
@@
 \label{pcaprojection}
-M(n)_{i}^r = V^T(n)_{ij}\tilde{M}_j^r \,\,\,\, ; \,\,\,\,  D(n)_i = V^T(n)_{ij}\tilde{D}_j.
-\end{equation}
-%
-Here we suppressed the first index of $M(n)$ for notational simplicity
-and we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$
+M(n)_{pi}^r = V^T(n)_{ij}\tilde{M}_{pj}^r \,\,\,\, ; \,\,\,\,  D(n)_i = V^T(n)_{ij}\tilde{D}_j.
+\end{equation}
+Here we indicate with $V^T(n)$ the truncation of $V^T$ to the first $n$
 rows (i.e. $i$ can now range from $1$ to $n$). As described above, the
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Results}
@@
 data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
-alternative parameterization, $(\Sigma_8,\alpha,w)$, with
-$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$.  We then use
-our simulations to perform a robustness analysis of the parameter
+alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
+$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. \textbf{In the next section} we give a justification on why we fix $\alpha$ to a value of $0.55$. 
+We then use our simulations to perform a robustness analysis of the parameter
 confidence intervals with respect to the number of PCA components used
 in the projection.
-%We first use our simulations to perform a robustness analysis
-%of the parameter confidence intervals with respect to the number of
-%PCA components used in the projection. We then show the cosmological
-%constraints from the CFHTLenS data.
-%ZH: I reversed the order of the above two.  
-%    It is better to first show the constraints,  and only THEN we can discuss their robustness.
-%    Also I moved the discussion of \Sigma_8 down below.
 We finally study whether the constraints can be tightened by combining
@@
 
-%AP: Justified value of alpha=0.55
-
-%AP: Added inline description of the figures
-
-%ZH: I reversed the order of this and the next subsection
 \subsection{Cosmological constraints}
-%
 We first make use of equations
@@
 
-%ZH: I moved this here -- fits better:
 Because of the relatively small size of this survey, degeneracies
@@
 to the error ``banana'' at the pivot point $\Omega_m=0.27$.  
-%ZH:  added above, about the pivot point.  Please check this is OK (or modify).
-%     It depends on how you computed alpha (see below).
 This is the direction of the lowest variance
@@
 \end{equation}
-%
 and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect
-to $\alpha$. 
-%ZH: Is this done at fixed Omega_m=0.27, or is the averaging above over all Omega_m and sigma8 (and w) ?
-%    Let's make it clear.
-%    I think either is fine (as long as we make it clear), but I think usually, people fix Omega_m.
-%    This could make a difference in the best-fit alpha values.
-%    Also, which descriptor is being used?  Let's make that clear, too.
+to $\alpha$. The expectation values are taken over the entire parameter box. 
 This procedure yields a value $\alpha\approx0.55$ for the
 statistical descriptors that we consider, 
-%ZH: which statistical descriptor do you mean here?   Or is alpha the same for all?
-%    it would also be nice to show an error bar on alpha, if it isn't too much work to compute it (in 
-%    principle, the minimization procedure above, done over the 1000 realizations, must give an error bar).
-%    and also to give an indication of (A) how much alpha varies for different descriptors, and (B) how much
-%    it depends on Omega_m, sigma8, and w.
-consistent with what is found in the literature.
-%ZH:  We should give references, if we say the above.
+consistent with what is found in the literature (see \citep{CFHTKilbinger} for example).
+Although $\alpha$ can mildly depend on the type of descriptor considered, we choose to keep it fixed, knowing that the width of the $\Sigma_8$ likelihood cannot vary significantly with different choices of $\alpha$.
 We show the probability distribution of the best-constrained parameter
@@
 
-% ZH: we need to state somewhere above, clearly, the actual fiducial
-%binnings we used (and maybe recap it here, too)
 The cosmological constraints should in principle be insensitive to
@@
 the covariance (due to a limited number of realizations) can introduce
-an $N_b$ dependence.  Here we show that the cosmological constraints
+an $N_b$ dependence. Our binning choices are summarized in Table \ref{desctable}.  
+Here we show that the cosmological constraints
 derived in this paper are numerically robust, i.e. they are reasonably
@@
 accuracy typically for $n=5-10$ (depending on the descriptor).
-%ZH: I added above.  I see later you quote larger n for V1 an V2, for 5% accuracy.
 This finding also addresses the inaccuracy of the MF emulator at high
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contoursOmega_m-sigma8_single.eps}
-\includegraphics[scale=0.45]{Figures/contoursmockOmega_m-sigma8_single.eps}
+\includegraphics[scale=0.45]{contoursOmega_m-sigma8_single.eps}
+\includegraphics[scale=0.45]{contoursmockOmega_m-sigma8_single.eps}
 \end{center}
@@
   parameter doublet using the power spectrum (red), the three
-  Minkowski Functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
-  the Moments (orange). We show the constraints from the data (left
+  Minkowski functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
+  the moments (orange). We show the constraints from the data (left
   panel) and from a mock observation constructed using the mean of
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contours_momentsOmega_m-sigma8.eps}
-\includegraphics[scale=0.45]{Figures/contours_momentsOmega_m-sigma8smooth.eps}
+\includegraphics[scale=0.45]{contours_momentsOmega_m-sigma8.eps}
+\includegraphics[scale=0.45]{contours_momentsOmega_m-sigma8smooth.eps}
 \end{center}
 \caption{$1\sigma$ (68\% CL) constraints on the $(\Omega_m,\sigma_8)$
-  parameter doublet using Moments, with different colors corresponding
+  parameter doublet using moments, with different colors corresponding
   to different moment combinations (see eq.~\ref{momentestimator} for
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contoursw-Sigma8Om055_single.eps}
+\includegraphics[scale=0.45]{contoursw-Sigma8Om055_single.eps}
 \end{center}
@@
   parameter doublet from the CFHTLenS data, obtained with the power
-  spectrum (red), the three Minkowski Functionals ($V_0$: green,
-  $V_1$: blue, $V_2$: black) and the Moments (orange).
-%ZH: You had V0=blue and V1=green here, but the figure label shows the opposite. 
-%  I assume figure label was correct, but please double-check:
-%%%% $V_0$ (blue), $V_1$ (green), $V_2$ (black) and
-%  Moments (orange) statistics. 
+  spectrum (red), the three Minkowski functionals ($V_0$: green,
+  $V_1$: blue, $V_2$: black) and the moments (orange).
    The contours are calculated from the parameter likelihood function
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contoursSigma8Om055_single.eps}
+\includegraphics[scale=0.45]{contoursSigma8Om055_single.eps}
 \end{center}
@@
   CFHTLenS data, obtained with the power spectrum (red), the three
-  Minkowski Functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
-  the Moments (orange).
-%ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
-%  I assume figure label was correct, but please double-check:
-%%%%  the Power Spectrum (red), $V_0$ (blue), $V_1$ (green),
-%%%%  $V_2$ (black) and Moments (orange) statistics. 
+  Minkowski functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
+  the moments (orange).
   The likelihood was computed with a constant optimized $\alpha=0.55$,
   but marginalized over both $\Omega_m$ and $w$. 
-%ZH: so we should make clear what we did - I think you fixed alpha, but marginalized over Omega and w
-%    (technically, the best-fit alpha is a function of Omega and w, but this was not included in your
-%     calculation, right?)
   The parentheses near the descriptor label refer to the number of
@@
 $(\Omega_m,\sigma_8)$ & PS(3),$V_0(5),V_1(20),V_2(20)$,LM(9) &\pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ and mock observations}  & \ref{contours3single},\ref{contours3single}b \\ \hline
-$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ Moments \\ combined at different $\theta_G$}  & \ref{contoursMoments},\ref{contoursMoments}b \\ \hline
+$(\Omega_m,\sigma_8)$ & $(\sigma_i^2,S_i,K_i)$ & \pbox{20cm}{$1\sigma$ constraints from CFHTLenS \\ using $\kappa$ moments \\ combined at different $\theta_G$}  & \ref{contoursMoments},\ref{contoursMoments}b \\ \hline
 $(w,\Sigma_8)$ & PS(3),$V_0(10),V_1(10),V_2(10)$,LM(9) & contours from CFHTLenS & \ref{contours3singleRep} \\ \hline 
@@
 \caption{Summary of our results and related figures.}
-%ZH: this is basically a list of figures.  It's a bit unusual to have such a table, but let's leave it in.
-%    I actually think it's quite useful.
-%    However: I suggest to make the rows be in the same order as the figures
-%    (start with Figures 3a,b, which are the main result). And, add the missing figures 7 and 8 for completeness.
 \label{summarytable}
 \end{table*}
-%
-
-%--------------------------------------------------------
-%ZH: Also changed the order of the Figures
-%
+
 \begin{figure*}
-\includegraphics[scale=0.4]{Figures/pca_components.eps}
-%ZH: The right panel figure is mostly wasted, since it just shows ``1''.
-%    You should either cut the figure and restrict it to n<10 or n<15,
-%    or else maybe make the x axis logarithmic, to show the n<5 points better.
+\includegraphics[scale=0.4]{pca_components.eps}
 \caption{Results from the Principal Components Analysis (PCA) of the
-  binned power spectrum (red), the three Minkowski Functionals ($V_0$:
-  green, $V_1$: blue, $V_2$: black) and the Moments (orange).
-%ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
-%  I assume figure label was correct, but please double-check:
-%%% the Power Spectrum(red), $V_0$
-%%%  (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange)
+  binned power spectrum (red), the three Minkowski functionals ($V_0$:
+  green, $V_1$: blue, $V_2$: black) and the moments (orange).
   The left panel shows the magnitudes of the PCA eigenvalues $S_i^2$
@@
 \end{figure*}
-%
-%AP: 3 is the dimensionality of our parameter space which may, or may not tell us something about the number of principal components
-%
 \begin{figure*}
-\includegraphics[scale=0.4]{Figures/robustness_pca_Omega_m-sigma8.eps}
+\includegraphics[scale=0.4]{robustness_pca_Omega_m-sigma8.eps}
 \caption{The dependence of the $1\sigma$ contours in the
@@
   different descriptors (from left to right, top to bottom) $V_0$,
-  $\partial V_0$(PDF), $V_1$, $V_2$, power spectrum and Moments.  The
+  $\partial V_0$(PDF), $V_1$, $V_2$, power spectrum and moments.  The
   labels in each panel show the number of PCA components included to
@@
 \end{figure*}
-%
-
-%--------------------------------------------------------
 
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contoursOmega_m-sigma8_cross.eps}
-\includegraphics[scale=0.45]{Figures/contoursw-Sigma8Om055_cross.eps}
+\includegraphics[scale=0.45]{contoursOmega_m-sigma8_cross.eps}
+\includegraphics[scale=0.45]{contoursw-Sigma8Om055_cross.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.45]{Figures/contoursSigma8Om055_cross.eps}
+\includegraphics[scale=0.45]{contoursSigma8Om055_cross.eps}
 \end{center}
@@
 CFHTLenS alone included combining the power spectrum and peak
-counts~\citep{Companion}, and combining quadratic (2PCF) statistics
-with the skewness of the CFHTLenS $\kappa$ field~\citep{CFHTFu}.
-%ZH: This was on the 3PCF, not the skewness -- right?  And didn't Shirasaki+Yoshida also combine PS+MF ?
-%    Please check and fix/complete these citations as necessary.
+counts~\citep{Companion}, combining the power spectrum and Minkowski functionals ~\citep{CFHTMasato} ,and combining quadratic (2PCF) statistics
+with cubic statistics derived from the 3PCF of the CFHTLenS $\kappa$ field~\citep{CFHTFu}.
 
@@
 
-%AP: Added the statistics combinations Zoltan suggested
-
-%%%%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Discussion}
@@
 
-%ZH: I added explanation:
 This does not necessarily mean, however, that the cosmological
@@
 stable at the $\sim$5\% level. All nine moments need to be included
-for the Moments contours to be stable to this accuracy.
+for the moments contours to be stable to this accuracy.
 
@@
 not shown, but obtained analogously to the Figures above.)
-% (in order to figures supporting this choice not shown).
 
@@
 in other experiments. For example, the current best-fit values of
-$(\Omega_m,\sigma_8)=(...,...)$ from cosmic microwave background
-anisotropies measured by the Planck
-%ZH: Let's give the actual numbers here.  I would also quote WMAP9
-%    for these numbers -- there's currently a sigma8-discrepancy that
-%    needs to be resolved between these two (and my suspicion is that WMAP is correct :)
-satellite~\citep{PlanckXVI2013} lie beyond the 99\% likelihood
+$(\Omega_m,\sigma_8)=(0.32,0.83),(0.28,0.82)$ from cosmic microwave background
+anisotropies measured respectively by the Planck
+~\citep{PlanckXVI2013} and WMAP~\citep{WMAP9} satellites lie beyond the 99\% likelihood
 contours obtained from the three MFs (not shown).
@@
 based on simulations (shown in the
-%left
-%ZH: changed left->right
 right panel of Figure \ref{contours3single}), we recover the correct
@@
 
-%Added that  the reason we think MFs are biased is that the best current values of Om, s8 lie beyond the 99% likelihood contours for MFs.
-Changed "We believe that this is due to uncorrected systematics" to "This may be due to"  .
-Added that bias is amplified by degeneracy.
-Morgan 2/16/2015
-
-We observe that the Moments give the tightest constraint on
+We observe that the moments give the tightest constraint on
 $(\Omega_m,\sigma_8)$.  Furthermore, this constraint is unbiased, in
@@
 rather than the rare statistical fluctuations found above.
-%ZH:  I guess the natural question: if you look at those ~10 realizations which give biased best-fits from the MFs,
-%     do they also give biased fits from the Moments?  I would guess so.
-The fact that the Moments are useful for deriving unbiased
+The fact that the moments are useful for deriving unbiased
 cosmological constraints has been noted in previous work, which
@@
 i.e. the variance, skewness, and kurtosis $(\sigma_0^2,S_0,K_0)$. We
-then add the remaining six moments of gradients one by one, starting
+then add the remaining six moments of derivatives one by one, starting
 from the quadratic moments.
@@
 Figure \ref{contoursMoments} shows that the biggest improvement on the
-parameter bounds comes from including quartic moments of gradients
+parameter bounds comes from including quartic moments of derivatives
 (i.e. $K_i$ with $i\ge1$) in the descriptor set. This might explain
@@
 \ref{contoursMoments} explicitly shows, however, that smoothing scale
-combinations are not as effective as moments of gradients in
+combinations are not as effective as moments of derivatives in
 constraining the $(\Omega_m,\sigma_8)$ doublet. Our results agree with
@@
 constrain $w$ to a reasonable precision.
-%ZH: Added this.  And I think it's nice that we could clarify the origin of the w=-2 best-fit...
 This is consistent with the previous analyses of
@@
 1$\sigma$).  We found a similar result when using a Fisher matrix to
-compute confidence levels.  We thus attribute this bias to the
-assumption of linear cosmology-parameter dependence of the
-descriptors.  
-%
+compute confidence levels.
+\textbf{Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear interpolations between the fiducial cosmology and its variations)}, we thus attribute this bias to the \textbf{oversimplifying} assumption of linear cosmology-parameter dependence of the descriptors.
 Although the right panel in Figure
-\ref{contours3combined} shows that the Moments confine $w$ to isolated
-regions in parameter space, we note that $w=-1$, the value favored by
-several other existing experiments, is excluded at the $1\sigma$
-level. The $2\sigma$ contours (not shown in the figure) close, and
+\ref{contours3combined} shows that the moments confine $w$ to isolated
+regions in parameter space, we note that $w=-1$, the value favored by other existing experiments, is excluded at the $1\sigma$
+level. The $2\sigma$ contours (not shown in the figure) join, and
 include $w=-1$.
-%ZH: Added above.  OK?
-
-%"using either of the MFs" changed to using the full descriptor set Morgan 2/16/2015
 
@@
 
-%MF constraints on Om, s8 are biased. However MFs can effectively constrain the non-degenerate direction, S8 for CFHTLenS
-
 Finally, we studied whether the combination of different statistical
@@
 of Figure \ref{contours3combined} shows that, although combining the
-power spectrum with the Minkowski Functionals and Moments helps
+power spectrum and the moments with the Minkowski functionals helps
 tighten the $(\Omega_m,\sigma_8)$ constraints, it does not help in
-reducing the inherent parameter bias. The right panel of Figure
+reducing the inherent parameter bias of the MFs. The right panel of Figure
 \ref{contours3combined} shows that even with these statistics
-combined, $w$ remains essentially unconstrained. Figure
-\ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
+combined, $w$ remains essentially unconstrained. \textbf{\citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly}. 
+Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
 already well constrained by any of the descriptors alone, without the
 need of combining different descriptors.
-%ZH: added this
-This further clarifies that the non-quadratic descriptor mainly help
+This further clarifies that the non--quadratic descriptors mainly help
 to break degeneracies, tightening contours along the
@@
 
-%\newpage 
-%%%%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusions}
@@
 
-\item We find that the power spectrum, combined with the Moments of
+\item We find that the power spectrum, combined with the moments of
   the $\kappa$ field provides the tightest constraint on the
@@
   tightness of these constraints comes mainly from the
-  Moments. Evidence of the unbiased nature of constraints from the
-  Moments has been found in \citep{PetriSpurious}. We further find
+  moments. Evidence of the unbiased nature of constraints from the
+  moments has been found in \citep{PetriSpurious}. We further find
   that the largest improvement on parameter bounds is achieved when we
-  include the quartic moments of gradients in the descriptor set. This
+  include the quartic moments of derivatives in the descriptor set. This
   level of improvement cannot be achieved by combining one-point
@@
   to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
-  using the Minkowski Functionals.
+  using the Minkowski functionals.
 
@@
 constraints on $w$.  The techniques developed here can be applied to
-larger, soon-forthcoming survey data sets.
-%ZH: we should cite the dark energy survey (DES), and Subaru, and maybe also WFIRST and LSST here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%% ACKNOWLEDGMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+larger, soon-forthcoming survey data sets, such as the Dark Energy Survey (DES)~\citep{DES}, Subaru~\citep{Subaru}, WFIRST~\citep{WFIRST} and LSST~\citep{LSST}.
 
@@
 number ACI-1053575, at the Yeti computing cluster at Columbia
-University,
-%ZH: added Yeti
-and at the New York Center for Computational Sciences, a cooperative
+University, and at the New York Center for Computational Sciences, a cooperative
 effort between Brookhaven National Laboratory and Stony Brook

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -106,7 +106,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
 	return out_Corr, out_DDRR
 
-pool = MPIPool()
+#pool = MPIPool()
 
 cosmosigmaG_arr = [[cosmo, sigmaG] for sigmaG in sigmaG_arr[::-1] for cosmo in cosmo_arr]
 def create_peakpeak_arr (cosmosigmaG):

### 2015-04-17 jia/tSZxCFHT.py

@@ -267,18 +267,51 @@ if SNR_calc:
 		return Cth
 	theory_all = concatenate(map(theoryGen, range(1,5)))
 	chisq_model_fcn = lambda A, CC, err: sum((CC-A*theory_all)**2/err**2)
+	figure(figsize=(16,10))
 	for ip in range(4):
-		factor=2.0*pi/(1+ell_arr[:-1])
+		factor=2.0*pi/(1+ell_arr)[:-1]
 		factors=concatenate(repeat(factor,4).reshape(-1,4).T)
-		ell_arr4 = concatenate(repeat(ell_arr[:-1],4).reshape(-1,4).T)
+		ell_arr4 = concatenate(repeat(ell_arr,4).reshape(-1,4).T)
 		fn = tSZ_dir+'cc_yxk_%s.npy'%(prefix_arr[ip])
 		cc_arr = concatenate(load(fn)[:,0,:-1])*factors
 		err_arr = concatenate(load(fn)[:,1,:-1])*factors
 		A_out = op.minimize(chisq_model_fcn, 1.0, args=(cc_arr, err_arr))
 		A_min = A_out.x
 		chisq_model = A_out.fun
-		chisq_null = sum(sqrt((cc_arr/err_arr)**2))
+		chisq_null = sum((cc_arr/err_arr)**2)
 		SNR = sqrt(chisq_null-chisq_model)
-		print '{4} A={0:.2f}, chisq_null={1:.2f}, chisq_model={2:.2f}, SNR={3:.2f}'.format(float(A_min), chisq_null, chisq_model, SNR, prefix_arr[ip])
+		temp = r'{4}: A={0:.2f}, $\chi^2_0$={1:.2f}, $\chi^2_A$={2:.2f}, SNR={3:.2f}'.format(float(A_min), chisq_null, chisq_model, SNR, prefix_arr[ip])
+		print temp
+		
+		subplot(2,2,ip+1)
+		#errorbar(range(40), cc_arr, err_arr, label='data')
+		#plot(range(40), theory_all, label='theory (A=1)')
+		#plot(range(40), theory_all*A_min, label='theory (A=%.2f)'%(A_min))
+		#for aa in (9.5, 19.5, 29.5):
+			#plot([aa,aa],[-amax(cc_arr)*1.2, amax(cc_arr)*1.2],'k-')
+
+		
+		######## inverse weighted
[…]

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -90,7 +90,10 @@ def single_corr(iRcosmosigmaG, edges = edges):
 			out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
 		save(fn, [out_Corr, out_DDRR])
 	else:
-		out_Corr, out_DDRR = load(fn)
+		try:
+			out_Corr, out_DDRR = load(fn)
+		except Exception:
+			print '!!!!!!!', R, cosmo, sigmaG
 	#fn = ipeaklist_fn(cosmo, R, sigmaG)
 	#if not os.path.isfile(fn):
 		#ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -90,10 +90,9 @@ def single_corr(iRcosmosigmaG, edges = edges):
 			out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
 		save(fn, [out_Corr, out_DDRR])
 	else:
-		try:
-			out_Corr, out_DDRR = load(fn)
-		except Exception:
-			print '!!!!!!!', R, cosmo, sigmaG
+		test = load(fn)
+		print test.shape
+		
 	#fn = ipeaklist_fn(cosmo, R, sigmaG)
 	#if not os.path.isfile(fn):
 		#ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
@@ -106,7 +105,8 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		#idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
 		#out_DDRR[i] = len(idx)
 		#out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
-	print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
+		print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
+		out_Corr, out_DDRR = load(fn)
 	return out_Corr, out_DDRR
 
 #pool = MPIPool()

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -90,6 +90,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 			out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
 		save(fn, [out_Corr, out_DDRR])
 	else:
+		print fn
 		test = load(fn)
 		print test.shape
 		

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -106,8 +106,9 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		#idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
 		#out_DDRR[i] = len(idx)
 		#out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
-		print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
 		out_Corr, out_DDRR = load(fn)
+		print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
+		
 	return out_Corr, out_DDRR
 
 #pool = MPIPool()

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -92,8 +92,18 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	else:
 		print fn
 		test = load(fn)
-		print test.shape
-		
+		if test.shape[0] != 2:
+			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
+			out_DDRR = zeros(len(edges)-1)
+			out_Corr = zeros(len(edges)-1)
+			for i in range(len(edges)-1):
+				idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
+				out_DDRR[i] = len(idx)
+				out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
+			save(fn, [out_Corr, out_DDRR])
+		else:
+			out_Corr, out_DDRR = load(fn)
+			
 	#fn = ipeaklist_fn(cosmo, R, sigmaG)
 	#if not os.path.isfile(fn):
 		#ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
@@ -106,7 +116,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		#idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
 		#out_DDRR[i] = len(idx)
 		#out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
-		out_Corr, out_DDRR = load(fn)
+		
 		print R, sigmaG, out_Corr.shape, out_DDRR.shape, cosmo
 		
 	return out_Corr, out_DDRR

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -93,6 +93,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		print fn
 		test = load(fn)
 		if test.shape[0] != 2:
+			print '!!! error', R, sigmaG, cosmo
 			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
 			out_DDRR = zeros(len(edges)-1)
 			out_Corr = zeros(len(edges)-1)

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -76,7 +76,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	R, cosmo, sigmaG = iRcosmosigmaG
 	
 	fn = icorr_fn(cosmo, R, sigmaG)
-	if not os.path.isfile(fn):
+	if not os.path.isfile(fn) or not os.path.isfile(ipeaklist_fn(cosmo, R, sigmaG)):
 		if not os.path.isfile(ipeaklist_fn(cosmo, R, sigmaG)):
 			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
 			save(fn, ipeaklist)

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -90,7 +90,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 			out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
 		save(fn, [out_Corr, out_DDRR])
 	else:
-		print fn
+		#print fn
 		test = load(fn)
 		if test.shape[0] != 2:
 			print '!!! error', R, sigmaG, cosmo

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -103,7 +103,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 				out_Corr[i] = mean(ipeaklist[1,idx]*ipeaklist[2,idx])
 			save(fn, [out_Corr, out_DDRR])
 		else:
-			out_Corr, out_DDRR = load(fn)
+			out_Corr, out_DDRR = test
 			
 	#fn = ipeaklist_fn(cosmo, R, sigmaG)
 	#if not os.path.isfile(fn):
@@ -122,7 +122,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		
 	return out_Corr, out_DDRR
 
-#pool = MPIPool()
+pool = MPIPool()
 
 cosmosigmaG_arr = [[cosmo, sigmaG] for sigmaG in sigmaG_arr[::-1] for cosmo in cosmo_arr]
 def create_peakpeak_arr (cosmosigmaG):

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -92,7 +92,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	else:
 		#print fn
 		test = load(fn)
-		if test.shape[0] != 2:
+		if test.shape[0] != 2 or test.shape[1] != 25:
 			print '!!! error', R, sigmaG, cosmo
 			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
 			out_DDRR = zeros(len(edges)-1)
@@ -122,7 +122,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		
 	return out_Corr, out_DDRR
 
-pool = MPIPool()
+
 
 cosmosigmaG_arr = [[cosmo, sigmaG] for sigmaG in sigmaG_arr[::-1] for cosmo in cosmo_arr]
 def create_peakpeak_arr (cosmosigmaG):
@@ -137,6 +137,7 @@ def create_peakpeak_arr (cosmosigmaG):
 		save(fn_kappa, peakpeak_arr[:,0,:])
 		save(fn_counts, peakpeak_arr[:,1,:])
 		return None
+pool = MPIPool()
 pool.map(create_peakpeak_arr, cosmosigmaG_arr)
 
 #for cosmo in cosmo_arr:

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -76,14 +76,13 @@ def single_corr(iRcosmosigmaG, edges = edges):
 	R, cosmo, sigmaG = iRcosmosigmaG
 	
 	fn = icorr_fn(cosmo, R, sigmaG)
-	if not os.path.isfile(fn) or not os.path.isfile(ipeaklist_fn(cosmo, R, sigmaG)):
-		if not os.path.isfile(ipeaklist_fn(cosmo, R, sigmaG)):
-			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
-			save(fn, ipeaklist)
-		else:
-			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
+	if not os.path.isfile(fn):
+		ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
+		save(ipeaklist_fn(cosmo, R, sigmaG), ipeaklist)
+		
 		out_DDRR = zeros(len(edges)-1)
 		out_Corr = zeros(len(edges)-1)
+		
 		for i in range(len(edges)-1):
 			idx = where( (ipeaklist[0]>edges[i]) & (ipeaklist[0]<edges[i+1]))[0]
 			out_DDRR[i] = len(idx)
@@ -94,7 +93,10 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		test = load(fn)
 		if test.shape[0] != 2 or test.shape[1] != 25:
 			print '!!! error', R, sigmaG, cosmo
-			ipeaklist = load(ipeaklist_fn(cosmo, R, sigmaG))
+			
+			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)
+			save(ipeaklist_fn(cosmo, R, sigmaG), ipeaklist)
+		
 			out_DDRR = zeros(len(edges)-1)
 			out_Corr = zeros(len(edges)-1)
 			for i in range(len(edges)-1):

### 2015-04-17 Paper_minkowski/Submission/reply/reply_referee.tex
finished referee reply

@@
 The appropriate explanation has been added to the text.
-
+\item \textit{Explain why the random rotations of galaxies make the lensing signal $O(\kappa^2)$}: the galaxy shapes measured by CFHTLenS contain both contributions from the original galaxy shape and lensing contributions from LSS.
+The lensing contributions are spatially correlated and the spatial correlations are $O(\psi)$ where $\psi$ is the lensing potential ($\kappa=O(\psi)$ also).
+When we rotate each galaxy randomly, we destroy these spatial correlations, which will not be $O(\psi)$ anymore, but $O(\psi^2)$ or smaller (if not zero at all).
+We do not assign intrinsic galaxy shapes drawing from $\mathcal{N}(0,\sigma_\epsilon)$ because we refrained from making any assumption on the distribution of intrinsic galaxy shape, choosing to use the shape distribution measured by CFHTLenS instead.
 \item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
@@
 The sentence "we suppressed the first index of $M(n)$ for notational simplicity" has been deleted
-
+\item \textit{Figure 3, right panel}: the reason why the the $1\sigma$ contour is not centered on the input model is that $\mathcal{L}(\Omega_m,\sigma_8)$ is skewed towards low $\Omega_m$ and high $\sigma_8$, as can be seen in Figure \ref{mock}
+%
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.6]{moments_mock.eps}
+\end{center}
+\caption{$(\Omega_m,\sigma_8)$ likelihood function (along with its $1,2,3\sigma$ contours) from the moments (corresponding to the right panel of Figure 3 in the manuscript)}
+\label{mock}
+\end{figure}
+%
 \item \textit{Comment of the large number of components needed in the PCA}: the referee is correct, one of the reasons why large numbers of PCA components are needed might be due to how the PCA is performed.
@@
 We are currently exploring different extensions to the PCA formalism, whose results will be included in future work
-
+\item \textit{Tabulated version of Figure 10}: the table has been added to the manuscript
 \item \textit{Citation to Heymans et al. (2013) for tomographic lensing constraints}: the citation has been addded
-
+\item \textit{Possible tension between CFHTLenS and Planck}: we agree with the referee that the comparison between cosmological constraints from weak lensing and CMB is an important point.
+In this work, however, we refrain from quantifying the precise amount of the discrepancy between CFHTLenS and Planck because we aware that the comparison will not be completely fair.
+Planck published constraints are marginalized over $H_0,\Omega_b,n_s$, which we keep fixed throughout our simulation effort.
+We are currently developing new simulation suites that will map this additional parameter space dependence of our descriptors.
 \item \textit{Logic and context of the sentence "We thus attribute this bias to the assumption of linear cosmology-parameter dependence"}: the Fisher matrix formalism is the linear order approximation of our emulator.
@@
 A clarifying sentence has been added in the appropriate section
+\item \textit{Conclusions}: we added a couple of sentences that discuss other possible causes of the tension between CFHTLenS and Planck constraints
+\item \textit{The "bias" wording}: we included a sentence "Here and throughout the remainder of this paper, by 'biased' (or 'unbiased') we refer to being incompatible (or compatible) with the concordance fiducial values at $1\sigma$ obtained in other experiments" to clarify the usage of the word "bias" in the context of this manuscript
 

### 2015-04-17 Paper_minkowski/Submission/paper.tex
finished referee reply

@@
 note that the observed ellipticity for a particular galaxy already
-contains the lensing shear by large scale structure, but the random
-rotation makes this contribution second order in $\kappa$. Consistent
-with the weak lensing approximation, the lensing signal from the
+contains the lensing shear by large scale structure \textbf{(LSS)}, but the random
+rotation makes this contribution \textbf{at least} second order in $\kappa$ \textbf{by destropying the shape spatial correlations induced by lensing from LSS}.
+Consistent with the weak lensing approximation, the lensing signal from the
 simulations is first order in $\kappa$ and hence the randomly rotated
@@
 
+\begin{table*}
+\begin{tabular}{c|c}
+Descriptor & $\Sigma_8=\sigma_8\Omega_m^{0.55}$ \\ \hline \hline
+PS(3) & $0.84^{+0.06}_{-0.09}$\\
+PS(3) $\times$ Moments(9) & $0.86^{+0.02}_{-0.09}$ \\
+$V_0(10)\times V_1(10) \times V_2(10)$  & $0.75^{+0.07}_{-0.04}$ \\
+PS(3) $\times V_0(10)\times V_1(10) \times V_2(10)$ & $0.76^{+0.04}_{-0.05}$ \\
+PS(3) $\times V_0(10)\times V_1(10) \times V_2(10) \times$ Moments(9) & $0.76^{+0.06}_{-0.04}$ \\ \hline
+\end{tabular}
+\caption{Tabulated values of $1\sigma$ constraints on $\Sigma_8$ corresponding to Figure \ref{likelihoodSi8cross}}
+\label{Sigma8Table}
+\end{table*}
+
 \subsection{Combining statistics}
@@
 \ref{contours3combined}, and on the best-constrained parameter
-$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. We discuss these
-findings in the next section.
+$\Sigma_8$ in Figure \ref{likelihoodSi8cross}.
+\textbf{We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}.
+We discuss these findings in the next section.
 
@@
   using the Minkowski functionals.
+\textbf{We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales.
+These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds.
+We will investigate these additional sources of error in future work.}
 

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -90,8 +90,12 @@ def single_corr(iRcosmosigmaG, edges = edges):
 		save(fn, [out_Corr, out_DDRR])
 	else:
 		#print fn
-		test = load(fn)
-		if test.shape[0] != 2 or test.shape[1] != 25:
+		ierror = 0
+		try:
+			test = load(fn)
+		except IOError:
+			ierror = 1
+		if test.shape[0] != 2 or test.shape[1] != 25, or ierror:
 			print '!!! error', R, sigmaG, cosmo
 			
 			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)

### 2015-04-17 jia/stampede_peakpeak.py
regular update

@@ -95,7 +95,7 @@ def single_corr(iRcosmosigmaG, edges = edges):
 			test = load(fn)
 		except IOError:
 			ierror = 1
-		if test.shape[0] != 2 or test.shape[1] != 25, or ierror:
+		if test.shape[0] != 2 or test.shape[1] != 25 or ierror:
 			print '!!! error', R, sigmaG, cosmo
 			
 			ipeaklist =  concatenate([single_peaklist(i, cosmo, R, sigmaG) for i in i_arr], axis=-1)

### 2015-04-20 Paper_minkowski/Submission/paper.tex
incorporated latest edits

@@
 three--point correlations as an additional probe for cosmology, and
-found modest ($10-20\%$) improvements over the 2PCF. \textbf{These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.
+found modest ($10-20\%$) improvements over the 2PCF. \textbf{\color{blue} These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.
 
@@
 $\pmb{\beta}(\chi_s;\pmb{\theta})$.
-\textbf{Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$.
+\textbf{\color{blue} Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$.
 We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.}
@@
 We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
-for the light ray trajectories based \textbf{on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
+for the light ray trajectories based \textbf{\color{blue} on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
 Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).}
@@
 first and third Pauli matrices.
-\textbf{We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{(from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{(from the \texttt{CFHTcov} simulations)} of our descriptors.
-\textbf{Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}
+\textbf{\color{blue} We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{\color{blue} (from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{\color{blue} (from the \texttt{CFHTcov} simulations)} of our descriptors.
+\textbf{\color{blue} Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}
 
@@
 note that the observed ellipticity for a particular galaxy already
-contains the lensing shear by large scale structure \textbf{(LSS)}, but the random
-rotation makes this contribution \textbf{at least} second order in $\kappa$ \textbf{by destropying the shape spatial correlations induced by lensing from LSS}.
+contains the lensing shear by large scale structure \textbf{\color{blue} (LSS)}, but the random
+rotation makes this contribution \textbf{\color{blue} at least} second order in $\kappa$ \textbf{\color{blue} by destroying the shape spatial correlations induced by lensing from LSS}.
 Consistent with the weak lensing approximation, the lensing signal from the
@@
 denotes gradients of the $\kappa$ field, which we evaluate using
-finite differences. \textbf{In this notation $\Theta(x)$ is the Heaviside function}
+finite differences. \textbf{\color{blue} In this notation $\Theta(x)$ is the Heaviside function}
 %
@@
 %
-\textbf{and $\delta_D(x)$ is the Dirac delta function.}
+\textbf{\color{blue} and $\delta_D(x)$ is the Dirac delta function.}
 The first Minkowski functional, $V_0$, is
@@
 coincides with $\mathbf{C}(\mathbf{p}_0)$. The simulated descriptors $\mathbf{M(p)}$ are
-measured from an average over the $R=1000$ realizations \textbf{in the \texttt{CFHTemu1} ensemble}  
+measured from an average over the $R=1000$ realizations \textbf{\color{blue} in the \texttt{CFHTemu1} ensemble}  
 \begin{equation}
@@
 \end{equation}
-is measured from the \textbf{$R=1000$} realizations \textbf{in the \texttt{CFHTcov} ensemble}.
+is measured from the \textbf{\color{blue} $R=1000$} realizations \textbf{\color{blue} in the \texttt{CFHTcov} ensemble}.
 While eq.~(\ref{datacov}) gives an unbiased estimator of the
@@
 simulations. Figure~\ref{emulatorAccuracy} shows that our power
-spectrum emulator has a \textbf{relative error} smaller than 20\% for the lower
+spectrum emulator has a \textbf{\color{blue} relative error} smaller than 20\% for the lower
 multipoles ($l<500$), and comparable to 1\% for the higher multipoles. The MF
-emulator has a \textbf{relative error} $\lesssim$10\% for the first 30 bins (which
+emulator has a \textbf{\color{blue} relative error} $\lesssim$10\% for the first 30 bins (which
 correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
@@
 implement a more sophisticated interpolation
-scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in \textbf{relative error} over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
+scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in \textbf{\color{blue} relative error} over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
 
@@
 alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
-$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. \textbf{In the next section} we give a justification on why we fix $\alpha$ to a value of $0.55$. 
+$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. \textbf{\color{blue} In the next section} we give a justification on why we fix $\alpha$ to a value of $0.55$. 
 We then use our simulations to perform a robustness analysis of the parameter
@@
 $\Sigma_8$ in Figure \ref{likelihoodSi8cross}.
-\textbf{We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}.
+\textbf{\color{blue} We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}.
 We discuss these findings in the next section.
@@
 compute confidence levels.
-\textbf{Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear interpolations between the fiducial cosmology and its variations)}, we thus attribute this bias to the \textbf{oversimplifying} assumption of linear cosmology-parameter dependence of the descriptors.
+\textbf{\color{blue} Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear)}, we thus attribute this bias to the \textbf{\color{blue} oversimplifying} assumption of linear cosmology-parameter dependence of the descriptors.
 Although the right panel in Figure
@@
 \ref{contours3combined} shows that even with these statistics
-combined, $w$ remains essentially unconstrained. \textbf{\citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly}. 
+combined, $w$ remains essentially unconstrained. \textbf{\color{blue} \citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly}. 
 Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
@@
   using the Minkowski functionals.
-\textbf{We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales.
+\textbf{\color{blue} We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales.
 These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds.

### 2015-04-20 jia/CFHTpaper_official_plots.py
regular update

@@ -26,6 +26,7 @@ contour_ps_fieldselect = 0
 contour_peaks_powspec = 0
 contour_including_w = 0
 contour_peaks_powspec_covariance = 0
+contour_peakpeak = 1 # added 4/19/2015
 
 good_bad_powspec = 0
 interp_2D_plane = 0
@@ -44,7 +45,7 @@ om_arr = linspace(0,1.2,l)[om0:om1]
 si8_arr = linspace(0,1.6,ll)[si80:si81]
 w_arr = linspace(0,-3,101)#[w0:w1]
 sigmaG_arr = [1.0, 1.8, 3.5, 5.3]
-fn_arr = ['idx_psPass7000_pk2smoothing', 'pk2smoothing', 'pk10', 'pk18', 'pk35', 'pk53', 'psPass', 'psAll', 'psPass7000', 'psAll7000', 'idx_psPass7000_pk2smoothing_SIMGA', 'pk2smoothing_SIMGA', 'psPass7000_SIGMA']
+fn_arr = ['idx_psPass7000_pk2smoothing', 'pk2smoothing', 'pk10', 'pk18', 'pk35', 'pk53', 'psPass', 'psAll', 'psPass7000', 'psAll7000', 'idx_psPass7000_pk2smoothing_SIMGA', 'pk2smoothing_SIMGA', 'psPass7000_SIGMA', 'idx_peakpeak_counts10', 'idx_peakpeak_counts18', 'idx_peakpeak_kappa10' , 'idx_peakpeak_kappa18']
 
 cube_arr = array([load(test_dir+'chisqcube_%s.npy'%(fn)) for fn in fn_arr])
 
@@ -111,6 +112,19 @@ if contour_peaks_smoothing:
 	labels.append(r'$\rm{1.0+1.8\, arcmin}$')
 	icube_arr = cube_arr[[2,3,4,5,1]]
 	fn = 'contour_peaks_smoothing'
+	nlev = 1
+	official_contour (icube_arr, labels, nlev, fn, colors, lws, lss)
+	
+
+if contour_peakpeak:
+	colors = ['r','b','g','m','k']
+	lws = [4,4,2,2,4]
+	lss =('dotted', 'dashed', 'solid', 'dashed', 'solid')
+	#labels = [r'$\rm{%.1f\, arcmin}$'%(sigmaG) for sigmaG in sigmaG_arr]
[…]

### 2015-04-20 jia/batch_filegen.py

@@ -1,10 +1,10 @@
 #!python
 ############# edite this block ###########
 ############# maybe also want to edit run time below #####
-errfn = 'chisq_cube' # error file name, will append variable automatically
-program_name = 'test_chisq_cube_MPI.py' #program name
+errfn = 'tarball' # error file name, will append variable automatically
+program_name = 'stampede_tarball.py' #program name
 N = 1 # number of nodes
-
+hrs = 20 # number of hours requested
 ##################
 
 n = N*16
@@ -17,12 +17,12 @@ def write_file(errfn, program_name, variable):
 #SBATCH -p normal       # Submit to the 'normal' or 'development' queue
 #SBATCH -N {3}           # Total number of nodes requested (16 cores/node)
 #SBATCH -n {4}          # Total number of mpi tasks requested
-#SBATCH -t 3:00:00      # Run time (hh:mm:ss)
+#SBATCH -t {5}:00:00      # Run time (hh:mm:ss)
 #SBATCH -A TG-AST140041
 
-ibrun python /home1/02977/jialiu/CFHTLens_analysis/jia/{1} {2}'''.format(errfn, program_name, variable, N, n)
+ibrun python /home1/02977/jialiu/CFHTLens_analysis/jia/{1} {2}'''.format(errfn, program_name, variable, N, n, hrs)
 	f.write(content)
 	f.close()
 
-for variable in range(12,16):
+for variable in (1,):
 	write_file(errfn, program_name, variable)

### 2015-04-20 jia/stampede_tarball.py

@@ -1,0 +1,23 @@
+import os
+import subprocess
+from emcee.utils import MPIPool
+
+inDIR_arr = ['/scratch/02977/jialiu/KSsim_noiseless/', '/scratch/02977/jialiu/KSsim/']
+
+outDIR_arr = ['/scratch/02977/jialiu/ranch_archive/KSsim_noiseless/', '/scratch/02977/jialiu/ranch_archive/KSsim/']
+
+for outDIR in outDIR_arr:
+	subprocess.check_call('lfs setstripe -c 4 %s' %(outDIR))
+
+pool = MPIPool()
+
+def create_tarball (FNs):
+	inFN, outFN = FNs
+	subprocess.check_call('tar -cfv %s.tar %s'%(outFN, inFN))
+
+for i in range(len(inDIR_arr)):
+	cosmo_arr = os.listdir(inDIR_arr[i])
+	FNs_arr = [['%s%s'%(inDIR_arr[i], cosmo),'%s%s'%(outDIR_arr[i], cosmo)] for cosmo in cosmo_arr]
+	pool.map(create_tarball, FNs_arr)
+	
+	

### 2015-04-24 Paper_minkowski/Submission/paper.tex
reverted blue to normal font

--- 2015-04-17 Paper_minkowski/Submission/paper.tex
@@
 three--point correlations as an additional probe for cosmology, and
-found modest ($10-20\%$) improvements over the 2PCF. \textbf{These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}}.
+found modest ($10-20\%$) improvements over the 2PCF. These results rely on the third order statistics systematic tests performed by Simon et al. \citep{CFHTSimon}.
 
@@
 $\pmb{\beta}(\chi_s;\pmb{\theta})$.
-\textbf{Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$.
-We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.}
+Since light rays travel undeflected from the observer to the first lens plane, the derivative initial condition in the Cauchy problem (\ref{raytrajectory}) reads $\dot{\pmb{\beta}}(0;\pmb{\theta})=0$.
+We indicate the derivative of $\pmb{\beta}$ with respect to $\chi$ as $\dot{\pmb{\beta}}$.
 %
 We use our proprietary implementation Inspector Gadget~(see, e.g., \cite{KHM2010}) to solve
-for the light ray trajectories based \textbf{on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
-Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).}
+for the light ray trajectories based on a discretized version of equation (\ref{raytrajectory}) that is based on the multi--lens--plane algorithm (see \citep{RayTracingHartlap} for example).
+Applying random periodical shifts and rotations to the $N$--body simulation data cubes, we generate $R=1000$ pseudo--independent realizations of the lens plane system used to solve (\ref{raytrajectory}).
 %
@@
 first and third Pauli matrices.
-\textbf{We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.} We use these different random realizations to estimate the means \textbf{(from the \texttt{CFHTemu1} simulations)} and covariance matrices \textbf{(from the \texttt{CFHTcov} simulations)} of our descriptors.
-\textbf{Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.}
+We perform this procedure for each of the $R$ realizations of the lens planes and we obtain $R$ pseudo--independent realizations of the $\pmb{\gamma}$ weak lensing field.
+We use these different random realizations to estimate the means (from the \texttt{CFHTemu1} simulations) and covariance matrices (from the \texttt{CFHTcov} simulations) of our descriptors.
+Since the random box rotations and translations that make up the \texttt{CFHTcov} simulations are based on 50 independent $N$--body runs, we believe the covariance matrices measured from this set to be more accurate than the ones measured from the \texttt{CFHTemu1} set.
 
@@
 note that the observed ellipticity for a particular galaxy already
-contains the lensing shear by large scale structure \textbf{(LSS)}, but the random
-rotation makes this contribution \textbf{at least} second order in $\kappa$ \textbf{by destropying the shape spatial correlations induced by lensing from LSS}.
+contains the lensing shear by large scale structure (LSS), but the random
+rotation makes this contribution at least second order in $\kappa$ by destroying the shape spatial correlations induced by lensing from LSS.
 Consistent with the weak lensing approximation, the lensing signal from the
@@
 denotes gradients of the $\kappa$ field, which we evaluate using
-finite differences. \textbf{In this notation $\Theta(x)$ is the Heaviside function}
-%
-\begin{equation}
-\Theta(x) = 
-\begin{cases}
-1 \,\,\,\,\,\,\,\, x\geq0 \\ \\
-0 \,\,\,\,\,\,\,\, \mathrm{otherwise}
-\end{cases}
-\end{equation}
-%
-\textbf{and $\delta_D(x)$ is the Dirac delta function.}
+finite differences. In this notation $\Theta(x)$ is the Heaviside function and $\delta_D(x)$ is the Dirac delta function.
 The first Minkowski functional, $V_0$, is
@@
 coincides with $\mathbf{C}(\mathbf{p}_0)$. The simulated descriptors $\mathbf{M(p)}$ are
-measured from an average over the $R=1000$ realizations \textbf{in the \texttt{CFHTemu1} ensemble}  
+measured from an average over the $R=1000$ realizations in the \texttt{CFHTemu1} ensemble  
 \begin{equation}
@@
 \end{equation}
-is measured from the \textbf{$R=1000$} realizations \textbf{in the \texttt{CFHTcov} ensemble}.
+is measured from the  $R=1000$ realizations in the \texttt{CFHTcov} ensemble.
 While eq.~(\ref{datacov}) gives an unbiased estimator of the
@@
 simulations. Figure~\ref{emulatorAccuracy} shows that our power
-spectrum emulator has a \textbf{relative error} smaller than 20\% for the lower
+spectrum emulator has a relative error smaller than 20\% for the lower
 multipoles ($l<500$), and comparable to 1\% for the higher multipoles. The MF
-emulator has a \textbf{relative error} $\lesssim$10\% for the first 30 bins (which
+emulator has a relative error $\lesssim$10\% for the first 30 bins (which
 correspond to $\kappa$ values in $[-0.04,0.08]$) and deteriorates due
@@
 implement a more sophisticated interpolation
-scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in \textbf{relative error} over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
+scheme~\footnote{Following ref.~\citep{coyote2}, we have experimented with interpolations using a Gaussian Process, but did not find a significant improvement in relative error over the much simpler polynomial scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
 
@@
 alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
-$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. \textbf{In the next section} we give a justification on why we fix $\alpha$ to a value of $0.55$. 
+$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. In the next section we give a justification on why we fix $\alpha$ to a value of $0.55$. 
 We then use our simulations to perform a robustness analysis of the parameter
@@
 \ref{contours3combined}, and on the best-constrained parameter
-$\Sigma_8$ in Figure \ref{likelihoodSi8cross}.
-\textbf{We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}.
-We discuss these findings in the next section.
+$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}. We discuss these findings in the next section.
 
@@
 compute confidence levels.
-\textbf{Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear interpolations between the fiducial cosmology and its variations)}, we thus attribute this bias to the \textbf{oversimplifying} assumption of linear cosmology-parameter dependence of the descriptors.
+Since the Fisher matrix formalism is equivalent to a linear approximation of our emulator (in which all cosmological parameter dependencies are assumed to be linear), we thus attribute this bias to the oversimplifying assumption of linear cosmology-parameter dependence of the descriptors.
 Although the right panel in Figure
@@
 \ref{contours3combined} shows that even with these statistics
-combined, $w$ remains essentially unconstrained. \textbf{\citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly}. 
+combined, $w$ remains essentially unconstrained. \citep{CFHTHeymansTomo} found that even weak lensing tomography alone is unable to constrain $w$ sensibly. 
 Figure \ref{likelihoodSi8cross} shows that the $\Sigma_8$ combination is
@@
   using the Minkowski functionals.
-\textbf{We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales.
+We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales.
 These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds.
-We will investigate these additional sources of error in future work.}
+We will investigate these additional sources of error in future work.
 

### 2015-05-22 jia/stampede_noiseless_PDF.py
update test_MPI.py

@@ -57,6 +57,14 @@ def PDFGen(cosmoR):
 		  #0.745429992676])
 
 PDF92 = mean(array([load(fn(cosmo)) for cosmo in cosmo_arr]), axis=1)
-plot(PDF92)
+for iPDF in PDF92:
+	plot(WLanalysis.edge2center(edges), iPDF)
+if noise:
+	title('noisy')
+else:
+	title('noiseless')
+xlabel('kappa')
+ylabel('PDF')
+	
 show()
 print 'done done done'

### 2015-05-22 jia/test_MPIpool.py

@@ -7,7 +7,7 @@ from emcee.utils import MPIPool
 import numpy as np
 from scipy import *
 from multiprocessing import Pool
-from scoop import futures
+#from scoop import futures
 
 print 'start'
 

### 2015-05-22 Paper_minkowski/Submission/reply/reply_referee.tex

@@
 \noindent
-We thank the referee for the interesting and insightful comments, which we address in this document.
+We thank the referee for the interesting and insightful comments, which we address in this document. The additions and modifications in the manuscript have been highlighted in blue.
 
@@
 \item \textit{Missing reference to Simon et. al.}: the reference has been added.
-\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Caucky problem well defined.
+\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Cauchy problem well defined.
 The appropriate explanation has been added to the text.
@@
 When we rotate each galaxy randomly, we destroy these spatial correlations, which will not be $O(\psi)$ anymore, but $O(\psi^2)$ or smaller (if not zero at all).
-We do not assign intrinsic galaxy shapes drawing from $\mathcal{N}(0,\sigma_\epsilon)$ because we refrained from making any assumption on the distribution of intrinsic galaxy shape, choosing to use the shape distribution measured by CFHTLenS instead.
+Assigning galaxy shapes drawing from $\mathcal{N}(0,\sigma_\epsilon)$ would require knowledge of $\sigma_\epsilon$, which depends on redshift, galaxy luminosity, and on galaxy type.
+Since we do not have this information, randomly rotating galaxies is much simpler; it is also more accurate since it avoids making the assumption the intrinsic shape distribution is Gaussian to begin with.
 \item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
 \item \textit{Cubic and quartic moments notations}: we are aware that the definitions of $S_i,K_i$ we adopt are different than the ones provided in [38,39].
-Within our statistical framework, these definition mismatches do not matter as they are related to each other via a constant lineat transformation that drops out in the likelihood calculations.
+Within our statistical framework, these definitions mismatches do not matter as they are related to each other via a constant linear transformation that drops out in the likelihood calculations.
 The typo $K_4\leftrightarrow K_3$ has been corrected.
@@
 \item \textit{Equation (15) (now equation (16)}: here, as throughout the paper, $R=1000$. We added the appropriate clarification
-\item \textit{"For this reason, the normalization constant in equation (12) is also model–independent"}: the sentence has been deleted
+\item \textit{"For this reason, the normalization constant in equation (12) is also model--independent"}: the sentence has been deleted
 \item \textit{Accuracy vs relative error}: the wording "accuracy" has been changed to "relative error". The relative error of the PS emulator at low $l$ has been correctly updated to 20\%

### 2015-05-22 Paper_minkowski/paper.tex

@@
 %ZH: changed title a bit
-\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from Moments and Minkowski Functionals}
+\title{Emulating the CFHTLenS Weak Lensing data:  Cosmological Constraints from moments and Minkowski functionals}
 
@@
 $\sigma_8$ and the dark energy (DE) equation of state $w$.  The
-statistics we consider in this work are the Minkowski Functionals
+statistics we consider in this work are the Minkowski functionals
 (MFs) and the low--order moments (LM) of the convergence field.
@@
 tightening of the $\Omega$ and $\sigma_8$ constraints, utilizing the
-abundance of WL peaks.
+abundance of WL peaks. Cosmological constraints using WL peaks in CFHTLenS Stripe82 data
+have also been investigated by Liu et. al.~\citep{Stripe82}. 
 %ZH: We should also cite the CFHT Stripe82 paper by the Chinese, using peak counts, here.
@@
 relevant parameters $(h,\Omega_b,n_s)$ fixed to the values (0.7,
-0.046, 0.96). 
+0.046, 0.96) (see \citep{WMAP9}).
 %ZH: cite WMAP9 paper here for the parameter choices.
@@
 where $\pmb{I}$ is the $2\times2$ identity and $\sigma^{1,3}$ are the
-first and third Pauli matrices. The convergence $\kappa$ is related to
+first and third Pauli matrices.
+
+Randomly rotating and periodically translating each of the N--body
+data cubes along the three axes before ray--tracing, we are able to generate
+different realizations of the weak lensing fields $\kappa,\gamma_{1,2}$. We use 
+these different random realizations to estimate the covariance matrices of our
+descriptors.
+
+The convergence $\kappa$ is related to
 the magnification, while the two components of the complex shear
@@
 \begin{tabular}{c|c|c} \hline
-Descriptor & Details & $N_b$ \\ \hline
+Descriptor & Details & $N_b$ (linear spacing) \\ \hline
 $V_0,V_1,V_2$ (MF) & $\kappa_0\in[-0.04,0.12]$ & 50 \\
@@
 simplicity, we here insert the value $\kappa=0$ in each masked pixel.
-Given the typical angular size of the masked regions we consider, this
-will have little effect on the power spectrum at the range of
-multipoles in Table \ref{desctable}. 
+Given the uniform spatial distribution of the masked regions in the data, we expect that masks have a little effect on the power spectrum at the range of
+multipoles in Table \ref{desctable}, except for an overall normalization which will be the same both in the data and the simulations.  
 %ZH: can you be more specific above and say what you mean by the angular scales?  Masks are much smaller than
@@
 impact of the masks and their treatment has been evaluated for the
-MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}.
+MFs, obtained from CFHTLenS, by ref.~\citep{CFHTMasato}, in which the authors find that the masked regions 
+are not a dominant source of systematic effects in the CFHTLenS data. 
 %ZH:  I think we need to state here something on what they found.
@@
 %AP: Stressed the fact that we apply the same mask to the simulations; added reference to Yoshida/Shirasaki 
-%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and Moments are well defined also in the presence of masked pixels, while the PS estimator is not
+%AP: I do not think the discussion on masked pixels is misleading: I just wanted to say that the estimators for MF and moments are well defined also in the presence of masked pixels, while the PS estimator is not
 %ZH:  OK, I rewrote above to say this.  I think what you mean to say here is that our results will not be biased,
@@
 9 for the LM statistic and from 0 to $N_b-1$ for a MF measured in
-$N_b$ different $\kappa$ bins).
+$N_b$ different, linearly spaced $\kappa$ bins, as indicated in Table \ref{desctable}).
 %on $N_b$ different excursion sets.
@@
   significant improvement in accuracy over the much simpler polynomial
-  scheme; this is in agreement with earlier results.}.
+  scheme; this is in agreement with earlier results (see for example \citep{KnoxGP})}.
 %ZH: we should add citation of Lloyd Knox's paper http://adsabs.harvard.edu/abs/2011ApJ...728..137S
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[scale=0.45]{Figures/emulator_accuracy.eps}
+\includegraphics[scale=0.4]{Figures/emulator_accuracy.eps}
 \end{center}
@@
 \caption{Accuracy of the emulator based on the \texttt{CFHTemu1}
-  simulations. The figure shows the difference between the descriptor
+  simulations. The figure shows the absolute difference between the descriptor
   interpolated at the fiducial parameter setting, and the descriptor
-  expected from the \texttt{CFHTcov} simulations. The descriptors are
+  expected from the \texttt{CFHTcov} simulations (these are the absoulte values of differences which oscillate around zero). The descriptors are
   shown in units of the standard deviation in each bin $i$ (determined
@@
   matrix). We show the accuracy results for the power spectrum (red)
-  and the three Minkowski Functionals $V_0$ (green), $V_1$ (blue) and
+  and the three Minkowski functionals $V_0$ (green), $V_1$ (blue) and
   $V_2$ (black). For reference, we also show, using dashed lines, the
   difference between the expected \texttt{CFHTcov} descriptors and the
-  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.}
+  interpolated descriptor at the non--fiducial point $\mathbf{p}=(0.8,-1.0,0.5)$.
+This non--fiducial point lies beyond the LM $1\sigma$ contour from the simulations shown in Figure \ref{contours3single} right panel, and corresponds to the target accuracy we wish to achieve}
 %ZH: This last one is chosen to lie along our 1 (or 2?) sigma contour, right?
@@
 \label{emulatorAccuracy}
-\end{figure}
+\end{figure*}
 
@@
 ref.~\citep{astroMLText}), we derive the {\it whitened} model matrix
-$\tilde{M}_{pi}$, defined by subtracting the mean (over the $R=1000$
-realizations) of each matrix element,
-%ZH: you wrote ``bin'' here, but I changed it to matrix element. All NxN_bin entries are whitened, presumably.
-and normalizing it by its variance. Next we proceed with a singular
+$\tilde{M}_{pi}$, defined by subtracting the mean (over the $N=91$ models) of each bin,
+and normalizing it by its variance (always over thw $N=91$ models). Next we proceed with a singular
 value decomposition (SVD) of $\mathbf{\tilde{M}}$,
@@
 data for the triplet $(\Omega_m,\sigma_8,w)$, as well as for an
-alternative parameterization, $(\Sigma_8,\alpha,w)$, with
-$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$.  We then use
-our simulations to perform a robustness analysis of the parameter
+alternative parameterization, $(\Omega_m,\Sigma_8,w)$, with
+$\Sigma_8(\alpha)\equiv \sigma_8(\Omega_m/0.27)^\alpha$. In the latter we give a justification on why we fix $\alpha$ to a value of $0.55$. 
+We then use our simulations to perform a robustness analysis of the parameter
 confidence intervals with respect to the number of PCA components used
@@
 and minimizing the ratio $\sqrt{\mathds{V}}/\mathds{E}$ with respect
-to $\alpha$. 
+to $\alpha$. The expectation values are taken over the entire parameter box. 
 %ZH: Is this done at fixed Omega_m=0.27, or is the averaging above over all Omega_m and sigma8 (and w) ?
@@
 %    it depends on Omega_m, sigma8, and w.
-consistent with what is found in the literature.
+consistent with what is found in the literature (see \citep{CFHTKilbinger} for example).
+Although $\alpha$ can mildly depend on the type of descriptor considered, we choose to keep it fixed, knowing that the width of the $\Sigma_8$ likelihood cannot vary significantly with different choices of $\alpha$.
 %ZH:  We should give references, if we say the above.
@@
 \caption{$1\sigma$ (68\% CL) constraints on the $(\Omega_m,\sigma_8)$
-  parameter doublet using Moments, with different colors corresponding
+  parameter doublet using moments, with different colors corresponding
   to different moment combinations (see eq.~\ref{momentestimator} for
@@
   parameter doublet from the CFHTLenS data, obtained with the power
-  spectrum (red), the three Minkowski Functionals ($V_0$: green,
-  $V_1$: blue, $V_2$: black) and the Moments (orange).
+  spectrum (red), the three Minkowski functionals ($V_0$: green,
+  $V_1$: blue, $V_2$: black) and the moments (orange).
 %ZH: You had V0=blue and V1=green here, but the figure label shows the opposite. 
@@
 %%%% $V_0$ (blue), $V_1$ (green), $V_2$ (black) and
-%  Moments (orange) statistics. 
+%  moments (orange) statistics. 
    The contours are calculated from the parameter likelihood function
@@
   CFHTLenS data, obtained with the power spectrum (red), the three
-  Minkowski Functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
-  the Moments (orange).
+  Minkowski functionals ($V_0$: green, $V_1$: blue, $V_2$: black) and
+  the moments (orange).
 %ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
 %  I assume figure label was correct, but please double-check:
-%%%%  the Power Spectrum (red), $V_0$ (blue), $V_1$ (green),
-%%%%  $V_2$ (black) and Moments (orange) statistics. 
+%%%%  the power spectrum (red), $V_0$ (blue), $V_1$ (green),
+%%%%  $V_2$ (black) and moments (orange) statistics. 
   The likelihood was computed with a constant optimized $\alpha=0.55$,
@@
 \caption{Results from the Principal Components Analysis (PCA) of the
-  binned power spectrum (red), the three Minkowski Functionals ($V_0$:
-  green, $V_1$: blue, $V_2$: black) and the Moments (orange).
+  binned power spectrum (red), the three Minkowski functionals ($V_0$:
+  green, $V_1$: blue, $V_2$: black) and the moments (orange).
 %ZH: Again, you had V0=blue and V1=green here, but the figure label shows the opposite. 
 %  I assume figure label was correct, but please double-check:
-%%% the Power Spectrum(red), $V_0$
-%%%  (blue), $V_1$ (green), $V_2$ (black) and the Moments (orange)
+%%% the power spectrum(red), $V_0$
+%%%  (blue), $V_1$ (green), $V_2$ (black) and the moments (orange)
   The left panel shows the magnitudes of the PCA eigenvalues $S_i^2$
@@
 CFHTLenS alone included combining the power spectrum and peak
-counts~\citep{Companion}, and combining quadratic (2PCF) statistics
-with the skewness of the CFHTLenS $\kappa$ field~\citep{CFHTFu}.
+counts~\citep{Companion}, combining the power spectrum and Minkowski functionals ~\citep{CFHTMasato} ,and combining quadratic (2PCF) statistics
+with cubic statistics derived from the 3PCF of the CFHTLenS $\kappa$ field~\citep{CFHTFu}.
 %ZH: This was on the 3PCF, not the skewness -- right?  And didn't Shirasaki+Yoshida also combine PS+MF ?
@@
 in other experiments. For example, the current best-fit values of
-$(\Omega_m,\sigma_8)=(...,...)$ from cosmic microwave background
-anisotropies measured by the Planck
+$(\Omega_m,\sigma_8)=(0.32,0.83),(0.28,0.82)$ from cosmic microwave background
+anisotropies measured respectively by the Planck
 %ZH: Let's give the actual numbers here.  I would also quote WMAP9
@@
 %    needs to be resolved between these two (and my suspicion is that WMAP is correct :)
-satellite~\citep{PlanckXVI2013} lie beyond the 99\% likelihood
+~\citep{PlanckXVI2013} and WMAP~\citep{WMAP9} satellites lie beyond the 99\% likelihood
 contours obtained from the three MFs (not shown).
@@
 
-We observe that the Moments give the tightest constraint on
+We observe that the moments give the tightest constraint on
 $(\Omega_m,\sigma_8)$.  Furthermore, this constraint is unbiased, in
@@
 %ZH:  I guess the natural question: if you look at those ~10 realizations which give biased best-fits from the MFs,
-%     do they also give biased fits from the Moments?  I would guess so.
-The fact that the Moments are useful for deriving unbiased
+%     do they also give biased fits from the moments?  I would guess so.
+The fact that the moments are useful for deriving unbiased
 cosmological constraints has been noted in previous work, which
@@
 Although the right panel in Figure
-\ref{contours3combined} shows that the Moments confine $w$ to isolated
-regions in parameter space, we note that $w=-1$, the value favored by
-several other existing experiments, is excluded at the $1\sigma$
-level. The $2\sigma$ contours (not shown in the figure) close, and
+\ref{contours3combined} shows that the moments confine $w$ to isolated
+regions in parameter space, we note that $w=-1$, the value favored by other existing experiments, is excluded at the $1\sigma$
+level. The $2\sigma$ contours (not shown in the figure) join, and
 include $w=-1$.
@@
 of Figure \ref{contours3combined} shows that, although combining the
-power spectrum with the Minkowski Functionals and Moments helps
+power spectrum and the moments with the Minkowski functionals helps
 tighten the $(\Omega_m,\sigma_8)$ constraints, it does not help in
-reducing the inherent parameter bias. The right panel of Figure
+reducing the inherent parameter bias of the MFs. The right panel of Figure
 \ref{contours3combined} shows that even with these statistics
@@
 %ZH: added this
-This further clarifies that the non-quadratic descriptor mainly help
+This further clarifies that the non--quadratic descriptors mainly help
 to break degeneracies, tightening contours along the
@@
 constraints on $w$.  The techniques developed here can be applied to
-larger, soon-forthcoming survey data sets.
-%ZH: we should cite the dark energy survey (DES), and Subaru, and maybe also WFIRST and LSST here.
+larger, soon-forthcoming survey data sets, such as the Dark Energy Survey (DES)~\citep{DES}, Subaru~\citep{Subaru}, WFIRST~\citep{WFIRST} and LSST~\citep{LSST}.
 
